### 2024-11-21 study1/analysis/2_analysis.qmd
scripts

---
title: "InteroceptionScale - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(EGAnet)
```

```{r}
#| code-fold: false

df <- read.csv("../data/rawdata_participants.csv")

items <- select(df, contains("_Q")) 
byfacet <- items[df$Condition=="Dimensions",]
bymodality <- items[df$Condition=="Domains",]
byrandom <- items[df$Condition=="Random",]

# labels <- list(
#   Anxious_State_Q4 = "Blablagl re'f sdf",
#   sref
# )
# 
# Make 
```

## Item Correlation

::: {.panel-tabset}

### Full Sample

```{r}
#| fig-width: 12
#| fig-height: 12

make_heatmap <- function(items, interactive=TRUE, title="Correlation Matrix") {
  fn <- if(interactive) heatmaply::heatmaply else heatmaply::ggheatmap

  fn(
    cor(items),
    symm = TRUE,
    colors=heatmaply::cool_warm,
    show_dendrogram =c(FALSE, TRUE),
    main=title,
    showticklabels = FALSE,
    hide_colorbar = TRUE,
    k_col = 4,
    # k_row = 4,
    limits = c(-1, 1)
    )
}

# p1 <- make_heatmap(items, title="Full Sample")
# p1
```

### By Facet

Also "Dimension" / "Domains" / "Context"

```{r}
# p2 <- make_heatmap(byfacet, title="By Facet")
# p2
```

### By Modality

```{r}
# p3 <- make_heatmap(bymodality, title="By Modality")
# p3
```

### Random Grouping

```{r}
# p4 <- make_heatmap(byrandom, title="Random Grouping")
# p4
```

### Figures

```{r}
#| output: false

# p1 <- make_heatmap(items, interactive=FALSE) |>
#   gridExtra::arrangeGrob(top = 'Full Sample')
# p2 <- make_heatmap(byfacet, interactive=FALSE, title="By Facet") |>
#   gridExtra::arrangeGrob(top = 'By Facet')
# p3 <- make_heatmap(bymodality, interactive=FALSE, title="By Modality") |>
#   gridExtra::arrangeGrob(top = 'By Modality')
# p4 <- make_heatmap(byrandom, interactive=FALSE, title="Random Grouping") |>
#   gridExtra::arrangeGrob(top = 'Random Grouping')
```

```{r}
#| fig-width: 12
#| fig-height: 12

# gridExtra::grid.arrange(
#   p1, p2, p3, p4,
#   layout_matrix=rbind(
#     c(1,1,1),
#     c(1,1,1),
#     c(2,3, 4)))
```

:::

### Similarity

```{r}
# bootstrap_similarity <- function(df) {
#   rez <- data.frame()
#   for(i in 1:200) {
#     idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
#     newdata <- df[idx,]
#     items <- select(df, contains("_Q"))
#     byfacet <- items[newdata$Condition=="Dimensions",]
#     bymodality <- items[newdata$Condition=="Domains",]
#     byrandom <- items[newdata$Condition=="Random",]
#     
#     rez <- rbind(
#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(items), cor(bymodality), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE)) |>
#       as.data.frame() |> 
#       mutate(
#         Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
#         Sample = c("Random", "Random", "Full", "Full"),
#         Iteration = i) |> 
#       mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |> 
#       rbind(rez)
#   }
#   rez
# }
# 
# 
# rez <- bootstrap_similarity(df)
# 
# rez |> 
#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
#   filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |> 
#   mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |> 
#   ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
#   ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
#   facet_wrap(~Sample) +
#   scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
#   scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
#   labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
#   theme_minimal()
# 
# rez |> 
#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
#   filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |> 
#   ggplot(aes(x=name, y=value)) +
#   ggdist::stat_eye(aes(fill = after_stat(y < 0))) +
#   facet_wrap(~Sample) +
#   geom_hline(yintercept=0, linetype="dashed") +
#   labs(x="Indices of Correlation Matrix Difference", y="Similarity Difference") +
#   theme_minimal() +
#   scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), guide="none")
```

## Item Selection

### Unique Variable Analysis (UVA)

```{r}
uva <- EGAnet::UVA(items, cut.off = 0.2)
# uva

toremove_table <- rbind(
  data.frame(
  Condition = "Full Sample",
  Remove = uva$keep_remove$remove),
  data.frame(
  Condition = "By Facet",
  Remove = EGAnet::UVA(byfacet, cut.off = 0.2)$keep_remove$remove),
  data.frame(
  Condition = "By Modality",
  Remove = EGAnet::UVA(bymodality, cut.off = 0.2)$keep_remove$remove),
  data.frame(
  Condition = "Random Grouping",
  Remove = EGAnet::UVA(byrandom, cut.off = 0.2)$keep_remove$remove)
) |>
  mutate(n = n(), .by=c("Remove")) |>
  mutate(Condition = fct_relevel(Condition, "Full Sample", "By Facet", "By Modality", "Random Grouping")) |>
  arrange(desc(n), Remove, Condition)

toremove <- filter(toremove_table, Condition=="Full Sample" & n > 1)$Remove

toremove_table |>
  select(-n) |>
  gt::gt() |>
  gt::data_color(columns=Remove, fn=\(x) ifelse(x %in% toremove, "#FFEBEE", "white"))
```

```{r}
items <- select(items, -all_of(toremove))
byfacet <- select(byfacet, -all_of(toremove))
bymodality <- select(bymodality, -all_of(toremove))
byrandom <- select(byrandom, -all_of(toremove))
```

### Cluster Stability

```{r}
ega <- bootEGA(
  items,
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  EGA.type = "hierEGA",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=100,
  seed=3, ncores = 4)

# EGAnet::dimensionStability(ega)
itemstability <- EGAnet::itemStability(ega, IS.plot=FALSE)
plot(itemstability)

itemstability_table <- itemstability$lower_order$item.stability$all.dimensions |>
  as.data.frame() |>
  datawizard::data_addprefix("C")
itemstability_table$Cluster <- colnames(itemstability_table)[max.col(itemstability_table, ties.method='first')]

itemstability_table <- itemstability_table |>
  rownames_to_column(var="Item") |>
  rowwise() |>
  mutate(Stability = max(c_across(-c(Item, Cluster)))) |>
  arrange(Cluster, desc(Stability))

toremove <- filter(itemstability_table, Stability < 0.5)$Item

itemstability_table |>
  select(-Cluster, -Stability) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  )
```

```{r}
items <- select(items, -all_of(toremove))
byfacet <- select(byfacet, -all_of(toremove))
bymodality <- select(bymodality, -all_of(toremove))
byrandom <- select(byrandom, -all_of(toremove))
```

## Exploratory Graph Analysis (EGA)

::: {.panel-tabset}

### Full Sample

```{r}
ega <- bootEGA(
  items,
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  EGA.type = "hierEGA",
  # plot.EGA = FALSE,
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  seed=3, ncores = 4)

plot(ega)
summary(ega)

# EGAnet::dimensionStability(ega)
itemstability <- EGAnet::itemStability(ega)
itemstability
plot(itemstability)

# Loadings
loadings <- ega$typicalGraph
loadings$parameters$lower_loadings
loadings$parameters$lower_scores
```

<!-- ```{r} -->
<!-- library(ggraph) -->

<!-- EGAnet::convert2tidygraph(ega$EGA) -->

<!-- graph <- ega$typicalGraph -->

<!-- edges_lower <- graph$lower_order$graph |>  -->
<!--   as.data.frame() |>  -->
<!--   rownames_to_column(var="from") |>  -->
<!--   pivot_longer(-from, names_to="to", values_to="weight") |>  -->
<!--   filter(weight > 0)  -->
<!-- nodes_lower <- graph$lower_order$typical.dim.variables -->

<!-- tidygraph::as_tbl_graph(edges_lower, nodes=nodes_lower, directed=FALSE) |>  -->
<!--   ggraph::ggraph(layout = 'circle') + -->
<!--   ggraph::geom_node_point() + -->
<!--   ggraph::geom_edge_bend(aes(edge_width = weight), alpha=0.5) + -->
<!--   # ggraph::geom_node_text(aes(label=item), repel=TRUE) + -->
<!--   theme_void() -->
<!-- ``` -->

<!-- ### By Dimension / Domains / Context -->

<!-- ```{r} -->
<!-- bydimension <- items[df$Condition=="Dimensions",] -->

<!-- ega_bydimension <- EGA(bydimension[, 1:20], plot.EGA = FALSE) -->

<!-- plot(ega_bydimension) -->
<!-- ``` -->

<!-- ### By Modalities -->

<!-- ```{r} -->
<!-- bymodality <- items[df$Condition=="Domains",] -->

<!-- ega_bymodality <- EGA(bymodality[, 1:20], plot.EGA = FALSE) -->

<!-- plot(ega_bymodality) -->
<!-- ``` -->

<!-- ::: -->

<!-- ## Model Comparison -->

<!-- ```{r} -->
<!-- EGAnet::EGM(items[, 1:60]) -->

<!-- # EGAnet::EGM.compare(items[, 1:20]) -->

<!-- rez <- EGAnet::network.compare(byfacet[, 1:20], bymodality[, 1:20], seed=3) -->
<!-- plot(rez) -->
<!-- ``` -->

### 2024-11-21 study1/analysis/0_preprocessing.R

@@ -4,6 +4,7 @@ library(jsonlite)
 # path for data
 # path <- "C:/Users/asf25/Box/InteroceptionScale/"
 path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
 
 # JsPsych experiment ------------------------------------------------------
 
@@ -11,10 +12,12 @@ files <- list.files(path, pattern = "*.csv")
 
 alldata <- data.frame()
 for (file in files) {
+  cat(".")
   rawdata <- read.csv(paste0(path, "/", file))
 
   # Initialize participant-level data
   dat <- rawdata[rawdata$screen == "browser_info", ]
+
 
   data_ppt <- data.frame(
     Participant = dat$participantID,
@@ -44,6 +47,7 @@ for (file in files) {
   demog$`Discipline-Comment` <- NULL
   demog$Discipline <- ifelse(!is.null(demog$Discipline), demog$Discipline, NA)
   demog$Student <- ifelse(!is.null(demog$Student), demog$Student, NA)
+  demog$Country <- ifelse(!is.null(demog$Country), demog$Country, NA)
   demog$Ethnicity <- ifelse(demog$Ethnicity == "other", demog$`Ethnicity-Comment`, demog$Ethnicity)
   demog$`Ethnicity-Comment` <- NULL
 
@@ -77,10 +81,9 @@ checks <- data.frame(
 )
 checks$Score <- rowMeans(checks)
 checks$Prolific_ID <- alldata$Prolific_ID
-checks$Comments <- alldata$Experiment_Feedback
 checks$Experiment_Duration <- alldata$Experiment_Duration
 checks$Reward <- alldata$Reward
-checks[, c("Prolific_ID", "Experiment_Duration", "Score", "Comments", "Reward")]
+checks[checks$Prolific_ID=="673cd254388deb8c41028474", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
 
 median(alldata$Experiment_Duration)
 plot(bayestestR::estimate_density(alldata$Experiment_Duration))

### 2024-11-21 study1/analysis/2_analysis.qmd
script

@@
 library(EGAnet)
+library(tidygraph)
+library(ggraph)
 ```
@@
 ```{r}
-ega <- bootEGA(
+#| eval: false
+
+ega1 <- bootEGA(
   items,
+  EGA.type = "EGA",
   model = "glasso",  # BGGM
   algorithm = "louvain",  # walktrap
-  EGA.type = "hierEGA",
+  type="resampling",
   plot.itemStability=FALSE,
@@
   plot.typicalGraph=TRUE,
-  iter=100,
+  iter=500,
   seed=3, ncores = 4)
 
+save(ega1, file="models/ega1.RData")
+```
+
+```{r}
+load("models/ega1.RData")
+
 # EGAnet::dimensionStability(ega)
-itemstability <- EGAnet::itemStability(ega, IS.plot=FALSE)
+itemstability <- EGAnet::itemStability(ega1, IS.plot=FALSE)
 plot(itemstability)
 
-itemstability_table <- itemstability$lower_order$item.stability$all.dimensions |>
-  as.data.frame() |>
+make_loadingtable <- function(x) {
+  t <- as.data.frame(x) |>
     datawizard::data_addprefix("C")
-itemstability_table$Cluster <- colnames(itemstability_table)[max.col(itemstability_table, ties.method='first')]
+  t$Cluster <- colnames(t)[max.col(t, ties.method='first')]
 
-itemstability_table <- itemstability_table |>
+  t |>
     rownames_to_column(var="Item") |>
     rowwise() |>
-  mutate(Stability = max(c_across(-c(Item, Cluster)))) |>
-  arrange(Cluster, desc(Stability))
+    mutate(Max = max(c_across(-c(Item, Cluster)))) |>
+    arrange(Cluster, desc(Max)) |> 
+    as.data.frame()
+}
 
-toremove <- filter(itemstability_table, Stability < 0.5)$Item
+itemstability_table <- make_loadingtable(itemstability$item.stability$all.dimensions)
+
+toremove2 <- filter(itemstability_table, Max < 0.7)$Item
 
 itemstability_table |>
-  select(-Cluster, -Stability) |>
+  select(-Cluster, -Max) |>
   gt::gt() |>
@@
                  domain = c(0, 1)) |>
-  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove, "#FFEBEE", "white")) |>
+  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
   gt::tab_header(
@@
 ```{r}
-items <- select(items, -all_of(toremove))
-byfacet <- select(byfacet, -all_of(toremove))
-bymodality <- select(bymodality, -all_of(toremove))
-byrandom <- select(byrandom, -all_of(toremove))
+items <- select(items, -all_of(toremove2))
+byfacet <- select(byfacet, -all_of(toremove2))
+bymodality <- select(bymodality, -all_of(toremove2))
+byrandom <- select(byrandom, -all_of(toremove2))
 ```
 
-## Exploratory Graph Analysis (EGA)
-
-::: {.panel-tabset}
-
-### Full Sample
+### Item Loadings
 
 ```{r}
-ega <- bootEGA(
+#| eval: false
+
+ega2 <- bootEGA(
   items,
+  EGA.type = "hierEGA",
   model = "glasso",  # BGGM
   algorithm = "louvain",  # walktrap
-  EGA.type = "hierEGA",
-  # plot.EGA = FALSE,
+  type="resampling",
   plot.itemStability=FALSE,
@@
   plot.typicalGraph=TRUE,
+  iter=500,
   seed=3, ncores = 4)
 
-plot(ega)
-summary(ega)
-
-# EGAnet::dimensionStability(ega)
-itemstability <- EGAnet::itemStability(ega)
-itemstability
-plot(itemstability)
-
-# Loadings
-loadings <- ega$typicalGraph
-loadings$parameters$lower_loadings
-loadings$parameters$lower_scores
+save(ega2, file="models/ega2.RData")
 ```
 
-<!-- ```{r} -->
-<!-- library(ggraph) -->
+```{r}
+load("models/ega2.RData")
 
-<!-- EGAnet::convert2tidygraph(ega$EGA) -->
+# itemStability(ega2)
 
-<!-- graph <- ega$typicalGraph -->
+lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)
 
-<!-- edges_lower <- graph$lower_order$graph |>  -->
-<!--   as.data.frame() |>  -->
-<!--   rownames_to_column(var="from") |>  -->
-<!--   pivot_longer(-from, names_to="to", values_to="weight") |>  -->
-<!--   filter(weight > 0)  -->
-<!-- nodes_lower <- graph$lower_order$typical.dim.variables -->
+toremove3 <- lower$Item[!lower$Item %in% slice_max(lower, Max, n=3, by="Cluster")$Item]
 
-<!-- tidygraph::as_tbl_graph(edges_lower, nodes=nodes_lower, directed=FALSE) |>  -->
-<!--   ggraph::ggraph(layout = 'circle') + -->
-<!--   ggraph::geom_node_point() + -->
-<!--   ggraph::geom_edge_bend(aes(edge_width = weight), alpha=0.5) + -->
-<!--   # ggraph::geom_node_text(aes(label=item), repel=TRUE) + -->
-<!--   theme_void() -->
-<!-- ``` -->
+lower |>
+  select(-Cluster, -Max) |>
+  gt::gt() |>
+  gt::data_color(columns=-Item,
+                 method = "numeric",
+                 palette = c("red", "white", "green"),
+                 domain = c(-1, 1)) |>
+  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
+  gt::tab_header(
+    title = gt::md("**Item Loadings**"),
+    subtitle = "Node centrality"
+  )
+```
+
+```{r}
+items <- select(items, -all_of(toremove3))
+byfacet <- select(byfacet, -all_of(toremove3))
+bymodality <- select(bymodality, -all_of(toremove3))
+byrandom <- select(byrandom, -all_of(toremove3))
+```
+
+## Structure Analysis
+
+```{r}
+#| eval: false
+
+ega3 <- bootEGA(
+  items,
+  EGA.type = "hierEGA",
+  model = "glasso",  # BGGM
+  algorithm = "louvain",  # walktrap
+  type="resampling",
+  plot.itemStability=FALSE,
+  typicalStructure=TRUE,
+  plot.typicalGraph=TRUE,
+  iter=500,
+  seed=3, ncores = 4)
+
+save(ega3, file="models/ega3.RData")
+```
+
+```{r}
+load("models/ega3.RData")
+
+# itemStability(ega2)
+
+lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) 
+higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std)) |> 
+  select(names(lower)) |> 
+  arrange(Item)
+higher$Item <- paste0("H", higher$Item)
+
+rbind(higher, lower) |>
+  select(-Cluster, -Max) |>
+  gt::gt() |>
+  gt::tab_row_group(
+    label = "Item",
+    rows = 1:(nrow(lower) + nrow(higher))
+  ) |>
+  gt::tab_row_group(
+    label = "Higher Order",
+    rows = 1:nrow(higher)
+  ) |> 
+  gt::data_color(columns=-Item,
+                 method = "numeric",
+                 palette = c("red", "white", "green"),
+                 domain = c(-1, 1)) |>
+  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
+  gt::tab_header(
+    title = gt::md("**Item Loadings**"),
+    subtitle = "Node centrality"
+  )
+```
+
+```{r}
+graph <- convert2tidygraph(ega3)
+
+tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
+  ggraph::ggraph(layout = 'graphopt') +
+  ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
+  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.1, strength=0) +
+  ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
+  ggraph::geom_node_text(aes(label=name), repel=TRUE) +
+  scale_edge_alpha(range = c(0, 0.9), guide="none") +
+  scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
+  theme_void()
+```
+
+<!-- ::: {.panel-tabset} -->
+
+<!-- ### Full Sample -->
 
@@
 <!-- ``` -->
+
+### Empirical vs. Model Scores
+
+```{r}
+EGAnet::net.scores()
+```

### 2024-11-21 study1/analysis/0_preprocessing.R

@@ -48,6 +48,7 @@ for (file in files) {
   demog$Discipline <- ifelse(!is.null(demog$Discipline), demog$Discipline, NA)
   demog$Student <- ifelse(!is.null(demog$Student), demog$Student, NA)
   demog$Country <- ifelse(!is.null(demog$Country), demog$Country, NA)
+  demog$Ethnicity <- ifelse(!is.null(demog$Ethnicity), demog$Ethnicity, NA)
   demog$Ethnicity <- ifelse(demog$Ethnicity == "other", demog$`Ethnicity-Comment`, demog$Ethnicity)
   demog$`Ethnicity-Comment` <- NULL
 
@@ -68,6 +69,7 @@ for (file in files) {
 }
 
 
+alldata[is.na(alldata$Prolific_ID), ]
 # Attention checks --------------------------------------------------------
 checks <- data.frame(
   Sexual_State_A = alldata$Sexual_State_A / 6,
@@ -83,10 +85,12 @@ checks$Score <- rowMeans(checks)
 checks$Prolific_ID <- alldata$Prolific_ID
 checks$Experiment_Duration <- alldata$Experiment_Duration
 checks$Reward <- alldata$Reward
-checks[checks$Prolific_ID=="673cd254388deb8c41028474", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
+checks <- checks[!is.na(checks$Prolific_ID), ]
+checks[checks$Prolific_ID=="672b6ad098ad5f2f5867fb6b", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
 
-median(alldata$Experiment_Duration)
-plot(bayestestR::estimate_density(alldata$Experiment_Duration))
+# Hi, unfortunately, we can't find your data (and Prolific information suggests that you did not finish the experiment?) Did anything go wrong? Sorry for that!
+
+
 
 # Anonymize ---------------------------------------------------------------
 alldata$Prolific_ID <- NULL

### 2024-11-21 study1/analysis/2_analysis.qmd
added items
not a fun task

@@
 
-# labels <- list(
-#   Anxious_State_Q4 = "Blablagl re'f sdf",
+labels <- list(
+  Anxious_State_Q4 = "Blablagl re'f sdf",
+  Sexual_State_Q1: "I always know when I am sexually aroused",
+  Sexual_State_Q2: "I always feel in my body if I am sexually aroused",
+  Sexual_State_Q3:
+        "My body is always in the same specific state  when I am sexually aroused",
+  Sexual_State_Q4:
+        "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
+  Sexual_State_Q5:
+        "I can always tell that I am sexually aroused from the way I feel inside",
+  Sexual_State_A: "I always know that I am attentively doing a study", // 'A' stands for attention
+  Sexual_Cardiac_Q1:
+        "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  Sexual_Respiratory_Q1:
+        "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  Sexual_Gastric_Q1:
+        "When I am sexually aroused, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
+  Sexual_Gastric_Q2:
+        "When I am sexually aroused, I often feel butterflies in my stomach",
+  Sexual_Genital_Q1:
+        "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
+  Sexual_Genital_Q2:
+        "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
+  Sexual_SkinThermo_Q1:
+        "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
+  Sexual_SkinThermo_Q2:
+        "When I am sexually aroused, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
+  Sexual_SkinThermo_Q3:
+        "When I am sexually aroused, I often feel my mouth becoming dry",
+  Sexual_ColonBladder_Q1:
+        "When I am sexually aroused, I often feel like I need to relieve myself by urinating or defecating",
+  Sexual_ColonBladder_Q2:
+        "During sex or masturbation, I often feel like I need to relieve myself by urinating or defecating",
+  Anxious_State_Q1: "I always know when I am anxious",
+  Anxious_State_Q2: "I always feel in my body if I am anxious",
+  Anxious_State_Q3:
+        "My body is always in the same specific state when I am anxious",
+  Anxious_State_Q4:
+        "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
+  Anxious_State_Q5:
+        "I often realize that I am anxious only when others tell me",
+  Anxious_Cardiac_Q1:
+        "When I am anxious, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  Anxious_Respiratory_Q1:
+        "When I am anxious, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  Anxious_Gastric_Q1:
+        "When I am anxious, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
+  Anxious_Genital_Q1:
+        "When I am anxious, I often notice specific sensations in my genital area (e.g., contractions, dryness)",
+  Anxious_SkinThermo_Q1:
+        "When I am anxious, I often feel changes in my temperature (e.g., feeling warm or cold)",
+  Anxious_SkinThermo_Q2:
+        "When I am anxious, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
+  Anxious_SkinThermo_Q3:
+        "When I am anxious, I often feel my mouth becoming dry",
+  Anxious_SkinThermo_Q4:
+        "When I am anxious, I often have difficulty swallowing",
+  Anxious_SkinThermo_A:
+        "Even if I am anxious, I should now answer all the way to the left",
+  Anxious_ColonBladder_Q1:
+        "When I am anxious, I often feel like I need to relieve myself by urinating or defecating",
+  Nociception_State_Q1: "I always feel in my body if I am ill",
+  Nociception_State_Q2:
+        "I can easily tell when I am feeling ill (e.g., nauseous or sick)",
+  Nociception_Cardiac_Q1:
+        "I often feel painful sensations coming from my heart",
+  Nociception_Cardiac_Q2:
+        "I often experience painful sensations coming from my chest",
+  Nociception_Respiratory_Q1:
+        "I often feel like I have difficulties breathing normally",
+  Nociception_Respiratory_Q2:
+        "I often feel like I can't get enough oxygen by breathing normally",
+  Nociception_Gastric_Q1: "I often feel pain in my stomach",
+  Nociception_Genital_Q1:
+        "My genital organs are very sensitive to pleasant stimulations",
+  Nociception_Genital_Q2:
+        "My genital organs are very sensitive to painful stimulations",
+  Nociception_SkinThermo_Q1:
+        "My skin is very sensitive to painful stimulations (e.g., pinching)",
+  Nociception_SkinThermo_Q2:
+        "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
+  Nociception_SkinThermo_Q3:
+        "Changes in temperature (e.g., feeling feverish or cold) are the first things I notice when I am becoming ill",
+  Nociception_ColonBladder_Q1:
+        "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
+  Nociception_ColonBladder_Q2:
+        "I often experience painful sensations when relieving myself when urinating or defecating",
+  Nociception_ColonBladder_A:
+        "I often experience sensations, and I will answer zero to this question",
+  Sensitivity_State_Q1: "I always know when I am relaxed",
+  Sensitivity_State_Q2: "I always feel in my body if I am relaxed",
+  Sensitivity_State_Q3:
+        "My body is always in the same specific state when I am relaxed",
+  Sensitivity_State_Q4:
+        "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
+  Sensitivity_State_Q5:
+        "When something important is happening in my life, I can feel it in my body",
+  Sensitivity_Cardiac_Q1:
+        "In general, I am very sensitive to changes in my heart rate",
+  Sensitivity_Cardiac_Q2: "I often notice changes in my heart rate",
+  Sensitivity_Cardiac_Q3:
+        "I can notice even very subtle changes in the way my heart beats",
+  Sensitivity_Cardiac_Q4:
+        "I am always very aware of my heartbeats, even when I am calm",
+  Sensitivity_Cardiac_Q5:
+        "I only notice my heart when it is thumping in my chest",
+  Sensitivity_Cardiac_Q6:
+        "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
+  Sensitivity_Cardiac_Q7:
+        "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
+  Sensitivity_Cardiac_A:
+        "In general, I am very sensitive and attentive to the questions I am currently answering",
+  Sensitivity_Respiratory_Q1:
+        "In general, I am very sensitive to changes in my breathing",
+  Sensitivity_Respiratory_Q2: "I often notice changes in my breathing",
+  Sensitivity_Respiratory_Q3:
+        "I can notice even very subtle changes in my breathing",
+  Sensitivity_Respiratory_Q4:
+        "I am always very aware of how I am breathing, even when I am calm",
+  Sensitivity_Respiratory_Q5:
+        "I often only notice how I am breathing when it becomes loud",
+  Sensitivity_Respiratory_Q6:
+        "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+  Sensitivity_Respiratory_Q7:
+        "When something important is happening in my life, I can immediately feel changes in my breathing",
+  Sensitivity_Gastric_Q1:
+        "In general, I am very sensitive to what my stomach is doing",
+  Sensitivity_Gastric_Q2:
+        "I can notice even very subtle changes in what my stomach is doing",
+  Sensitivity_Gastric_Q3:
+        "I am always very aware of what my stomach is doing, even when I am calm",
+  Sensitivity_Gastric_Q4: "I often check the smell of my own breath",
+  Sensitivity_Gastric_Q5: "I often check the smell of my farts",
+    ensitivity_Gastric_Q6: "I often pay attention to the noises of my stomach",
+    Sensitivity_Gastric_A: "I often pay attention to the answers I am giving",
+    Sensitivity_Genital_Q1:
+        "In general, I am very sensitive to changes in my genital organs",
+    Sensitivity_Genital_Q2:
+        "I can notice even very subtle changes in the state of my genital organs",
+    Sensitivity_Genital_Q3:
+        "I am always very aware of the state of my genital organs, even when I am calm",
+    Sensitivity_SkinThermo_Q1: "In general, my skin is very sensitive",
+    Sensitivity_SkinThermo_Q2:
+        "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
+    Sensitivity_SkinThermo_Q3:
+        "I can notice even very subtle changes if my skin becomes dry or sweaty",
+    Sensitivity_SkinThermo_Q4:
+        "I am always very aware if my hands and feet are cold or warm",
+    Sensitivity_SkinThermo_Q5: "I often check the smell of my armpits",
+    Sensitivity_SkinThermo_Q6: "I am very prone to having goosebumps",
+    Sensitivity_SkinThermo_Q7:
+        "My skin is susceptible to itchy fabrics and materials",
+    Sensitivity_SkinThermo_Q8:
+        "I enjoy the sensations of touching different materials (e.g., soft fabrics, wooden objects, smooth surfaces)",
+    Sensitivity_ColonBladder_Q1:
+        "In general, I am very aware of the sensations that are happening when I am defecating",
+    Sensitivity_ColonBladder_Q2:
+        "In general, I am very aware of the sensations that are happening when I am urinating",
+    Sensitivity_ColonBladder_Q3: "I often check the colour of my urine",
+    Sensitivity_ColonBladder_Q4: "I often check the colour of my faeces",
+    Accuracy_State_Q1: "I can always accurately feel when I am about to cough",
+    Accuracy_State_Q2: "I can always accurately feel when I am about to sneeze",
+    Accuracy_State_Q3: "I can always accurately feel when I am about to vomit",
+    Accuracy_State_Q4:
+        "I can always accurately feel when I am starting to be hungry",
+    Accuracy_State_Q5:
+        "I can always accurately feel when I am starting to be thirsty",
+    Accuracy_Cardiac_Q1:
+        "I can always accurately feel if my heart rate is slow or fast",
+    Accuracy_Cardiac_Q2:
+        "I sometimes feel like my heart is racing or beating faster than usual, but when I check my pulse, it is not as intense as I thought",
+    Accuracy_Respiratory_Q1:
+        "I can always accurately feel how I am breathing (e.g., fast or slow, deep or shallow)",
+    Accuracy_Respiratory_A:
+        "I can always accurately answer to the left on this question to show that I am reading it",
+    Accuracy_Gastric_Q1: "I can always accurately feel when I am about to fart",
+    Accuracy_Gastric_Q2: "I can always accurately feel when I am about to burp",
+    Accuracy_Gastric_Q3: "I often feel thirsty even if I drank recently",
+    Accuracy_Gastric_Q4:
+        "I don't always feel the need to drink until I am really thirsty",
+    Accuracy_Gastric_Q5: "I often feel hungry even if I ate recently",
+    Accuracy_Gastric_Q6:
+        "I don't always feel the need to eat until I am really hungry",
+    Accuracy_Gastric_Q7:
+        "I often sneeze suddenly without feeling the need building up",
+    Accuracy_Gastric_Q8:
+        "I sometimes feel that burping will produce some relief but then it doesn't",
+    Accuracy_Genital_Q1:
+        "I can always accurately perceive if my genital organs are in a state of arousal (e.g., hard, wet, pulsating)",
+    Accuracy_Genital_Q2:
+        "I sometimes feel like I am sexually aroused, but when I try to satisfy the feeling, I realise that I am not as sexually aroused as I initially thought",
+    Accuracy_Genital_A:
+        "I can always accurately perceive that to this question I should answer the lowest option",
+    Accuracy_SkinThermo_Q1:
+        "I can always accurately feel when something is going to be itchy",
+    Accuracy_SkinThermo_Q2:
+        "I can always accurately feel when I start to have a fever",
+    Accuracy_SkinThermo_Q3:
+        "When something touches my skin, I can always accurately feel if it's hot or cold",
+    Accuracy_SkinThermo_Q4:
+        "I sometimes feel my skin itching, but when I scratch it, it doesn't produce the relief I expected",
+    Accuracy_ColonBladder_Q1:
+        "I often feel the need to urinate even when my bladder is not full",
+    Accuracy_ColonBladder_Q2:
+        "I don't always feel the need to urinate until my bladder is very full",
+    Accuracy_ColonBladder_Q3:
+        "I often feel the need to defecate even when my intestine is not full",
+    Accuracy_ColonBladder_Q4:
+        "I don't always feel the need to defecate until my intestine is very full",
+    Accuracy_ColonBladder_Q5:
+        "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+    Confusion_State_Q1:
+        "Sometimes I can't tell if the sensations in my body are good or bad",
+    Confusion_State_Q2:
+        "Sometimes I am confused about what sensations in my body mean",
+    Confusion_Cardiac_Q1:
+        "Sometimes my heart starts racing and I often don't know why",
+    Confusion_Respiratory_Q1:
+        "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+    Confusion_Gastric_Q1:
+        "Sometimes I feel negative and realise after eating that I was just hungry",
+    Confusion_Gastric_Q2:
+        "Sometimes I don't realise I was hungry until I ate something",
+    Confusion_Genital_Q1:
+        "Sometimes I notice arousal in my genital areas (e.g., stiffness, wetness) when I am not feeling sexually aroused",
+    Confusion_SkinThermo_Q1:
+        "Sometimes I have sensations on my skin (e.g., itches, goosebumps) without any clear cause",
+    Confusion_ColonBladder_Q1:
+        "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+    Confusion_ColonBladder_A:
+        "Sometimes I notice that I need to answer all the way to the right",
 #   sref
 # )
-# 
+
 # Make 

### 2024-11-21 study1/analysis/2_analysis.qmd
items FORMATTED PROPERLY

--- 2024-11-21 study1/analysis/2_analysis.qmd
@@
 
-# labels <- list(
-#   Anxious_State_Q4 = "Blablagl re'f sdf",
-#   sref
-# )
-# 
+labels <- list(
+  Sexual_State_Q1 = "I always know when I am sexually aroused",
+  Sexual_State_Q2 = "I always feel in my body if I am sexually aroused",
+  Sexual_State_Q3 = "My body is always in the same specific state  when I am sexually aroused",
+  Sexual_State_Q4 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
+  Sexual_State_Q5 = "I can always tell that I am sexually aroused from the way I feel inside",
+  Sexual_State_A = "I always know that I am attentively doing a study",
+  Sexual_Cardiac_Q1 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  Sexual_Respiratory_Q1 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  Sexual_Gastric_Q1 = "When I am sexually aroused, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
+  Sexual_Gastric_Q2 = "When I am sexually aroused, I often feel butterflies in my stomach",
+  Sexual_Genital_Q1 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
+  Sexual_Genital_Q2 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
+  Sexual_SkinThermo_Q1 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
+  Sexual_SkinThermo_Q2 = "When I am sexually aroused, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
+  Sexual_SkinThermo_Q3 = "When I am sexually aroused, I often feel my mouth becoming dry",
+  Sexual_ColonBladder_Q1 = "When I am sexually aroused, I often feel like I need to relieve myself by urinating or defecating",
+  Sexual_ColonBladder_Q2 = "During sex or masturbation, I often feel like I need to relieve myself by urinating or defecating",
+  Anxious_State_Q1 = "I always know when I am anxious",
+  Anxious_State_Q2 =  "I always feel in my body if I am anxious",
+  Anxious_State_Q3 = "My body is always in the same specific state when I am anxious",
+  Anxious_State_Q4 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
+  Anxious_State_Q5 = "I often realize that I am anxious only when others tell me",
+  Anxious_Cardiac_Q1 = "When I am anxious, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  Anxious_Respiratory_Q1 = "When I am anxious, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  Anxious_Gastric_Q1 = "When I am anxious, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
+  Anxious_Genital_Q1 = "When I am anxious, I often notice specific sensations in my genital area (e.g., contractions, dryness)",
+  Anxious_SkinThermo_Q1 = "When I am anxious, I often feel changes in my temperature (e.g., feeling warm or cold)",
+  Anxious_SkinThermo_Q2 = "When I am anxious, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
+  Anxious_SkinThermo_Q3 = "When I am anxious, I often feel my mouth becoming dry",
+  Anxious_SkinThermo_Q4 = "When I am anxious, I often have difficulty swallowing",
+  Anxious_SkinThermo_A = "Even if I am anxious, I should now answer all the way to the left",
+  Anxious_ColonBladder_Q1 = "When I am anxious, I often feel like I need to relieve myself by urinating or defecating",
+  Nociception_State_Q1 = "I always feel in my body if I am ill",
+  Nociception_State_Q2 =  "I can easily tell when I am feeling ill (e.g., nauseous or sick)",
+  Nociception_Cardiac_Q1 = "I often feel painful sensations coming from my heart",
+  Nociception_Cardiac_Q2 = "I often experience painful sensations coming from my chest",
+  Nociception_Respiratory_Q1 = "I often feel like I have difficulties breathing normally",
+  Nociception_Respiratory_Q2 = "I often feel like I can't get enough oxygen by breathing normally",
+  Nociception_Gastric_Q1 = "I often feel pain in my stomach",
+  Nociception_Genital_Q1 = "My genital organs are very sensitive to pleasant stimulations",
+  Nociception_Genital_Q2 = "My genital organs are very sensitive to painful stimulations",
+  Nociception_SkinThermo_Q = "My skin is very sensitive to painful stimulations (e.g., pinching)",
+  Nociception_SkinThermo_Q2 = "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
+  Nociception_SkinThermo_Q3 = "Changes in temperature (e.g., feeling feverish or cold) are the first things I notice when I am becoming ill",
+  Nociception_ColonBladder_Q1 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
+  Nociception_ColonBladder_Q2 = "I often experience painful sensations when relieving myself when urinating or defecating",
+  Nociception_ColonBladder_A = "I often experience sensations, and I will answer zero to this question",
+  Sensitivity_State_Q1 =  "I always know when I am relaxed",
+  Sensitivity_State_Q2 =  "I always feel in my body if I am relaxed",
+  Sensitivity_State_Q3 = "My body is always in the same specific state when I am relaxed",
+  Sensitivity_State_Q4 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
+  Sensitivity_State_Q5 = "When something important is happening in my life, I can feel it in my body",
+  Sensitivity_Cardiac_Q1 = "In general, I am very sensitive to changes in my heart rate",
+  Sensitivity_Cardiac_Q2 = "I often notice changes in my heart rate",
+  Sensitivity_Cardiac_Q3 = "I can notice even very subtle changes in the way my heart beats",
+  Sensitivity_Cardiac_Q4 = "I am always very aware of my heartbeats, even when I am calm",
+  Sensitivity_Cardiac_Q5 = "I only notice my heart when it is thumping in my chest",
+  Sensitivity_Cardiac_Q6 = "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
+  Sensitivity_Cardiac_Q7 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
+  Sensitivity_Cardiac_A = "In general, I am very sensitive and attentive to the questions I am currently answering",
+  Sensitivity_Respiratory_Q1 = "In general, I am very sensitive to changes in my breathing",
+  Sensitivity_Respiratory_Q = "I often notice changes in my breathing",
+  Sensitivity_Respiratory_Q3 = "I can notice even very subtle changes in my breathing",
+  Sensitivity_Respiratory_Q4 = "I am always very aware of how I am breathing, even when I am calm",
+  Sensitivity_Respiratory_Q5 = "I often only notice how I am breathing when it becomes loud",
+  Sensitivity_Respiratory_Q6 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+  Sensitivity_Respiratory_Q7 = "When something important is happening in my life, I can immediately feel changes in my breathing",
+  Sensitivity_Gastric_Q1 = "In general, I am very sensitive to what my stomach is doing",
+  Sensitivity_Gastric_Q2 = "I can notice even very subtle changes in what my stomach is doing",
+  Sensitivity_Gastric_Q3 = "I am always very aware of what my stomach is doing, even when I am calm",
+  Sensitivity_Gastric_Q4 = "I often check the smell of my own breath",
+  Sensitivity_Gastric_Q5 = "I often check the smell of my farts",
+  Sensitivity_Gastric_Q6 = "I often pay attention to the noises of my stomach",
+  Sensitivity_Gastric_A = "I often pay attention to the answers I am giving",
+  Sensitivity_Genital_Q1 = "In general, I am very sensitive to changes in my genital organs",
+  Sensitivity_Genital_Q2 = "I can notice even very subtle changes in the state of my genital organs",
+  Sensitivity_Genital_Q3 = "I am always very aware of the state of my genital organs, even when I am calm",
+  Sensitivity_SkinThermo_Q1 = "In general, my skin is very sensitive",
+  Sensitivity_SkinThermo_Q2 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
+  Sensitivity_SkinThermo_Q3 =  "I can notice even very subtle changes if my skin becomes dry or sweaty",
+  Sensitivity_SkinThermo_Q4 ="I am always very aware if my hands and feet are cold or warm",
+  Sensitivity_SkinThermo_Q5 = "I often check the smell of my armpits",
+  Sensitivity_SkinThermo_Q6 = "I am very prone to having goosebumps",
+  Sensitivity_SkinThermo_Q7 ="My skin is susceptible to itchy fabrics and materials",
+  Sensitivity_SkinThermo_Q8 = "I enjoy the sensations of touching different materials (e.g., soft fabrics, wooden objects, smooth surfaces)",
+  Sensitivity_ColonBladder_Q1 = "In general, I am very aware of the sensations that are happening when I am defecating",
+  Sensitivity_ColonBladder_Q2 = "In general, I am very aware of the sensations that are happening when I am urinating",
+  Sensitivity_ColonBladder_Q3 = "I often check the colour of my urine",
+  Sensitivity_ColonBladder_Q4 =  "I often check the colour of my faeces",
+  Accuracy_State_Q1 =  "I can always accurately feel when I am about to cough",
+  Accuracy_State_Q2 = "I can always accurately feel when I am about to sneeze",
+  Accuracy_State_Q3 = "I can always accurately feel when I am about to vomit",
+  Accuracy_State_Q4 = "I can always accurately feel when I am starting to be hungry",
+  Accuracy_State_Q5 = "I can always accurately feel when I am starting to be thirsty",
+  Accuracy_Cardiac_Q1 = "I can always accurately feel if my heart rate is slow or fast",
+  Accuracy_Cardiac_Q2 = "I sometimes feel like my heart is racing or beating faster than usual, but when I check my pulse, it is not as intense as I thought",
+  Accuracy_Respiratory_Q1 = "I can always accurately feel how I am breathing (e.g., fast or slow, deep or shallow)",
+  Accuracy_Respiratory_A = "I can always accurately answer to the left on this question to show that I am reading it",
+  Accuracy_Gastric_Q1 = "I can always accurately feel when I am about to fart",
+  Accuracy_Gastric_Q2 = "I can always accurately feel when I am about to burp",
+  Accuracy_Gastric_Q3 = "I often feel thirsty even if I drank recently",
+  Accuracy_Gastric_Q4 = "I don't always feel the need to drink until I am really thirsty",
+  Accuracy_Gastric_Q5 = "I often feel hungry even if I ate recently",
+  Accuracy_Gastric_Q6 = "I don't always feel the need to eat until I am really hungry",
+  Accuracy_Gastric_Q7 = "I often sneeze suddenly without feeling the need building up",
+  Accuracy_Gastric_Q8 = "I sometimes feel that burping will produce some relief but then it doesn't",
+  Accuracy_Genital_Q1 = "I can always accurately perceive if my genital organs are in a state of arousal (e.g., hard, wet, pulsating)",
+  Accuracy_Genital_Q2 = "I sometimes feel like I am sexually aroused, but when I try to satisfy the feeling, I realise that I am not as sexually aroused as I initially thought",
+  Accuracy_Genital_A = "I can always accurately perceive that to this question I should answer the lowest option",
+  Accuracy_SkinThermo_Q1 = "I can always accurately feel when something is going to be itchy",
+  Accuracy_SkinThermo_Q2 = "I can always accurately feel when I start to have a fever",
+  Accuracy_SkinThermo_Q3 = "When something touches my skin, I can always accurately feel if it's hot or cold",
+  Accuracy_SkinThermo_Q4 = "I sometimes feel my skin itching, but when I scratch it, it doesn't produce the relief I expected",
+  Accuracy_ColonBladder_Q1 = "I often feel the need to urinate even when my bladder is not full",
+  Accuracy_ColonBladder_Q2 = "I don't always feel the need to urinate until my bladder is very full",
+  Accuracy_ColonBladder_Q3 = "I often feel the need to defecate even when my intestine is not full",
+  Accuracy_ColonBladder_Q4 = "I don't always feel the need to defecate until my intestine is very full",
+  Accuracy_ColonBladder_Q5 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+  Confusion_State_Q1 = "Sometimes I can't tell if the sensations in my body are good or bad",
+  Confusion_State_Q2 = "Sometimes I am confused about what sensations in my body mean",
+  Confusion_Cardiac_Q1 = "Sometimes my heart starts racing and I often don't know why",
+  Confusion_Respiratory_Q1 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+  Confusion_Gastric_Q1 = "Sometimes I feel negative and realise after eating that I was just hungry",
+  Confusion_Gastric_Q2 = "Sometimes I don't realise I was hungry until I ate something",
+  Confusion_Genital_Q1 = "Sometimes I notice arousal in my genital areas (e.g., stiffness, wetness) when I am not feeling sexually aroused",
+  Confusion_SkinThermo_Q1 = "Sometimes I have sensations on my skin (e.g., itches, goosebumps) without any clear cause",
+  Confusion_ColonBladder_Q1 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+  Confusion_ColonBladder_A = "Sometimes I notice that I need to answer all the way to the right"
+)
+
 # Make 

### 2024-11-25 study1/analysis/0_preprocessing.R
docs

@@ -4,7 +4,7 @@ library(jsonlite)
 # path for data
 # path <- "C:/Users/asf25/Box/InteroceptionScale/"
 path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
-path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
+# path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
 
 # JsPsych experiment ------------------------------------------------------
 
@@ -86,7 +86,7 @@ checks$Prolific_ID <- alldata$Prolific_ID
 checks$Experiment_Duration <- alldata$Experiment_Duration
 checks$Reward <- alldata$Reward
 checks <- checks[!is.na(checks$Prolific_ID), ]
-checks[checks$Prolific_ID=="672b6ad098ad5f2f5867fb6b", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
+# checks[checks$Prolific_ID=="670e851632b444a56d13cfb8", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
 
 # Hi, unfortunately, we can't find your data (and Prolific information suggests that you did not finish the experiment?) Did anything go wrong? Sorry for that!
 

### 2024-11-25 study1/analysis/2_analysis.qmd
Update 2_analysis.qmd

@@
     toc: true
+execute: 
+  cache: true
 ---
@@
 byrandom <- items[df$Condition=="Random",]
+```
 
+```{r}
 labels <- list(
@@
   Nociception_Genital_Q2 = "My genital organs are very sensitive to painful stimulations",
-  Nociception_SkinThermo_Q = "My skin is very sensitive to painful stimulations (e.g., pinching)",
+  Nociception_SkinThermo_Q1 = "My skin is very sensitive to painful stimulations (e.g., pinching)",
   Nociception_SkinThermo_Q2 = "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
@@
 )
-
-# Make 
 ```
@@
 ## Item Correlation
-
-::: {.panel-tabset}
 
@@
 
-# p1 <- make_heatmap(items, title="Full Sample")
-# p1
+make_heatmap(items, title="Full Sample")
 ```
-
-### By Facet
-
-Also "Dimension" / "Domains" / "Context"
-
-```{r}
-# p2 <- make_heatmap(byfacet, title="By Facet")
-# p2
-```
-
-### By Modality
-
-```{r}
-# p3 <- make_heatmap(bymodality, title="By Modality")
-# p3
-```
-
-### Random Grouping
-
-```{r}
-# p4 <- make_heatmap(byrandom, title="Random Grouping")
-# p4
-```
-
-### Figures
-
-```{r}
-#| output: false
-
-# p1 <- make_heatmap(items, interactive=FALSE) |>
-#   gridExtra::arrangeGrob(top = 'Full Sample')
-# p2 <- make_heatmap(byfacet, interactive=FALSE, title="By Facet") |>
-#   gridExtra::arrangeGrob(top = 'By Facet')
-# p3 <- make_heatmap(bymodality, interactive=FALSE, title="By Modality") |>
-#   gridExtra::arrangeGrob(top = 'By Modality')
-# p4 <- make_heatmap(byrandom, interactive=FALSE, title="Random Grouping") |>
-#   gridExtra::arrangeGrob(top = 'Random Grouping')
-```
-
-```{r}
-#| fig-width: 12
-#| fig-height: 12
-
-# gridExtra::grid.arrange(
-#   p1, p2, p3, p4,
-#   layout_matrix=rbind(
-#     c(1,1,1),
-#     c(1,1,1),
-#     c(2,3, 4)))
-```
-
-:::
 
@@
 ```{r}
-# bootstrap_similarity <- function(df) {
-#   rez <- data.frame()
-#   for(i in 1:200) {
-#     idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
-#     newdata <- df[idx,]
-#     items <- select(df, contains("_Q"))
-#     byfacet <- items[newdata$Condition=="Dimensions",]
-#     bymodality <- items[newdata$Condition=="Domains",]
-#     byrandom <- items[newdata$Condition=="Random",]
-#     
-#     rez <- rbind(
-#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet), 
-#                                          ncomp1=10, ncomp2=10, plot=FALSE),
-#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality), 
-#                                          ncomp1=10, ncomp2=10, plot=FALSE),
-#       MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
-#                                          ncomp1=10, ncomp2=10, plot=FALSE),
-#       MatrixCorrelation::allCorrelations(cor(items), cor(bymodality), 
-#                                          ncomp1=10, ncomp2=10, plot=FALSE)) |>
-#       as.data.frame() |> 
-#       mutate(
-#         Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
-#         Sample = c("Random", "Random", "Full", "Full"),
-#         Iteration = i) |> 
-#       mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |> 
-#       rbind(rez)
-#   }
-#   rez
-# }
-# 
-# 
-# rez <- bootstrap_similarity(df)
-# 
-# rez |> 
-#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
-#   filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |> 
-#   mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |> 
-#   ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
-#   ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
-#   facet_wrap(~Sample) +
-#   scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
-#   scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
-#   labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
-#   theme_minimal()
-# 
-# rez |> 
-#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
-#   filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |> 
-#   ggplot(aes(x=name, y=value)) +
-#   ggdist::stat_eye(aes(fill = after_stat(y < 0))) +
-#   facet_wrap(~Sample) +
-#   geom_hline(yintercept=0, linetype="dashed") +
-#   labs(x="Indices of Correlation Matrix Difference", y="Similarity Difference") +
-#   theme_minimal() +
-#   scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), guide="none")
+bootstrap_similarity <- function(df) {
+  rez <- data.frame()
+  for(i in 1:200) {
+    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
+    newdata <- df[idx,]
+    items <- select(df, contains("_Q"))
+    byfacet <- items[newdata$Condition=="Dimensions",]
+    bymodality <- items[newdata$Condition=="Domains",]
+    byrandom <- items[newdata$Condition=="Random",]
+
+    rez <- rbind(
+      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
+                                         ncomp1=10, ncomp2=10, plot=FALSE),
+      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
+                                         ncomp1=10, ncomp2=10, plot=FALSE),
+      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
+                                         ncomp1=10, ncomp2=10, plot=FALSE),
+      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
+                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
+      as.data.frame() |>
+      mutate(
+        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
+        Sample = c("Random", "Random", "Full", "Full"),
+        Iteration = i) |>
+      mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
+      rbind(rez)
+  }
+  rez
+}
+
+rez <- bootstrap_similarity(df)
+
+rez |>
+  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
+  filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |>
+  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
+  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
+  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
+  facet_wrap(~Sample) +
+  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
+  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
+  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
+  theme_minimal()
+```
+
+```{r}
+#| fig-width: 10
+#| fig-height: 10
+
+p_sim <- rez |>
+  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
+  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
+  filter(Sample == "Random") |> 
+  ggplot(aes(x=value, y=name)) +
+  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
+  geom_vline(xintercept=0, linetype="dashed") +
+  labs(x="Similarity Difference", y="Indices of pattern difference",
+       title="To which matrix is the random one more similar?",
+       fill="More similar to") +
+  theme_minimal() +
+  scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), labels = c("By modality", "By facet"))
+
+r <- correlation::cor_sort(cor(byrandom))
+order <- colnames(r)
+
+make_corplot <- function(data, order) {
+  rownames_to_column(as.data.frame(cor(data)), "item") |> 
+    pivot_longer(-item) |> 
+    mutate(item = fct_relevel(item, order),
+           name = fct_relevel(name, order)) |>
+    ggplot(aes(x=name, y=item, fill=value)) +
+    geom_tile() +
+    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+    theme_minimal() +
+    theme(axis.text = element_blank(),
+          axis.title = element_blank(),
+          legend.position = "none")
+}
+
+p1 <- make_corplot(byrandom, order) +
+  ggtitle("Grouped randomly")
+p2 <- make_corplot(byfacet, order) +
+  ggtitle("Grouped by facet")
+p3 <- make_corplot(bymodality, order) +
+  ggtitle("Grouped by modality")
+
+p1 / (p2 | p_sim | p3) + patchwork::plot_layout(heights=c(3, 1)) + patchwork::plot_annotation(title="Effect of Item-presentation Grouping", theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
 ```
@@
 ```{r}
+#| fig-width: 10
+#| fig-height: 8
+
 uva <- EGAnet::UVA(items, cut.off = 0.2)
-# uva
 
-toremove_table <- rbind(
-  data.frame(
-  Condition = "Full Sample",
-  Remove = uva$keep_remove$remove),
-  data.frame(
-  Condition = "By Facet",
-  Remove = EGAnet::UVA(byfacet, cut.off = 0.2)$keep_remove$remove),
-  data.frame(
-  Condition = "By Modality",
-  Remove = EGAnet::UVA(bymodality, cut.off = 0.2)$keep_remove$remove),
-  data.frame(
-  Condition = "Random Grouping",
-  Remove = EGAnet::UVA(byrandom, cut.off = 0.2)$keep_remove$remove)
-) |>
-  mutate(n = n(), .by=c("Remove")) |>
-  mutate(Condition = fct_relevel(Condition, "Full Sample", "By Facet", "By Modality", "Random Grouping")) |>
-  arrange(desc(n), Remove, Condition)
+correlation::correlation(items[unlist(uva$redundant)],
+                         items[names(uva$redundant)]) |>
+  mutate(Parameter1 = fct_relevel(Parameter1, unlist(uva$redundant)),
+         Parameter2 = fct_relevel(Parameter2, names(uva$redundant))) |>
+  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
+  geom_tile() +
+  geom_text(aes(label=insight::format_value(r)), color="white") +
+  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(x="Removed Items", y="Kept Items", fill="Correlation")
 
-toremove <- filter(toremove_table, Condition=="Full Sample" & n > 1)$Remove
-
-toremove_table |>
-  select(-n) |>
-  gt::gt() |>
-  gt::data_color(columns=Remove, fn=\(x) ifelse(x %in% toremove, "#FFEBEE", "white"))
+toremove1 <- uva$keep_remove$remove
 ```
@@
 ```{r}
-items <- select(items, -all_of(toremove))
-byfacet <- select(byfacet, -all_of(toremove))
-bymodality <- select(bymodality, -all_of(toremove))
-byrandom <- select(byrandom, -all_of(toremove))
+items <- select(items, -all_of(toremove1))
+byfacet <- select(byfacet, -all_of(toremove1))
+bymodality <- select(bymodality, -all_of(toremove1))
+byrandom <- select(byrandom, -all_of(toremove1))
 ```
@@
   items,
-  EGA.type = "EGA",
+  EGA.type = "hierEGA",
   model = "glasso",  # BGGM
@@
   typicalStructure=TRUE,
-  plot.typicalGraph=TRUE,
+  plot.typicalGraph=FALSE,
   iter=500,
@@
 ```{r}
+#| fig-width: 10
+#| fig-height: 12
+
 load("models/ega1.RData")
@@
 
-itemstability_table <- make_loadingtable(itemstability$item.stability$all.dimensions)
+itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
 
-toremove2 <- filter(itemstability_table, Max < 0.7)$Item
+toremove2 <- filter(itemstability_table, Max < 0.8)$Item
 
@@
     subtitle = "Proportion of times an item is assigned to the same cluster"
-  )
+  ) |>
+  gt::fmt_number(columns=-Item, decimals=3)
 ```
@@
 ```{r}
+#| fig-width: 10
+#| fig-height: 12
+
 load("models/ega2.RData")
 
-# itemStability(ega2)
+plot(itemStability(ega2, IS.plot=FALSE))
+```
 
+```{r}
 lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)
@@
     subtitle = "Node centrality"
-  )
+  ) |>
+  gt::fmt_number(columns=-Item, decimals=3)
 ```
@@
 
-lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) 
-higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std)) |> 
-  select(names(lower)) |> 
-  arrange(Item)
+higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std))
+cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]
+
+lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) |>
+  select(names(higher)) |>
+  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
+  arrange(Cluster, desc(Max))
+
 higher$Item <- paste0("H", higher$Item)
+higher$Label <- paste("TODO", 1:nrow(higher))
+lower <- mutate(lower, Label = labels[Item], Item = 1:n())
 
 rbind(higher, lower) |>
+  datawizard::data_relocate("Label", after = "Item") |>
   select(-Cluster, -Max) |>
@@
                  domain = c(-1, 1)) |>
-  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
+  gt::tab_style(
+    style = gt::cell_text(size="small", style="italic"),
+    locations = gt::cells_body(columns="Label")
+  ) |>
+  gt::tab_style(
+    style = list(gt::cell_text(weight="bold"),
+                 gt::cell_fill(color = "#F5F5F5")),
+    locations = list(
+      gt::cells_row_groups(groups = "Item"),
+      gt::cells_row_groups(groups = "Higher Order")
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFCDD2"),
+    locations = list(
+      gt::cells_column_labels(columns = 3),
+      gt::cells_body(columns="Item", rows=c(1, 6:8))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFCCBC"),
+    locations = list(
+      gt::cells_column_labels(columns = 4),
+      gt::cells_body(columns="Item", rows=c(9:11))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFE0B2"),
+    locations = list(
+      gt::cells_column_labels(columns = 5),
+      gt::cells_body(columns="Item", rows=c(12:14))
+    )
+  ) |>
+  gt::fmt_number(columns=-Item, decimals=2) |>
   gt::tab_header(
@@
 ```{r}
+# REMOVE ONCE https://github.com/hfgolino/EGAnet/pull/167 is merged
+convert2tidygraph <- function(EGA.object)
+{
+
+  if("bootEGA" %in% class(EGA.object)) {
+    # Bootstrapped EGA ---
+    if(!"typicalGraph" %in% names(EGA.object)) {
+      stop("The bootEGA object must contain a typicalGraph object. Set `typicalStructure=TRUE`.")
+    }
+
+    if("lower_order" %in% names(EGA.object$typicalGraph)) {
+      # Hierarchical EGA ---
+      lower_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$lower_order$wc)
+      lower_nodes$dimension <- paste0("L", lower_nodes$dimension)  # Discriminate from higher
+      lower_nodes$level <- "Lower"
+      higher_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$higher_order$wc)
+      higher_nodes$name <- paste0("L", as.numeric(higher_nodes$name))
+      higher_nodes$dimension <- paste0("H", higher_nodes$dimension)  # Discriminate from lower
+      higher_nodes$level <- "Higher"
+      nodes <- rbind(lower_nodes, higher_nodes)
+
+      lower_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$lower_order$graph)
+      higher_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$higher_order$graph)
+      higher_edges$from <- paste0("L", as.numeric(higher_edges$from))
+      higher_edges$to <- paste0("L", as.numeric(higher_edges$to))
+      edges <- rbind(lower_edges, higher_edges)
+      edges$type <- "real"
+
+      # Make edges from lower to higher order
+      for(i in 1:nrow(lower_nodes)) {
+        edges <- rbind(
+          edges,
+          data.frame(from = lower_nodes$name[i], to = lower_nodes$dimension[i], link = 1, type = "virtual")
+          )
+      }
+    } else {
+      # Non-hierarchical EGA ---
+      nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$wc)
+      edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$graph)
+    }
+
+  } else {
+    # Normal EGA ---
+    nodes <- .convert2tidygraph_nodes(EGA.object$wc)
+    edges <- .convert2tidygraph_edges(EGA.object$network)
+  }
+
+  # Return result
+  return(
+    list(
+      nodes = nodes,
+      edges = edges[edges$link != 0,]
+    )
+  )
+}
+
+#' @keywords internal
+#' @noRd
+.convert2tidygraph_nodes <- function(wc){
+  data.frame(
+    name = names(wc),
+    dimension = as.character(wc)
+  )
+}
+
+#' @keywords internal
+#' @noRd
+.convert2tidygraph_edges <- function(network){
+  data.frame(
+    from = rep(rownames(network), times = ncol(network)),
+    to = rep(colnames(network), each = nrow(network)),
+    link = as.vector(network)
+  )
+}
+```
+
+```{r}
 graph <- convert2tidygraph(ega3)
@@
 tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
-  ggraph::ggraph(layout = 'graphopt') +
+  ggraph::ggraph(layout = 'mds') +
+  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.2, strength=0, color="grey") +
   ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
-  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.1, strength=0) +
   ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
@@
   scale_edge_alpha(range = c(0, 0.9), guide="none") +
+  scale_edge_width(range = c(0.2, 3), guide="none") +
   scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
@@
 <!-- ```{r} -->
-<!-- EGAnet::EGM(items[, 1:60]) -->
+<!-- # EGAnet::EGM(items[, 1:60]) -->
 
@@
 
-<!-- rez <- EGAnet::network.compare(byfacet[, 1:20], bymodality[, 1:20], seed=3) -->
-<!-- plot(rez) -->
+<!-- # rez <- EGAnet::network.compare(byfacet, bymodality, seed=3) -->
+<!-- # plot(rez) -->
 <!-- ``` -->
 
-### Empirical vs. Model Scores
+## Empirical vs. Model Scores
 
 ```{r}
-EGAnet::net.scores()
+# Modelbased scores
+scores <- EGAnet::net.scores(
+  items[names(ega3$typicalGraph$lower_order$wc)],
+  A=ega3$typicalGraph$lower_order$graph,
+  wc=ega3$typicalGraph$lower_order$wc)$scores$std.scores |>
+  as.data.frame()
+names(scores) <- paste0("C", names(scores))
+
+# Empirical scores
+clusters <- data.frame(Item = names(ega3$typicalGraph$lower_order$wc),
+                       Cluster = ega3$typicalGraph$lower_order$wc) |>
+  mutate(Cluster = paste0("E", sprintf("%02d", Cluster)))
+
+empirical <- data.frame(Participant=df$Participant)
+for(c in unique(clusters$Cluster)) {
+  s <- rowMeans(items[clusters[clusters$Cluster==c, "Item"]])
+  empirical <- cbind(empirical, setNames(data.frame(x = s), c))
+}
+
+correlation::correlation(empirical, scores) |>
+  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
+  geom_tile() +
+  geom_text(aes(label=sprintf("%.2f", r)), size=3) +
+  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+  labs(x="Empirical Scores", y="Model Scores") +
+  theme_minimal()
 ```

### 2024-11-25 study1/analysis/1_cleaning.qmd
Uploaded cleaning script

---
title: "1_cleaning"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(easystats)
library(ggplot2)
library(readr)
library(jsonlite)

df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

# Age demographics
p_age <- estimate_density(df$Age) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=20) +
  # geom_line(aes(y = y), color = "orange", linewidth=2) +
  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5) +
  # geom_label(data = data.frame(x = mean(df$Age) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Age)))) +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_age

# Education demographics
p_edu <- df |>
  mutate(Education = fct_relevel(Education, "Other", "Elementary school", "High school", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Education)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )

# Discipline demographics
p_dis <- df |>
  ggplot(aes(x = Discipline)) +
  geom_bar(aes(fill = Discipline)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Discipline", y = "Number of Participants", subtitle = "Participants per discipline") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )

#
```

### 2024-11-25 study1/analysis/0_preprocessing.R

@@ -6,6 +6,7 @@ library(jsonlite)
 path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
 
+
 # JsPsych experiment ------------------------------------------------------
 
 files <- list.files(path, pattern = "*.csv")
@@ -106,3 +107,4 @@ alldata$Participant <- ids[alldata$Participant]
 # Save --------------------------------------------------------------------
 
 write.csv(alldata, "../data/rawdata_participants.csv", row.names = FALSE)
+

### 2024-11-25 study1/analysis/1_cleaning.qmd
cleaning updated

@@
 ---
-title: "1_cleaning"
-format: html
+title: "Data Cleaning"
+format: 
+  html:
+      code-fold: true
 editor: visual
@@
 ```{r}
+#/ output
+
 library(tidyverse)
 library(easystats)
-library(ggplot2)
-library(readr)
-library(jsonlite)
+library(patchwork)
+library(ggside)
 
-df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
-# Age demographics
+```
+
+## Age and Gender
+
+```{r}
+#/ code-fold: TRUE
+
 p_age <- estimate_density(df$Age) |>
@@
   ggplot(aes(x = x)) +
-  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=20) +
+  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28) +
   # geom_line(aes(y = y), color = "orange", linewidth=2) +
@@
   scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
+  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
   theme_modern(axis.title.space = 10) +
@@
 p_age
+```
 
-# Education demographics
+## Education
+
+```{r}
+#/ code-fold: TRUE
+
+# Education 
+# did not do education disiplines
+
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "Other", "Elementary school", "High school", "Bachelor", "Master", "Doctorate")) |>
+  mutate(Education = fct_relevel(Education, "Secondary (technical) School", "Elementary School", "High School", "Bachelor", "Master", "Doctorate")) |>
   ggplot(aes(x = Education)) +
@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.7)),
     axis.title.x = element_blank()
@@
 
-# Discipline demographics
-p_dis <- df |>
-  ggplot(aes(x = Discipline)) +
-  geom_bar(aes(fill = Discipline)) +
+p_edu
+
+# Student
+
+table(df$Student)
+```
+
+## Ethinicity
+
+```{r}
+#/ code-fold: TRUE
+# Ethnicity
+
+p_eth <- df |>
+  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
+  ggplot(aes(x = Ethnicity)) +
+  geom_bar(aes(fill = Ethnicity)) +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
   scale_fill_viridis_d(guide = "none") +
-  labs(title = "Discipline", y = "Number of Participants", subtitle = "Participants per discipline") +
+  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.8)),
+    axis.title.x = element_blank())
+
+p_eth
+```
+
+## Residence
+
+```{r}
+
+# Country participants are currently living
+
+p_cou <- df |>
+  mutate(Country = fct_relevel(Country,"United Kingdom", "Ireland", "United States", "Australia")) |>
+  ggplot(aes(x = Country)) +
+  geom_bar(aes(fill = Country)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
   theme_modern(axis.title.space = 15) +
@@
     axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
-  )
+    axis.title.x = element_blank())
 
-#
+p_cou
 ```

### 2024-11-26 study1/analysis/1_cleaning.qmd
Changes to cleaning script

@@
 
-df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+# df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+
+df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
@@
   # geom_line(aes(y = y), color = "orange", linewidth=2) +
-  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5) +
+  geom_vline(xintercept = mean(df$Age), color = "pink", linewidth=1.5) +
   # geom_label(data = data.frame(x = mean(df$Age) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Age)))) +
-  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange")) +
+  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
   scale_x_continuous(expand = c(0, 0)) +
@@
 p_cou
+
+p_country <- dplyr::select(df, region = Country) |>
+  group_by(region) |>
+  summarize(n = n()) |>
+  right_join(map_data("world"), by = "region") |>
+  ggplot(aes(long, lat, group = group)) +
+  geom_polygon(aes(fill = n)) +
+  scale_fill_gradientn(colors = c("#FFEB3B", "red", "purple")) +
+  labs(fill = "N") +
+  theme_void() +
+  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2))
+  )
+p_country
 ```

### 2024-11-26 study1/analysis/1_cleaning.qmd
Cleaning script updates

--- 2024-11-25 study1/analysis/1_cleaning.qmd
@@
 ```{r}
+#/ output
+
 library(tidyverse)
 library(easystats)
-library(ggplot2)
-library(readr)
-library(jsonlite)
+library(patchwork)
+library(ggside)
 
-df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
-# Age demographics
+# df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+
+```
+
+## Age and Gender
+
+```{r}
+#/ code-fold: TRUE
+
 p_age <- estimate_density(df$Age) |>
@@
   ggplot(aes(x = x)) +
-  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=20) +
+  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28) +
   # geom_line(aes(y = y), color = "orange", linewidth=2) +
-  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5) +
+  geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
   # geom_label(data = data.frame(x = mean(df$Age) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Age)))) +
-  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange")) +
+  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
   scale_x_continuous(expand = c(0, 0)) +
   scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
+  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
   theme_modern(axis.title.space = 10) +
@@
 p_age
+```
 
-# Education demographics
+## Education
+
+```{r}
+#/ code-fold: TRUE
+
+# Education 
+# did not add education disiplines
+
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "Other", "Elementary school", "High school", "Bachelor", "Master", "Doctorate")) |>
+  mutate(Education = fct_relevel(Education, "Secondary (technical) School", "Elementary School", "High School", "Bachelor", "Master", "Doctorate")) |>
   ggplot(aes(x = Education)) +
@@
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  scale_fill_viridis_d(guide = "none") +
+  # scale_fill_viridis_d(guide = "none") +
   labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
   theme_modern(axis.title.space = 15) +
+   scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.5)),
+    axis.title.x = element_blank()
+  )
+
+p_edu
+
+# Student
+
+table(df$Student)
+```
+
+## Ethinicity
+
+```{r}
+#/ code-fold: TRUE
+# Ethnicity
+
+p_eth <- df |>
+  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
+  ggplot(aes(x = Ethnicity)) +
+  geom_bar(aes(fill = Ethnicity)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
+  theme_modern(axis.title.space = 15) +
+  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#FDB863", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.6)),
+    axis.title.x = element_blank())
+
+p_eth
+
+```
+
+## Residence
+
+```{r}
+
+# Country participants are currently living
+
+p_cou <- df |>
+  mutate(Country = fct_relevel(Country,"United Kingdom", "Ireland", "USA", "Australia")) |>
+  ggplot(aes(x = Country)) +
+  geom_bar(aes(fill = Country)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
+  theme_modern(axis.title.space = 15) +
+  scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.7)),
+    axis.title.x = element_blank())
+
+p_cou
+
+```
+
+```{r}
+
+# <!--Do it-->
+
+p_country <- dplyr::select(df, region = Country) |>
+  group_by(region) |>
+  summarize(n = n()) |>
+  right_join(map_data("world"), by = "region") |>
+  ggplot(aes(long, lat, group = group)) +
+  geom_polygon(aes(fill = n)) +
+  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#d01c8b")) +
+  labs(fill = "N") +
+  theme_void() +
+  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2))
+  )
+p_country
+```
+
+```{r}
+
+table(df$Country)
+```
+
+```{r}
+
+dplyr::select(df, region = Country) |>
+  group_by(region) |>
+  summarize(n = n()) |>
+  right_join(map_data("world"), by = "region") |>
+  ggplot(aes(long, lat, group = group)) +
+  geom_polygon(aes(fill = n))
+
+```
+
+```{r}
+
+p_feed <- estimate_density(df$Experiment_Enjoyment) |>
+  normalize(select = y) |>
+  mutate(y = y * 86) |>  # To match the binwidth
+  ggplot(aes(x = x)) +
+  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
+  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", color = NULL, x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
+  # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
+  theme_modern(axis.title.space = 10) +
   theme(
@@
   )
+p_feed
 
-# Discipline demographics
-p_dis <- df |>
-  ggplot(aes(x = Discipline)) +
-  geom_bar(aes(fill = Discipline)) +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  scale_fill_viridis_d(guide = "none") +
-  labs(title = "Discipline", y = "Number of Participants", subtitle = "Participants per discipline") +
-  theme_modern(axis.title.space = 15) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
-  )
-
-#
+  #geom_line(aes(y = y), color = "orange", linewidth=2) +
+#geom_vline(xintercept = mean(df$Experiment_Enjoyment), color = "#ca0020", linewidth=1.5) +
 ```

### 2024-11-27 study1/analysis/1_cleaning.qmd
updating cleaning script

@@
   theme_modern(axis.title.space = 15) +
-  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#FDB863", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
+  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
   theme(
@@
 
-p_country <- dplyr::select(df, region = Country) |>
+p_country <- df |>
+  mutate(Country = case_when(
+    Country=="United States"~ "USA",
+    Country=="United Kingdom" ~ "UK",
+    TRUE ~ Country
+  ))|>
+  dplyr::select(region = Country) |>
   group_by(region) |>
@@
   right_join(map_data("world"), by = "region") |>
+  # mutate(n = replace_na(n, 0)) |>
   ggplot(aes(long, lat, group = group)) +
   geom_polygon(aes(fill = n)) +
-  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#d01c8b")) +
+  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
   labs(fill = "N") +
@@
   )
+
 p_country
+
+```
+
+```{r}
+# Create mapping from df's country names to world_map's country names. I think the map is not working because the names do not match.
+
+country_mapping <- data.frame(
+  df_name = c("United States", "United Kingdom"),
+  world_map = c("USA", "UK") 
+)
+
+country_mapping
+
 ```
@@
 table(df$Country)
-```
-
-```{r}
-
-dplyr::select(df, region = Country) |>
-  group_by(region) |>
-  summarize(n = n()) |>
-  right_join(map_data("world"), by = "region") |>
-  ggplot(aes(long, lat, group = group)) +
-  geom_polygon(aes(fill = n))
-
 ```
@@
   scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", color = NULL, x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
+  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
   # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
+  facet_wrap(~Condition) +
   theme_modern(axis.title.space = 10) +
@@
     axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
+    #axis.title.x = element_blank()
   )

### 2024-11-27 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

@@
 
-df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+# df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
-# df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
@@
 
-```{r}
-
-table(df$Country)
-```
+\## Experiment Enjoyment
 

### 2024-11-27 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

@@
 ```
+
+## Attention Checks
+
+```{r}
+df <- df |>
+  dplyr::mutate(
+    A1 = dplyr::case_when(
+      Sexual_State_A == 6 | Sexual_State_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A2 = dplyr::case_when(
+      Anxious_SkinThermo_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A3 = dplyr::case_when(
+      Nociception_ColonBladder_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A4 = dplyr::case_when(
+      Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A5 = dplyr::case_when(
+      Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A6 = dplyr::case_when(
+      Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A7 = dplyr::case_when(
+      Accuracy_Genital_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A8 = dplyr::case_when(
+      Confusion_ColonBladder_A == 6 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+  )
+
+df
+```

### 2024-11-28 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

--- 2024-11-27 study1/analysis/1_cleaning.qmd
@@
 ```{r}
-#/ output
+#| warning: false
+#| code-fold: true
+#| error: false
 
@@
 
-df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+#df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
+df <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study1/data/rawdata_participants.csv")
 ```
@@
 ```{r}
-#/ code-fold: TRUE
+#| warning: false
+#| code-fold: true
+#| error: false
 
@@
 ```{r}
-#/ code-fold: TRUE
+#| warning: false
+#| code-fold: true
+#| error: false
 
-# Education 
 # did not add education disiplines
@@
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  # scale_fill_viridis_d(guide = "none") +
+  scale_fill_viridis_d(guide = "none") +
   labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
   theme_modern(axis.title.space = 15) +
-   scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
+  # scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
   theme(
@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.5)),
+    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
     axis.title.x = element_blank()
@@
 
-## Ethinicity
+## Ethnicity
 
 ```{r}
-#/ code-fold: TRUE
+#| warning: false
+#| code-fold: true
+#| error: false
+
 # Ethnicity
@@
   theme_modern(axis.title.space = 15) +
-  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
+  #scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
   theme(
@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.6)),
+    axis.text.x = element_text(size = rel(0.6), angle = 45, hjust = 1),
     axis.title.x = element_blank())
@@
 ```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
 
@@
   theme_modern(axis.title.space = 15) +
-  scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
+  #scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
   theme(
@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.7)),
+    axis.text.x = element_text(size = rel(0.7),  angle = 45, hjust =1),
     axis.title.x = element_blank())
@@
 ```{r}
-
-# <!--Do it-->
+#| warning: false
+#| code-fold: true
+#| error: false
 
@@
 
-```{r}
-# Create mapping from df's country names to world_map's country names. I think the map is not working because the names do not match.
-
-country_mapping <- data.frame(
-  df_name = c("United States", "United Kingdom"),
-  world_map = c("USA", "UK") 
-)
-
-country_mapping
-
-```
-
-\## Experiment Enjoyment
+## Experiment Enjoyment
 
 ```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
 

### 2024-11-28 study1/analysis/1_cleaning.qmd
Updated cleaning script with attention checks

@@
 ---
-title: "Data Cleaning"
+title: "Interoception Scale - Data Cleaning"
+editor: source
+editor_options: 
+  chunk_output_type: console
 format:
@@
     code-fold: true
-editor: visual
+    self-contained: false
+    toc: true
 ---
+
+## Data Preparation
 
@@
 library(ggside)
+```
+```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+# Load the data
 
@@
 
-#df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
-
-df <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study1/data/rawdata_participants.csv")
+df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 ```
 
-## Age and Gender
+## Attention Checks
 
@@
 
+df <- df |>
+  dplyr::mutate(
+    A1 = dplyr::case_when(
+      Sexual_State_A == 6 | Sexual_State_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A2 = dplyr::case_when(
+      Anxious_SkinThermo_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A3 = dplyr::case_when(
+      Nociception_ColonBladder_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A4 = dplyr::case_when(
+      Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A5 = dplyr::case_when(
+      Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A6 = dplyr::case_when(
+      Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A7 = dplyr::case_when(
+      Accuracy_Genital_A == 0 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+    A8 = dplyr::case_when(
+      Confusion_ColonBladder_A == 6 ~ "Pass",
+      TRUE ~ "Fail"
+    ),
+  )
+
+df$count.Fail <- apply(df[, c("A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8")], 1, function(x) length(which(x == "Fail")))
+
+p_fail <- df |>
+  ggplot(aes(x = count.Fail)) +
+  geom_bar(aes(fill = count.Fail)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  # scale_fill_viridis_d(guide = "none") +
+  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
+  theme_modern(axis.title.space = 15) +
+   scale_fill_manual(values = c("0"="#0571B0","1"= "#d01c8b", "2"="#cc66cc", "3"="#E66101", "4" =  "#ca0020", "5"="#5E3C99", "6"="#92C5DE")) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.5)),
+    axis.title.x = element_blank()
+  )
+
+p_fail
+
+df <- df |> filter(count.Fail == 0)
+```
+
+## Experiment Enjoyment
+
+```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+p_feed <- estimate_density(df$Experiment_Enjoyment) |>
+  normalize(select = y) |>
+  mutate(y = y * 86) |>  # To match the binwidth
+  ggplot(aes(x = x)) +
+  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
+  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
+  facet_wrap(~Condition) +
+  theme_modern(axis.title.space = 10) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+  )
+p_feed
+
+```
+
+## Final Sample
+
+::: {.panel-tabset}
+
+## Age and Gender
+
+```{r p_demographics_age_gender}
 p_age <- estimate_density(df$Age) |>
@@
   geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28) +
-  # geom_line(aes(y = y), color = "orange", linewidth=2) +
   geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
-  # geom_label(data = data.frame(x = mean(df$Age) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Age)))) +
   scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
@@
     plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
-  )
-p_age
+    axis.text.y = element_text(size = rel(1.1)),)
 ```
@@
 
-```{r}
-#| warning: false
-#| code-fold: true
-#| error: false
-
-# did not add education disiplines
+```{r p_demographics_education}
+# Did not add education disciplines
 
@@
 
-## Ethnicity
+## Ethinicity
 
-```{r}
-#| warning: false
-#| code-fold: true
-#| error: false
-
-# Ethnicity
-
+```{r p_demographics_ethnicity}
 p_eth <- df |>
@@
   theme_modern(axis.title.space = 15) +
-  #scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
+  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
   theme(
@@
 
-## Residence
+## Country of Residence
 
-```{r}
-#| warning: false
-#| code-fold: true
-#| error: false
-
-# Country participants are currently living
-
+```{r p_demographics_country}
 p_cou <- df |>
@@
  theme_modern(axis.title.space = 15) +
-  #scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
+ scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
  theme(
@@
    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.7),  angle = 45, hjust =1),
+   axis.text.x = element_text(size = rel(0.7)),
    axis.title.x = element_blank())
@@
 p_cou
-
 ```
 
-```{r}
-#| warning: false
-#| code-fold: true
-#| error: false
-
-p_country <- df |>
+```{r p_demographics_map}
+p_map <- df |>
   mutate(Country = case_when(
@@
 
-p_country
-
+p_map
 ```
-
-## Experiment Enjoyment
 
@@
 
-p_feed <- estimate_density(df$Experiment_Enjoyment) |>
-  normalize(select = y) |>
-  mutate(y = y * 86) |>  # To match the binwidth
-  ggplot(aes(x = x)) +
-  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
-  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
-  # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
-  facet_wrap(~Condition) +
-  theme_modern(axis.title.space = 10) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    #axis.title.x = element_blank()
+# Create mapping from df's country names to world_map's country names. I think the map is not working because the names do not match.
+
+country_mapping <- data.frame(
+  df_name = c("United States", "United Kingdom"),
+  world_map = c("USA", "UK") 
 )
-p_feed
 
-  #geom_line(aes(y = y), color = "orange", linewidth=2) +
-#geom_vline(xintercept = mean(df$Experiment_Enjoyment), color = "#ca0020", linewidth=1.5) +
+country_mapping
+
 ```
+:::
+
+```{r p_summary}
+#| fig-width: 15
+#| fig-height: 15
+
+p_map / 
+  (p_age + p_edu)
+```
+
+## Save
+
+```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+write.csv(df, "../data/data_participants.csv", row.names = FALSE)
+```

### 2024-11-28 study1/analysis/1_cleaning.qmd
Changes to cleaning files

--- 2024-11-28 study1/analysis/1_cleaning.qmd
@@
 
-#df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
+# df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
 
 df <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study1/data/rawdata_participants.csv")
+
 ```
+
+## Attention Checks
+
+```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+df <- df |>
+  dplyr::mutate(
+    A1 = dplyr::case_when(
+      # "I always know that I am attentively doing a study"
+      Sexual_State_A == 6 | Sexual_State_A == 5 ~ "Pass",
+      TRUE ~ "Fail"),
+    A2 = dplyr::case_when(
+      # "Even if I am anxious, I should now answer all the way to the left"
+      Anxious_SkinThermo_A == 0 ~ "Pass",
+      TRUE ~ "Fail"),
+    A3 = dplyr::case_when(
+      # "I often experience sensations, and I will answer zero to this question"
+      Nociception_ColonBladder_A == 0 ~ "Pass",
+      TRUE ~ "Fail"),
+    A4 = dplyr::case_when(
+      # "In general, I am very sensitive and attentive to the questions I am       currently answering"
+      Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5 ~ "Pass",
+      TRUE ~ "Fail"),
+    A5 = dplyr::case_when(
+      # "I often pay attention to the answers I am giving"
+      Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5 ~ "Pass",
+      TRUE ~ "Fail"),
+    A6 = dplyr::case_when(
+      # "I can always accurately answer to the left on this question to show that I am reading it" 
+      Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1 ~ "Pass",
+      TRUE ~ "Fail"),
+    A7 = dplyr::case_when(
+      # "I can always accurately perceive that to this question I should answer the lowest option"
+      Accuracy_Genital_A == 0 ~ "Pass",
+      TRUE ~ "Fail"),
+    A8 = dplyr::case_when(
+      #  "Sometimes I notice that I need to answer all the way to the right"
+      Confusion_ColonBladder_A == 6 ~ "Pass",
+      TRUE ~ "Fail"),
+  )
+
+# Create colum with the total number of Failed attention checks 
+df$Total_Attention_Failed <- apply(df[, c("A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8")], 1, function(x) sum((x == "Fail")))
+
+p_fail <- df |>
+  ggplot(aes(x = Total_Attention_Failed)) +
+  geom_bar(aes(fill = factor(Total_Attention_Failed))) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(0.5)),
+    axis.title.x = element_blank()
+  )
+
+p_fail
+
+```
+
+```{r}
+
+removed_participants <- nrow(df |> filter(Total_Attention_Failed >= 1))
+
+df <- df |>
+  filter(Total_Attention_Failed == 0)
+```
+
+`r removed_participants` participants were removed for having failed at least 1 attention check.
+
+## Experiment Enjoyment
+
+```{r}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+p_feed <- estimate_density(df$Experiment_Enjoyment) |>
+  normalize(select = y) |>
+  mutate(y = y * 86) |>  # To match the binwidth
+  ggplot(aes(x = x)) +
+  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
+  scale_fill_manual(values = c("Dimensions"= "#ff944d","Domains" = "#ca0020", "Random"="#ff80d5")) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
+  facet_wrap(~Condition) +
+  theme_modern(axis.title.space = 10) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+  )
+p_feed
+
+```
+
+## Final Sample
+
+::: panel-tabset
+
+## Summary
+
+-The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
 
@@
 
-```{r}
+```{r p_demographics_age_gender}
 #| warning: false
@@
     plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
-  )
+    axis.text.y = element_text(size = rel(1.1)),)
+
 p_age
@@
 
-```{r}
+```{r p_demographics_education}
 #| warning: false
@@
 
-# did not add education disiplines
+# Did not add education disciplines
 
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "Secondary (technical) School", "Elementary School", "High School", "Bachelor", "Master", "Doctorate")) |>
   ggplot(aes(x = Education)) +
@@
   theme_modern(axis.title.space = 15) +
-  # scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
   theme(
@@
 # Student
-
-table(df$Student)
+table(df$Student) |>
+  as.data.frame() |>
+  rename(Student = Var1, Frequency = Freq) |>
+  knitr::kable()
 ```
 
-## Ethnicity
+## Ethinicity
 
-```{r}
+```{r p_demographics_ethnicity}
 #| warning: false
@@
 
-# Ethnicity
-
 p_eth <- df |>
-  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
   ggplot(aes(x = Ethnicity)) +
@@
   theme_modern(axis.title.space = 15) +
-  #scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
   theme(
@@
 
-## Residence
+## Country of Residence
 
-```{r}
+```{r p_demographics_country}
 #| warning: false
@@
 
-# Country participants are currently living
-
 p_cou <- df |>
-  mutate(Country = fct_relevel(Country,"United Kingdom", "Ireland", "USA", "Australia")) |>
  ggplot(aes(x = Country)) +
@@
  theme_modern(axis.title.space = 15) +
-  #scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
  theme(
@@
    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.7),  angle = 45, hjust =1),
+   axis.text.x = element_text(size = rel(0.7), angle = 45, hjust = 1),
    axis.title.x = element_blank())
@@
 p_cou
-
 ```
 
-```{r}
+```{r p_demographics_map}
 #| warning: false
@@
 
-p_country <- df |>
+p_map <- df |>
   mutate(Country = case_when(
@@
 
-p_country
+p_map
+```
+:::
 
+```{r p_summary}
+#| warning: false
+#| code-fold: true
+#| error: false
+
+p_map 
+p_age 
+p_edu
 ```
 
-## Experiment Enjoyment
+## Save
 
@@
 
-p_feed <- estimate_density(df$Experiment_Enjoyment) |>
-  normalize(select = y) |>
-  mutate(y = y * 86) |>  # To match the binwidth
-  ggplot(aes(x = x)) +
-  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
-  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
-  # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
-  facet_wrap(~Condition) +
-  theme_modern(axis.title.space = 10) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    #axis.title.x = element_blank()
-  )
-p_feed
-
-  #geom_line(aes(y = y), color = "orange", linewidth=2) +
-#geom_vline(xintercept = mean(df$Experiment_Enjoyment), color = "#ca0020", linewidth=1.5) +
+write.csv(df, "../data/data_participants.csv", row.names = FALSE)
 ```

### 2024-11-29 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd
@AnafNeves @EmmaLBenn @maisiebennett added another outlier detection check + streamlined the code a bit + added some TODOs

@@
 #| warning: false
-#| code-fold: true
+#| code-fold: false
 #| error: false
@@
 
-# df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
-
-# df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")
-
-df <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study1/data/rawdata_participants.csv")
-
+df <- read.csv("../data/rawdata_participants.csv")
 ```
 
-## Attention Checks
+## Feedback
+
+### Experiment Enjoyment
 
@@
 #| warning: false
-#| code-fold: true
-#| error: false
 
-df <- df |>
-  dplyr::mutate(
-    A1 = dplyr::case_when(
-      # "I always know that I am attentively doing a study"
-      Sexual_State_A == 6 | Sexual_State_A == 5 ~ "Pass",
-      TRUE ~ "Fail"),
-    A2 = dplyr::case_when(
-      # "Even if I am anxious, I should now answer all the way to the left"
-      Anxious_SkinThermo_A == 0 ~ "Pass",
-      TRUE ~ "Fail"),
-    A3 = dplyr::case_when(
-      # "I often experience sensations, and I will answer zero to this question"
-      Nociception_ColonBladder_A == 0 ~ "Pass",
-      TRUE ~ "Fail"),
-    A4 = dplyr::case_when(
-      # "In general, I am very sensitive and attentive to the questions I am       currently answering"
-      Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5 ~ "Pass",
-      TRUE ~ "Fail"),
-    A5 = dplyr::case_when(
-      # "I often pay attention to the answers I am giving"
-      Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5 ~ "Pass",
-      TRUE ~ "Fail"),
-    A6 = dplyr::case_when(
-      # "I can always accurately answer to the left on this question to show that I am reading it" 
-      Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1 ~ "Pass",
-      TRUE ~ "Fail"),
-    A7 = dplyr::case_when(
-      # "I can always accurately perceive that to this question I should answer the lowest option"
-      Accuracy_Genital_A == 0 ~ "Pass",
-      TRUE ~ "Fail"),
-    A8 = dplyr::case_when(
-      #  "Sometimes I notice that I need to answer all the way to the right"
-      Confusion_ColonBladder_A == 6 ~ "Pass",
-      TRUE ~ "Fail"),
-  )
-
-# Create colum with the total number of Failed attention checks 
-df$Total_Attention_Failed <- apply(df[, c("A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8")], 1, function(x) sum((x == "Fail")))
-
-p_fail <- df |>
-  ggplot(aes(x = Total_Attention_Failed)) +
-  geom_bar(aes(fill = factor(Total_Attention_Failed))) +
-  scale_fill_viridis_d(guide = "none") +
-  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
-  theme_modern(axis.title.space = 15) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.5)),
-    axis.title.x = element_blank()
-  )
-
-p_fail
-
-```
-
-```{r}
-
-removed_participants <- nrow(df |> filter(Total_Attention_Failed >= 1))
-
-df <- df |>
-  filter(Total_Attention_Failed == 0)
-```
-
-`r removed_participants` participants were removed for having failed at least 1 attention check.
-
-## Experiment Enjoyment
-
-```{r}
-#| warning: false
-#| code-fold: true
 #| error: false
@@
 
+**TODO: Add feedback comments table**
+
+## Exclusions
+
+```{r}
+outliers <- list()
+```
+
+### Attention Checks
+
+```{r}
+#| warning: false
+#| error: false
+
+dfchecks <- df |>
+  dplyr::mutate(
+    # "I always know that I am attentively doing a study"
+    A1 = ifelse(Sexual_State_A == 6 | Sexual_State_A == 5, 0, 1),
+    # "Even if I am anxious, I should now answer all the way to the left"
+    A2 = ifelse(Anxious_SkinThermo_A == 0, 0, 1),
+    # "I often experience sensations, and I will answer zero to this question"
+    A3 = ifelse(Nociception_ColonBladder_A == 0, 0, 1),
+    # "In general, I am very sensitive and attentive to the questions I am currently answering"
+    A4 = ifelse(Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5, 0, 1),
+    # "I often pay attention to the answers I am giving"
+    A5 = ifelse(Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5, 0, 1),
+    # "I can always accurately answer to the left on this question to show that I am reading it"
+    A6 = ifelse(Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1, 0, 1),
+    # "I can always accurately perceive that to this question I should answer the lowest option"
+    A7 = ifelse(Accuracy_Genital_A == 0, 0, 1),
+    # "Sometimes I notice that I need to answer all the way to the right"
+    A8 = ifelse(Confusion_ColonBladder_A == 6, 0, 1),
+    .keep = "none"
+  ) 
+dfchecks$Total <- rowSums(dfchecks)
+
+dfchecks |>
+  mutate(Total = as.factor(paste0(Total, "/8"))) |> 
+  ggplot(aes(x = Total)) +
+  geom_bar(aes(fill = Total)) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.title.x = element_blank(),
+  )
+```
+
+```{r}
+outliers$attentionchecks <- df$Participant[dfchecks$Total >= 1]
+```
+
+We removed `r length(outliers$attentionchecks)` (`insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).
+
+### Mahalanobis Distance
+
+```{r}
+# Compute distance
+dfoutlier <- performance::check_outliers(select(df, contains("_Q")), 
+                                         method=c("lof"),
+                                         threshold=list(lof = 0.0001)) |> 
+  as.data.frame() |> 
+  mutate(Participant = fct_reorder(df$Participant, Distance_LOF),
+         Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
+         Outlier = ifelse(Outlier_LOF == 1, "Distance Outlier", "Valid"),
+         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Check", Outlier))
+
+# parameters::parameters(glm(Outlier_AttentionCheck ~ Distance_LOF, data = dfoutlier, family = "binomial"))
+
+outliers$distance <- as.character(dfoutlier[dfoutlier$Outlier_LOF == 1, "Participant"])
+outliers$distance <- outliers$distance[!outliers$distance %in% outliers$attentionchecks]
+
+dfoutlier |> 
+  ggplot(aes(x=Participant, y=Distance_LOF)) +
+  geom_bar(aes(fill=Outlier), stat="identity") +
+  theme_minimal() +
+  theme(axis.text.x = element_blank())
+```
+
+**TODO: Add a little paragraph explaining what it is etc.**
+We removed `r length(outliers$distance)` (`insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.
+
+```{r}
+df <- filter(df, !Participant %in% outliers$attentionchecks)
+df <- filter(df, !Participant %in% outliers$distance)
+```
+
 ## Final Sample
@@
 #| warning: false
-#| code-fold: true
+
 #| error: false

### 2024-11-29 study1/analysis/1_cleaning.qmd
finished TODO on cleaning script

@@
     toc: true
+bibliography: references.bib
 ---
@@
 
-**TODO: Add feedback comments table**
+### Comments
+
+```{r}
+data.frame(Condition = df$Condition,
+          Comments = df$Experiment_Feedback) |> 
+  filter(!tolower(Comments) %in% c(NA, "None", "no", "none", "No thank you", "no thank you", "no not at all", "no thanks", "No comment", "No", "nil", "N.A", "n/a", "N/A", "na", "Not Really")) |> 
+  gt::gt() |> 
+  gt::opt_stylize() |> 
+  gt::opt_interactive(use_compact_mode = TRUE) 
+```
 
@@
 
-We removed `r length(outliers$attentionchecks)` (`insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).
+We removed `r length(outliers$attentionchecks)` (`r insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).
 
@@
 
-**TODO: Add a little paragraph explaining what it is etc.**
-We removed `r length(outliers$distance)` (`insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.
+Mahalanobis distance [@demaesschalck2000] is commonly used to detect multivariate outliers, which are data points with unusual combinations of scores on two or more variables [@filzmoser2016].
+This distance is calculated relative to the centroid—a central point where the means of all variables intersect—with larger distances indicating greater deviation from the center.
+
+This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping itmes.
+
+We removed `r length(outliers$distance)` (`r insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.
 
@@
 ::: panel-tabset
-
 ## Summary

### 2024-11-30 study1/analysis/1_cleaning.qmd
update

@@
 library(ggside)
+library(ggdist)
 
@@
 ```{r}
-#| warning: false
+df |> 
+  summarise(n = n(), .by=c("Condition", "Experiment_Enjoyment")) |>
+  filter(!is.na(Experiment_Enjoyment)) |> 
+  mutate(n = n / sum(n),
+         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
+         .by="Condition") |>
+  ggplot(aes(y = Condition, x = n, fill = Experiment_Enjoyment)) +
+  geom_bar(stat="identity", position="stack") +
+  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
+  scale_x_continuous(expand=c(0, 0))  +
+  labs(title="Experiment Enjoyment",
+       subtitle="Proportion of participants by condition") + 
+  guides(fill = guide_legend(reverse=TRUE)) +
+  theme_minimal() +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        legend.position = "top",
+        legend.title = element_blank())
 
-#| error: false
-
-p_feed <- estimate_density(df$Experiment_Enjoyment) |>
-  normalize(select = y) |>
-  mutate(y = y * 86) |>  # To match the binwidth
-  ggplot(aes(x = x)) +
-  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
-  scale_fill_manual(values = c("Dimensions"= "#ff944d","Domains" = "#ca0020", "Random"="#ff80d5")) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
-  facet_wrap(~Condition) +
-  theme_modern(axis.title.space = 10) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-  )
-p_feed
-
+lm(Experiment_Enjoyment ~ Condition, data = df) |> 
+  modelbased::estimate_contrasts(p_adjust="none", contrast = "Condition") |> 
+  display()
 ```
@@
 ```{r}
-data.frame(Condition = df$Condition,
-          Comments = df$Experiment_Feedback) |> 
-  filter(!tolower(Comments) %in% c(NA, "None", "no", "none", "No thank you", "no thank you", "no not at all", "no thanks", "No comment", "No", "nil", "N.A", "n/a", "N/A", "na", "Not Really")) |> 
+data.frame(Comments = df$Experiment_Feedback) |> 
+  filter(!tolower(Comments) %in% c(NA, "no", "none", "no thank you", "no not at all", "no thanks", "no comment", "nil", "n.a", "n/a", "na", "not really", "thank you", "nothing", "no not at the moment", "none for now", "thank you!", "thanks", "not really.")) |>
   gt::gt() |> 
@@
 ```{r}
-#| warning: false
-#| error: false
-
 dfchecks <- df |>
@@
 
-### Mahalanobis Distance
+### Multivariate Distance
 
@@
          Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Check", Outlier))
-
-# parameters::parameters(glm(Outlier_AttentionCheck ~ Distance_LOF, data = dfoutlier, family = "binomial"))
 
@@
 
-This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping itmes.
+This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping items.
 
@@
 
+### Predictors
+
 ```{r}
-df <- filter(df, !Participant %in% outliers$attentionchecks)
-df <- filter(df, !Participant %in% outliers$distance)
+dfoutlier <- full_join(dfoutlier, select(df, Participant, Experiment_Duration), by = join_by(Participant))
+
+parameters::parameters(glm(Outlier_AttentionCheck ~ Distance_LOF, data = dfoutlier, family = "binomial"))
+parameters::parameters(glm(Outlier_AttentionCheck ~ poly(Experiment_Duration, 2), data = dfoutlier, family = "binomial"))
+parameters::parameters(glm(Distance_LOF ~ poly(Experiment_Duration, 2), data = dfoutlier))
+```
+
+```{r}
+r_full <- cor(select(df, contains("_Q")))
+r_cleaned <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$distance)) |> 
+  select(contains("_Q")) |> 
+  cor()
+
+data.frame(Full=r_full[lower.tri(r_full)], Clean=r_cleaned[lower.tri(r_cleaned)]) |> 
+  pivot_longer(everything()) |> 
+  ggplot(aes(x=value)) +
+  geom_histogram(aes(fill=name, color=name), bins=60, alpha=0.3, position="identity") +
+  theme_minimal()
+```
+
+```{r}
+#| code-fold: false
+
+df <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$distance))
 ```

### 2024-11-30 study1/analysis/0_preprocessing.R

@@ -73,7 +73,6 @@ for (file in files) {
 }
 
 
-alldata[is.na(alldata$Prolific_ID), ]
 # Attention checks --------------------------------------------------------
 checks <- data.frame(
   Sexual_State_A = alldata$Sexual_State_A / 6,
@@ -90,7 +89,7 @@ checks$Prolific_ID <- alldata$Prolific_ID
 checks$Experiment_Duration <- alldata$Experiment_Duration
 checks$Reward <- alldata$Reward
 checks <- checks[!is.na(checks$Prolific_ID), ]
-# checks[checks$Prolific_ID=="670e851632b444a56d13cfb8", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
+# checks[checks$Prolific_ID=="60f059aff7f931e2d83bacb5", c("Prolific_ID", "Experiment_Duration", "Score", "Reward")]
 
 # Hi, unfortunately, we can't find your data (and Prolific information suggests that you did not finish the experiment?) Did anything go wrong? Sorry for that!
 

### 2024-11-30 study1/analysis/1_cleaning.qmd
add TODO in cleaning
@AnafNeves @EmmaLBenn @maisiebennett

@@
 ::: panel-tabset
-## Summary
 
--The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
+### Summary
 
-## Age and Gender
+- The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
+
+**TODO**
+- The age plot code should be streamlined (there is no need to compute estimate_density)
+- Education: add in the preprocessing a manual reassignment of some of the "Other" manual inputs to our categories (and put Other if not in the categories)
+- We can merge the edu and student plot by having student be a "color" aesthethic 
+- Make Pie chart for ethnicity (see doggonogo for example). 
+- Ethnicity: manually check the others and either assign them to the correct category or put them in "Other"
+
+### Age and Gender
 
 ```{r p_demographics_age_gender}
-#| warning: false
-
-#| error: false
-
 p_age <- estimate_density(df$Age) |>
@@
   ggplot(aes(x = x)) +
-  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28) +
+  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28, position="identity", alpha=0.5) +
   geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
@@
 
-## Education
+### Education
 
@@
 
-## Ethinicity
+### Ethinicity
 
@@
 
-## Country of Residence
-
-```{r p_demographics_country}
-#| warning: false
-
-#| error: false
-
-p_cou <- df |>
- ggplot(aes(x = Country)) +
- geom_bar(aes(fill = Country)) +
- scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
- scale_fill_viridis_d(guide = "none") +
- labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
- theme_modern(axis.title.space = 15) +
- theme(
-   plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-   plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-   axis.text.y = element_text(size = rel(1.1)),
-   axis.text.x = element_text(size = rel(0.7), angle = 45, hjust = 1),
-   axis.title.x = element_blank())
-
-p_cou
-```
+### Country of Residence
 
 ```{r p_demographics_map}
-#| warning: false
-
-#| error: false
-
 p_map <- df |>
@@
 ```
+
+```{r}
+sort(table(df$Country)) |> 
+  as.data.frame() |> 
+  gt::gt()
+```
+
 :::
@@
 ```{r p_summary}
-#| warning: false
-
-#| error: false
-
 p_map 
@@
 ```{r}
-#| warning: false
-
-#| error: false
-
 write.csv(df, "../data/data_participants.csv", row.names = FALSE)

### 2024-12-02 study1/analysis/1_cleaning.qmd
Finished TODO on cleaning and pre-processing scripts

@@
 ::: panel-tabset
-
 ### Summary
@@
 
-**TODO**
-- The age plot code should be streamlined (there is no need to compute estimate_density)
-- Education: add in the preprocessing a manual reassignment of some of the "Other" manual inputs to our categories (and put Other if not in the categories)
-- We can merge the edu and student plot by having student be a "color" aesthethic 
-- Make Pie chart for ethnicity (see doggonogo for example). 
-- Ethnicity: manually check the others and either assign them to the correct category or put them in "Other"
-
 ### Age and Gender
@@
 ```{r p_demographics_age_gender}
-p_age <- estimate_density(df$Age) |>
-  normalize(select = y) |>
-  mutate(y = y * 86) |>  # To match the binwidth
-  ggplot(aes(x = x)) +
-  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28, position="identity", alpha=0.5) +
-  geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
-  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
-  scale_x_continuous(expand = c(0, 0)) +
+p_age <- df |>
+  ggplot(aes(x = Age, fill = Gender)) + 
+  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
+  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
+  scale_fill_viridis_d() +
+  scale_x_continuous(expand = c(0, 0), breaks = seq(20, max(df$Age), by = 10 )) +
   scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
+  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
   theme_modern(axis.title.space = 10) +
@@
     plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),)
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
 
@@
 #| warning: false
-
 #| error: false
@@
 p_edu <- df |>
+  mutate (Student = ifelse(is.na(Student), FALSE, Student)) |>
   ggplot(aes(x = Education)) +
-  geom_bar(aes(fill = Education)) +
+  geom_bar(aes(fill = Student)) +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  scale_fill_viridis_d(guide = "none") +
-  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
+  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
   theme_modern(axis.title.space = 15) +
@@
 p_edu
-
-# Student
-table(df$Student) |>
-  as.data.frame() |>
-  rename(Student = Var1, Frequency = Freq) |>
-  knitr::kable()
 ```
@@
 p_eth <- df |> 
-  ggplot(aes(x = Ethnicity)) +
-  geom_bar(aes(fill = Ethnicity)) +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  scale_fill_viridis_d(guide = "none") +
-  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
-  theme_modern(axis.title.space = 15) +
+  mutate(Ethnicity = case_when(
+    Ethnicity == "central Asia" ~ "Central Asian",
+    Ethnicity == "American of African descent, Native American and European" ~ "Mixed",
+    Ethnicity == "southern european" ~ "White",
+    Ethnicity == "persian" ~ "Middle Eastern/North African",
+    Ethnicity %in% c("Berber","Native American","Turkish","turkish") ~ "Other",
+    TRUE ~ Ethnicity, 
+    )) |>
+  filter(!is.na(Ethnicity)) |> 
+  ggplot(aes(x = "", fill = Ethnicity)) +
+  geom_bar() +
+  coord_polar("y") +
+  theme_minimal() +
   theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(0.6), angle = 45, hjust = 1),
-    axis.title.x = element_blank())
+    axis.text.x = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.title.y = element_blank()
+  )
 
@@
 ```
-
 :::
@@
 ```{r p_summary}
+
 p_map

### 2024-12-02 study1/analysis/0_preprocessing.R

@@ -2,8 +2,8 @@ library(jsonlite)
 library(progress)
 
 # path for data
-# path <- "C:/Users/asf25/Box/InteroceptionScale/"
-path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+path <- "C:/Users/asf25/Box/InteroceptionScale/"
+#path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
 
 
@@ -44,8 +44,12 @@ for (file in files) {
 
   # Demographics
   demog <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
+  
+  category_map_edu <- c("Doctorate", "Master", "Bachelor", "High school", "Elementary school")
 
-  demog$Education <- ifelse(demog$Education == "other", demog$`Education-Comment`, demog$Education)
+  demog$Education <- ifelse(demog$Education == "other", 
+                            ifelse(demog$`Education-Comment` %in% category_map_edu, category_map[demog$`Education-Comment`], "Other"),
+                            demog$Education)
   demog$`Education-Comment` <- NULL
   demog$Discipline <- ifelse(demog$Discipline == "other", demog$`Discipline-Comment`, demog$Discipline)
   demog$`Discipline-Comment` <- NULL

### 2024-12-02 study1/analysis/0_preprocessing.R
add preprocessing TODO
@AnafNeves @EmmaLBenn @maisiebennett

@@ -2,8 +2,8 @@ library(jsonlite)
 library(progress)
 
 # path for data
-path <- "C:/Users/asf25/Box/InteroceptionScale/"
-#path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+# path <- "C:/Users/asf25/Box/InteroceptionScale/"
+path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
 
 
@@ -44,18 +44,20 @@ for (file in files) {
 
   # Demographics
   demog <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
-  
-  category_map_edu <- c("Doctorate", "Master", "Bachelor", "High school", "Elementary school")
 
-  demog$Education <- ifelse(demog$Education == "other", 
-                            ifelse(demog$`Education-Comment` %in% category_map_edu, category_map[demog$`Education-Comment`], "Other"),
-                            demog$Education)
+  demog$Education <- ifelse(demog$Education == "other", demog$`Education-Comment`, demog$Education)
   demog$`Education-Comment` <- NULL
+  # TODO: manually check (`unique(alldata$Education` and replace with closer)
+  demog$Education <- ifelse(demog$Education %in% c("Less than high school"), "Elementary school", demog$Education)
+
+  # TODO: same with `unique(alldata$Discipline)`, depending on the number either put in Other or make a category
   demog$Discipline <- ifelse(demog$Discipline == "other", demog$`Discipline-Comment`, demog$Discipline)
   demog$`Discipline-Comment` <- NULL
   demog$Discipline <- ifelse(!is.null(demog$Discipline), demog$Discipline, NA)
   demog$Student <- ifelse(!is.null(demog$Student), demog$Student, NA)
   demog$Country <- ifelse(!is.null(demog$Country), demog$Country, NA)
+
+  # TODO: same here
   demog$Ethnicity <- ifelse(!is.null(demog$Ethnicity), demog$Ethnicity, NA)
   demog$Ethnicity <- ifelse(demog$Ethnicity == "other", demog$`Ethnicity-Comment`, demog$Ethnicity)
   demog$`Ethnicity-Comment` <- NULL
@@ -93,7 +95,7 @@ checks$Prolific_ID <- alldata$Prolific_ID
 checks$Experiment_Duration <- alldata$Experiment_Duration
[…]

### 2024-12-02 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

@@
 
+### Experiment Duration
+
+```{r}
+dfchecks$Duration <- df$Experiment_Duration
+dfchecks$Outlier <- ifelse(dfchecks$Total >= 1, 1, 0)
+dfchecks <- filter(dfchecks, Duration < 45)
+
+m <- mgcv::gam(Outlier ~ s(Duration), data = dfchecks, family = "binomial")
+
+estimate_relation(m, length=50) |> 
+  ggplot(aes(x = Duration, y = Predicted)) +
+  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
+  geom_line() +
+  geom_vline(xintercept=5, linetype="dashed", color="red") +
+  theme_minimal() +
+  ggside::geom_xsidedensity(data=mutate(dfchecks, 
+                                        Outlier=ifelse(Outlier==1, "Failed attention check", "Valid")), 
+                            aes(fill=Outlier), alpha=0.3) +
+  ggside::theme_ggside_void() +
+  labs(title = "Experiment Duration",
+       subtitle = "Predicted probability of failing attention checks by duration",
+       x = "Experiment Duration (minutes)",
+       y = "Probability of failing attention checks") 
+```
+
+```{r}
+outliers$duration <- as.character(df[df$Experiment_Duration < 5, "Participant"])
+outliers$duration <- outliers$duration[!outliers$duration %in% outliers$attentionchecks]
+```
+
 ### Multivariate Distance
@@
 dfoutlier <- performance::check_outliers(select(df, contains("_Q")), 
-                                         method=c("lof"),
-                                         threshold=list(lof = 0.0001)) |> 
+                                         method=c("optics"),
+                                         threshold=list(optics=2.5, optics_xi=0.03)) |> 
   as.data.frame() |> 
-  mutate(Participant = fct_reorder(df$Participant, Distance_LOF),
+  mutate(Participant = fct_reorder(df$Participant, Distance_OPTICS),
          Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
-         Outlier = ifelse(Outlier_LOF == 1, "Distance Outlier", "Valid"),
-         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Check", Outlier))
+         Outlier_Duration = ifelse(Participant %in% outliers$duration, 1, 0),
+         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Checks", "Passed"),
+         Outlier = ifelse(Outlier == "Passed" & Outlier_Duration == 1, "Duration", Outlier))
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Outlier_LOF == 1, "Participant"])
-outliers$distance <- outliers$distance[!outliers$distance %in% outliers$attentionchecks]
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12, "Participant"])
+outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
 
-dfoutlier |> 
-  ggplot(aes(x=Participant, y=Distance_LOF)) +
+p1 <- dfoutlier |> 
+  ggplot(aes(x=Participant, y=Distance_OPTICS)) +
   geom_bar(aes(fill=Outlier), stat="identity") +
+  geom_hline(yintercept = 12.5, linetype="dashed", color="red") +
+  labs(fill = "Status") +
   theme_minimal() +
-  theme(axis.text.x = element_blank())
+  theme(axis.text.x = element_blank(),
+        panel.grid.major.x = element_blank())
+
+m <- mgcv::gam(Outlier_AttentionCheck ~ s(Distance_OPTICS), data = dfoutlier, family = "binomial")
+# parameters::parameters(m)
+
+p2 <- estimate_relation(m, length=30) |> 
+  ggplot(aes(x=Distance_OPTICS, y=Predicted)) +
+  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
+  geom_line() +
+  geom_vline(xintercept=12.5, linetype="dashed", color="red") +
+  theme_minimal()
+
+p1 | p2
 ```
+
+**TODO: describe OPTICS**.
 
@@
 
-### Predictors
+```{r}
+#| eval: false
 
-```{r}
-dfoutlier <- full_join(dfoutlier, select(df, Participant, Experiment_Duration), by = join_by(Participant))
-
-parameters::parameters(glm(Outlier_AttentionCheck ~ Distance_LOF, data = dfoutlier, family = "binomial"))
-parameters::parameters(glm(Outlier_AttentionCheck ~ poly(Experiment_Duration, 2), data = dfoutlier, family = "binomial"))
-parameters::parameters(glm(Distance_LOF ~ poly(Experiment_Duration, 2), data = dfoutlier))
-```
-
-```{r}
 r_full <- cor(select(df, contains("_Q")))
-r_cleaned <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$distance)) |> 
+r_cleaned <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$duration, outliers$distance)) |> 
   select(contains("_Q")) |> 
@@
 
-df <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$distance))
+df <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$duration, outliers$distance))
 ```
@@
 ::: panel-tabset
+
 ### Summary
 
--   The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
+The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
 

### 2024-12-04 study1/analysis/1_cleaning.qmd
Done Education, Ethnicity, Disciple ToDos

@@
 p_eth <- df |>
-  mutate(Ethnicity = case_when(
-    Ethnicity == "central Asia" ~ "Central Asian",
-    Ethnicity == "American of African descent, Native American and European" ~ "Mixed",
-    Ethnicity == "southern european" ~ "White",
-    Ethnicity == "persian" ~ "Middle Eastern/North African",
-    Ethnicity %in% c("Berber","Native American","Turkish","turkish") ~ "Other",
-    TRUE ~ Ethnicity, 
-    )) |>
   filter(!is.na(Ethnicity)) |> 

### 2024-12-04 study1/analysis/0_preprocessing.R

@@ -2,9 +2,10 @@ library(jsonlite)
 library(progress)
 
 # path for data
-# path <- "C:/Users/asf25/Box/InteroceptionScale/"
-path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+#path <- "C:/Users/asf25/Box/InteroceptionScale/"
+#path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
+path <- "C:/Users/asf25/OneDrive - University of Sussex/Desktop/data/InteroceptionScale/"
 
 
 # JsPsych experiment ------------------------------------------------------
@@ -44,23 +45,47 @@ for (file in files) {
 
   # Demographics
   demog <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
-
+  
+  #Education
   demog$Education <- ifelse(demog$Education == "other", demog$`Education-Comment`, demog$Education)
   demog$`Education-Comment` <- NULL
-  # TODO: manually check (`unique(alldata$Education` and replace with closer)
   demog$Education <- ifelse(demog$Education %in% c("Less than high school"), "Elementary school", demog$Education)
-
-  # TODO: same with `unique(alldata$Discipline)`, depending on the number either put in Other or make a category
+  demog$Education <- ifelse(demog$Education %in% c("Diploma", "nvq", "Vocational Diploma", "Secondary (technical) school"), "Other", demog$Education)
+  demog$Education <- ifelse(demog$Education %in% c("Level A (Maturity Diploma abroad)", "Vocational School/ High school", "College (NVQ level 3)", "College graduate", "College", "3 years at collage", "College Certicificate 3"), "High school", demog$Education)
+  demog$Education <- ifelse(demog$Education %in% c("2 year", "Associates degree (2 yr academic program)", "Associate's Degree", "Some college", "Associates", 
+                                                   "Some community college", "A.S. Degree", "Associates Degree", "Associate's degree", "Associates degree", 
+                                                   "BTEC HND"), "Associates degree", demog$Education)
+  demog$Education <- ifelse(demog$Education %in% c("Post graduate qualification"), "Master", demog$Education)
+  
+  #Discipline 
[…]

### 2024-12-06 study1/experiment/intero.js
Fixed typo in questionnaire

@@ -142,7 +142,7 @@ const intero_items = {
     Sensitivity_Cardiac_Q6:
         "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
     Sensitivity_Cardiac_Q7:
-        "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
+        "When something important is happening in my life, I can immediately feel changes in my heart rate",
     Sensitivity_Cardiac_A:
         "In general, I am very sensitive and attentive to the questions I am currently answering",
     Sensitivity_Respiratory_Q1:

### 2024-12-06 study2/experiment/demographics.js
Started implementing study 2

@@ -1,0 +1,472 @@
+// Consent Form =================================================================
+// The consent form is dynamically generated based on the URL variables.
+
+const ConsentForm = {
+    type: jsPsychSurvey,
+    survey_json: function () {
+        // Get URL variables
+        let urlvars = jsPsych.data.urlVariables()
+
+        // Logo and title
+        let text =
+            "<img src='https://blogs.brighton.ac.uk/sussexwrites/files/2019/06/University-of-Sussex-logo-transparent.png' width='150px' align='right'/><br><br><br><br><br>" +
+            "<h1>Informed Consent</h1>"
+
+        // this part is about specific messages for participants based on the recruitment platform
+        if (urlvars["exp"] == "surveyswap") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive a <i style='color:purple;'>SurveySwap.iocompletion code</i>  at the end of the experiment.</b></p>"
+        }
+
+        if (jsPsych.data.urlVariables()["exp"] == "prolific") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive information regarding your <i style='color:purple;'>Prolific</i> participation at the end of the experiment.</b></p>"
+        }
+
+        if (jsPsych.data.urlVariables()["exp"] == "sona") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive a <i style='color:purple;'>Sona completion code</i> at the end of the experiment.</b></p>"
+        }
+        // Main Text
+        text +=
+            // Overview
+            "<p align='left'><b>Invitation to Take Part</b><br>" +
+            "Thank you for considering to take part in this study conducted by Dr Dominique Makowski from the University of Sussex and his team (see contact information below).</p>" +
+            // Description
+            "<p align='left'><b>Why have I been invited and what will I do?</b><br>" +
+            "The aim of this study is to validate a new questionnaire measuring Interoception. Interoception refers to the sensing, interpretation and processing of internal bodily signals (e.g., feeling changes in the way one's heart beats). " +
+            "The whole experiment will take you <b style='color:#FF5722;'>~30 min</b> to complete. Please make you sure that you are <b>attentive and in a quiet environment</b>, and that you have time to complete it in one go.</p>" +
+            // Results and personal information
+            "<p align='left'><b>What will happen to the results and my personal information?</b><br>" +
[…]

### 2024-12-11 study1/analysis/1_cleaning.qmd
update
@EmmaLBenn @maisiebennett could you remove the paragraph on mahalanobis distance and try to add a few sentences + ref on what we actually did (OPTICS)

@@
 
+We removed `r length(outliers$duration)` (`r insight::format_percent(length(outliers$duration) / nrow(df))`) participants for having completed the experiment in less than 5 minutes.
+
 ### Multivariate Distance
@@
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12, "Participant"])
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12.5, "Participant"])
 outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
@@
 
-### Ethinicity
+### Ethnicity
 
@@
 ```
+
 :::
@@
 ```{r p_summary}
+#| fig-width: 14
+#| fig-height: 14
 
-p_map
-p_age
-p_edu
+(p_age | p_edu) / p_map
 ```

### 2024-12-11 study1/analysis/0_preprocessing.R

@@ -3,9 +3,9 @@ library(progress)
 
 # path for data
 #path <- "C:/Users/asf25/Box/InteroceptionScale/"
-#path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
-path <- "C:/Users/asf25/OneDrive - University of Sussex/Desktop/data/InteroceptionScale/"
+# path <- "C:/Users/asf25/OneDrive - University of Sussex/Desktop/data/InteroceptionScale/"
 
 
 # JsPsych experiment ------------------------------------------------------
@@ -45,19 +45,19 @@ for (file in files) {
 
   # Demographics
   demog <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
-  
+
   #Education
   demog$Education <- ifelse(demog$Education == "other", demog$`Education-Comment`, demog$Education)
   demog$`Education-Comment` <- NULL
   demog$Education <- ifelse(demog$Education %in% c("Less than high school"), "Elementary school", demog$Education)
   demog$Education <- ifelse(demog$Education %in% c("Diploma", "nvq", "Vocational Diploma", "Secondary (technical) school"), "Other", demog$Education)
   demog$Education <- ifelse(demog$Education %in% c("Level A (Maturity Diploma abroad)", "Vocational School/ High school", "College (NVQ level 3)", "College graduate", "College", "3 years at collage", "College Certicificate 3"), "High school", demog$Education)
-  demog$Education <- ifelse(demog$Education %in% c("2 year", "Associates degree (2 yr academic program)", "Associate's Degree", "Some college", "Associates", 
-                                                   "Some community college", "A.S. Degree", "Associates Degree", "Associate's degree", "Associates degree", 
+  demog$Education <- ifelse(demog$Education %in% c("2 year", "Associates degree (2 yr academic program)", "Associate's Degree", "Some college", "Associates",
+                                                   "Some community college", "A.S. Degree", "Associates Degree", "Associate's degree", "Associates degree",
                                                    "BTEC HND"), "Associates degree", demog$Education)
   demog$Education <- ifelse(demog$Education %in% c("Post graduate qualification"), "Master", demog$Education)
-  
-  #Discipline 
+
+  #Discipline
[…]

### 2024-12-11 study1/analysis/2_analysis.qmd
Cleaning script updates
analysis

@@
 library(ggraph)
+
+set.seed(42)
 ```
@@
 
-df <- read.csv("../data/rawdata_participants.csv")
+df <- read.csv("../data/data_participants.csv")
 
@@
 ```{r}
+#| eval: true
+
 bootstrap_similarity <- function(df) {
@@
 rez <- bootstrap_similarity(df)
+```
+
+```{r}
+#| fig-width: 10
+#| fig-height: 10
 
@@
   pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
-  filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |>
+  filter(name %in% c("PSI", "RVadj", "SMI")) |>
   mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
@@
 #| fig-height: 10
+#| eval: true
 
@@
   theme_minimal() +
-  scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), labels = c("By modality", "By facet"))
+  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))
 
@@
     geom_tile() +
-    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+    # scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, values=c(-1, 0, 1)) +
+    scale_fill_gradientn(
+      colors=c("blue", "white", "#FFEE58", "#FFC107", "#FF9800", "#FF5722", 
+               "#F44336", "#E91E63", "#9C27B0", "#8231B4", "#673AB7", "white"), 
+      values=c(-1, seq(0, 1, 0.1))) +
     theme_minimal() +
@@
 
-p1 / (p2 | p_sim | p3) + patchwork::plot_layout(heights=c(3, 1)) + patchwork::plot_annotation(title="Effect of Item-presentation Grouping", theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
+p1 / (p2 | p_sim | p3) + 
+  patchwork::plot_layout(heights=c(3, 1)) + 
+  patchwork::plot_annotation(
+    title="Effect of Item-presentation Grouping", 
+    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
 ```
@@
 
-uva <- EGAnet::UVA(items, cut.off = 0.2)
+uva <- EGAnet::UVA(items, cut.off = 0.25, reduce.method="remove", verbose=FALSE)
 
-correlation::correlation(items[unlist(uva$redundant)],
-                         items[names(uva$redundant)]) |>
-  mutate(Parameter1 = fct_relevel(Parameter1, unlist(uva$redundant)),
-         Parameter2 = fct_relevel(Parameter2, names(uva$redundant))) |>
+toremove1 <- unique(uva$keep_remove$remove)
+keep <- uva$keep_remove$keep[!uva$keep_remove$keep %in% toremove1]
+
+sorted <- correlation::cor_sort(cor(items[toremove1],items[keep]))
+
+correlation::correlation(items[toremove1], items[keep]) |>
+  mutate(Parameter1 = fct_relevel(Parameter1, rownames(sorted)),
+         Parameter2 = fct_relevel(Parameter2, colnames(sorted))) |>
   ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
@@
   geom_text(aes(label=insight::format_value(r)), color="white") +
-  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, guide="none") +
   theme_minimal() +
@@
   labs(x="Removed Items", y="Kept Items", fill="Correlation")
-
-toremove1 <- uva$keep_remove$remove
 ```
@@
   model = "glasso",  # BGGM
-  algorithm = "louvain",  # walktrap
+  algorithm = "leiden",
   type="resampling",
@@
 ```{r}
-#| fig-width: 10
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 14
+#| fig-keep: "first"
 
@@
 
+# Remove items
 toremove2 <- filter(itemstability_table, Max < 0.8)$Item
+toremove2 <- itemstability_table |> 
+  filter(!Item %in% toremove2) |>
+  mutate(Item, n=n(), .by="Cluster", .keep="used") |> 
+  filter(n < 3) |>  # Remove small clusters
+  pull(Item) |> 
+  c(toremove2)
+```
 
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| fig-keep: "first"
+
+# plot(itemstability)
+```
+
+```{r}
 itemstability_table |>
@@
   model = "glasso",  # BGGM
-  algorithm = "louvain",  # walktrap
+  algorithm = "leiden",  # walktrap
   type="resampling",
@@
 plot(itemStability(ega2, IS.plot=FALSE))
+
+# itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
+# toremove2 <- filter(itemstability_table, Max < 0.7)$Item
 ```
@@
 ```{r}
+#| message: false
+
 lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)
@@
 ```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| fig-keep: "first"
+
 load("models/ega3.RData")
 
-# itemStability(ega2)
+plot(itemStability(ega3))
+```
+
+```{r}
+#| message: false
 
@@
 higher$Label <- paste("TODO", 1:nrow(higher))
-lower <- mutate(lower, Label = labels[Item], Item = 1:n())
+lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())
 
-rbind(higher, lower) |>
+rbind(higher, select(lower, -ID)) |>
   datawizard::data_relocate("Label", after = "Item") |>
   select(-Cluster, -Max) |>
+  # datawizard::data_rename(c(XC1 = "C01", XC2 = "C02")) |> 
   gt::gt() |>
   gt::tab_row_group(
-    label = "Item",
+    label = "Items",
     rows = 1:(nrow(lower) + nrow(higher))
@@
   gt::tab_row_group(
-    label = "Higher Order",
+    label = "Metaclusters",
     rows = 1:nrow(higher)
@@
     locations = list(
-      gt::cells_row_groups(groups = "Item"),
-      gt::cells_row_groups(groups = "Higher Order")
+      gt::cells_row_groups(groups = "Items"),
+      gt::cells_row_groups(groups = "Metaclusters")
+    )
+  ) |>
+  # Metacluster 1
+  gt::tab_style(
+    style = gt::cell_fill(color = "#B39DDB"),
+    locations = list(
+      gt::cells_column_labels(columns = 3),
+      gt::cells_body(columns="Item", rows=c(4:6))
     )
@@
   gt::tab_style(
-    style = gt::cell_fill(color = "#FFCDD2"),
+    style = gt::cell_fill(color = "#9FA8DA"),
     locations = list(
-      gt::cells_column_labels(columns = 3),
-      gt::cells_body(columns="Item", rows=c(1, 6:8))
+      gt::cells_column_labels(columns = 4),
+      gt::cells_body(columns="Item", rows=c(7:9))
     )
@@
   gt::tab_style(
-    style = gt::cell_fill(color = "#FFCCBC"),
+    style = gt::cell_fill(color = "#90CAF9"),
     locations = list(
-      gt::cells_column_labels(columns = 4),
-      gt::cells_body(columns="Item", rows=c(9:11))
+      gt::cells_column_labels(columns = 5),
+      gt::cells_body(columns="Item", rows=c(1, 10:12))
     )
@@
   gt::tab_style(
-    style = gt::cell_fill(color = "#FFE0B2"),
+    style = gt::cell_fill(color = "#81D4FA"),
     locations = list(
-      gt::cells_column_labels(columns = 5),
-      gt::cells_body(columns="Item", rows=c(12:14))
+      gt::cells_column_labels(columns = 6),
+      gt::cells_body(columns="Item", rows=c(13:15))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#80DEEA"),
+    locations = list(
+      gt::cells_column_labels(columns = 7),
+      gt::cells_body(columns="Item", rows=c(16:18))
+    )
+  ) |>
+  # Metacluster 2
+  gt::tab_style(
+    style = gt::cell_fill(color = "#F3F29D"),
+    locations = list(
+      gt::cells_column_labels(columns = 8),
+      gt::cells_body(columns="Item", rows=c(19:21))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#E6EE9C"),
+    locations = list(
+      gt::cells_column_labels(columns = 9),
+      gt::cells_body(columns="Item", rows=c(22:24))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#D6E8A1"),
+    locations = list(
+      gt::cells_column_labels(columns = 10),
+      gt::cells_body(columns="Item", rows=c(25:27))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#C5E1A5"),
+    locations = list(
+      gt::cells_column_labels(columns = 11),
+      gt::cells_body(columns="Item", rows=c(2, 28:30))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#B5DCA6"),
+    locations = list(
+      gt::cells_column_labels(columns = 12),
+      gt::cells_body(columns="Item", rows=c(31:33))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#A5D6A7"),
+    locations = list(
+      gt::cells_column_labels(columns = 13),
+      gt::cells_body(columns="Item", rows=c(34:36))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#93D1B6"),
+    locations = list(
+      gt::cells_column_labels(columns = 14),
+      gt::cells_body(columns="Item", rows=c(37:39))
+    )
+  ) |>
+  # Metacluster 3
+  gt::tab_style(
+    style = gt::cell_fill(color = "#CE93D8"),
+    locations = list(
+      gt::cells_column_labels(columns = 15),
+      gt::cells_body(columns="Item", rows=c(40:42))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#F48FB1"),
+    locations = list(
+      gt::cells_column_labels(columns = 16),
+      gt::cells_body(columns="Item", rows=c(43:45))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#EF9A9A"),
+    locations = list(
+      gt::cells_column_labels(columns = 17),
+      gt::cells_body(columns="Item", rows=c(3, 46:48))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFAB91"),
+    locations = list(
+      gt::cells_column_labels(columns = 18),
+      gt::cells_body(columns="Item", rows=c(49:51))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFCC80"),
+    locations = list(
+      gt::cells_column_labels(columns = 19),
+      gt::cells_body(columns="Item", rows=c(52:54))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFE082"),
+    locations = list(
+      gt::cells_column_labels(columns = 20),
+      gt::cells_body(columns="Item", rows=c(55:57))
     )
@@
     subtitle = "Node centrality"
-  )
+  ) |> 
+  gt::opt_vertical_padding(scale = 0.7) |>
+  gt::opt_horizontal_padding(scale = 0.5) |>
+  # gt::tab_options(table.width = gt::pct(100)) |> 
+  gt::cols_width(Label ~ gt::pct(30)) |>
+  gt::gtsave("table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
 ```
+
+<object type="text/html" data="table1.html" width="120%" height="1000"></object>
 
@@
 
+### Graph
+
 ```{r}
+#| fig-width: 9
+#| fig-height: 8
+#| warning: false
+
 graph <- convert2tidygraph(ega3)
 
-tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
-  ggraph::ggraph(layout = 'mds') +
-  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.2, strength=0, color="grey") +
-  ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
-  ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
-  ggraph::geom_node_text(aes(label=name), repel=TRUE) +
+replace_lowernames <- function(names, lower) {
+  rownames(lower) <- lower$ID
+  sprintf("%02d", as.numeric(lower[names, "Item"]))
+}
+replace_highernames <- function(names) {
+  x <- as.numeric(str_remove(names, "L"))  
+  paste0("C", sprintf("%02d", x))
+}
+
+# Arrange lower nodes in circle
+lower_nodes <- graph$nodes |> 
+  filter(level == "Lower") |> 
+  mutate(name = fct_relevel(name, as.character(lower$ID)),
+         ID = name) |> 
+  arrange(name)  
+lower_edges <- graph$edges |> 
+  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
+lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
+  ggraph::create_layout(layout = 'circle')
+rownames(lower_layout) <- lower_nodes$name
+
+# Arrange higher nodes in circle
+higher_nodes <- graph$nodes |> 
+  filter(level == "Higher") |> 
+  mutate(ID = name,
+         name = replace_highernames(name),
+         name = fct_relevel(name, names(select(higher, -Item, -Cluster,-Max,-Label)))) |>
+  arrange(name)
+higher_edges <- graph$edges |> 
+  filter(from %in% higher_nodes$name & to %in% higher_nodes$name)
+higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
+  ggraph::create_layout(layout = 'circle')
+rownames(higher_layout) <- higher_nodes$ID
+
+# Put circles together
+layout <- tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |> 
+  ggraph::create_layout(layout = 'linear', circular = TRUE)
+layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", "name"], "x"]
+layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", "name"], "y"]
+layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", "name"], "x"] * 0.5
+layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", "name"], "y"] * 0.5
+layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", "name"], lower)
+layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", "name"])
+
+# layout$dimmension_label <- layout$dimension
+# layout[layout$level == "Higher", "dimmension_label"] <- NA
+
+# layout[layout$level == "Higher", "dimension"] <- layout[layout$level == "Higher", "dimension"]
+
+ggraph(layout) +
+  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
+  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
+  geom_node_point(aes(color=dimension, shape=level), size=12) +
+  geom_node_text(aes(label=name), fontface="bold") +
+  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
   scale_edge_alpha(range = c(0, 0.9), guide="none") +
   scale_edge_width(range = c(0.2, 3), guide="none") +
-  scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
-  theme_void()
+  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
+                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
+  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
+  scale_color_manual(values=c(
+    "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
+    "L1"="#CE93D8", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
+    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
+    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
+                     breaks=c("H1", "H2", "H3")) +
+  theme_void() +
+  labs(color="Metaclusters")
 ```
 
-<!-- ::: {.panel-tabset} -->
+### Model Comparison
 
-<!-- ### Full Sample -->
+```{r}
+#| eval: false
 
-<!-- ### By Dimension / Domains / Context -->
+# EGAnet::EGM(items[, 1:60])
+EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
+rez <- EGAnet::network.compare(byfacet, bymodality, model = "glasso", seed=3)
 
-<!-- ```{r} -->
-<!-- bydimension <- items[df$Condition=="Dimensions",] -->
-
-<!-- ega_bydimension <- EGA(bydimension[, 1:20], plot.EGA = FALSE) -->
-
-<!-- plot(ega_bydimension) -->
-<!-- ``` -->
-
-<!-- ### By Modalities -->
-
-<!-- ```{r} -->
-<!-- bymodality <- items[df$Condition=="Domains",] -->
-
-<!-- ega_bymodality <- EGA(bymodality[, 1:20], plot.EGA = FALSE) -->
-
-<!-- plot(ega_bymodality) -->
-<!-- ``` -->
-
-<!-- ::: -->
-
-<!-- ## Model Comparison -->
-
-<!-- ```{r} -->
-<!-- # EGAnet::EGM(items[, 1:60]) -->
-
-<!-- # EGAnet::EGM.compare(items[, 1:20]) -->
-
-<!-- # rez <- EGAnet::network.compare(byfacet, bymodality, seed=3) -->
-<!-- # plot(rez) -->
-<!-- ``` -->
+plot(rez)
+```
 
@@
 ```{r}
+#| message: false
+
 # Modelbased scores

### 2024-12-11 study1/analysis/2_analysis.qmd
final

@@
         Iteration = i) |>
-      mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
+      mutate(d_PSI = diff(PSI), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
       rbind(rez)
@@
 ```
+
+### Item Table
 

### 2024-12-11 study1/analysis/2_analysis.qmd
minor fig

@@
     "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
-    "L1"="#CE93D8", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
+    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
     "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",

### 2024-12-13 study2/experiment/demographics.js
Study 2 updates

@@ -77,31 +77,31 @@ const ConsentForm = {
     },
 }
 
-var demographics_browser_info = {
-    type: jsPsychBrowserCheck,
-    data: {
-        screen: "browser_info",
-        date: new Date().toLocaleDateString("en-GB"),
-        time: new Date().toLocaleTimeString("en-GB"),
-    },
-    on_finish: function (data) {
-        data["participantID"] = participantID
-        data["condition"] = intero_condition
+// var demographics_browser_info = {
+//     type: jsPsychBrowserCheck,
+//     data: {
+//         screen: "browser_info",
+//         date: new Date().toLocaleDateString("en-GB"),
+//         time: new Date().toLocaleTimeString("en-GB"),
+//     },
+//     on_finish: function (data) {
+//         data["participantID"] = participantID
+//         data["condition"] = intero_condition
 
-        // Rename
-        dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
-        data["screen_height"] = dat["height"]
-        data["screen_width"] = dat["width"]
+//         // Rename
+//         dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
+//         data["screen_height"] = dat["height"]
+//         data["screen_width"] = dat["width"]
 
-        // Add URL variables - ?sona_id=x&exp=1
-        let urlvars = jsPsych.data.urlVariables()
-        data["researcher"] = urlvars["exp"]
-        data["sona_id"] = urlvars["sona_id"]
-        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
-        data["study_id"] = urlvars["STUDY_ID"] // Prolific
-        data["session_id"] = urlvars["SESSION_ID"] // Prolific
-    },
-}
+//         // Add URL variables - ?sona_id=x&exp=1
+//         let urlvars = jsPsych.data.urlVariables()
+//         data["researcher"] = urlvars["exp"]
+//         data["sona_id"] = urlvars["sona_id"]
+//         data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
+//         data["study_id"] = urlvars["STUDY_ID"] // Prolific
+//         data["session_id"] = urlvars["SESSION_ID"] // Prolific
+//     },
+// }
 
 var demographic_questions = {
     type: jsPsychSurvey,
@@ -274,7 +274,6 @@ var wearables_questions = {
                             "Calorie intake",
                             "Sleep quality",
                             "Respiratory rate",
-                            "I do not own a device that can monitor this",
[…]

### 2024-12-13 study2/experiment/intero.js

@@ -1,0 +1,39 @@
+// Instructions ================================================
+const intero_instructions = {
+    type: jsPsychSurvey,
+    survey_json: {
+        showQuestionNumbers: false,
+        completeText: "Let's start",
+        pages: [
+            {
+                elements: [
+                    {
+                        type: "html",
+                        name: "ConsentForm",
+                        html:
+                            "<div style='display: flex;'>" +
+                            "<div style='width: 60%; margin-right: 20px;'>" +
+                            "<h1>About you and your body...</h1>" +
+                            "<h2>Instructions</h2>" +
+                            "<p>In the following questionnaires, you will be asked various questions about the way you feel and you think about your body. " +
+                            "There are no right or wrong answers.</p>" +
+                            "<p>Please note that <b style='color:#FF5722;'>various checks will be performed to ensure the validity of the data</b>. We reserve the right to withhold credit awards or reimbursement should we detect non-valid responses (e.g., random patterns of answers, instructions not read, ...).</li>" +
+                            "<p> We are aware that answering these questionnaires <b>might feel long and repetitive</b>, but having similar questions is necessary to ensure the validity of the results (we expect similar questions to be related). " +
+                            "Please read carefully each item and consider it <i>on its own</i> (<b>without trying to relate it or remember your answers to previous items</b>), and don't hesitate to take breaks if you need.</p>" +
+                            "<p style='color:green;'>At the end, you will be shown a <b>graph</b> summarizing your answers.<p>" +
+                            "</div>" +
+                            "<div style='width: 40%;'>" +
+                            "<img src='https://www.newthinking.com/wp-content/uploads/2023/06/2-ways-to-improve-mind-body-scaled.jpg' alt='Mind and Body' style='width: 100%;'>" +
+                            "</div>" +
+                            "</div>",
+                    },
+                ],
+            },
+        ],
+    },
+}
+
+// MAIA Items ================================================
+const MAIA_items = {
+    
+}

### 2024-12-13 study2/experiment/demographics.js
Updates on study 2

@@ -103,6 +103,9 @@ const ConsentForm = {
 //     },
 // }
 
+
+// Demographic questions
+
 var demographic_questions = {
     type: jsPsychSurvey,
     survey_json: {
@@ -246,9 +249,10 @@ var demographic_questions = {
     },
 }
 
+
 // Wearable devices survey
 
-var wearables_questions = {
+var demographics_wearables = {
     type: jsPsychSurvey,
     survey_json: {
         title: "Wearable Device Usage",
@@ -321,6 +325,309 @@ var wearables_questions = {
     },
 }
 
+
+// Single-Item Life Satisfaction Scale
+
+var demographics_sils = {
+    type: jsPsychSurvey,
+    survey_json: {
+        title: "Single-Item Life Satisfaction Scale",
+        completeText: "Continue",
+        pageNextText: "Next",
+        pagePrevText: "Previous",
+        goNextPageAutomatic: false,
+        showQuestionNumbers: false,
+        showProgressBar: "aboveHeader",
+        pages: [
+            {
+                elements: [
+                    {
+                        title: "Thinking about your own life and personal circumstances, how satisfied are you with your life as a whole?",
+                        name: "SILS",
+                        type: "rating",
+                        rateCount: 11,
+                        rateMin: 0,
+                        rateMax: 10,
+                        minRateDescription: "No satisfaction at all",
+                        maxRateDescription: "Completely satisfied",
+                    },
+                ],
+            },
+        ],
+    },
+
+    data: {
+        screen: "demographics_sils",
+    },
+}
+
+
+// TAS-20
+
+var TAS_items = [
+    "I am often confused about what emotion I am feeling",
+    "I have physical sensations that even doctors don't understand",
+    "When I am upset, I don't know if I am sad, frightened, or angry",
+    "I am often puzzled by sensations in my body",
+    "I have feelings that I can't quite identify",
+    "I don't know what's going on inside me",
+    "I often don't know why I am angry",
+    "It is difficult for me to find the right words for my feelings",
+    "I am able to describe my feelings easily",
+    "I find it hard to describe how I feel about people",
+    "People tell me to describe my feelings more",
+    "It is difficult for me to reveal my innermost feelings, even to close friends",
+    "I prefer to analyze problems rather than just describe them",
+    "I prefer to just let things happen rather than to understand why they turned out that way",
+    "Being in touch with emotions is essential",
+    "I prefer talking to people about their daily activities rather than their feelings",
+    "I prefer to watch 'light' entertainment shows rather than psychological dramas",
[…]

### 2024-12-13 study2/experiment/intero.js
Adding questionnaires to study 2

@@ -33,7 +33,450 @@ const intero_instructions = {
     },
 }
 
-// MAIA Items ================================================
-const MAIA_items = {
-    
+// MAIA-2 questionnaire
+var MAIA_items = [
+    "When I am tense I notice where the tension is located in my body",
+    "I notice when I am uncomfortable in my body",
+    "I notice where in my body I am comfortable",
+    "I notice changes in my breathing, such as whether it slows down or speeds up",
+    "I ignore physical tension or discomfort until they become more severe",
+    "I distract myself from sensations of discomfort",
+    "When I feel pain or discomfort, I try to power through it",
+    "I try to ignore pain",
+    "I push feelings of discomfort away by focusing on something",
+    "When I feel unpleasant body sensations, I occupy myself with something else so I do not have to feel them",
+    "When I feel physical pain, I become upset",
+    "I start to worry that something is wrong if I feel any discomfort",
+    "I can notice an unpleasant body sensation without worrying about it",
+    "I can stay calm and not worry when I have feelings of discomfort or pain",
+    "When I am in discomfort or pain I cannot get it out of my mind",
+    "I can pay attention to my breath without being distracted by things happening around me",
+    "I can maintain awareness of my inner bodily sensations even when there is a lot going on around me",
+    "When I am in conversation with someone, I can pay attention to my posture",
+    "I can return awareness to my body if I am distracted",
+    "I can refocus my attention from thinking to sensing my body",
+    "I can maintain awareness of my whole body even when a part of me is in pain or discomfort",
+    "I am able to consciously focus on my body as a whole",
+    "I notice how my body changes when I am angry",
+    "When something is wrong in my life I can feel it in my body",
+    "I notice that my body feels different after a peaceful experience",
+    "I notice that my breathing becomes free and easy when I feel comfortable",
+    "I notice how my body changes when I feel happy / joyful",
+    "When I feel overwhelmed I can find a calm place inside",
+    "When I bring awareness to my body I feel a sense of calm",
+    "I can use my breath to reduce tension",
+    "When I am caught up in thoughts, I can calm my mind by focusing on my body/breathing",
[…]

### 2024-12-13 study2/experiment/intero.js
intero.js not finished
do not touch it

@@ -33,8 +33,9 @@ const intero_instructions = {
     },
 }
 
+// Questionnaires
 // MAIA-2 questionnaire
-var MAIA_items = [
+const MAIA_items = [
     "When I am tense I notice where the tension is located in my body",
     "I notice when I am uncomfortable in my body",
     "I notice where in my body I am comfortable",
@@ -73,7 +74,8 @@ var MAIA_items = [
     "I feel my body is a safe place",
     "I trust my body sensations",
 ]
-var MAIA_dimensions = [
+
+const MAIA_dimensions = [
     "Noticing_1",
     "Noticing_2",
     "Noticing_3",
@@ -113,8 +115,63 @@ var MAIA_dimensions = [
     "Trusting_3",
 ]
 
+
+function maia_questions(
+    required = true,
+    ticks = ["Never", "Always"],
+    items = MAIA_items,
+    dimensions = MAIA_dimensions
+) {
+    // Make questions
+    var questions = []
+    for (const [index, element] of items.entries()) {
+        q = {
+            title: element,
+            name: dimensions[index],
+            type: "rating",
+            displayMode: "buttons",
+            // scaleColorMode: "colored",
+            isRequired: required,
+            minRateDescription: ticks[0],
+            maxRateDescription: ticks[1],
+            rateValues: [0, 1, 2, 3, 4, 5], // 6-point likert-scale 
+        }
+        questions.push(q)
+    }
+
+    // Randomize order
+    for (let i = questions.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+            ;[questions[i], questions[j]] = [questions[j], questions[i]]
+    }
+
+    return [
+        { elements: questions },
+    ]
+}
+
+const maia_questionnaire = {
+    type: jsPsychSurvey,
+    survey_json: function () {
+        return {
+            title: "About your body sensations...",
+            description:
+                "Please indicate how often each statement applies to you generally in daily life.",
+            showQuestionNumbers: false,
+            goNextPageAutomatic: true,
+            pageNextText: "Next",
+            pagePrevText: "Previous",
+            showProgressBar: "aboveHeader",
+            pages: maia_questions(),
+        }
+    },
+    data: {
+        screen: "MAIA_questionnaire",
+    },
+}
+
 // MINT Items ================================================
-var MINT_items = [
+const MINT_items = [
     "Sometimes my breathing becomes erratic or shallow and I often don't know why",
[…]

### 2024-12-14 study2/experiment_ana/demographics.js
added a new folder with my attempt at it
@EmmaLBenn @maisiebennett  create a script with the rest of the questionnaires (do not add them in demographics)  in the same format as the intero_questionnaires one please

@@ -1,0 +1,470 @@
+// Consent Form =================================================================
+// The consent form is dynamically generated based on the URL variables.
+
+const ConsentForm = {
+    type: jsPsychSurvey,
+    survey_json: function () {
+        // Get URL variables
+        let urlvars = jsPsych.data.urlVariables()
+
+        // Logo and title
+        let text =
+            "<img src='https://blogs.brighton.ac.uk/sussexwrites/files/2019/06/University-of-Sussex-logo-transparent.png' width='150px' align='right'/><br><br><br><br><br>" +
+            "<h1>Informed Consent</h1>"
+
+        // this part is about specific messages for participants based on the recruitment platform
+        if (urlvars["exp"] == "surveyswap") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive a <i style='color:purple;'>SurveySwap.iocompletion code</i>  at the end of the experiment.</b></p>"
+        }
+
+        if (jsPsych.data.urlVariables()["exp"] == "prolific") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive information regarding your <i style='color:purple;'>Prolific</i> participation at the end of the experiment.</b></p>"
+        }
+
+        if (jsPsych.data.urlVariables()["exp"] == "sona") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive a <i style='color:purple;'>Sona completion code</i> at the end of the experiment.</b></p>"
+        }
+        // Main Text
+        text +=
+            // Overview
+            "<p align='left'><b>Invitation to Take Part</b><br>" +
+            "Thank you for considering to take part in this study conducted by Dr Dominique Makowski from the University of Sussex and his team (see contact information below).</p>" +
+            // Description
+            "<p align='left'><b>Why have I been invited and what will I do?</b><br>" +
+            "The aim of this study is to validate a new questionnaire measuring Interoception. Interoception refers to the sensing, interpretation and processing of internal bodily signals (e.g., feeling changes in the way one's heart beats). " +
+            "The whole experiment will take you <b style='color:#FF5722;'>~30 min</b> to complete. Please make you sure that you are <b>attentive and in a quiet environment</b>, and that you have time to complete it in one go.</p>" +
+            // Results and personal information
+            "<p align='left'><b>What will happen to the results and my personal information?</b><br>" +
[…]

### 2024-12-14 study2/experiment_ana/intero_questionnaires.js

@@ -1,5 +1,5 @@
 // Instructions ================================================
-const intero_instructions = {
+const instructions = {
     type: jsPsychSurvey,
     survey_json: {
         showQuestionNumbers: false,
@@ -13,14 +13,14 @@ const intero_instructions = {
                         html:
                             "<div style='display: flex;'>" +
                             "<div style='width: 60%; margin-right: 20px;'>" +
-                            "<h1>About you and your body...</h1>" +
+                            //"<h1>About you and your body...</h1>" +
                             "<h2>Instructions</h2>" +
-                            "<p>In the following questionnaires, you will be asked various questions about the way you feel and you think about your body. " +
+                            //REPHRASE
+                            "<p>In the stage, you will be asked various questions about the way you feel and think about your body. " +
                             "There are no right or wrong answers.</p>" +
                             "<p>Please note that <b style='color:#FF5722;'>various checks will be performed to ensure the validity of the data</b>. We reserve the right to withhold credit awards or reimbursement should we detect non-valid responses (e.g., random patterns of answers, instructions not read, ...).</li>" +
                             "<p> We are aware that answering these questionnaires <b>might feel long and repetitive</b>, but having similar questions is necessary to ensure the validity of the results (we expect similar questions to be related). " +
-                            "Please read carefully each item and consider it <i>on its own</i> (<b>without trying to relate it or remember your answers to previous items</b>), and don't hesitate to take breaks if you need.</p>" +
-                            "<p style='color:green;'>At the end, you will be shown a <b>graph</b> summarizing your answers.<p>" +
+                            // "<p style='color:green;'>At the end, you will be shown a <b>graph</b> summarizing your answers.<p>" +
                             "</div>" +
                             "<div style='width: 40%;'>" +
                             "<img src='https://www.newthinking.com/wp-content/uploads/2023/06/2-ways-to-improve-mind-body-scaled.jpg' alt='Mind and Body' style='width: 100%;'>" +
[…]

### 2024-12-14 study2/intero_questionnaires_dimensions.js

@@ -1,0 +1,156 @@
+// Interoception questionnaires dimensions
+
+const MAIA_dimensions = [
+    "Noticing_1",
+    "Noticing_2",
+    "Noticing_3",
+    "Noticing_4",
+    "NotDistracting_1_R",
+    "NotDistracting_2_R",
+    "NotDistracting_3_R",
+    "NotDistracting_4_R",
+    "NotDistracting_5_R",
+    "NotDistracting_6_R",
+    "NotWorrying_1_R",
+    "NotWorrying_2_R",
+    "NotWorrying_3",
+    "NotWorrying_4",
+    "NotWorrying_5_R",
+    "AttentionRegulation_1",
+    "AttentionRegulation_2",
+    "AttentionRegulation_3",
+    "AttentionRegulation_4",
+    "AttentionRegulation_5",
+    "AttentionRegulation_6",
+    "AttentionRegulation_7",
+    "EmotionalAwareness_1",
+    "EmotionalAwareness_2",
+    "EmotionalAwareness_3",
+    "EmotionalAwareness_4",
+    "EmotionalAwareness_5",
+    "SelfRegulation_1",
+    "SelfRegulation_2",
+    "SelfRegulation_3",
+    "SelfRegulation_4",
+    "BodyListening_1",
+    "BodyListening_2",
+    "BodyListening_3",
+    "Trusting_1",
+    "Trusting_2",
+    "Trusting_3",
+]
+
+const MINT_dimensions = [
+    "InteroceptiveFailures_1",
+    "InteroceptiveFailures",
+    "InteroceptiveFailures_3",
+    "InteroceptiveFailures_4",
+    "InteroceptiveFailures_5",
+    "InteroceptiveFailures_6",
+    "InteroceptiveFailures_7",
+    "InteroceptiveFailures_8",
+    "InteroceptiveFailures_9",
+    "InteroceptiveFailures_10",
+    "InteroceptiveFailures_11",
+    "InteroceptiveFailures_12",
+    "InteroceptiveFailures_13",
+    "InteroceptiveFailures_14",
+    "InteroceptiveFailures_15",
+    "InteroceptiveSensitivityPleasure_1",
+    "InteroceptiveSensitivityPleasure_2",
+    "InteroceptiveSensitivityPleasure_3",
+    "InteroceptiveSensitivityPleasure_4",
[…]

### 2024-12-16 study2/experiment_ana/convergence_questionnaires.js
creating script with convergent questionnaires called (convergence_questionnaires)

@@ -1,0 +1,300 @@
+
+// Single-Item Life Satisfaction Scale
+
+var demographics_sils = {
+    type: jsPsychSurvey,
+    survey_json: {
+        title: "Single-Item Life Satisfaction Scale",
+        completeText: "Continue",
+        pageNextText: "Next",
+        pagePrevText: "Previous",
+        goNextPageAutomatic: false,
+        showQuestionNumbers: false,
+        showProgressBar: "aboveHeader",
+        pages: [
+            {
+                elements: [
+                    {
+                        title: "Thinking about your own life and personal circumstances, how satisfied are you with your life as a whole?",
+                        name: "SILS",
+                        type: "rating",
+                        rateCount: 11,
+                        rateMin: 0,
+                        rateMax: 10,
+                        minRateDescription: "No satisfaction at all",
+                        maxRateDescription: "Completely satisfied",
+                    },
+                ],
+            },
+        ],
+    },
+
+    data: {
+        screen: "demographics_sils",
+    },
+}
+
+
+// TAS-20
+
+var TAS_items = [
+    "I am often confused about what emotion I am feeling",
+    "I have physical sensations that even doctors don't understand",
+    "When I am upset, I don't know if I am sad, frightened, or angry",
+    "I am often puzzled by sensations in my body",
+    "I have feelings that I can't quite identify",
+    "I don't know what's going on inside me",
+    "I often don't know why I am angry",
+    "It is difficult for me to find the right words for my feelings",
+    "I am able to describe my feelings easily",
+    "I find it hard to describe how I feel about people",
+    "People tell me to describe my feelings more",
+    "It is difficult for me to reveal my innermost feelings, even to close friends",
+    "I prefer to analyze problems rather than just describe them",
+    "I prefer to just let things happen rather than to understand why they turned out that way",
+    "Being in touch with emotions is essential",
+    "I prefer talking to people about their daily activities rather than their feelings",
+    "I prefer to watch 'light' entertainment shows rather than psychological dramas",
+    "I can feel close to someone, even in moments of silence",
+    "I find examination of my feelings useful in solving personal problems",
+    "Looking for hidden meanings in movies or plays distracts from their enjoyment",
+]
+
+var TAS_dimensions = [
+    "IdentifyingFeelings_1",
+    "IdentifyingFeelings_2",
+    "IdentifyingFeelings_3",
[…]

### 2024-12-17 study2/experiment_ana/convergence_questionnaires.js
Updates to study 2

@@ -1,43 +1,6 @@
+// TAS-20 questionnaire
 
-// Single-Item Life Satisfaction Scale
-
-var demographics_sils = {
-    type: jsPsychSurvey,
-    survey_json: {
-        title: "Single-Item Life Satisfaction Scale",
-        completeText: "Continue",
-        pageNextText: "Next",
-        pagePrevText: "Previous",
-        goNextPageAutomatic: false,
-        showQuestionNumbers: false,
-        showProgressBar: "aboveHeader",
-        pages: [
-            {
-                elements: [
-                    {
-                        title: "Thinking about your own life and personal circumstances, how satisfied are you with your life as a whole?",
-                        name: "SILS",
-                        type: "rating",
-                        rateCount: 11,
-                        rateMin: 0,
-                        rateMax: 10,
-                        minRateDescription: "No satisfaction at all",
-                        maxRateDescription: "Completely satisfied",
-                    },
-                ],
-            },
-        ],
-    },
-
-    data: {
-        screen: "demographics_sils",
-    },
-}
-
-
-// TAS-20
-
-var TAS_items = [
+const tas_items = [
     "I am often confused about what emotion I am feeling",
     "I have physical sensations that even doctors don't understand",
     "When I am upset, I don't know if I am sad, frightened, or angry",
@@ -60,60 +23,9 @@ var TAS_items = [
     "Looking for hidden meanings in movies or plays distracts from their enjoyment",
 ]
 
-var TAS_dimensions = [
-    "IdentifyingFeelings_1",
-    "IdentifyingFeelings_2",
-    "IdentifyingFeelings_3",
-    "IdentifyingFeelings_4",
-    "IdentifyingFeelings_5",
-    "IdentifyingFeelings_6",
-    "IdentifyingFeelings_7",
-    "DescribingFeelings_1",
-    "DescribingFeelings_2",
-    "DescribingFeelings_3",
-    "DescribingFeelings_4",
-    "DescribingFeelings_5",
-    "ExternalThinking_1",
-    "ExternalThinking_2",
-    "ExternalThinking_3",
-    "ExternalThinking_4",
-    "ExternalThinking_5",
-    "ExternalThinking_6",
-    "ExternalThinking_7",
-    "ExternalThinking_8",
-]
-
-var TAS_questions = []
-for (const [index, element] of TAS_items.entries()) {
-    TAS_questions.push({
-        prompt: "<b>" + element + "</b>",
[…]

### 2024-12-17 study2/experiment_ana/demographics.js

@@ -298,8 +298,7 @@ var demographics_wearables = {
                         maxRateDescription: "Very much",
                     },
                     {
-                        visibleIf:
-                            "{Wearables_Ownership} contains 'Heart rate'",
+                        visibleIf: "{Wearables_Ownership} contains 'Heart rate'",
                         title: "How often do you check your heart rate with your device?",
                         name: "Wearables_Heart",
                         type: "rating",
@@ -330,13 +329,18 @@ var experiment_feedback = {
     type: jsPsychSurvey,
     survey_json: {
         title: "Feedback",
-        description:
+        description: 
             "It is the end of the experiment! Don't hesitate to leave us a feedback.",
         completeText: "Complete the experiment",
         showQuestionNumbers: false,
         pages: [
             {
                 elements: [
+                    {
+                        type: "html",
+                        name: "Feedback_Alert",
+                        html: "<p><b style='color:red;'>Answers to these questions will not affect your reward but will help us to contextualize your answers</b></p>"
+                    },
                     {
                         type: "rating",
                         name: "Feedback_Enjoyment",
@@ -352,6 +356,12 @@ var experiment_feedback = {
                         title: "Anything else you would like to share with us?",
                         description:
                             "Please note that these comments might be shared publicly as part of the results of this study - avoid sharing personal information.",
+                        isRequired: false,
+                    },
+                    {
+                        type: "rating",
+                        name: "Feedback_Performance",
+                        title: "To what extent did you do the experiment carefully and to the best of your abilities?",
                         isRequired: false,
                     },
                 ],

### 2024-12-17 study2/experiment_ana/intero_questionnaires.js

@@ -294,7 +294,7 @@ function bpq_questions(
     return shuffledQuestions
 }
 
-const questionnaires = {
+const intero_questionnaires = {
     type: jsPsychSurvey,
     survey_json: function () {
         return {

### 2024-12-17 study2/experiment_ana/convergence_questionnaires.js
Update convergence_questionnaires

@@ -143,6 +143,7 @@ function erqs_questions(
 function phq4_questions(
     phq4_items,
     required = true,
+    ticks = ["Not al all", "Nearly every day"],
     pageId = "PHQ4"
 ) {
     // Convert items into survey questions

### 2024-12-18 study1/analysis/2_analysis.qmd
finalize analysis

@@
 #| fig-height: 10
-#| eval: true
 
@@
 
-higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std))
+dimensions <- list(
+  C01 = "UrIn",       # Urointestinal Inaccuracy
+  C09 = "CaCo",       # Cardiorespiratory Confusion
+  C13 = "CaNo",       # Cardiorespiratory Noticing
+  C18 = "Olfa",       # Olfactory Compensation
+  C03 = "Sati",       # Satiety Noticing
+  C04 = "SexA",       # Sexual Arousal Awareness
+  C06 = "SexS",       # Sexual Arousal Sensitivity
+  C15 = "SexO",       # Sexual Organs Sensitivity
+  C08 = "UrSe",       # Urointestinal Sensitivity
+  C10 = "RelA",       # Relaxation Awareness
+  C05 = "StaS",       # State Specificity
+  C02 = "ExAc",       # Expulsion Accuracy
+  C17 = "Card",       # Cardioception
+  C14 = "Resp",       # Respiroception
+  C12 = "Sign",       # Signalling
+  C16 = "Gast",       # Gastroception
+  C11 = "Derm",       # Dermatoception
+  C07 = "SexC"        # Sexual Arousal Changes
+)
+
+higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order, loading.method="revised")$std))
 cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]
 
-lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) |>
+lower <- make_loadingtable(net.loads(ega3$EGA$lower_order, loading.method="revised")$std) |>
   select(names(higher)) |>
@@
 
-higher$Item <- paste0("H", higher$Item)
-higher$Label <- paste("TODO", 1:nrow(higher))
+higher$Item <- paste0("M", higher$Item)
+higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
 lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())
 
-rbind(higher, select(lower, -ID)) |>
+tab1 <- rbind(higher, select(lower, -ID)) |>
   datawizard::data_relocate("Label", after = "Item") |>
   select(-Cluster, -Max) |>
-  # datawizard::data_rename(c(XC1 = "C01", XC2 = "C02")) |> 
+  # datawizard::data_rename(dimensions) |>  # https://github.com/easystats/datawizard/issues/576
+  datawizard::data_rename(names(dimensions), dimensions) |> 
+  mutate(`|` = "") |> 
   gt::gt() |>
@@
     style = gt::cell_text(size="small", style="italic"),
-    locations = gt::cells_body(columns="Label")
+    locations = gt::cells_body(columns="Label", rows=c(4:57))
   ) |>
@@
   # gt::tab_options(table.width = gt::pct(100)) |> 
-  gt::cols_width(Label ~ gt::pct(30)) |>
-  gt::gtsave("table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
+  gt::cols_width(Label ~ gt::pct(66),
+                 `|` ~ gt::pct(1))
+
+gt::gtsave(gt::cols_hide(tab1, `|`), "table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
+
+Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
+
+gt::gtsave(tab1, "table1.png", vwidth=1660, expand=0, quiet=TRUE)
 ```
 
-<object type="text/html" data="table1.html" width="120%" height="1000"></object>
+<object type="text/html" data="table1.html" width="125%" height="1000"></object>
+
+<!-- ![](table1.png) -->
+
+### Graph
 
@@
 
-### Graph
-
 ```{r}
@@
 lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
-  ggraph::create_layout(layout = 'circle')
+  ggraph::create_layout(layout = 'circle') |> 
+  as.data.frame()
 rownames(lower_layout) <- lower_nodes$name
@@
 higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
-  ggraph::create_layout(layout = 'circle')
+  ggraph::create_layout(layout = 'circle') |> 
+  as.data.frame()
 rownames(higher_layout) <- higher_nodes$ID
@@
   ggraph::create_layout(layout = 'linear', circular = TRUE)
-layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", "name"], "x"]
-layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", "name"], "y"]
-layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", "name"], "x"] * 0.5
-layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", "name"], "y"] * 0.5
-layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", "name"], lower)
-layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", "name"])
+layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", ]$name, "x"]
+layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", ]$name, "y"]
+layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", ]$name, "x"] * 0.5
+layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", ]$name, "y"] * 0.5
+layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", ]$name, lower)
+layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", ]$name)
+
+# Final renaming
+layout[layout$level == "Higher", "name"] <- unlist(dimensions)[layout[layout$level == "Higher", ]$name]
+layout[layout$level == "Higher", "dimension"] <- layout[layout$level == "Higher", ]$dimension |> 
+  str_replace("H1", "Deficit") |> 
+  str_replace("H2", "Awareness") |> 
+  str_replace("H3", "Sensitivity")
 
@@
   scale_color_manual(values=c(
-    "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
+    "Deficit"="#90CAF9", "Awareness"="#C5E1A5", "Sensitivity"="#EF9A9A", 
     "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
@@
     "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
-                     breaks=c("H1", "H2", "H3")) +
+                     breaks=c("Deficit", "Awareness", "Sensitivity")) +
   theme_void() +
+  theme(legend.title = element_text(face="bold")) +
   labs(color="Metaclusters")

### 2024-12-18 study1/analysis/2_analysis.qmd
final

@@
 
-```{r}
+```{r corsimilarity}
 #| fig-width: 10
 #| fig-height: 10
+#| fig-dpi: 200
 
@@
 
-```{r}
+```{r graph}
 #| fig-width: 9
 #| fig-height: 8
+#| fig-dpi: 200
+
 #| warning: false
@@
   scale_edge_alpha(range = c(0, 0.9), guide="none") +
-  scale_edge_width(range = c(0.2, 3), guide="none") +
+  scale_edge_width(range = c(0.2, 7), guide="none") +
   scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 

### 2024-12-20 study2/experiment/demographics.js
make start on study 2 experiment

@@ -77,32 +77,31 @@ const ConsentForm = {
     },
 }
 
-// var demographics_browser_info = {
-//     type: jsPsychBrowserCheck,
-//     data: {
-//         screen: "browser_info",
-//         date: new Date().toLocaleDateString("en-GB"),
-//         time: new Date().toLocaleTimeString("en-GB"),
-//     },
-//     on_finish: function (data) {
-//         data["participantID"] = participantID
-//         data["condition"] = intero_condition
+var demographics_browser_info = {
+    type: jsPsychBrowserCheck,
+    data: {
+        screen: "browser_info",
+        date: new Date().toLocaleDateString("en-GB"),
+        time: new Date().toLocaleTimeString("en-GB"),
+    },
+    on_finish: function (data) {
+        data["participantID"] = participantID
+        //data["condition"] = intero_condition
 
-//         // Rename
-//         dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
-//         data["screen_height"] = dat["height"]
-//         data["screen_width"] = dat["width"]
+        // Rename
+        dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
+        data["screen_height"] = dat["height"]
+        data["screen_width"] = dat["width"]
 
-//         // Add URL variables - ?sona_id=x&exp=1
-//         let urlvars = jsPsych.data.urlVariables()
-//         data["researcher"] = urlvars["exp"]
-//         data["sona_id"] = urlvars["sona_id"]
-//         data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
-//         data["study_id"] = urlvars["STUDY_ID"] // Prolific
-//         data["session_id"] = urlvars["SESSION_ID"] // Prolific
-//     },
-// }
-
+        // Add URL variables - ?sona_id=x&exp=1
+        let urlvars = jsPsych.data.urlVariables()
+        data["researcher"] = urlvars["exp"]
+        data["sona_id"] = urlvars["sona_id"]
+        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
+        data["study_id"] = urlvars["STUDY_ID"] // Prolific
+        data["session_id"] = urlvars["SESSION_ID"] // Prolific
+    },
+}
 
 // Demographic questions
 
@@ -249,7 +248,6 @@ var demographic_questions = {
     },
 }
 
-
 // Wearable devices survey
 
 var demographics_wearables = {
[…]

### 2024-12-20 study2/experiment/intero.js

@@ -1,582 +1,0 @@
-// Instructions ================================================
-const intero_instructions = {
-    type: jsPsychSurvey,
-    survey_json: {
-        showQuestionNumbers: false,
-        completeText: "Let's start",
-        pages: [
-            {
-                elements: [
-                    {
-                        type: "html",
-                        name: "ConsentForm",
-                        html:
-                            "<div style='display: flex;'>" +
-                            "<div style='width: 60%; margin-right: 20px;'>" +
-                            "<h1>About you and your body...</h1>" +
-                            "<h2>Instructions</h2>" +
-                            "<p>In the following questionnaires, you will be asked various questions about the way you feel and you think about your body. " +
-                            "There are no right or wrong answers.</p>" +
-                            "<p>Please note that <b style='color:#FF5722;'>various checks will be performed to ensure the validity of the data</b>. We reserve the right to withhold credit awards or reimbursement should we detect non-valid responses (e.g., random patterns of answers, instructions not read, ...).</li>" +
-                            "<p> We are aware that answering these questionnaires <b>might feel long and repetitive</b>, but having similar questions is necessary to ensure the validity of the results (we expect similar questions to be related). " +
-                            "Please read carefully each item and consider it <i>on its own</i> (<b>without trying to relate it or remember your answers to previous items</b>), and don't hesitate to take breaks if you need.</p>" +
-                            "<p style='color:green;'>At the end, you will be shown a <b>graph</b> summarizing your answers.<p>" +
-                            "</div>" +
-                            "<div style='width: 40%;'>" +
-                            "<img src='https://www.newthinking.com/wp-content/uploads/2023/06/2-ways-to-improve-mind-body-scaled.jpg' alt='Mind and Body' style='width: 100%;'>" +
-                            "</div>" +
-                            "</div>",
-                    },
-                ],
-            },
-        ],
-    },
-}
-
-// Questionnaires
-// MAIA-2 questionnaire
-const MAIA_items = [
-    "When I am tense I notice where the tension is located in my body",
-    "I notice when I am uncomfortable in my body",
-    "I notice where in my body I am comfortable",
[…]

### 2024-12-20 study2/experiment/questionnaires_convergent.js

@@ -1,0 +1,126 @@
+// TAS-20 questionnaire ================================================
+// Short alexithymia: PAQ-S questionnaire? (https://www.sciencedirect.com/science/article/pii/S0165032723000460à
+
+const items_tas = {
+    TAS_DIF_1: "I am often confused about what emotion I am feeling",
+    TAS_DDF_2: "I have physical sensations that even doctors don't understand",
+    TAS_DIF_3: "When I am upset, I don't know if I am sad, frightened, or angry",
+    TAS_DDF_4: "I am often puzzled by sensations in my body",
+    TAS_EOT_5: "I have feelings that I can't quite identify",
+    TAS_DIF_6: "I don't know what's going on inside me",
+    TAS_DIF_7: "I often don't know why I am angry",
+    TAS_EOT_8: "It is difficult for me to find the right words for my feelings",
+    TAS_DIF_9: "I am able to describe my feelings easily",
+    TAS_EOT_10: "I find it hard to describe how I feel about people",
+    TAS_DDF_11: "People tell me to describe my feelings more",
+    TAS_DDF_12: "It is difficult for me to reveal my innermost feelings, even to close friends",
+    TAS_DIF_13: "I prefer to analyze problems rather than just describe them",
+    TAS_DIF_14:
+        "I prefer to just let things happen rather than to understand why they turned out that way",
+    TAS_EOT_15: "Being in touch with emotions is essential",
+    TAS_EOT_16:
+        "I prefer talking to people about their daily activities rather than their feelings",
+    TAS_DDF_17: "I prefer to watch 'light' entertainment shows rather than psychological dramas",
+    TAS_EOT_18: "I can feel close to someone, even in moments of silence",
+    TAS_EOT_19: "I find examination of my feelings useful in solving personal problems",
+    TAS_EOT_20: "Looking for hidden meanings in movies or plays distracts from their enjoyment",
+}
+
+function make_tas(items, required = true, ticks = ["Strongly Disagree", "Strongly Agree"]) {
+    questions = []
+
+    // Make questions
+    for (const key of Object.keys(items)) {
+        q = {
+            title: items[key],
+            name: key,
+            type: "rating",
+            displayMode: "buttons",
+            isRequired: required,
+            minRateDescription: ticks[0],
+            maxRateDescription: ticks[1],
+            rateValues: [1, 2, 3, 4, 5], // 5-point Likert scale
+        }
+        questions.push(q)
+    }
+
[…]

### 2024-12-20 study2/experiment/questionnaires_interoception.js

@@ -1,0 +1,50 @@
+// MAIA-2 =================================================================================================
+const items_maia = {
+    MAIA_Noticing_1: "When I am tense I notice where the tension is located in my body",
+    MAIA_Noticing_2: "I notice when I am uncomfortable in my body",
+    MAIA_Noticing_3: "I notice where in my body I am comfortable",
+    MAIA_Noticing_4: "I notice changes in my breathing, such as whether it slows down or speeds up",
+    MAIA_NotDistracting_1_R:
+        "I ignore physical tension or discomfort until they become more severe",
+    MAIA_NotDistracting_2_R: "I distract myself from sensations of discomfort",
+    MAIA_NotDistracting_3_R: "When I feel pain or discomfort, I try to power through it",
+    MAIA_NotDistracting_4_R: "I try to ignore pain",
+    MAIA_NotDistracting_5_R: "I push feelings of discomfort away by focusing on something",
+    MAIA_NotDistracting_6_R:
+        "When I feel unpleasant body sensations, I occupy myself with something else so I do not have to feel them",
+    MAIA_NotWorrying_1_R: "When I feel physical pain, I become upset",
+    MAIA_NotWorrying_2_R: "I start to worry that something is wrong if I feel any discomfort",
+    MAIA_NotWorrying_3: "I can notice an unpleasant body sensation without worrying about it",
+    MAIA_NotWorrying_4: "I can stay calm and not worry when I have feelings of discomfort or pain",
+    MAIA_NotWorrying_5_R: "When I am in discomfort or pain I cannot get it out of my mind",
+    MAIA_AttentionRegulation_1:
+        "I can pay attention to my breath without being distracted by things happening around me",
+    MAIA_AttentionRegulation_2:
+        "I can maintain awareness of my inner bodily sensations even when there is a lot going on around me",
+    MAIA_AttentionRegulation_3:
+        "When I am in conversation with someone, I can pay attention to my posture",
+    MAIA_AttentionRegulation_4: "I can return awareness to my body if I am distracted",
+    MAIA_AttentionRegulation_5: "I can refocus my attention from thinking to sensing my body",
+    MAIA_AttentionRegulation_6:
+        "I can maintain awareness of my whole body even when a part of me is in pain or discomfort",
+    MAIA_AttentionRegulation_7: "I am able to consciously focus on my body as a whole",
[…]

### 2024-12-20 study2/experiment/questionnaires_mint.js

@@ -1,0 +1,93 @@
+const questionnaires_instructions = {
+    type: jsPsychSurvey,
+    survey_json: {
+        showQuestionNumbers: false,
+        completeText: "Let's start",
+        pages: [
+            {
+                elements: [
+                    {
+                        type: "html",
+                        name: "Instructions",
+                        html:
+                            "<div style='display: flex;'>" +
+                            "<div style='width: 60%; margin-right: 20px;'>" +
+                            "<h2>Instructions</h2>" +
+                            "<p>In this study, you will be asked to complete various questionnaires. Please read each question carefully, and don't hesitate to take breaks in-between them.</p>" +
+                            "<p>Please note that <b style='color:#FF5722;'>various checks will be performed to ensure the validity of the data</b>. We reserve the right to withhold credit awards or reimbursement should we detect non-valid responses (e.g., random patterns of answers, instructions not read, failed attention checks...).</li>" +
+                            "<p> We are aware that answering these questionnaires <b>might feel long and repetitive</b>, but having similar questions is necessary to ensure the validity of the results (we expect similar questions to be related, and opposite questions to be inversely related). " +
+                            "<p style='color:green;'>At the end, you will be shown a <b>graph</b> summarizing your answers, and provided with an explanation about why we are asking all of this.<p>" +
+                            "</div>" +
+                            "<div style='width: 40%;'>" +
+                            "<img src='https://www.simplypsychology.org/wp-content/uploads/psychology.jpeg' alt='Illustration' style='width: 100%;'>" +
+                            "</div>" +
+                            "</div>",
+                    },
+                ],
+            },
+        ],
+    },
+}
+
+// Items ================================================
+const items_mint = {
+    MINT_UrIn_1: "Blabla question 1",
+    MINT_UrIn_2: "Blabla question 2",
+    MINT_UrIn_3: "Blabla question 3",
+}
+
+// Generation code ================================================
+// Convernience function to shuffle an object (used internally)
+function shuffleObject(obj) {
+    const entries = Object.entries(obj)
+    for (let i = entries.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[entries[i], entries[j]] = [entries[j], entries[i]]
+    }
+    return Object.fromEntries(entries)
+}
+
+// This function formats each question into a jsPsych-survey question that contains information about the question format
[…]

### 2024-12-20 study2/experiment/questionnaires_pathology.js
add psychiatric and phq4

@@ -1,0 +1,151 @@
+// PHQ-4 ================================================
+const items_phq4 = {
+    PHQ4_Anxiety_1: "Feeling nervous, anxious or on edge",
+    PHQ4_Anxiety_2: "Not being able to stop or control worrying",
+    PHQ4_Depression_3: "Feeling down, depressed, or hopeless",
+    PHQ4_Depression_4: "Little interest or pleasure in doing things",
+}
+
+const instructions_phq4 = {
+    type: "html",
+    name: "instructions_phq4",
+    html: "<p>Over the <b>last 2 weeks</b>, how often have you been bothered by the following problems?</p>",
+}
+
+function make_phq4(items, required = true) {
+    questions = [instructions_phq4]
+
+    // Make questions
+    for (const key of Object.keys(items)) {
+        q = {
+            title: items[key],
+            name: key,
+            type: "rating",
+            isRequired: required,
+            rateValues: [
+                {
+                    value: 0,
+                    text: "Not at all",
+                },
+                {
+                    value: 0.5,
+                    text: "Once or twice",
+                },
+                {
+                    value: 1,
+                    text: "Several days",
+                },
+                {
+                    value: 2,
+                    text: "More than half the days",
+                },
+                {
+                    value: 3,
+                    text: "Nearly every day",
+                },
+            ],
+        }
+        questions.push(q)
+    }
+
+    return { elements: questions }
+}
+
+const questionnaire_phq4 = {
+    type: jsPsychSurvey,
+    survey_json: function () {
+        return {
+            title: "About your mood",
+            showQuestionNumbers: false,
+            goNextPageAutomatic: true,
+            pages: make_phq4(items_phq4),
+        }
+    },
+    data: {
+        screen: "questionnaire_phq4",
+    },
+}
+
+// Psychiatric Disorders ================================================
+const questions_mentalhealth = {
+    type: jsPsychSurvey,
+    survey_json: {
+        title: "Mental health",
+        completeText: "Continue",
+        pageNextText: "Next",
+        pagePrevText: "Previous",
+        goNextPageAutomatic: true,
+        showQuestionNumbers: false,
+        // showProgressBar: "aboveHeader",
+        pages: [
+            {
+                elements: [
+                    {
+                        title: "Are you currently living with one of the following medically diagnosed difficulty?",
+                        name: "Disorders_Psychiatric",
+                        type: "checkbox",
+                        choices: [
+                            "Addiction",
+                            "Attention Deficit Hyperactivity Disorder (ADHD)",
+                            "Autism",
[…]

### 2024-12-20 study2/experiment/demographics.js
fix wearables

@@ -253,13 +253,13 @@ var demographic_questions = {
 var demographics_wearables = {
     type: jsPsychSurvey,
     survey_json: {
-        title: "Wearable Device Usage",
+        title: "Health Monitoring",
         completeText: "Continue",
         pageNextText: "Next",
         pagePrevText: "Previous",
         goNextPageAutomatic: false,
         showQuestionNumbers: false,
-        showProgressBar: "aboveHeader",
+        // showProgressBar: "aboveHeader",
         pages: [
             {
                 elements: [
@@ -275,7 +275,7 @@ var demographics_wearables = {
                             "Calories burnt",
                             "Calorie intake",
                             "Sleep quality",
-                            "Respiratory rate",
+                            "Weight (including with a regular scale)",
                         ],
                         showSelectAllItem: false,
                         showNoneItem: true,
@@ -285,17 +285,7 @@ var demographics_wearables = {
                         separateSpecialChoices: true,
                         colCount: 0,
                         colCount: 1,
-                    },
-                    {
-                        visibleIf: "{Wearables_Ownership} notcontains 'None'",
-                        title: "How important is this information about your body to you?",
-                        name: "Wearables_Importance",
-                        type: "rating",
-                        rateCount: 8,
-                        rateMin: 0,
-                        rateMax: 7,
-                        minRateDescription: "Not at all",
-                        maxRateDescription: "Very much",
+                        isRequired: true,
                     },
                     {
                         visibleIf: "{Wearables_Ownership} contains 'Heart rate'",
@@ -304,15 +294,16 @@ var demographics_wearables = {
                         type: "rating",
                         displayMode: "buttons",
                         rateValues: [
+                            "Never",
                             "Very rarely",
                             "A few times per week",
                             "A few times per day",
                             "A few times per hour",
-                            "Whenever I have the occasion",
                         ],
                         isRequired: true,
                         colCount: 0,
                     },
+                    // TODO: add subquestions for each device
                 ],
             },
         ],
@@ -329,8 +320,7 @@ var experiment_feedback = {
     type: jsPsychSurvey,
     survey_json: {
         title: "Feedback",
-        description: 
-            "It is the end of the experiment! Don't hesitate to leave us a feedback.",
+        description: "It is the end of the experiment! Don't hesitate to leave us a feedback.",
         completeText: "Complete the experiment",
[…]

### 2024-12-20 study2/experiment/questionnaires_pathology.js

@@ -118,7 +118,8 @@ const questions_mentalhealth = {
                         colCount: 1,
                     },
                     {
-                        visibleIf: "{Disorders_Psychiatric} notempty",
+                        visibleIf:
+                            "{Disorders_Psychiatric} notempty and {Disorders_Psychiatric} notcontains 'None'",
                         title: "Are you currently undergoing any of the following treatments",
                         name: "Disorders_PsychiatricTreatment",
                         type: "checkbox",

### 2025-02-04 study2/analysis/preprocessing.R
fix attention checks

@@ -37,6 +37,8 @@ for (file in files) {
 
   if("prolific_id" %in% colnames(dat)){
     data_ppt$Prolific_ID <- dat$prolific_id
+  } else {
+    stop("Not prolific")
   }
 
   data_ppt$Reward <- rawdata[rawdata$screen == "demographics_debrief", "Reward"]
@@ -45,7 +47,7 @@ for (file in files) {
   resp <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
 
   # Education
-  data_ppt$Education <- ifelse(resp$Education == "other", demog$`Education-Comment`, resp$Education)
+  data_ppt$Education <- ifelse(resp$Education == "other", resp$`Education-Comment`, resp$Education)
 
   data_ppt$Student <- ifelse(!is.null(resp$Student), resp$Student, NA)
   data_ppt$Country <- ifelse(!is.null(resp$Country), resp$Country, NA)
@@ -68,6 +70,8 @@ for (file in files) {
 
   # Mint questionnaire
   mint <- jsonlite::fromJSON(rawdata[rawdata$screen == "questionnaire_mint", "response"])
+  names(mint) <- as.character(sapply(names(mint), function(x) gsub("InteroceptiHypervigilance", "InteroceptiveHypervigilance", x)))
+  names(mint) <- as.character(sapply(names(mint), function(x) gsub("Interoceptive", "MINT_Interoceptive", x)))
   data_ppt <- cbind(data_ppt, as.data.frame(mint))
 
   # Interoception questionnaires
@@ -106,33 +110,71 @@ for (file in files) {
   cefsa$instructions_cefsa <- NULL
   data_ppt <- cbind(data_ppt, as.data.frame(cefsa))
 
-  # mentalhealth <- jsonlite::fromJSON(rawdata[rawdata$screen == "questions_mentalhealth", "response"])
-  # mentalhealth <- as.data.frame(mentalhealth)
-  # data_ppt <- cbind(data_ppt, mentalhealth)
-  #
-  # somatichealth <- jsonlite::fromJSON(rawdata[rawdata$screen == "questions_somatichealth", "response"])
-  # somatichealth <- as.data.frame(somatichealthhealth)
[…]

### 2025-02-04 study2/experiment/postprocessing.js

@@ -11,14 +11,14 @@ function check_attentionchecks() {
 
     // compute scores for tas) }).values()[0].response
     let data_tas = get_screen("questionnaire_tas")
-    let tas_score_A = 1 - data_tas["TAS_AttentionCheck_1"] / 5
+    let tas_score_A = 1 - (data_tas["TAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for pi18
     let data_pi = get_screen("questionnaire_pi18")
     let pi_score_A = data_pi["PI18_AttentionCheck_1"] / 5
 
     // compute scores for CEFSA
-    let data_cefsa = get_screen("questionnaire_cefsa")//.values()[0].response
+    let data_cefsa = get_screen("questionnaire_cefsa") //.values()[0].response
     let cefsa_score_A = 1 - data_cefsa["CEFSA_AttentionCheck_1"] / 4
 
     //compute scores for MAIA
@@ -27,23 +27,14 @@ function check_attentionchecks() {
 
     //compute scores for IAS
     let data_ias = get_screen("questionnaire_ias")
-    let ias_score_A = 1 - data_ias["IAS_AttentionCheck_1"] / 5
+    let ias_score_A = 1 - (data_ias["IAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for BPQ
     let data_bpq = get_screen("questionnaire_bpq")
     let bpq_score_A = data_bpq["BodyAwareness_AttentionCheck_1"] / 5
 
     // Average
-    return (
-        (mint_score_A +
-            tas_score_A +
-            pi_score_A +
-            cefsa_score_A +
-            maia_score_A +
-            ias_score_A +
-            bpq_score_A) /
-        7
-    )
+    return (mint_score_A + tas_score_A + pi_score_A + cefsa_score_A + maia_score_A + ias_score_A + bpq_score_A) / 7
 }
 
 // Make general chart ========================================================================================================
@@ -56,19 +47,15 @@ function radar_plotdata() {
 
     // Compute average and rescale to percentage
     BodyConnect = Object.keys(data_ias).filter((key) => key.includes("IAS"))
-    BodyConnect =
-        BodyConnect.map((key) => data_ias[key]).reduce((a, b) => a + b) / BodyConnect.length
+    BodyConnect = BodyConnect.map((key) => data_ias[key]).reduce((a, b) => a + b) / BodyConnect.length
     BodyConnect = (BodyConnect / 5) * 100
 
[…]

### 2025-02-04 study2sona/experiment/postprocessing.js
fixed attention checks

@@ -11,7 +11,7 @@ function check_attentionchecks() {
 
     // compute scores for tas) }).values()[0].response
     let data_tas = get_screen("questionnaire_tas")
-    let tas_score_A = 1 - data_tas["TAS_AttentionCheck_1"] / 5
+    let tas_score_A = (5 - data_tas["TAS_AttentionCheck_1"]) / 4
 
     //compute scores for pi18
     let data_pi = get_screen("questionnaire_pi18")
@@ -27,11 +27,11 @@ function check_attentionchecks() {
 
     //compute scores for IAS
     let data_ias = get_screen("questionnaire_ias")
-    let ias_score_A = 1 - data_ias["IAS_AttentionCheck_1"] / 5
+    let ias_score_A = (5 - data_ias["IAS_AttentionCheck_1"]) / 4
 
     //compute scores for BPQ
     let data_bpq = get_screen("questionnaire_bpq")
-    let bpq_score_A = data_bpq["BodyAwareness_AttentionCheck_1"] / 5
+    let bpq_score_A = data_bpq["BodyAwareness_AttentionCheck_1"] / 4
 
     // Average
     return (

### 2025-02-04 study2sona/experiment/postprocessing.js
matched attention checks with sona study

@@ -11,14 +11,14 @@ function check_attentionchecks() {
 
     // compute scores for tas) }).values()[0].response
     let data_tas = get_screen("questionnaire_tas")
-    let tas_score_A = (5 - data_tas["TAS_AttentionCheck_1"]) / 4
+    let tas_score_A = 1 - (data_tas["TAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for pi18
     let data_pi = get_screen("questionnaire_pi18")
     let pi_score_A = data_pi["PI18_AttentionCheck_1"] / 5
 
     // compute scores for CEFSA
-    let data_cefsa = get_screen("questionnaire_cefsa")//.values()[0].response
+    let data_cefsa = get_screen("questionnaire_cefsa") //.values()[0].response
     let cefsa_score_A = 1 - data_cefsa["CEFSA_AttentionCheck_1"] / 4
 
     //compute scores for MAIA
@@ -27,23 +27,14 @@ function check_attentionchecks() {
 
     //compute scores for IAS
     let data_ias = get_screen("questionnaire_ias")
-    let ias_score_A = (5 - data_ias["IAS_AttentionCheck_1"]) / 4
+    let ias_score_A = 1 - (data_ias["IAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for BPQ
     let data_bpq = get_screen("questionnaire_bpq")
     let bpq_score_A = data_bpq["BodyAwareness_AttentionCheck_1"] / 4
 
     // Average
-    return (
-        (mint_score_A +
-            tas_score_A +
-            pi_score_A +
-            cefsa_score_A +
-            maia_score_A +
-            ias_score_A +
-            bpq_score_A) /
-        7
-    )
+    return (mint_score_A + tas_score_A + pi_score_A + cefsa_score_A + maia_score_A + ias_score_A + bpq_score_A) / 7
 }
 
 // Make general chart ========================================================================================================

### 2025-02-04 study2sona/experiment/questionnaires_pathology.js
hotfix make required for sona

@@ -75,6 +75,7 @@ const questionnaire_phq4 = {
                             rateMax: 10,
                             minRateDescription: "No satisfaction at all",
                             maxRateDescription: "Completely satisfied",
+                            isRequired: true,
                         },
                     ],
                 },

### 2025-02-04 study2/analysis/1_cleaning.qmd
todo

--- 2024-12-11 study1/analysis/1_cleaning.qmd
@@
 ---
-title: "Interoception Scale - Data Cleaning"
+title: "Interoception Scale (Study 2) - Data Cleaning"
 editor: source
@@
     toc: true
-bibliography: references.bib
 ---
@@
 df |> 
-  summarise(n = n(), .by=c("Condition", "Experiment_Enjoyment")) |>
+  summarise(n = n(), .by=c("Experiment_Enjoyment")) |>
   filter(!is.na(Experiment_Enjoyment)) |> 
   mutate(n = n / sum(n),
-         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
-         .by="Condition") |>
-  ggplot(aes(y = Condition, x = n, fill = Experiment_Enjoyment)) +
+         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment))) |>
+  ggplot(aes(y = n, x = 1, fill = Experiment_Enjoyment)) +
   geom_bar(stat="identity", position="stack") +
   scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
+  coord_flip() +
   scale_x_continuous(expand=c(0, 0))  +
+  scale_y_continuous(labels = scales::percent)  +
   labs(title="Experiment Enjoyment",
@@
   theme_minimal() +
-  theme(axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
+  theme(
+    axis.title = element_blank(),
+    axis.text.y = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.y = element_blank(),
     legend.position = "top",
     legend.title = element_blank()) 
-
-lm(Experiment_Enjoyment ~ Condition, data = df) |> 
-  modelbased::estimate_contrasts(p_adjust="none", contrast = "Condition") |> 
-  display()
 ```
@@
   dplyr::mutate(
-    # "I always know that I am attentively doing a study"
-    A1 = ifelse(Sexual_State_A == 6 | Sexual_State_A == 5, 0, 1),
-    # "Even if I am anxious, I should now answer all the way to the left"
-    A2 = ifelse(Anxious_SkinThermo_A == 0, 0, 1),
-    # "I often experience sensations, and I will answer zero to this question"
-    A3 = ifelse(Nociception_ColonBladder_A == 0, 0, 1),
-    # "In general, I am very sensitive and attentive to the questions I am currently answering"
-    A4 = ifelse(Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5, 0, 1),
-    # "I often pay attention to the answers I am giving"
-    A5 = ifelse(Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5, 0, 1),
-    # "I can always accurately answer to the left on this question to show that I am reading it"
-    A6 = ifelse(Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1, 0, 1),
-    # "I can always accurately perceive that to this question I should answer the lowest option"
-    A7 = ifelse(Accuracy_Genital_A == 0, 0, 1),
-    # "Sometimes I notice that I need to answer all the way to the right"
-    A8 = ifelse(Confusion_ColonBladder_A == 6, 0, 1),
+    # "I can always accurately answer to the extreme left on this question to show that I am reading it"
+    A1 = ifelse(MINT_AttentionCheck_1 == 0, 0, 1),
+    # "I notice that I am being asked to respond all the way to the right"
+    A2 = ifelse(MAIA_AttentionCheck_1 == 6, 0, 1),
+    # "I can always accurately choose the lowest option"
+    A3 = ifelse(IAS_AttentionCheck_1 == 1, 0, 1),
+    # "Respond all the way to the right."
+    A4 = ifelse(BodyAwareness_AttentionCheck_1 == 5, 0, 1),
+    # "I am able to respond all the way to the left"
+    A5 = ifelse(TAS_AttentionCheck_1 == 1, 0, 1),
+    # "On the whole, I know I must press the highest option"
+    A6 = ifelse(PI18_AttentionCheck_1 == 5, 0, 1),
+    # "I feel that to show I'm being attentive I will press the lowest option"
+    A7 = ifelse(CEFSA_AttentionCheck_1 == 0, 0, 1),
     .keep = "none"
@@
 # Compute distance
-dfoutlier <- performance::check_outliers(select(df, contains("_Q")), 
+dfoutlier <- performance::check_outliers(select(df, contains("MINT_")), 
                                          method=c("optics"),
@@
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 12.5, "Participant"])
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 8, "Participant"])
 outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
@@
   geom_bar(aes(fill=Outlier), stat="identity") +
-  geom_hline(yintercept = 12.5, linetype="dashed", color="red") +
+  geom_hline(yintercept = 8, linetype="dashed", color="red") +
   labs(fill = "Status") +
@@
   geom_line() +
-  geom_vline(xintercept=12.5, linetype="dashed", color="red") +
+  geom_vline(xintercept=8, linetype="dashed", color="red") +
   theme_minimal()
@@
 
-**TODO: describe OPTICS**.
-
-Mahalanobis distance [@demaesschalck2000] is commonly used to detect multivariate outliers, which are data points with unusual combinations of scores on two or more variables [@filzmoser2016].
-This distance is calculated relative to the centroid—a central point where the means of all variables intersect—with larger distances indicating greater deviation from the center.
-
-This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping items.
-
 We removed `r length(outliers$distance)` (`r insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.
-
-```{r}
-#| eval: false
-
-r_full <- cor(select(df, contains("_Q")))
-r_cleaned <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$duration, outliers$distance)) |> 
-  select(contains("_Q")) |> 
-  cor()
-
-data.frame(Full=r_full[lower.tri(r_full)], Clean=r_cleaned[lower.tri(r_cleaned)]) |> 
-  pivot_longer(everything()) |> 
-  ggplot(aes(x=value)) +
-  geom_histogram(aes(fill=name, color=name), bins=60, alpha=0.3, position="identity") +
-  theme_minimal()
-```
 
@@
 
-# Did not add education disciplines
-
 p_edu <- df |>
@@
 p_eth
-
 ```
@@
 
+### BMI
+
+```{r}
+df |> 
+  ggplot(aes(x=BMI)) +
+  annotate("rect", xmin=10, xmax=18.5, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
+  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.1) +
+  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.1) +
+  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.1) +
+  annotate("rect", xmin=40, xmax=Inf, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
+  geom_density(aes(color=Gender, fill=Gender), alpha=0.3, linewidth=1) +
+  labs(title = "BMI distribution") +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.text.y = element_blank())
+
+df |> 
+  ggplot(aes(x=Age, y=BMI, color=Gender)) +
+  geom_point() +
+  geom_smooth(aes(fill=Gender), alpha=0.3, method = 'loess', formula = 'y ~ x') +
+  labs(title = "BMI and Age") +
+  theme_minimal() 
+```
+
+### Mental Health
+
+```{r}
+df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
+df$Disorders_Psychiatric_MoodTreatment <- ifelse(
+  df$Disorders_Psychiatric_Mood & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Mood|Antidepressant|Anxiolytic|Psychotherapy"), TRUE, FALSE)
+# df$Disorders_Psychiatric_Other <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
+
+p1 <- select(df, Participant, Gender, Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment) |> 
+  pivot_longer(cols = starts_with("Disorders_"), names_to = "Disorder", values_to = "Value") |> 
+  mutate(Disorder = str_remove_all(Disorder, fixed("Disorders_Psychiatric_")),
+         Disorder = str_replace(Disorder, "MoodTreatment", "Mood Disorder (with treatment)"),
+         Disorder = str_replace(Disorder, "Mood$", "Mood Disorder")) |> 
+  summarize(N = sum(Value) / nrow(df), .by=c("Gender", "Disorder")) |> 
+  mutate(N_tot = sum(N), .by="Disorder") |>
+  mutate(Disorder = fct_reorder(Disorder, desc(N_tot))) |>
+  ggplot(aes(x = Disorder, y = N, fill=Gender)) +
+  geom_bar(stat = "identity") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_y_continuous(expand = c(0, 0), labels=scales::percent) +
+  labs(title = "Mood Disorders", y = "Number of Participants", subtitle = "Participants per self-declared mood disorder", x="Type") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme_minimal()
+
+df$Disorders_Somatic_Number <- ifelse(df$Disorders_Somatic == "", 0, str_count(df$Disorders_Somatic, ";")+1)
+
+p2 <- df |> 
+  ggplot(aes(x = Disorders_Somatic_Number, fill=Gender)) +
+  geom_bar() +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_x_continuous(breaks = c(0:10)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Type") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme_minimal()
+
+p1 / p2
+```
+
 :::
@@
 ```{r}
-write.csv(df, "../data/data_participants.csv", row.names = FALSE)
+df |> 
+  select(-contains("AttentionCheck")) |> 
+  write.csv("../data/data_participants.csv", row.names = FALSE)
 ```

### 2025-02-04 study2/analysis/2_analysis.qmd
todo

--- 2024-12-11 study1/analysis/2_analysis.qmd
@@
 ---
-title: "InteroceptionScale - Data Analysis"
+title: "InteroceptionScale (study 2) - Data Analysis"
 editor: source
@@
 df <- read.csv("../data/data_participants.csv")
+```
 
-items <- select(df, contains("_Q")) 
-byfacet <- items[df$Condition=="Dimensions",]
-bymodality <- items[df$Condition=="Domains",]
-byrandom <- items[df$Condition=="Random",]
+## Structure Validation
+
+```{r}
+#| code-fold: false
+
+items <- select(df, starts_with("MINT_"))
 ```
@@
 labels <- list(
-  Sexual_State_Q1 = "I always know when I am sexually aroused",
-  Sexual_State_Q2 = "I always feel in my body if I am sexually aroused",
-  Sexual_State_Q3 = "My body is always in the same specific state  when I am sexually aroused",
-  Sexual_State_Q4 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
-  Sexual_State_Q5 = "I can always tell that I am sexually aroused from the way I feel inside",
-  Sexual_State_A = "I always know that I am attentively doing a study",
-  Sexual_Cardiac_Q1 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
-  Sexual_Respiratory_Q1 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
-  Sexual_Gastric_Q1 = "When I am sexually aroused, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
-  Sexual_Gastric_Q2 = "When I am sexually aroused, I often feel butterflies in my stomach",
-  Sexual_Genital_Q1 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
-  Sexual_Genital_Q2 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
-  Sexual_SkinThermo_Q1 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
-  Sexual_SkinThermo_Q2 = "When I am sexually aroused, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
-  Sexual_SkinThermo_Q3 = "When I am sexually aroused, I often feel my mouth becoming dry",
-  Sexual_ColonBladder_Q1 = "When I am sexually aroused, I often feel like I need to relieve myself by urinating or defecating",
-  Sexual_ColonBladder_Q2 = "During sex or masturbation, I often feel like I need to relieve myself by urinating or defecating",
-  Anxious_State_Q1 = "I always know when I am anxious",
-  Anxious_State_Q2 =  "I always feel in my body if I am anxious",
-  Anxious_State_Q3 = "My body is always in the same specific state when I am anxious",
-  Anxious_State_Q4 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
-  Anxious_State_Q5 = "I often realize that I am anxious only when others tell me",
-  Anxious_Cardiac_Q1 = "When I am anxious, I often feel changes in the way my heart beats (e.g., faster or stronger)",
-  Anxious_Respiratory_Q1 = "When I am anxious, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
-  Anxious_Gastric_Q1 = "When I am anxious, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
-  Anxious_Genital_Q1 = "When I am anxious, I often notice specific sensations in my genital area (e.g., contractions, dryness)",
-  Anxious_SkinThermo_Q1 = "When I am anxious, I often feel changes in my temperature (e.g., feeling warm or cold)",
-  Anxious_SkinThermo_Q2 = "When I am anxious, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
-  Anxious_SkinThermo_Q3 = "When I am anxious, I often feel my mouth becoming dry",
-  Anxious_SkinThermo_Q4 = "When I am anxious, I often have difficulty swallowing",
-  Anxious_SkinThermo_A = "Even if I am anxious, I should now answer all the way to the left",
-  Anxious_ColonBladder_Q1 = "When I am anxious, I often feel like I need to relieve myself by urinating or defecating",
-  Nociception_State_Q1 = "I always feel in my body if I am ill",
-  Nociception_State_Q2 =  "I can easily tell when I am feeling ill (e.g., nauseous or sick)",
-  Nociception_Cardiac_Q1 = "I often feel painful sensations coming from my heart",
-  Nociception_Cardiac_Q2 = "I often experience painful sensations coming from my chest",
-  Nociception_Respiratory_Q1 = "I often feel like I have difficulties breathing normally",
-  Nociception_Respiratory_Q2 = "I often feel like I can't get enough oxygen by breathing normally",
-  Nociception_Gastric_Q1 = "I often feel pain in my stomach",
-  Nociception_Genital_Q1 = "My genital organs are very sensitive to pleasant stimulations",
-  Nociception_Genital_Q2 = "My genital organs are very sensitive to painful stimulations",
-  Nociception_SkinThermo_Q1 = "My skin is very sensitive to painful stimulations (e.g., pinching)",
-  Nociception_SkinThermo_Q2 = "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
-  Nociception_SkinThermo_Q3 = "Changes in temperature (e.g., feeling feverish or cold) are the first things I notice when I am becoming ill",
-  Nociception_ColonBladder_Q1 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
-  Nociception_ColonBladder_Q2 = "I often experience painful sensations when relieving myself when urinating or defecating",
-  Nociception_ColonBladder_A = "I often experience sensations, and I will answer zero to this question",
-  Sensitivity_State_Q1 =  "I always know when I am relaxed",
-  Sensitivity_State_Q2 =  "I always feel in my body if I am relaxed",
-  Sensitivity_State_Q3 = "My body is always in the same specific state when I am relaxed",
-  Sensitivity_State_Q4 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
-  Sensitivity_State_Q5 = "When something important is happening in my life, I can feel it in my body",
-  Sensitivity_Cardiac_Q1 = "In general, I am very sensitive to changes in my heart rate",
-  Sensitivity_Cardiac_Q2 = "I often notice changes in my heart rate",
-  Sensitivity_Cardiac_Q3 = "I can notice even very subtle changes in the way my heart beats",
-  Sensitivity_Cardiac_Q4 = "I am always very aware of my heartbeats, even when I am calm",
-  Sensitivity_Cardiac_Q5 = "I only notice my heart when it is thumping in my chest",
-  Sensitivity_Cardiac_Q6 = "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
-  Sensitivity_Cardiac_Q7 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
-  Sensitivity_Cardiac_A = "In general, I am very sensitive and attentive to the questions I am currently answering",
-  Sensitivity_Respiratory_Q1 = "In general, I am very sensitive to changes in my breathing",
-  Sensitivity_Respiratory_Q = "I often notice changes in my breathing",
-  Sensitivity_Respiratory_Q3 = "I can notice even very subtle changes in my breathing",
-  Sensitivity_Respiratory_Q4 = "I am always very aware of how I am breathing, even when I am calm",
-  Sensitivity_Respiratory_Q5 = "I often only notice how I am breathing when it becomes loud",
-  Sensitivity_Respiratory_Q6 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
-  Sensitivity_Respiratory_Q7 = "When something important is happening in my life, I can immediately feel changes in my breathing",
-  Sensitivity_Gastric_Q1 = "In general, I am very sensitive to what my stomach is doing",
-  Sensitivity_Gastric_Q2 = "I can notice even very subtle changes in what my stomach is doing",
-  Sensitivity_Gastric_Q3 = "I am always very aware of what my stomach is doing, even when I am calm",
-  Sensitivity_Gastric_Q4 = "I often check the smell of my own breath",
-  Sensitivity_Gastric_Q5 = "I often check the smell of my farts",
-  Sensitivity_Gastric_Q6 = "I often pay attention to the noises of my stomach",
-  Sensitivity_Gastric_A = "I often pay attention to the answers I am giving",
-  Sensitivity_Genital_Q1 = "In general, I am very sensitive to changes in my genital organs",
-  Sensitivity_Genital_Q2 = "I can notice even very subtle changes in the state of my genital organs",
-  Sensitivity_Genital_Q3 = "I am always very aware of the state of my genital organs, even when I am calm",
-  Sensitivity_SkinThermo_Q1 = "In general, my skin is very sensitive",
-  Sensitivity_SkinThermo_Q2 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
-  Sensitivity_SkinThermo_Q3 =  "I can notice even very subtle changes if my skin becomes dry or sweaty",
-  Sensitivity_SkinThermo_Q4 ="I am always very aware if my hands and feet are cold or warm",
-  Sensitivity_SkinThermo_Q5 = "I often check the smell of my armpits",
-  Sensitivity_SkinThermo_Q6 = "I am very prone to having goosebumps",
-  Sensitivity_SkinThermo_Q7 ="My skin is susceptible to itchy fabrics and materials",
-  Sensitivity_SkinThermo_Q8 = "I enjoy the sensations of touching different materials (e.g., soft fabrics, wooden objects, smooth surfaces)",
-  Sensitivity_ColonBladder_Q1 = "In general, I am very aware of the sensations that are happening when I am defecating",
-  Sensitivity_ColonBladder_Q2 = "In general, I am very aware of the sensations that are happening when I am urinating",
-  Sensitivity_ColonBladder_Q3 = "I often check the colour of my urine",
-  Sensitivity_ColonBladder_Q4 =  "I often check the colour of my faeces",
-  Accuracy_State_Q1 =  "I can always accurately feel when I am about to cough",
-  Accuracy_State_Q2 = "I can always accurately feel when I am about to sneeze",
-  Accuracy_State_Q3 = "I can always accurately feel when I am about to vomit",
-  Accuracy_State_Q4 = "I can always accurately feel when I am starting to be hungry",
-  Accuracy_State_Q5 = "I can always accurately feel when I am starting to be thirsty",
-  Accuracy_Cardiac_Q1 = "I can always accurately feel if my heart rate is slow or fast",
-  Accuracy_Cardiac_Q2 = "I sometimes feel like my heart is racing or beating faster than usual, but when I check my pulse, it is not as intense as I thought",
-  Accuracy_Respiratory_Q1 = "I can always accurately feel how I am breathing (e.g., fast or slow, deep or shallow)",
-  Accuracy_Respiratory_A = "I can always accurately answer to the left on this question to show that I am reading it",
-  Accuracy_Gastric_Q1 = "I can always accurately feel when I am about to fart",
-  Accuracy_Gastric_Q2 = "I can always accurately feel when I am about to burp",
-  Accuracy_Gastric_Q3 = "I often feel thirsty even if I drank recently",
-  Accuracy_Gastric_Q4 = "I don't always feel the need to drink until I am really thirsty",
-  Accuracy_Gastric_Q5 = "I often feel hungry even if I ate recently",
-  Accuracy_Gastric_Q6 = "I don't always feel the need to eat until I am really hungry",
-  Accuracy_Gastric_Q7 = "I often sneeze suddenly without feeling the need building up",
-  Accuracy_Gastric_Q8 = "I sometimes feel that burping will produce some relief but then it doesn't",
-  Accuracy_Genital_Q1 = "I can always accurately perceive if my genital organs are in a state of arousal (e.g., hard, wet, pulsating)",
-  Accuracy_Genital_Q2 = "I sometimes feel like I am sexually aroused, but when I try to satisfy the feeling, I realise that I am not as sexually aroused as I initially thought",
-  Accuracy_Genital_A = "I can always accurately perceive that to this question I should answer the lowest option",
-  Accuracy_SkinThermo_Q1 = "I can always accurately feel when something is going to be itchy",
-  Accuracy_SkinThermo_Q2 = "I can always accurately feel when I start to have a fever",
-  Accuracy_SkinThermo_Q3 = "When something touches my skin, I can always accurately feel if it's hot or cold",
-  Accuracy_SkinThermo_Q4 = "I sometimes feel my skin itching, but when I scratch it, it doesn't produce the relief I expected",
-  Accuracy_ColonBladder_Q1 = "I often feel the need to urinate even when my bladder is not full",
-  Accuracy_ColonBladder_Q2 = "I don't always feel the need to urinate until my bladder is very full",
-  Accuracy_ColonBladder_Q3 = "I often feel the need to defecate even when my intestine is not full",
-  Accuracy_ColonBladder_Q4 = "I don't always feel the need to defecate until my intestine is very full",
-  Accuracy_ColonBladder_Q5 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-  Confusion_State_Q1 = "Sometimes I can't tell if the sensations in my body are good or bad",
-  Confusion_State_Q2 = "Sometimes I am confused about what sensations in my body mean",
-  Confusion_Cardiac_Q1 = "Sometimes my heart starts racing and I often don't know why",
-  Confusion_Respiratory_Q1 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-  Confusion_Gastric_Q1 = "Sometimes I feel negative and realise after eating that I was just hungry",
-  Confusion_Gastric_Q2 = "Sometimes I don't realise I was hungry until I ate something",
-  Confusion_Genital_Q1 = "Sometimes I notice arousal in my genital areas (e.g., stiffness, wetness) when I am not feeling sexually aroused",
-  Confusion_SkinThermo_Q1 = "Sometimes I have sensations on my skin (e.g., itches, goosebumps) without any clear cause",
-  Confusion_ColonBladder_Q1 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-  Confusion_ColonBladder_A = "Sometimes I notice that I need to answer all the way to the right"
+  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+  MINT_Deficit_CaCo_5 =  "I often feel like I can't get enough oxygen by breathing normally"
 )
-```
-
-## Item Correlation
-
-### Full Sample
-
-```{r}
-#| fig-width: 12
-#| fig-height: 12
-
-make_heatmap <- function(items, interactive=TRUE, title="Correlation Matrix") {
-  fn <- if(interactive) heatmaply::heatmaply else heatmaply::ggheatmap
-
-  fn(
-    cor(items),
-    symm = TRUE,
-    colors=heatmaply::cool_warm,
-    show_dendrogram =c(FALSE, TRUE),
-    main=title,
-    showticklabels = FALSE,
-    hide_colorbar = TRUE,
-    k_col = 4,
-    # k_row = 4,
-    limits = c(-1, 1)
-    )
-}
-
-make_heatmap(items, title="Full Sample")
-```
-
-### Similarity
-
-```{r}
-#| eval: true
-
-bootstrap_similarity <- function(df) {
-  rez <- data.frame()
-  for(i in 1:200) {
-    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
-    newdata <- df[idx,]
-    items <- select(df, contains("_Q"))
-    byfacet <- items[newdata$Condition=="Dimensions",]
-    bymodality <- items[newdata$Condition=="Domains",]
-    byrandom <- items[newdata$Condition=="Random",]
-
-    rez <- rbind(
-      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
-                                         ncomp1=10, ncomp2=10, plot=FALSE),
-      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
-                                         ncomp1=10, ncomp2=10, plot=FALSE),
-      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
-                                         ncomp1=10, ncomp2=10, plot=FALSE),
-      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
-                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
-      as.data.frame() |>
-      mutate(
-        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
-        Sample = c("Random", "Random", "Full", "Full"),
-        Iteration = i) |>
-      mutate(d_PSI = diff(PSI), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
-      rbind(rez)
-  }
-  rez
-}
-
-rez <- bootstrap_similarity(df)
-```
-
-```{r}
-#| fig-width: 10
-#| fig-height: 10
-
-rez |>
-  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
-  filter(name %in% c("PSI", "RVadj", "SMI")) |>
-  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
-  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
-  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
-  facet_wrap(~Sample) +
-  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
-  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
-  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
-  theme_minimal()
-```
-
-```{r}
-#| fig-width: 10
-#| fig-height: 10
-#| eval: true
-
-p_sim <- rez |>
-  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
-  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
-  filter(Sample == "Random") |> 
-  ggplot(aes(x=value, y=name)) +
-  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
-  geom_vline(xintercept=0, linetype="dashed") +
-  labs(x="Similarity Difference", y="Indices of pattern difference",
-       title="To which matrix is the random one more similar?",
-       fill="More similar to") +
-  theme_minimal() +
-  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))
-
-r <- correlation::cor_sort(cor(byrandom))
-order <- colnames(r)
-
-make_corplot <- function(data, order) {
-  rownames_to_column(as.data.frame(cor(data)), "item") |> 
-    pivot_longer(-item) |> 
-    mutate(item = fct_relevel(item, order),
-           name = fct_relevel(name, order)) |>
-    ggplot(aes(x=name, y=item, fill=value)) +
-    geom_tile() +
-    # scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, values=c(-1, 0, 1)) +
-    scale_fill_gradientn(
-      colors=c("blue", "white", "#FFEE58", "#FFC107", "#FF9800", "#FF5722", 
-               "#F44336", "#E91E63", "#9C27B0", "#8231B4", "#673AB7", "white"), 
-      values=c(-1, seq(0, 1, 0.1))) +
-    theme_minimal() +
-    theme(axis.text = element_blank(),
-          axis.title = element_blank(),
-          legend.position = "none")
-}
-
-p1 <- make_corplot(byrandom, order) +
-  ggtitle("Grouped randomly")
-p2 <- make_corplot(byfacet, order) +
-  ggtitle("Grouped by facet")
-p3 <- make_corplot(bymodality, order) +
-  ggtitle("Grouped by modality")
-
-p1 / (p2 | p_sim | p3) + 
-  patchwork::plot_layout(heights=c(3, 1)) + 
-  patchwork::plot_annotation(
-    title="Effect of Item-presentation Grouping", 
-    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
-```
-
-## Item Selection
-
-### Unique Variable Analysis (UVA)
-
-```{r}
-#| fig-width: 10
-#| fig-height: 8
-
-uva <- EGAnet::UVA(items, cut.off = 0.25, reduce.method="remove", verbose=FALSE)
-
-toremove1 <- unique(uva$keep_remove$remove)
-keep <- uva$keep_remove$keep[!uva$keep_remove$keep %in% toremove1]
-
-sorted <- correlation::cor_sort(cor(items[toremove1],items[keep]))
-
-correlation::correlation(items[toremove1], items[keep]) |>
-  mutate(Parameter1 = fct_relevel(Parameter1, rownames(sorted)),
-         Parameter2 = fct_relevel(Parameter2, colnames(sorted))) |>
-  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
-  geom_tile() +
-  geom_text(aes(label=insight::format_value(r)), color="white") +
-  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, guide="none") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(x="Removed Items", y="Kept Items", fill="Correlation")
-```
-
-```{r}
-items <- select(items, -all_of(toremove1))
-byfacet <- select(byfacet, -all_of(toremove1))
-bymodality <- select(bymodality, -all_of(toremove1))
-byrandom <- select(byrandom, -all_of(toremove1))
+# TODO
 ```
@@
 ```
-
-```{r}
-#| fig-width: 12
-#| fig-height: 14
-#| fig-keep: "first"
-
-# plot(itemstability)
-```
-
-```{r}
-itemstability_table |>
-  select(-Cluster, -Max) |>
-  gt::gt() |>
-  gt::data_color(columns=-Item,
-                 method = "numeric",
-                 palette = c("white", "orange", "green"),
-                 domain = c(0, 1)) |>
-  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
-  gt::tab_header(
-    title = gt::md("**Item Stability**"),
-    subtitle = "Proportion of times an item is assigned to the same cluster"
-  ) |>
-  gt::fmt_number(columns=-Item, decimals=3)
-```
-
-```{r}
-items <- select(items, -all_of(toremove2))
-byfacet <- select(byfacet, -all_of(toremove2))
-bymodality <- select(bymodality, -all_of(toremove2))
-byrandom <- select(byrandom, -all_of(toremove2))
-```
-
-### Item Loadings
-
-```{r}
-#| eval: false
-
-ega2 <- bootEGA(
-  items,
-  EGA.type = "hierEGA",
-  model = "glasso",  # BGGM
-  algorithm = "leiden",  # walktrap
-  type="resampling",
-  plot.itemStability=FALSE,
-  typicalStructure=TRUE,
-  plot.typicalGraph=FALSE,
-  iter=500,
-  seed=3, ncores = 4)
-
-save(ega2, file="models/ega2.RData")
-```
-
-```{r}
-#| fig-width: 12
-#| fig-height: 14
-#| fig-keep: "first"
-
-load("models/ega2.RData")
-
-plot(itemStability(ega2, IS.plot=FALSE))
-
-# itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
-# toremove2 <- filter(itemstability_table, Max < 0.7)$Item
-```
-
-```{r}
-#| message: false
-
-lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)
-
-toremove3 <- lower$Item[!lower$Item %in% slice_max(lower, Max, n=3, by="Cluster")$Item]
-
-lower |>
-  select(-Cluster, -Max) |>
-  gt::gt() |>
-  gt::data_color(columns=-Item,
-                 method = "numeric",
-                 palette = c("red", "white", "green"),
-                 domain = c(-1, 1)) |>
-  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
-  gt::tab_header(
-    title = gt::md("**Item Loadings**"),
-    subtitle = "Node centrality"
-  ) |>
-  gt::fmt_number(columns=-Item, decimals=3)
-```
-
-```{r}
-items <- select(items, -all_of(toremove3))
-byfacet <- select(byfacet, -all_of(toremove3))
-bymodality <- select(bymodality, -all_of(toremove3))
-byrandom <- select(byrandom, -all_of(toremove3))
-```
-
-## Structure Analysis
-
-```{r}
-#| eval: false
-
-ega3 <- bootEGA(
-  items,
-  EGA.type = "hierEGA",
-  model = "glasso",  # BGGM
-  algorithm = "leiden",  # walktrap
-  type="resampling",
-  plot.itemStability=FALSE,
-  typicalStructure=TRUE,
-  plot.typicalGraph=TRUE,
-  iter=500,
-  seed=3, ncores = 4)
-
-save(ega3, file="models/ega3.RData")
-```
-
-```{r}
-#| fig-width: 12
-#| fig-height: 14
-#| fig-keep: "first"
-
-load("models/ega3.RData")
-
-plot(itemStability(ega3))
-```
-
-### Item Table
-
-```{r}
-#| message: false
-
-higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std))
-cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]
-
-lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) |>
-  select(names(higher)) |>
-  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
-  arrange(Cluster, desc(Max))
-
-higher$Item <- paste0("H", higher$Item)
-higher$Label <- paste("TODO", 1:nrow(higher))
-lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())
-
-rbind(higher, select(lower, -ID)) |>
-  datawizard::data_relocate("Label", after = "Item") |>
-  select(-Cluster, -Max) |>
-  # datawizard::data_rename(c(XC1 = "C01", XC2 = "C02")) |> 
-  gt::gt() |>
-  gt::tab_row_group(
-    label = "Items",
-    rows = 1:(nrow(lower) + nrow(higher))
-  ) |>
-  gt::tab_row_group(
-    label = "Metaclusters",
-    rows = 1:nrow(higher)
-  ) |>
-  gt::data_color(columns=-Item,
-                 method = "numeric",
-                 palette = c("red", "white", "green"),
-                 domain = c(-1, 1)) |>
-  gt::tab_style(
-    style = gt::cell_text(size="small", style="italic"),
-    locations = gt::cells_body(columns="Label")
-  ) |>
-  gt::tab_style(
-    style = list(gt::cell_text(weight="bold"),
-                 gt::cell_fill(color = "#F5F5F5")),
-    locations = list(
-      gt::cells_row_groups(groups = "Items"),
-      gt::cells_row_groups(groups = "Metaclusters")
-    )
-  ) |>
-  # Metacluster 1
-  gt::tab_style(
-    style = gt::cell_fill(color = "#B39DDB"),
-    locations = list(
-      gt::cells_column_labels(columns = 3),
-      gt::cells_body(columns="Item", rows=c(4:6))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#9FA8DA"),
-    locations = list(
-      gt::cells_column_labels(columns = 4),
-      gt::cells_body(columns="Item", rows=c(7:9))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#90CAF9"),
-    locations = list(
-      gt::cells_column_labels(columns = 5),
-      gt::cells_body(columns="Item", rows=c(1, 10:12))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#81D4FA"),
-    locations = list(
-      gt::cells_column_labels(columns = 6),
-      gt::cells_body(columns="Item", rows=c(13:15))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#80DEEA"),
-    locations = list(
-      gt::cells_column_labels(columns = 7),
-      gt::cells_body(columns="Item", rows=c(16:18))
-    )
-  ) |>
-  # Metacluster 2
-  gt::tab_style(
-    style = gt::cell_fill(color = "#F3F29D"),
-    locations = list(
-      gt::cells_column_labels(columns = 8),
-      gt::cells_body(columns="Item", rows=c(19:21))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#E6EE9C"),
-    locations = list(
-      gt::cells_column_labels(columns = 9),
-      gt::cells_body(columns="Item", rows=c(22:24))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#D6E8A1"),
-    locations = list(
-      gt::cells_column_labels(columns = 10),
-      gt::cells_body(columns="Item", rows=c(25:27))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#C5E1A5"),
-    locations = list(
-      gt::cells_column_labels(columns = 11),
-      gt::cells_body(columns="Item", rows=c(2, 28:30))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#B5DCA6"),
-    locations = list(
-      gt::cells_column_labels(columns = 12),
-      gt::cells_body(columns="Item", rows=c(31:33))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#A5D6A7"),
-    locations = list(
-      gt::cells_column_labels(columns = 13),
-      gt::cells_body(columns="Item", rows=c(34:36))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#93D1B6"),
-    locations = list(
-      gt::cells_column_labels(columns = 14),
-      gt::cells_body(columns="Item", rows=c(37:39))
-    )
-  ) |>
-  # Metacluster 3
-  gt::tab_style(
-    style = gt::cell_fill(color = "#CE93D8"),
-    locations = list(
-      gt::cells_column_labels(columns = 15),
-      gt::cells_body(columns="Item", rows=c(40:42))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#F48FB1"),
-    locations = list(
-      gt::cells_column_labels(columns = 16),
-      gt::cells_body(columns="Item", rows=c(43:45))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#EF9A9A"),
-    locations = list(
-      gt::cells_column_labels(columns = 17),
-      gt::cells_body(columns="Item", rows=c(3, 46:48))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#FFAB91"),
-    locations = list(
-      gt::cells_column_labels(columns = 18),
-      gt::cells_body(columns="Item", rows=c(49:51))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#FFCC80"),
-    locations = list(
-      gt::cells_column_labels(columns = 19),
-      gt::cells_body(columns="Item", rows=c(52:54))
-    )
-  ) |>
-  gt::tab_style(
-    style = gt::cell_fill(color = "#FFE082"),
-    locations = list(
-      gt::cells_column_labels(columns = 20),
-      gt::cells_body(columns="Item", rows=c(55:57))
-    )
-  ) |>
-  gt::fmt_number(columns=-Item, decimals=2) |>
-  gt::tab_header(
-    title = gt::md("**Item Loadings**"),
-    subtitle = "Node centrality"
-  ) |> 
-  gt::opt_vertical_padding(scale = 0.7) |>
-  gt::opt_horizontal_padding(scale = 0.5) |>
-  # gt::tab_options(table.width = gt::pct(100)) |> 
-  gt::cols_width(Label ~ gt::pct(30)) |>
-  gt::gtsave("table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
-```
-
-<object type="text/html" data="table1.html" width="120%" height="1000"></object>
-
-```{r}
-# REMOVE ONCE https://github.com/hfgolino/EGAnet/pull/167 is merged
-convert2tidygraph <- function(EGA.object)
-{
-
-  if("bootEGA" %in% class(EGA.object)) {
-    # Bootstrapped EGA ---
-    if(!"typicalGraph" %in% names(EGA.object)) {
-      stop("The bootEGA object must contain a typicalGraph object. Set `typicalStructure=TRUE`.")
-    }
-
-    if("lower_order" %in% names(EGA.object$typicalGraph)) {
-      # Hierarchical EGA ---
-      lower_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$lower_order$wc)
-      lower_nodes$dimension <- paste0("L", lower_nodes$dimension)  # Discriminate from higher
-      lower_nodes$level <- "Lower"
-      higher_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$higher_order$wc)
-      higher_nodes$name <- paste0("L", as.numeric(higher_nodes$name))
-      higher_nodes$dimension <- paste0("H", higher_nodes$dimension)  # Discriminate from lower
-      higher_nodes$level <- "Higher"
-      nodes <- rbind(lower_nodes, higher_nodes)
-
-      lower_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$lower_order$graph)
-      higher_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$higher_order$graph)
-      higher_edges$from <- paste0("L", as.numeric(higher_edges$from))
-      higher_edges$to <- paste0("L", as.numeric(higher_edges$to))
-      edges <- rbind(lower_edges, higher_edges)
-      edges$type <- "real"
-
-      # Make edges from lower to higher order
-      for(i in 1:nrow(lower_nodes)) {
-        edges <- rbind(
-          edges,
-          data.frame(from = lower_nodes$name[i], to = lower_nodes$dimension[i], link = 1, type = "virtual")
-          )
-      }
-    } else {
-      # Non-hierarchical EGA ---
-      nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$wc)
-      edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$graph)
-    }
-
-  } else {
-    # Normal EGA ---
-    nodes <- .convert2tidygraph_nodes(EGA.object$wc)
-    edges <- .convert2tidygraph_edges(EGA.object$network)
-  }
-
-  # Return result
-  return(
-    list(
-      nodes = nodes,
-      edges = edges[edges$link != 0,]
-    )
-  )
-}
-
-#' @keywords internal
-#' @noRd
-.convert2tidygraph_nodes <- function(wc){
-  data.frame(
-    name = names(wc),
-    dimension = as.character(wc)
-  )
-}
-
-#' @keywords internal
-#' @noRd
-.convert2tidygraph_edges <- function(network){
-  data.frame(
-    from = rep(rownames(network), times = ncol(network)),
-    to = rep(colnames(network), each = nrow(network)),
-    link = as.vector(network)
-  )
-}
-```
-
-### Graph
-
-```{r}
-#| fig-width: 9
-#| fig-height: 8
-#| warning: false
-
-graph <- convert2tidygraph(ega3)
-
-replace_lowernames <- function(names, lower) {
-  rownames(lower) <- lower$ID
-  sprintf("%02d", as.numeric(lower[names, "Item"]))
-}
-replace_highernames <- function(names) {
-  x <- as.numeric(str_remove(names, "L"))  
-  paste0("C", sprintf("%02d", x))
-}
-
-# Arrange lower nodes in circle
-lower_nodes <- graph$nodes |> 
-  filter(level == "Lower") |> 
-  mutate(name = fct_relevel(name, as.character(lower$ID)),
-         ID = name) |> 
-  arrange(name)  
-lower_edges <- graph$edges |> 
-  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
-lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
-  ggraph::create_layout(layout = 'circle')
-rownames(lower_layout) <- lower_nodes$name
-
-# Arrange higher nodes in circle
-higher_nodes <- graph$nodes |> 
-  filter(level == "Higher") |> 
-  mutate(ID = name,
-         name = replace_highernames(name),
-         name = fct_relevel(name, names(select(higher, -Item, -Cluster,-Max,-Label)))) |>
-  arrange(name)
-higher_edges <- graph$edges |> 
-  filter(from %in% higher_nodes$name & to %in% higher_nodes$name)
-higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
-  ggraph::create_layout(layout = 'circle')
-rownames(higher_layout) <- higher_nodes$ID
-
-# Put circles together
-layout <- tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |> 
-  ggraph::create_layout(layout = 'linear', circular = TRUE)
-layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", "name"], "x"]
-layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", "name"], "y"]
-layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", "name"], "x"] * 0.5
-layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", "name"], "y"] * 0.5
-layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", "name"], lower)
-layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", "name"])
-
-# layout$dimmension_label <- layout$dimension
-# layout[layout$level == "Higher", "dimmension_label"] <- NA
-
-# layout[layout$level == "Higher", "dimension"] <- layout[layout$level == "Higher", "dimension"]
-
-ggraph(layout) +
-  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
-  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
-  geom_node_point(aes(color=dimension, shape=level), size=12) +
-  geom_node_text(aes(label=name), fontface="bold") +
-  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
-  scale_edge_alpha(range = c(0, 0.9), guide="none") +
-  scale_edge_width(range = c(0.2, 3), guide="none") +
-  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
-                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
-  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
-  scale_color_manual(values=c(
-    "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
-    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
-    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
-    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
-                     breaks=c("H1", "H2", "H3")) +
-  theme_void() +
-  labs(color="Metaclusters")
-```
-
-### Model Comparison
-
-```{r}
-#| eval: false
-
-# EGAnet::EGM(items[, 1:60])
-EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
-rez <- EGAnet::network.compare(byfacet, bymodality, model = "glasso", seed=3)
-
-plot(rez)
-```
-
-## Empirical vs. Model Scores
-
-```{r}
-#| message: false
-
-# Modelbased scores
-scores <- EGAnet::net.scores(
-  items[names(ega3$typicalGraph$lower_order$wc)],
-  A=ega3$typicalGraph$lower_order$graph,
-  wc=ega3$typicalGraph$lower_order$wc)$scores$std.scores |>
-  as.data.frame()
-names(scores) <- paste0("C", names(scores))
-
-# Empirical scores
-clusters <- data.frame(Item = names(ega3$typicalGraph$lower_order$wc),
-                       Cluster = ega3$typicalGraph$lower_order$wc) |>
-  mutate(Cluster = paste0("E", sprintf("%02d", Cluster)))
-
-empirical <- data.frame(Participant=df$Participant)
-for(c in unique(clusters$Cluster)) {
-  s <- rowMeans(items[clusters[clusters$Cluster==c, "Item"]])
-  empirical <- cbind(empirical, setNames(data.frame(x = s), c))
-}
-
-correlation::correlation(empirical, scores) |>
-  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
-  geom_tile() +
-  geom_text(aes(label=sprintf("%.2f", r)), size=3) +
-  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
-  labs(x="Empirical Scores", y="Model Scores") +
-  theme_minimal()
-```

### 2025-02-04 study2/analysis/preprocessing.R

@@ -6,7 +6,41 @@ library(progress)
 # path <- "C:/Users/maisi/Box/InteroceptionScale/study2"
 path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
 
-# JsPsych experiment ------------------------------------------------------
+
+
+# Convenience Functions ---------------------------------------------------
+
+convert_feet_to_meters <- function(height) {
+  # Remove extra spaces and quotes
+  height <- trimws(gsub("\"", "", height))
+
+  # Error if warning during as.numeric
+  options(warn = 2)
+
+
+  # Handle integer input like "6" (assume feet only, zero inches)
+  if (grepl("^\\d+$", height)) {
+    feet <- as.numeric(height)
+    inches <- 0
+  } else {
+    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-"
+    parts <- unlist(strsplit(height, "[ ' .,\\-]"))
+
+    # Extract feet and inches
+    feet <- as.numeric(parts[1])
+    inches <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
+  }
+
+  # Retsore default warning behavior
+  options(warn = 0)
+
+  # Convert to meters (1 foot = 0.3048 m, 1 inch = 0.0254 m)
+  feet * 0.3048 + inches * 0.0254
+}
+
+
+# Run loop ----------------------------------------------------------------
+
 
 files <- list.files(path, pattern = "*.csv")
 
@@ -46,6 +80,9 @@ for (file in files) {
   # Demographics
   resp <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
 
+  data_ppt$Gender <- ifelse(!is.null(resp$Gender), resp$Gender, NA)
+  data_ppt$Age <- ifelse(!is.null(resp$Age), resp$Age, NA)
+
   # Education
   data_ppt$Education <- ifelse(resp$Education == "other", resp$`Education-Comment`, resp$Education)
 
@@ -57,8 +94,8 @@ for (file in files) {
   data_ppt$Ethnicity <- ifelse(resp$Ethnicity == "other", resp$`Ethnicity-Comment`, resp$Ethnicity)
 
   # BMI
[…]

### 2025-02-04 study2/experiment/questionnaires_mint.js
updated item on mint questionnaire

@@ -46,7 +46,7 @@ const items_mint = {
     InteroceptiveFailures_12: "I often check the smell of my farts",
     InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
     InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
-    InteroceptiveFailures_15: "I don't always feel the need to urinate until my bladder is very full",
+    InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
     InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
     InteroceptiveSensitivityPleasure_2: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
     InteroceptiveSensitivityPleasure_3: "My genital organs are very sensitive to pleasant stimulations",

### 2025-02-04 study2sona/experiment/questionnaires_mint.js

@@ -57,7 +57,7 @@ const items_mint = {
     InteroceptiveFailures_12: "I often check the smell of my farts",
     InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
     InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
-    InteroceptiveFailures_15: "I don't always feel the need to urinate until my bladder is very full",
+    InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
     InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
     InteroceptiveSensitivityPleasure_2: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
     InteroceptiveSensitivityPleasure_3: "My genital organs are very sensitive to pleasant stimulations",

### 2025-02-04 study2/analysis/2_analysis.qmd
Big changes
1) update items based on latest discussions
2) change keys of items to match dimensions on the table.html
3) added labels to the new items (analysis.qmd)

TODO
1. updated pre-processing

@@
 
+-   items commneted out - need to decide if keep or not
+
 ```{r}
 labels <- list(
+  MINT_Deficit_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+  MINT_Deficit_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
+  MINT_Deficit_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
   MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-  MINT_Deficit_CaCo_5 =  "I often feel like I can't get enough oxygen by breathing normally"
-)
-# TODO
+  MINT_Deficit_CaCo_5 = "I often feel like I can't get enough oxygen by breathing normally",
+  MINT_Deficit_CaCo_6 = "Sometimes my heart starts racing and I often don't know why",
+  MINT_Deficit_CaNo_7 = "I often only notice how I am breathing when it becomes loud",
+  MINT_Deficit_CaNo_8 = "I only notice my heart when it is thumping in my chest",
+  MINT_Deficit_CaNo_9 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+  MINT_Deficit_Olfa_10 = "I often check the smell of my armpits",
+  MINT_Deficit_Olfa_11 = "I often check the smell of my own breath",
+  MINT_Deficit_Olfa_12 = "I often check the smell of my farts",
+  #MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
+  #MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
+  #MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
+  # MINT_Awareness_SexA_16 = "I always feel in my body if I am sexually aroused",
+  # MINT_Awareness_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
+  # MINT_Awareness_SexA_18 = "I always know when I am sexually aroused",
+  MINT_Awareness_SexS_19 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
+  MINT_Awareness_SexS_20 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
+  MINT_Awareness_SexS_21 = "My genital organs are very sensitive to pleasant stimulations",
+  MINT_Awareness_SexO_22 = "In general, I am very sensitive to changes in my genital organs",
+  MINT_Awareness_SexO_23 = "I can notice even very subtle changes in the state of my genital organs",
+  MINT_Awareness_SexO_24 = "I am always very aware of the state of my genital organs, even when I am calm",
+  MINT_Awareness_UrSe_25 = "In general, I am very aware of the sensations that are happening when I am urinating",
+  MINT_Awareness_UrSe_26 = "In general, I am very aware of the sensations that are happening when I am defecating",
+  MINT_Awareness_UrSe_27 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
+  MINT_Awareness_RelA_28 = "I always know when I am relaxed",
+  MINT_Awareness_RelA_29 = "I always feel in my body if I am relaxed",
+  MINT_Awareness_RelA_30 = "My body is always in the same specific state when I am relaxed",
+  MINT_Awareness_StaS_31 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
+  MINT_Awareness_StaS_32 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
+  MINT_Awareness_StaS_33 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
+  MINT_Awareness_ExAc_34 = "I can always accurately feel when I am about to burp",
+  MINT_Awareness_ExAc_35 = "I can always accurately feel when I am about to fart",
+  MINT_Awareness_ExAc_36 = "I can always accurately feel when I am about to sneeze",
+  MINT_Sensitivity_Card_37 = "In general, I am very sensitive to changes in my heart rate",
+  MINT_Sensitivity_Card_38 = "I can notice even very subtle changes in the way my heart beats",
+  MINT_Sensitivity_Card_39 = "I often notice changes in my heart rate",
+  MINT_Sensitivity_Resp_40 = "I can notice even very subtle changes in my breathing",
+  MINT_Sensitivity_Resp_41 = "I am always very aware of how I am breathing, even when I am calm",
+  MINT_Sensitivity_Resp_42 = "In general, I am very sensitive to changes in my breathing",
+  # MINT_Sensitivity_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
+  # MINT_Sensitivity_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
+  # MINT_Sensitivity_Sign_45 = "When something important is happening in my life, I can feel it in my body",
+  MINT_Sensitivity_Gast_46 = "I can notice even very subtle changes in what my stomach is doing",
+  MINT_Sensitivity_Gast_47 = "In general, I am very sensitive to what my stomach is doing",
+  MINT_Sensitivity_Gast_48 = "I am always very aware of what my stomach is doing, even when I am calm",
+  MINT_Sensitivity_Derm_49 = "In general, my skin is very sensitive",
+  MINT_Sensitivity_Derm_50 = "My skin is susceptible to itchy fabrics and materials",
+  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
+  # MINT_Sensitivity_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  # MINT_Sensitivity_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
+  MINT_AttentionCheck_1 = "I can always accurately answer to the extreme left on this question to show that I am reading it")
 ```

### 2025-02-04 study2/analysis/preprocessing.R

@@ -4,7 +4,8 @@ library(progress)
 # path for data
 
 # path <- "C:/Users/maisi/Box/InteroceptionScale/study2"
-path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
+# path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
+path <- "C:/Users/asf25/Box/InteroceptionScale/"
 
 
 
@@ -110,7 +111,20 @@ for (file in files) {
     dplyr::rename(MINT_Deficit_CaCo_4 = InteroceptiveFailures_1,
                   MINT_Deficit_CaCo_5 = InteroceptiveFailures_2,
                   MINT_Deficit_CaCo_6 = InteroceptiveFailures_3,
-                  MINT_Deficit_UrIn_1 = InteroceptiveFailures_4)
+                  MINT_Deficit_UrIn_1 = InteroceptiveFailures_4,
+                  MINT_Deficit_Urin_2 = InteroceptiveFailures_5,
+                  MINT_Deficit_Urin_3 = InteroceptiveFailures_6,
+                  MINT_Deficit_CaNo_7 = InteroceptiveFailures_7, 
+                  MINT_Deficit_CaNo_8 = InteroceptiveFailures_8, 
+                  MINT_Deficit_CaNo_9  = InteroceptiveFailures_9,
+                  MINT_Deficit_Olfa_11 = InteroceptiveFailures_10,
+                  MINT_Deficit_Olfa_10 = InteroceptiveFailures_11,
+                  MINT_Deficit_Olfa_12 = InteroceptiveFailures_12,
+                  MINT_Deficit_Sati_15 = InteroceptiveFailures_13,
+                  MINT_Deficit_Sati_13 = InteroceptiveFailures_14,
+                  MINT_Deficit_Sati_14 = InteroceptiveFailures_14,) # does not match the table 
+                  MINT_Awareness_SexS_19 = InteroceptiveSensitivityPleasure_1, 
+                  
   # TODO
 
   data_ppt <- cbind(data_ppt, as.data.frame(mint))

### 2025-02-04 study2/experiment/OldScaleItems.py

@@ -1,0 +1,42 @@
+// Items from the old experiment scripts and their mapping to the new interoceptive dimensions from table.html 
+
+MINT_Deficit_CaCo_4 = InteroceptiveFailures_1: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+MINT_Deficit_CaCo_5 = InteroceptiveFailures_2: "I often feel like I can't get enough oxygen by breathing normally",
+MINT_Deficit_CaCo_6 = InteroceptiveFailures_3: "Sometimes my heart starts racing and I often don't know why",
+INT_Deficit_Urin_1 = InteroceptiveFailures_4: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+MINT_Deficit_Urin_2 = InteroceptiveFailures_5: "I often feel the need to urinate even when my bladder is not full",
+MINT_Deficit_Urin_3 = InteroceptiveFailures_6: "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+MINT_Deficit_CaNo_7 = InteroceptiveFailures_7: "I often only notice how I am breathing when it becomes loud",
+MINT_Deficit_CaNo_8 = InteroceptiveFailures_8: "I only notice my heart when it is thumping in my chest",
+MINT_Deficit_CaNo_9 = InteroceptiveFailures_9: "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+MINT_Deficit_Olfa_11 = InteroceptiveFailures_10: "I often check the smell of my own breath",
+MINT_Deficit_Olfa_10 = InteroceptiveFailures_11: "I often check the smell of my armpits",
+MINT_Deficit_Olfa_12 = InteroceptiveFailures_12: "I often check the smell of my farts",
+# MINT_Deficit_Sati_15 = InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
+# MINT_Deficit_Sati_13 = InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
+# MINT_Deficit_Sati_14 = InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
+MINT_Awareness_SexS_19 = InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
[…]

### 2025-02-04 study2/experiment/questionnaires_mint.js

@@ -32,45 +32,60 @@ const questionnaires_instructions = {
 
 // Items ================================================
 const items_mint = {
-    InteroceptiveFailures_1: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-    InteroceptiveFailures_2: "I often feel like I can't get enough oxygen by breathing normally",
-    InteroceptiveFailures_3: "Sometimes my heart starts racing and I often don't know why",
-    InteroceptiveFailures_4: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-    InteroceptiveFailures_5: "I often feel the need to urinate even when my bladder is not full",
-    InteroceptiveFailures_6: "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-    InteroceptiveFailures_7: "I often only notice how I am breathing when it becomes loud",
-    InteroceptiveFailures_8: "I only notice my heart when it is thumping in my chest",
-    InteroceptiveFailures_9: "I often only notice how I am breathing when my breathing becomes shallow or irregular",
-    InteroceptiveFailures_10: "I often check the smell of my own breath",
-    InteroceptiveFailures_11: "I often check the smell of my armpits",
-    InteroceptiveFailures_12: "I often check the smell of my farts",
-    InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
-    InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
-    InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
-    InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
-    InteroceptiveSensitivityPleasure_2: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
-    InteroceptiveSensitivityPleasure_3: "My genital organs are very sensitive to pleasant stimulations",
-    InteroceptiveSensitivityPleasure_4: "I always feel it in my body if I am sexually aroused",
-    InteroceptiveSensitivityPleasure_5: "I always know when I am sexually aroused",
-    InteroceptiveSensitivityPleasure_6: "I can always tell that I am sexually aroused from the way I feel inside",
[…]

### 2025-02-04 study2sona/experiment/questionnaires_mint.js

@@ -43,45 +43,60 @@ const questionnaires_instructions = {
 
 // Items ================================================
 const items_mint = {
-    InteroceptiveFailures_1: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-    InteroceptiveFailures_2: "I often feel like I can't get enough oxygen by breathing normally",
-    InteroceptiveFailures_3: "Sometimes my heart starts racing and I often don't know why",
-    InteroceptiveFailures_4: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-    InteroceptiveFailures_5: "I often feel the need to urinate even when my bladder is not full",
-    InteroceptiveFailures_6: "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-    InteroceptiveFailures_7: "I often only notice how I am breathing when it becomes loud",
-    InteroceptiveFailures_8: "I only notice my heart when it is thumping in my chest",
-    InteroceptiveFailures_9: "I often only notice how I am breathing when my breathing becomes shallow or irregular",
-    InteroceptiveFailures_10: "I often check the smell of my own breath",
-    InteroceptiveFailures_11: "I often check the smell of my armpits",
-    InteroceptiveFailures_12: "I often check the smell of my farts",
-    InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
-    InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
-    InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
-    InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
-    InteroceptiveSensitivityPleasure_2: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
-    InteroceptiveSensitivityPleasure_3: "My genital organs are very sensitive to pleasant stimulations",
-    InteroceptiveSensitivityPleasure_4: "I always feel it in my body if I am sexually aroused",
-    InteroceptiveSensitivityPleasure_5: "I always know when I am sexually aroused",
-    InteroceptiveSensitivityPleasure_6: "I can always tell that I am sexually aroused from the way I feel inside",
[…]

### 2025-02-05 study2/experiment/questionnaires_mint.js
add notes, add Sati @AnafNeves

@@ -31,6 +31,10 @@ const questionnaires_instructions = {
 }
 
 // Items ================================================
+// We dropped the following dimensions:
+// - Awareness_SexA: too high level and abstract compared to other items.
+// - Sensitivity_Sign: Potentially ambiguous nature of "something important"
+// - Sensitivity_SexC: Less consistent with the other dimensions of Sensitivity that were about different modalities
 const items_mint = {
     MINT_Deficit_Urin_1: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
     MINT_Deficit_Urin_2: "I often feel the need to urinate even when my bladder is not full",
@@ -44,14 +48,15 @@ const items_mint = {
     MINT_Deficit_Olfa_10: "I often check the smell of my armpits",
     MINT_Deficit_Olfa_11: "I often check the smell of my own breath",
     MINT_Deficit_Olfa_12: "I often check the smell of my farts",
-    // MINT_Deficit_Sati_13: "I don't always feel the need to eat until I am really hungry",
-    // MINT_Deficit_Sati_14: "Sometimes I don't realise I was hungry until I ate something",
-    // MINT_Deficit_Sati_15: "I don't always feel the need to drink until I am really thirsty",
+    MINT_Deficit_Sati_13: "I don't always feel the need to eat until I am really hungry",
+    MINT_Deficit_Sati_14: "Sometimes I don't realise I was hungry until I ate something",
+    MINT_Deficit_Sati_15: "I don't always feel the need to drink until I am really thirsty",
     // MINT_Awareness_SexA_16: "I always feel in my body if I am sexually aroused",
     // MINT_Awareness_SexA_17: "I can always tell that I am sexually aroused from the way I feel inside",
     // MINT_Awareness_SexA_18: "I always know when I am sexually aroused",
     MINT_Awareness_SexS_19: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
-    MINT_Awareness_SexS_20: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
+    MINT_Awareness_SexS_20:
+        "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
     MINT_Awareness_SexS_21: "My genital organs are very sensitive to pleasant stimulations",
     MINT_Awareness_SexO_22: "In general, I am very sensitive to changes in my genital organs",
[…]

### 2025-02-05 study2/experiment/questionnaires_mint.js
Update questionnaires_mint.js

@@ -32,9 +32,9 @@ const questionnaires_instructions = {
 
 // Items ================================================
 // We dropped the following dimensions:
-// - Awareness_SexA: too high level and abstract compared to other items.
-// - Sensitivity_Sign: Potentially ambiguous nature of "something important"
-// - Sensitivity_SexC: Less consistent with the other dimensions of Sensitivity that were about different modalities
+// - Awareness_SexA: too high level and abstract ("in my body") compared to other items
+// - Sensitivity_Sign: Potentially ambiguous phrasing of "something important"
+// - Sensitivity_SexC: Less consistent with the other dimensions of Sensitivity that are about different modalities
 const items_mint = {
     MINT_Deficit_Urin_1: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
     MINT_Deficit_Urin_2: "I often feel the need to urinate even when my bladder is not full",

### 2025-02-05 study2/analysis/preprocessing.R
Update preprocessing.R

@@ -1,11 +1,12 @@
 library(jsonlite)
 library(progress)
 
-# path for data
+
+options(warn = 2)  # Stop on warnings
 
 # path <- "C:/Users/maisi/Box/InteroceptionScale/study2"
-# path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
-path <- "C:/Users/asf25/Box/InteroceptionScale/"
+path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
+# path <- "C:/Users/asf25/Box/InteroceptionScale/"
 
 
 
@@ -15,28 +16,41 @@ convert_feet_to_meters <- function(height) {
   # Remove extra spaces and quotes
   height <- trimws(gsub("\"", "", height))
 
-  # Error if warning during as.numeric
-  options(warn = 2)
-
-
   # Handle integer input like "6" (assume feet only, zero inches)
   if (grepl("^\\d+$", height)) {
     feet <- as.numeric(height)
     inches <- 0
   } else {
-    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-"
-    parts <- unlist(strsplit(height, "[ ' .,\\-]"))
+    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " ft "
+    parts <- unlist(strsplit(height, "[ ' .,\\-]| ft "))
 
     # Extract feet and inches
     feet <- as.numeric(parts[1])
     inches <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
   }
 
-  # Retsore default warning behavior
-  options(warn = 0)
-
   # Convert to meters (1 foot = 0.3048 m, 1 inch = 0.0254 m)
   feet * 0.3048 + inches * 0.0254
+}
+
+convert_stones_to_kg <- function(weight) {
+  weight <- trimws(gsub("\"", "", weight))
+
+  # Handle integer input like "6" (assume stones only, zero pounds)
+  if (grepl("^\\d+$", weight)) {
+    stones <- as.numeric(weight)
+    pounds <- 0
+  } else {
+    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " st "
+    parts <- unlist(strsplit(weight, "[ ' .,\\-]| st "))
+
+    # Extract stones and pounds
+    stones <- as.numeric(parts[1])
[…]

### 2025-02-05 study2/analysis/preprocessing.R
Update preprocessing.R

@@ -22,7 +22,7 @@ convert_feet_to_meters <- function(height) {
     inches <- 0
   } else {
     # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " ft "
-    parts <- unlist(strsplit(height, "[ ' .,\\-]| ft "))
+    parts <- unlist(strsplit(height, "[ ' .,’\\-]| ft "))
 
     # Extract feet and inches
     feet <- as.numeric(parts[1])
@@ -122,7 +122,22 @@ for (file in files) {
   data_ppt$Experiment_Feedback <- ifelse(is.null(feedback$Feedback_Text), NA, feedback$Feedback_Text)
 
   # Mint questionnaire
-  # mint <- as.data.frame(jsonlite::fromJSON(rawdata[rawdata$screen == "questionnaire_mint", "response"])) |>
+  mint <- as.data.frame(jsonlite::fromJSON(rawdata[rawdata$screen == "questionnaire_mint", "response"]))
+  if("InteroceptiveFailures_1" %in% colnames(mint)){
+    data_ppt$MINT_Deficit_CaCo_4 <- mint$InteroceptiveFailures_1
+    data_ppt$MINT_Deficit_CaCo_5 <- mint$InteroceptiveFailures_2
+    data_ppt$MINT_Deficit_CaCo_6 <- mint$InteroceptiveFailures_3
+    data_ppt$MINT_Deficit_UrIn_1 <- mint$InteroceptiveFailures_4
+    data_ppt$MINT_Deficit_Urin_2 <- mint$InteroceptiveFailures_5
+    data_ppt$MINT_Deficit_Urin_3 <- mint$InteroceptiveFailures_6
+    data_ppt$MINT_Deficit_CaNo_7 <- mint$InteroceptiveFailures_7
+    data_ppt$MINT_Deficit_CaNo_8 <- mint$InteroceptiveFailures_8
+    data_ppt$MINT_Deficit_CaNo_9 <- mint$InteroceptiveFailures_9
+    data_ppt$MINT_Deficit_Olfa_11 <- mint$InteroceptiveFailures_11
+  } else {
+    stop("Not MINT")
+  }
+
   #   dplyr::rename(MINT_Deficit_CaCo_4 = InteroceptiveFailures_1,
   #                 MINT_Deficit_CaCo_5 = InteroceptiveFailures_2,
   #                 MINT_Deficit_CaCo_6 = InteroceptiveFailures_3,
[…]

### 2025-02-05 study2/analysis/preprocessing.R
renamed old items to the new ones

@@ -134,10 +134,37 @@ for (file in files) {
     data_ppt$MINT_Deficit_CaNo_8 <- mint$InteroceptiveFailures_8
     data_ppt$MINT_Deficit_CaNo_9 <- mint$InteroceptiveFailures_9
     data_ppt$MINT_Deficit_Olfa_11 <- mint$InteroceptiveFailures_11
+    data_ppt$MINT_Deficit_Olfa_12 <- mint$InteroceptiveFailures_12
+    data_ppt$MINT_Deficit_Sati_15 <- mint$InteroceptiveFailures_13
+    data_ppt$MINT_Deficit_Sati_13 <- mint$InteroceptiveFailures_14
+    data_ppt$MINT_Deficit_Sati_14 <- mint$InteroceptiveFailures_15
+    data_ppt$MINT_Awareness_SexS_19 <- mint$InteroceptiveSensitivityPleasure_1
+    data_ppt$MINT_Awareness_SexS_20 <- mint$InteroceptiveSensitivityPleasure_2
+    data_ppt$MINT_Awareness_SexS_21 <- mint$InteroceptiveSensitivityPleasure_3
+    data_ppt$MINT_Extra_1 <- mint$InteroceptiveSensitivityPleasure_4
+    data_ppt$MINT_Awareness_SexA_18 <- mint$InteroceptiveSensitivityPleasure_5 # not on the final items
+    data_ppt$MINT_Awareness_SexA_17 <- mint$InteroceptiveSensitivityPleasure_6 # not on the final items
+    data_ppt$MINT_Awareness_StaS_31 <- mint$InteroceptiveSensitivityPleasure_7
+    data_ppt$MINT_Awareness_StaS_33 <- mint$InteroceptiveSensitivityPleasure_8
+    data_ppt$MINT_Awareness_StaS_32 <- mint$InteroceptiveSensitivityPleasure_9
+    data_ppt$MINT_Awareness_ExAc_36 <- mint$InteroceptiveSensitivityPleasure_10
+    data_ppt$MINT_Extra_2 <- mint$nteroceptiveSensitivityPleasure_11
+    data_ppt$MINT_Awareness_ExAc_34 <- mint$InteroceptiveSensitivityPleasure_12
+    data_ppt$MINT_Sensitivity_Derm_50 <- mint$InteroceptiveSensitivityPleasure_13
+    data_ppt$MINT_Extra_3 <- mint$InteroceptiveSensitivityPleasure_14
[…]

### 2025-02-05 study2/analysis/preprocessing.R
Update preprocessing.R

@@ -142,26 +142,26 @@ for (file in files) {
     data_ppt$MINT_Awareness_SexS_20 <- mint$InteroceptiveSensitivityPleasure_2
     data_ppt$MINT_Awareness_SexS_21 <- mint$InteroceptiveSensitivityPleasure_3
     data_ppt$MINT_Extra_1 <- mint$InteroceptiveSensitivityPleasure_4
-    data_ppt$MINT_Awareness_SexA_18 <- mint$InteroceptiveSensitivityPleasure_5 # not on the final items
-    data_ppt$MINT_Awareness_SexA_17 <- mint$InteroceptiveSensitivityPleasure_6 # not on the final items
+    data_ppt$MINT_Extra_2 <- mint$InteroceptiveSensitivityPleasure_5
+    data_ppt$MINT_Extra_3 <- mint$InteroceptiveSensitivityPleasure_6
     data_ppt$MINT_Awareness_StaS_31 <- mint$InteroceptiveSensitivityPleasure_7
     data_ppt$MINT_Awareness_StaS_33 <- mint$InteroceptiveSensitivityPleasure_8
     data_ppt$MINT_Awareness_StaS_32 <- mint$InteroceptiveSensitivityPleasure_9
     data_ppt$MINT_Awareness_ExAc_36 <- mint$InteroceptiveSensitivityPleasure_10
-    data_ppt$MINT_Extra_2 <- mint$nteroceptiveSensitivityPleasure_11
+    data_ppt$MINT_Extra_4 <- mint$nteroceptiveSensitivityPleasure_11
     data_ppt$MINT_Awareness_ExAc_34 <- mint$InteroceptiveSensitivityPleasure_12
     data_ppt$MINT_Sensitivity_Derm_50 <- mint$InteroceptiveSensitivityPleasure_13
-    data_ppt$MINT_Extra_3 <- mint$InteroceptiveSensitivityPleasure_14
+    data_ppt$MINT_Extra_5 <- mint$InteroceptiveSensitivityPleasure_14
     data_ppt$MINT_Sensitivity_Derm_51 <- mint$InteroceptiveSensitivityPleasure_15
     data_ppt$MINT_Sensitivity_Resp_40 <- mint$InteroceptiHypervigilance_1
     data_ppt$MINT_Sensitivity_Resp_42 <- mint$InteroceptiHypervigilance_2
[…]

### 2025-02-05 study2/experiment/OldScaleItems.py
minor

@@ -1,4 +1,4 @@
-// Items from the old experiment scripts and their mapping to the new interoceptive dimensions from table.html 
+# Items from the old experiment scripts and their mapping to the new interoceptive dimensions from table.html 
 
 MINT_Deficit_CaCo_4 = InteroceptiveFailures_1: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
 MINT_Deficit_CaCo_5 = InteroceptiveFailures_2: "I often feel like I can't get enough oxygen by breathing normally",
@@ -12,9 +12,9 @@ MINT_Deficit_CaNo_9 = InteroceptiveFailures_9: "I often only notice how I am bre
 MINT_Deficit_Olfa_11 = InteroceptiveFailures_10: "I often check the smell of my own breath",
 MINT_Deficit_Olfa_10 = InteroceptiveFailures_11: "I often check the smell of my armpits",
 MINT_Deficit_Olfa_12 = InteroceptiveFailures_12: "I often check the smell of my farts",
-# MINT_Deficit_Sati_15 = InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
-# MINT_Deficit_Sati_13 = InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
-# MINT_Deficit_Sati_14 = InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
+MINT_Deficit_Sati_15 = InteroceptiveFailures_13: "I don't always feel the need to drink until I am really thirsty",
+MINT_Deficit_Sati_13 = InteroceptiveFailures_14: "I don't always feel the need to eat until I am really hungry",
+MINT_Deficit_Sati_14 = InteroceptiveFailures_15: "Sometimes I don't realise I was hungry until I ate something",
 MINT_Awareness_SexS_19 = InteroceptiveSensitivityPleasure_1: "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
 MINT_Awareness_SexS_20 = InteroceptiveSensitivityPleasure_2: "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
 MINT_Awareness_SexS_21 = InteroceptiveSensitivityPleasure_3: "My genital organs are very sensitive to pleasant stimulations",

### 2025-02-05 study2/experiment/questionnaires_mint.js
minor

@@ -36,65 +36,100 @@ const questionnaires_instructions = {
 // - Sensitivity_Sign: Potentially ambiguous phrasing of "something important"
 // - Sensitivity_SexC: Less consistent with the other dimensions of Sensitivity that are about different modalities
 const items_mint = {
-    MINT_Deficit_Urin_1: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-    MINT_Deficit_Urin_2: "I often feel the need to urinate even when my bladder is not full",
-    MINT_Deficit_Urin_3: "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-    MINT_Deficit_CaCo_4: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-    MINT_Deficit_CaCo_5: "I often feel like I can't get enough oxygen by breathing normally",
-    MINT_Deficit_CaCo_6: "Sometimes my heart starts racing and I often don't know why",
-    MINT_Deficit_CaNo_7: "I often only notice how I am breathing when it becomes loud",
-    MINT_Deficit_CaNo_8: "I only notice my heart when it is thumping in my chest",
-    MINT_Deficit_CaNo_9: "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+    MINT_Deficit_Urin_1:
+        "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+    MINT_Deficit_Urin_2:
+        "I often feel the need to urinate even when my bladder is not full",
+    MINT_Deficit_Urin_3:
+        "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+    MINT_Deficit_CaCo_4:
+        "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+    MINT_Deficit_CaCo_5:
+        "I often feel like I can't get enough oxygen by breathing normally",
+    MINT_Deficit_CaCo_6:
+        "Sometimes my heart starts racing and I often don't know why",
+    MINT_Deficit_CaNo_7:
+        "I often only notice how I am breathing when it becomes loud",
+    MINT_Deficit_CaNo_8:
+        "I only notice my heart when it is thumping in my chest",
+    MINT_Deficit_CaNo_9:
+        "I often only notice how I am breathing when my breathing becomes shallow or irregular",
[…]

### 2025-02-05 study2sona/experiment/questionnaires_mint.js

@@ -32,7 +32,7 @@ const questionnaires_instructions = {
                         {
                             type: "html",
                             name: "Instructions",
-                            html: text
+                            html: text,
                         },
                     ],
                 },
@@ -42,62 +42,105 @@ const questionnaires_instructions = {
 }
 
 // Items ================================================
+// We dropped the following dimensions:
+// - Awareness_SexA: too high level and abstract ("in my body") compared to other items
+// - Sensitivity_Sign: Potentially ambiguous phrasing of "something important"
+// - Sensitivity_SexC: Less consistent with the other dimensions of Sensitivity that are about different modalities
 const items_mint = {
-    MINT_Deficit_Urin_1: "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-    MINT_Deficit_Urin_2: "I often feel the need to urinate even when my bladder is not full",
-    MINT_Deficit_Urin_3: "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-    MINT_Deficit_CaCo_4: "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-    MINT_Deficit_CaCo_5: "I often feel like I can't get enough oxygen by breathing normally",
-    MINT_Deficit_CaCo_6: "Sometimes my heart starts racing and I often don't know why",
-    MINT_Deficit_CaNo_7: "I often only notice how I am breathing when it becomes loud",
-    MINT_Deficit_CaNo_8: "I only notice my heart when it is thumping in my chest",
-    MINT_Deficit_CaNo_9: "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+    MINT_Deficit_Urin_1:
+        "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+    MINT_Deficit_Urin_2:
+        "I often feel the need to urinate even when my bladder is not full",
+    MINT_Deficit_Urin_3:
+        "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+    MINT_Deficit_CaCo_4:
+        "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+    MINT_Deficit_CaCo_5:
+        "I often feel like I can't get enough oxygen by breathing normally",
+    MINT_Deficit_CaCo_6:
[…]

### 2025-02-05 study2sona/experiment/demographics.js
updated ethics number

@@ -45,7 +45,7 @@ const ConsentForm = {
         // End
         text +=
             "<li align='left'>By participating, you agree to follow the instructions and provide honest answers. If you do not wish to participate or if you don't have the time, simply close your browser.</li></p>" +
-            "<p align='left'><br><sub><sup>For further information about this research, or if you have any concerns, please contact Dr Dominique Makowski (<i style='color:DodgerBlue;'>D.Makowski@sussex.ac.uk</i>) and/or Ana Neves (<i style='color:DodgerBlue;'>A.Neves@sussex.ac.uk</i>). This research has been approved (ER/EB672/2) by the Sciences & Technology Cross-Schools Research Ethics Committee (C-REC) (<i style='color:DodgerBlue;'>crecscitec@sussex.ac.uk</i>). The University of Sussex has insurance in place to cover its legal liabilities in respect of this study.</sup></sub></p>"
+            "<p align='left'><br><sub><sup>For further information about this research, or if you have any concerns, please contact Dr Dominique Makowski (<i style='color:DodgerBlue;'>D.Makowski@sussex.ac.uk</i>) and/or Ana Neves (<i style='color:DodgerBlue;'>A.Neves@sussex.ac.uk</i>). This research has been approved (ER/EB672/3) by the Sciences & Technology Cross-Schools Research Ethics Committee (C-REC) (<i style='color:DodgerBlue;'>crecscitec@sussex.ac.uk</i>). The University of Sussex has insurance in place to cover its legal liabilities in respect of this study.</sup></sub></p>"
 
         // Return Survey
         return {
@@ -240,7 +240,8 @@ var demographic_questions = {
                     //     otherPlaceholder: "Please specify",
                     // },
                     {
-                        visibleIf: "{Education} == 'High school' || {Education} == 'Master' || {Education} == 'Bachelor'",
+                        visibleIf:
+                            "{Education} == 'High school' || {Education} == 'Master' || {Education} == 'Bachelor'",
                         title: "Are you currently a student?",
                         name: "Student",
                         type: "boolean",
@@ -362,7 +363,8 @@ var demographics_wearables = {
             {
                 elements: [
                     {
-                        visibleIf: "{Wearables_Ownership} contains 'Heart rate'",
+                        visibleIf:
+                            "{Wearables_Ownership} contains 'Heart rate'",
                         title: "How often do you check your heart rate?",
                         name: "Wearables_Heart",
                         type: "rating",
[…]

### 2025-02-05 study2/experiment/postprocessing.js
fixed AC @AnafNeves

@@ -11,7 +11,7 @@ function check_attentionchecks() {
 
     // compute scores for tas) }).values()[0].response
     let data_tas = get_screen("questionnaire_tas")
-    let tas_score_A = 1 - (data_tas["TAS_AttentionCheck_1"] - 1) / 4
+    let tas_score_A = (data_tas["TAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for pi18
     let data_pi = get_screen("questionnaire_pi18")

### 2025-02-05 study2/experiment/postprocessing.js
restore @AnafNeves

@@ -11,7 +11,7 @@ function check_attentionchecks() {
 
     // compute scores for tas) }).values()[0].response
     let data_tas = get_screen("questionnaire_tas")
-    let tas_score_A = (data_tas["TAS_AttentionCheck_1"] - 1) / 4
+    let tas_score_A = 1 - (data_tas["TAS_AttentionCheck_1"] - 1) / 4
 
     //compute scores for pi18
     let data_pi = get_screen("questionnaire_pi18")

### 2025-02-05 study2/analysis/1_cleaning.qmd
update cleaning

@@
 # Compute distance
-dfoutlier <- performance::check_outliers(select(df, contains("MINT_")), 
+dfoutlier <- performance::check_outliers(select(df, contains("MAIA_")), 
                                          method=c("optics"),
@@
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 8, "Participant"])
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 4, "Participant"])
 outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
@@
   geom_bar(aes(fill=Outlier), stat="identity") +
-  geom_hline(yintercept = 8, linetype="dashed", color="red") +
+  geom_hline(yintercept = 4, linetype="dashed", color="red") +
   labs(fill = "Status") +
@@
   geom_line() +
-  geom_vline(xintercept=8, linetype="dashed", color="red") +
+  geom_vline(xintercept=4, linetype="dashed", color="red") +
   theme_minimal()
@@
 df <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$duration, outliers$distance))
+```
+
+## Imputation
+
+```{r}
+#| eval: FALSE
+
+set.seed(3)
+
+d <- datawizard::data_partition(df, proportion = 0.8)
+
+m1 <- glm(MINT_InteroceptiveFailures_10 ~ .,
+          family = poisson(),
+          data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+
+m2 <- parsnip::rand_forest("regression", mtry = 10, trees = 2000) |> 
+  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+
+m3 <- parsnip::mlp(mode="regression") |> 
+  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+
+# m4 <- parsnip::bart(mode="regression") |> 
+#   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+
+library(baguette)
+
+m5 <- parsnip::bag_mlp(mode="regression") |>
+  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+
+# glmmTMB::glmmTMB(MINT_InteroceptiveFailures_10 ~ .,
+#                  family = poisson(),
+#                  ziformula=~1,
+#                  data = select(df, starts_with("MINT_"), -contains("AttentionCheck")))
+
+parsnip::glance(m5)
+parsnip::tidy(m5)
+
+results <- data.frame(
+  TrueScore = d$test$MINT_InteroceptiveFailures_10,
+  # Poisson = predict(m1, d$test),
+  RandomForest = predict(m2, d$test)$.pred,
+  MLP = predict(m3, d$test)$.pred,
+  BagMLP = predict(m5, d$test)$.pred
+) |> 
+  pivot_longer(-TrueScore)
+
+results |> 
+  ggplot(aes(x=TrueScore, y=value, color=name)) +
+  geom_abline(slope=1) +
+  geom_point()
+
+# Compute R^2
+SS_res <- sum((df$TrueScore - df$PredictedScore)^2)
+SS_tot <- sum((df$TrueScore - mean(df$TrueScore))^2)
+R2 <- 1 - (SS_res / SS_tot)
+
+results |> 
+  summarize(RMSE = sqrt(mean((TrueScore - value)^2)),
+            SS_res = sum((TrueScore - value)^2),
+            SS_tot = sum((TrueScore - mean(value))^2),
+            R2 = 1 - (SS_res / SS_tot),
+            .by="name")
+
+# Compute R2
+
 ```
@@
 p_edu <- df |>
-  mutate (Student = ifelse(is.na(Student), FALSE, Student)) |>
+  mutate(Student = ifelse(is.na(Student), FALSE, Student),
+         Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate")) |>
   ggplot(aes(x = Education)) +
@@
 
-### Country of Residence
+### Country
 
@@
   as.data.frame() |>
+  rename(Country = Var1) |> 
+  arrange(desc(Freq)) |> 
   gt::gt()
@@
 
-### Mental Health
+### Health
 

### 2025-02-05 study2/analysis/2_analysis.qmd
update cleaning

@@
   MINT_Sensitivity_Derm_50 = "My skin is susceptible to itchy fabrics and materials",
-  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
+  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"
   # MINT_Sensitivity_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
   # MINT_Sensitivity_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
-  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
-  MINT_AttentionCheck_1 = "I can always accurately answer to the extreme left on this question to show that I am reading it")
+  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"
+)
 ```
@@
   items,
+  na.data = "pairwise",
   EGA.type = "hierEGA",

### 2025-02-05 study2/analysis/0_preprocessing.R

@@ -13,6 +13,7 @@ path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
 # Convenience Functions ---------------------------------------------------
 
 convert_feet_to_meters <- function(height) {
+  height[height == "5\"11"] <- "5'11"
   # Remove extra spaces and quotes
   height <- trimws(gsub("\"", "", height))
 
@@ -127,7 +128,7 @@ for (file in files) {
     data_ppt$MINT_Deficit_CaCo_4 <- mint$InteroceptiveFailures_1
     data_ppt$MINT_Deficit_CaCo_5 <- mint$InteroceptiveFailures_2
     data_ppt$MINT_Deficit_CaCo_6 <- mint$InteroceptiveFailures_3
-    data_ppt$MINT_Deficit_UrIn_1 <- mint$InteroceptiveFailures_4
+    data_ppt$MINT_Deficit_Urin_1 <- mint$InteroceptiveFailures_4
     data_ppt$MINT_Deficit_Urin_2 <- mint$InteroceptiveFailures_5
     data_ppt$MINT_Deficit_Urin_3 <- mint$InteroceptiveFailures_6
     data_ppt$MINT_Deficit_CaNo_7 <- mint$InteroceptiveFailures_7
@@ -141,50 +142,29 @@ for (file in files) {
     data_ppt$MINT_Awareness_SexS_19 <- mint$InteroceptiveSensitivityPleasure_1
     data_ppt$MINT_Awareness_SexS_20 <- mint$InteroceptiveSensitivityPleasure_2
     data_ppt$MINT_Awareness_SexS_21 <- mint$InteroceptiveSensitivityPleasure_3
-    data_ppt$MINT_Extra_1 <- mint$InteroceptiveSensitivityPleasure_4
-    data_ppt$MINT_Extra_2 <- mint$InteroceptiveSensitivityPleasure_5
-    data_ppt$MINT_Extra_3 <- mint$InteroceptiveSensitivityPleasure_6
+    # data_ppt$MINT_Extra_1 <- mint$InteroceptiveSensitivityPleasure_4
+    # data_ppt$MINT_Extra_2 <- mint$InteroceptiveSensitivityPleasure_5
+    # data_ppt$MINT_Extra_3 <- mint$InteroceptiveSensitivityPleasure_6
     data_ppt$MINT_Awareness_StaS_31 <- mint$InteroceptiveSensitivityPleasure_7
[…]

### 2025-02-05 study2sona/analysis/0_preprocessing.R
added pre-processing

@@ -1,0 +1,265 @@
+library(jsonlite)
+library(progress)
+
+
+options(warn = 2)  # Stop on warnings
+
+# path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
+# path <- "C:/Users/asf25/Box/InteroceptionScale/"
+path <- "C:/Users/aneve/Box/InteroceptionScale/study2sona/"
+
+
+# Convenience Functions ---------------------------------------------------
+
+convert_feet_to_meters <- function(height) {
+  height[height == "5\"11"] <- "5'11"
+  # Remove extra spaces and quotes
+  height <- trimws(gsub("\"", "", height))
+
+  # Handle integer input like "6" (assume feet only, zero inches)
+  if (grepl("^\\d+$", height)) {
+    feet <- as.numeric(height)
+    inches <- 0
+  } else {
+    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " ft "
+    parts <- unlist(strsplit(height, "[ ' .,’\\-]| ft "))
+
+    # Extract feet and inches
+    feet <- as.numeric(parts[1])
+    inches <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
+  }
+
+  # Convert to meters (1 foot = 0.3048 m, 1 inch = 0.0254 m)
+  feet * 0.3048 + inches * 0.0254
+}
+
+convert_stones_to_kg <- function(weight) {
+  weight <- trimws(gsub("\"", "", weight))
+
+  # Handle integer input like "6" (assume stones only, zero pounds)
+  if (grepl("^\\d+$", weight)) {
+    stones <- as.numeric(weight)
+    pounds <- 0
+  } else {
+    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " st "
+    parts <- unlist(strsplit(weight, "[ ' .,\\-]| st "))
+
+    # Extract stones and pounds
+    stones <- as.numeric(parts[1])
+    pounds <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
+  }
+
+  # Convert to kg (1 stone = 6.35029 kg, 1 pound = 0.453592 kg)
+  stones * 6.35029 + pounds * 0.453592
+}
+
+
+# Run loop ----------------------------------------------------------------
+
+
[…]

### 2025-02-05 study2sona/experiment/demographics.js

@@ -662,9 +662,6 @@ var demographics_debriefing = {
                     ],
                 },
             ],
-            data: {
-                screen: "demographics_debrief",
-            },
             // on_finish: function (data) {
             //     let score = check_attentionchecks()
             //     if (score >= 0.75) {
@@ -677,6 +674,9 @@ var demographics_debriefing = {
             //     }
             // }
         }
+    },
+    data: {
+        screen: "demographics_debrief",
     },
 }
 

### 2025-02-05 study2/analysis/1_cleaning.qmd
update

@@
 
-## Imputation
+## Dimension Computation
 
 ```{r}
-#| eval: FALSE
+#| code-fold: true
 
-set.seed(3)
+compute_and_remove <- function(df, name="BodyAwareness", pattern=name, method="mean") {
+  items <- select(df, starts_with(pattern), -contains("AttentionCheck"))
+  df <- df[!names(df) %in% names(items)]
+  if(method == "mean") {
+    df[[name]] <- rowMeans(items, na.rm=TRUE)
+  } else {
+    df[[name]] <- rowSums(items, na.rm=TRUE)
+  }
+  df
+}
+```
 
-d <- datawizard::data_partition(df, proportion = 0.8)
+```{r}
+#| code-fold: false
 
-m1 <- glm(MINT_InteroceptiveFailures_10 ~ .,
-          family = poisson(),
-          data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="IAS", method="sum")
 
-m2 <- parsnip::rand_forest("regression", mtry = 10, trees = 2000) |> 
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="MAIA_AttentionRegulation", method="mean")
+df <- compute_and_remove(df, name="MAIA_BodyListening", method="mean")
+df <- compute_and_remove(df, name="MAIA_EmotionalAwareness", method="mean")
+df <- compute_and_remove(df, name="MAIA_NotDistracting", method="mean")
+df <- compute_and_remove(df, name="MAIA_Noticing", method="mean")
+df <- compute_and_remove(df, name="MAIA_NotWorrying", method="mean")
+df <- compute_and_remove(df, name="MAIA_SelfRegulation", method="mean")
+df <- compute_and_remove(df, name="MAIA_Trusting", method="mean")
 
-m3 <- parsnip::mlp(mode="regression") |> 
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="BPQ", pattern="BodyAwareness", method="mean")
+```
 
-# m4 <- parsnip::bart(mode="regression") |> 
-#   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+<!-- ## Imputation -->
 
-library(baguette)
+<!-- ```{r} -->
+<!-- #| eval: FALSE -->
 
-m5 <- parsnip::bag_mlp(mode="regression") |>
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+<!-- set.seed(3) -->
 
-# glmmTMB::glmmTMB(MINT_InteroceptiveFailures_10 ~ .,
-#                  family = poisson(),
-#                  ziformula=~1,
-#                  data = select(df, starts_with("MINT_"), -contains("AttentionCheck")))
+<!-- d <- datawizard::data_partition(df, proportion = 0.8) -->
 
-parsnip::glance(m5)
-parsnip::tidy(m5)
+<!-- m1 <- glm(MINT_InteroceptiveFailures_10 ~ ., -->
+<!--           family = poisson(), -->
+<!--           data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck"))) -->
 
-results <- data.frame(
-  TrueScore = d$test$MINT_InteroceptiveFailures_10,
-  # Poisson = predict(m1, d$test),
-  RandomForest = predict(m2, d$test)$.pred,
-  MLP = predict(m3, d$test)$.pred,
-  BagMLP = predict(m5, d$test)$.pred
-) |> 
-  pivot_longer(-TrueScore)
+<!-- m2 <- parsnip::rand_forest("regression", mtry = 10, trees = 2000) |>  -->
+<!--   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck"))) -->
 
-results |> 
-  ggplot(aes(x=TrueScore, y=value, color=name)) +
-  geom_abline(slope=1) +
-  geom_point()
+<!-- m3 <- parsnip::mlp(mode="regression") |>  -->
+<!--   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck"))) -->
 
-# Compute R^2
-SS_res <- sum((df$TrueScore - df$PredictedScore)^2)
-SS_tot <- sum((df$TrueScore - mean(df$TrueScore))^2)
-R2 <- 1 - (SS_res / SS_tot)
+<!-- # m4 <- parsnip::bart(mode="regression") |>  -->
+<!-- #   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck"))) -->
 
-results |> 
-  summarize(RMSE = sqrt(mean((TrueScore - value)^2)),
-            SS_res = sum((TrueScore - value)^2),
-            SS_tot = sum((TrueScore - mean(value))^2),
-            R2 = 1 - (SS_res / SS_tot),
-            .by="name")
+<!-- library(baguette) -->
 
-# Compute R2
+<!-- m5 <- parsnip::bag_mlp(mode="regression") |> -->
+<!--   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck"))) -->
 
-```
+<!-- # glmmTMB::glmmTMB(MINT_InteroceptiveFailures_10 ~ ., -->
+<!-- #                  family = poisson(), -->
+<!-- #                  ziformula=~1, -->
+<!-- #                  data = select(df, starts_with("MINT_"), -contains("AttentionCheck"))) -->
+
+<!-- parsnip::glance(m5) -->
+<!-- parsnip::tidy(m5)   -->
+
+<!-- results <- data.frame( -->
+<!--   TrueScore = d$test$MINT_InteroceptiveFailures_10, -->
+<!--   # Poisson = predict(m1, d$test), -->
+<!--   RandomForest = predict(m2, d$test)$.pred, -->
+<!--   MLP = predict(m3, d$test)$.pred, -->
+<!--   BagMLP = predict(m5, d$test)$.pred -->
+<!-- ) |>  -->
+<!--   pivot_longer(-TrueScore) -->
+
+<!-- results |>  -->
+<!--   ggplot(aes(x=TrueScore, y=value, color=name)) + -->
+<!--   geom_abline(slope=1) + -->
+<!--   geom_point() -->
+
+<!-- # Compute R^2 -->
+<!-- SS_res <- sum((df$TrueScore - df$PredictedScore)^2) -->
+<!-- SS_tot <- sum((df$TrueScore - mean(df$TrueScore))^2) -->
+<!-- R2 <- 1 - (SS_res / SS_tot) -->
+
+<!-- results |>  -->
+<!--   summarize(RMSE = sqrt(mean((TrueScore - value)^2)), -->
+<!--             SS_res = sum((TrueScore - value)^2), -->
+<!--             SS_tot = sum((TrueScore - mean(value))^2), -->
+<!--             R2 = 1 - (SS_res / SS_tot), -->
+<!--             .by="name")  -->
+
+<!-- # Compute R2 -->
+
+<!-- ``` -->
 
@@
 ```{r}
-df |> 
+p_bmi <- df |> 
+  filter(!is.na(BMI)) |> 
   ggplot(aes(x=BMI)) +
   annotate("rect", xmin=10, xmax=18.5, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
-  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.1) +
-  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.1) +
-  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.1) +
+  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.25) +
+  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.25) +
+  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.25) +
   annotate("rect", xmin=40, xmax=Inf, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
-  geom_density(aes(color=Gender, fill=Gender), alpha=0.3, linewidth=1) +
+  geom_density(aes(color=Gender, fill=Gender), alpha=0.5, linewidth=2) +
   labs(title = "BMI distribution") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
   theme_minimal() +
@@
 
-df |> 
+p_bmi_a <- df |> 
+  filter(!is.na(BMI)) |> 
   ggplot(aes(x=Age, y=BMI, color=Gender)) +
-  geom_point() +
+  geom_point(size=3, alpha=0.5) +
   geom_smooth(aes(fill=Gender), alpha=0.3, method = 'loess', formula = 'y ~ x') +
-  labs(title = "BMI and Age") +
-  theme_minimal() 
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+p_bmi_b <- df |> 
+  filter(!is.na(BMI)) |> 
+  ggplot(aes(x=Physical_Active, y=BMI)) +
+  geom_jitter(aes(color=Gender), width=0.1, size=3, alpha=0.5) +
+  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
+  labs(x = "Physically Active", y = "") +
+  scale_x_continuous(breaks=0:7) +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none",
+        panel.grid.minor.x = element_blank()) +
+  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
+  ggside::theme_ggside_void()
+
+df$Physical_Workout[df$Physical_Workout > 25] <- NA
+
+p_bmi_c <- df |> 
+  filter(!is.na(BMI) & !is.na(Physical_Workout)) |> 
+  ggplot(aes(x=Physical_Workout, y=BMI)) +
+  geom_point(aes(color=Gender), size=3, alpha=0.5) +
+  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
+  labs(x = "Hours of Active Workout", y = "") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none") +
+  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
+  ggside::theme_ggside_void()
+
+p_bmi / (p_bmi_a | p_bmi_b | p_bmi_c)
 ```
 
-### Health
+### Mental Health
 
 ```{r}
-df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
+df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "GAD|Bipolar"), TRUE, FALSE)
 df$Disorders_Psychiatric_MoodTreatment <- ifelse(
   df$Disorders_Psychiatric_Mood & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Mood|Antidepressant|Anxiolytic|Psychotherapy"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Anxiety <- ifelse(str_detect(df$Disorders_Psychiatric, "Panic|GAD|Social Phobia|Phobia"), TRUE, FALSE)
+df$Disorders_Psychiatric_AnxietyTreatment <- ifelse(
+  df$Disorders_Psychiatric_Anxiety & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Anxiolytic|Psychotherapy|Mindfulness"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Eating <- ifelse(str_detect(df$Disorders_Psychiatric, "Eating"), TRUE, FALSE)
+df$Disorders_Psychiatric_Addiction <- ifelse(str_detect(df$Disorders_Psychiatric, "Addiction"), TRUE, FALSE)
+df$Disorders_Psychiatric_Borderline <- ifelse(str_detect(df$Disorders_Psychiatric, "BPD"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Autism <- ifelse(str_detect(df$Disorders_Psychiatric, "ASD"), TRUE, FALSE)
+df$Disorders_Psychiatric_ADHD <- ifelse(str_detect(df$Disorders_Psychiatric, "ADHD"), TRUE, FALSE)
+
 # df$Disorders_Psychiatric_Other <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
 
-p1 <- select(df, Participant, Gender, Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment) |> 
+p1 <- select(df, Participant, Gender, 
+             Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment,
+             Disorders_Psychiatric_Anxiety, Disorders_Psychiatric_AnxietyTreatment,
+             Disorders_Psychiatric_Eating, Disorders_Psychiatric_Addiction, Disorders_Psychiatric_Borderline,
+             Disorders_Psychiatric_Autism, Disorders_Psychiatric_ADHD) |> 
   pivot_longer(cols = starts_with("Disorders_"), names_to = "Disorder", values_to = "Value") |> 
@@
          Disorder = str_replace(Disorder, "MoodTreatment", "Mood Disorder (with treatment)"),
+         Disorder = str_replace(Disorder, "AnxietyTreatment", "Anxiety (with treatment)"),
          Disorder = str_replace(Disorder, "Mood$", "Mood Disorder")) |> 
@@
   mutate(N_tot = sum(N), .by="Disorder") |>
-  mutate(Disorder = fct_reorder(Disorder, desc(N_tot))) |>
+  mutate(Disorder = fct_reorder(Disorder, desc(N_tot)),
+         Treatment = ifelse(str_detect(Disorder,  "Treatment"), "With treatment", "Without treatment")) |>
   ggplot(aes(x = Disorder, y = N, fill=Gender)) +
@@
 
+p1
+```
+
+### Somatic
+
+```{r}
+somatic <- data.frame(
+  Hypermobility = ifelse(str_detect(df$Disorders_Somatic, "Hypermobility Syndrome"), TRUE, FALSE),
+  Fibromyalgia = ifelse(str_detect(df$Disorders_Somatic, "Fibromyalgia"), TRUE, FALSE),
+  ChronicFatigue = ifelse(str_detect(df$Disorders_Somatic, "Chronic Fatigue Syndrome"), TRUE, FALSE),
+  ChronicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pain Syndrome"), TRUE, FALSE),
+  BackPain = ifelse(str_detect(df$Disorders_Somatic, "Back Pain"), TRUE, FALSE),
+  MuscleTension = ifelse(str_detect(df$Disorders_Somatic, "Muscle Tension"), TRUE, FALSE),
+  SkinRashes = ifelse(str_detect(df$Disorders_Somatic, "Skin Rashes"), TRUE, FALSE),
+  Eczema = ifelse(str_detect(df$Disorders_Somatic, "Eczema"), TRUE, FALSE),
+  Psoriasis = ifelse(str_detect(df$Disorders_Somatic, "Psoriasis"), TRUE, FALSE),
+  Sjogrens = ifelse(str_detect(df$Disorders_Somatic, "Sjogren's Syndrome"), TRUE, FALSE),
+  ChestPain = ifelse(str_detect(df$Disorders_Somatic, "Chest Pain"), TRUE, FALSE),
+  Arrhythmia = ifelse(str_detect(df$Disorders_Somatic, "Cardiac Arrhythmia"), TRUE, FALSE),
+  Hypertension = ifelse(str_detect(df$Disorders_Somatic, "Hypertension"), TRUE, FALSE),
+  Hypotension = ifelse(str_detect(df$Disorders_Somatic, "Hypotension"), TRUE, FALSE),
+  IBS = ifelse(str_detect(df$Disorders_Somatic, "Irritable Bowel Syndrome"), TRUE, FALSE),
+  GERD = ifelse(str_detect(df$Disorders_Somatic, "Gastroesophageal Reflux Disease"), TRUE, FALSE),
+  Crohns = ifelse(str_detect(df$Disorders_Somatic, "Crohn's Disease"), TRUE, FALSE),
+  UlcerativeColitis = ifelse(str_detect(df$Disorders_Somatic, "Ulcerative Colitis"), TRUE, FALSE),
+  Celiac = ifelse(str_detect(df$Disorders_Somatic, "Celiac Disease"), TRUE, FALSE),
+  Gluten = ifelse(str_detect(df$Disorders_Somatic, "Gluten Intolerance"), TRUE, FALSE),
+  Lactose = ifelse(str_detect(df$Disorders_Somatic, "Lactose Intolerance"), TRUE, FALSE),
+  ShortBreath = ifelse(str_detect(df$Disorders_Somatic, "Shortness of Breath"), TRUE, FALSE),
+  Asthma = ifelse(str_detect(df$Disorders_Somatic, "Asthma"), TRUE, FALSE),
+  COPD = ifelse(str_detect(df$Disorders_Somatic, "Chronic Obstructive Pulmonary Disease"), TRUE, FALSE),
+  SleepApnea = ifelse(str_detect(df$Disorders_Somatic, "Sleep Apnea"), TRUE, FALSE),
+  Bronchitis = ifelse(str_detect(df$Disorders_Somatic, "Chronic Bronchitis"), TRUE, FALSE),
+  Nausea = ifelse(str_detect(df$Disorders_Somatic, "Nausea/Vomiting"), TRUE, FALSE),
+  Dizziness = ifelse(str_detect(df$Disorders_Somatic, "Dizziness/Lightheadedness"), TRUE, FALSE),
+  Migraine = ifelse(str_detect(df$Disorders_Somatic, "Migraine"), TRUE, FALSE),
+  Neuropathy = ifelse(str_detect(df$Disorders_Somatic, "Neuropathy"), TRUE, FALSE),
+  Epilepsy = ifelse(str_detect(df$Disorders_Somatic, "Epilepsy"), TRUE, FALSE),
+  MS = ifelse(str_detect(df$Disorders_Somatic, "Multiple Sclerosis"), TRUE, FALSE),
+  FrequentUrination = ifelse(str_detect(df$Disorders_Somatic, "Frequent Urination"), TRUE, FALSE),
+  Endometriosis = ifelse(str_detect(df$Disorders_Somatic, "Endometriosis"), TRUE, FALSE),
+  Cystitis = ifelse(str_detect(df$Disorders_Somatic, "Interstitial Cystitis"), TRUE, FALSE),
+  PelvicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pelvic Pain Syndrome"), TRUE, FALSE)
+)
+
+somatic |> 
+  select(where(~n_distinct(.) > 1)) |> 
+  correlation::correlation() |> 
+  summary(redundant = TRUE) |> 
+  correlation::cor_sort() |> 
+  plot() +
+  theme(axis.text.x = element_text(angle=45, hjust=1))
+
 df$Disorders_Somatic_Number <- ifelse(df$Disorders_Somatic == "", 0, str_count(df$Disorders_Somatic, ";")+1)
@@
   scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
-  scale_x_continuous(breaks = c(0:10)) +
+  scale_x_continuous(breaks = c(0:max(df$Disorders_Somatic_Number)), expand=c(0, 0)) +
   scale_y_continuous(expand = c(0, 0)) +
@@
 
-p1 / p2
+p2
 ```
+
+### Wearables
+
+TODO.
 

### 2025-02-05 study2/analysis/0_preprocessing.R

@@ -14,6 +14,9 @@ path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
 
 convert_feet_to_meters <- function(height) {
   height[height == "5\"11"] <- "5'11"
+  height[height == "511"] <- "5'11"
+  height[height == "5ft2in"] <- "5'12"
+  height[height == "5ft 5 in"] <- "5'5"
   # Remove extra spaces and quotes
   height <- trimws(gsub("\"", "", height))
 
@@ -35,6 +38,8 @@ convert_feet_to_meters <- function(height) {
 }
 
 convert_stones_to_kg <- function(weight) {
+  weight[weight == "10st1lb"] <- "10'1"
+  weight[weight == "64"] <- "6'4"
   weight <- trimws(gsub("\"", "", weight))
 
   # Handle integer input like "6" (assume stones only, zero pounds)
@@ -77,7 +82,7 @@ for (file in files) {
     Participant = dat$participantID,
     Recruitment = dat$researcher,
     Experiment_StartDate = as.POSIXct(paste(dat$date, dat$time), format = "%d/%m/%Y %H:%M:%S"),
-    Experiment_Duration = rawdata[rawdata$screen == "demographics_debrief", "time_elapsed"] / 1000 / 60,
+    Experiment_Duration = max(rawdata$time_elapsed) / 1000 / 60,
     Browser_Version = paste(dat$browser, dat$browser_version),
     Mobile = dat$mobile,
     Platform = dat$os,
@@ -112,7 +117,11 @@ for (file in files) {
 
   # BMI
   data_ppt$Height <- ifelse(is.null(resp$Height_ft), resp$Height_cm / 100, convert_feet_to_meters(resp$Height_ft))
-  data_ppt$Weight <- ifelse(is.null(resp$Weight_st), resp$Weight_kg, convert_stones_to_kg(resp$Weight_st))
+  if(!is.na(data_ppt$Height) && data_ppt$Height > 2.5) stop("Height too high")
+  data_ppt$Weight <- ifelse(is.null(resp$Weight_st),
+                            ifelse(is.null(resp$Weight_kg), NA, resp$Weight_kg),
+                            convert_stones_to_kg(resp$Weight_st))
+  if(!is.na(data_ppt$Weight) && data_ppt$Weight > 300) stop("Weight too high")
   data_ppt$BMI <- data_ppt$Weight / data_ppt$Height^2
 
 
[…]

### 2025-02-07 study2sona/analysis/0_preprocessing.R
updated SONA data

@@ -5,8 +5,8 @@ library(progress)
 options(warn = 2)  # Stop on warnings
 
 # path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
-# path <- "C:/Users/asf25/Box/InteroceptionScale/"
-path <- "C:/Users/aneve/Box/InteroceptionScale/study2sona/"
+path <- "C:/Users/asf25/Box/InteroceptionScale/study2sona/"
+# path <- "C:/Users/aneve/Box/InteroceptionScale/study2sona/"
 
 
 # Convenience Functions ---------------------------------------------------
@@ -74,7 +74,9 @@ for (file in files) {
 
   data_ppt <- data.frame(
     Participant = dat$participantID,
-    #Recruitment = dat$researcher,
+    SonaID = dat$sona_id,
+    Condition = dat$condition,
+    Recruitment = dat$researcher,
     Experiment_StartDate = as.POSIXct(paste(dat$date, dat$time), format = "%d/%m/%Y %H:%M:%S"),
     Experiment_Duration = max(rawdata$time_elapsed) / 1000 / 60,
     Browser_Version = paste(dat$browser, dat$browser_version),
@@ -248,7 +250,7 @@ checks <- checks[order(checks$Score, decreasing = TRUE), ]
 
 
 # Anonymize ---------------------------------------------------------------
-alldata$Prolific_ID <- NULL
+alldata$SonaID <- NULL
 
 # Generate IDs
 ids <- paste0("S", format(sprintf("%03d", 1:nrow(alldata))))

### 2025-02-07 study2sona/analysis/preprocessing.R

@@ -1,156 +1,0 @@
-library(jsonlite)
-library(progress)
-
-# path for data
-
-# path <- "C:/Users/maisi/Box/InteroceptionScale/study2"
-path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
-
-# JsPsych experiment ------------------------------------------------------
-
-files <- list.files(path, pattern = "*.csv")
-
-
-# Progress bar
-progbar <- progress_bar$new(total = length(files))
-
-alldata <- data.frame()
-for (file in files) {
-  progbar$tick()
-  rawdata <- read.csv(paste0(path, "/", file))
-
-
-  # Initialize participant-level data
-  dat <- rawdata[rawdata$screen == "browser_info", ]
-
-  data_ppt <- data.frame(
-    Participant = dat$participantID,
-    Recruitment = dat$researcher,
-    Experiment_StartDate = as.POSIXct(paste(dat$date, dat$time), format = "%d/%m/%Y %H:%M:%S"),
-    Experiment_Duration = rawdata[rawdata$screen == "demographics_debrief", "time_elapsed"] / 1000 / 60,
-    Browser_Version = paste(dat$browser, dat$browser_version),
-    Mobile = dat$mobile,
-    Platform = dat$os,
-    Screen_Width = dat$screen_width,
-    Screen_Height = dat$screen_height
-  )
-
-  if("prolific_id" %in% colnames(dat)){
-    data_ppt$Prolific_ID <- dat$prolific_id
-  }
-
-  data_ppt$Reward <- rawdata[rawdata$screen == "demographics_debrief", "Reward"]
-
-  # Demographics
-  resp <- jsonlite::fromJSON(rawdata[rawdata$screen == "demographic_questions", ]$response)
-
-  # Education
-  data_ppt$Education <- ifelse(resp$Education == "other", demog$`Education-Comment`, resp$Education)
-
-  data_ppt$Student <- ifelse(!is.null(resp$Student), resp$Student, NA)
-  data_ppt$Country <- ifelse(!is.null(resp$Country), resp$Country, NA)
-
-  # Ethnicity
-  data_ppt$Ethnicity <- ifelse(!is.null(resp$Ethnicity), resp$Ethnicity, NA)
[…]

### 2025-02-12 study2sona/analysis/0_preprocessing.R
updated data and minor change to pre-processing

@@ -106,8 +106,12 @@ for (file in files) {
   data_ppt$Ethnicity <- ifelse(resp$Ethnicity == "other", resp$`Ethnicity-Comment`, resp$Ethnicity)
 
   # BMI
-  data_ppt$Height <- ifelse(is.null(resp$Height_ft), resp$Height_cm / 100, convert_feet_to_meters(resp$Height_ft))
-  data_ppt$Weight <- ifelse(is.null(resp$Weight_st), resp$Weight_kg, convert_stones_to_kg(resp$Weight_st))
+  data_ppt$Height <-  ifelse(is.null(resp$Height_ft), 
+                             ifelse(is.null(resp$Height_cm), NA, resp$Height_cm / 100), 
+                             convert_feet_to_meters(resp$Height_ft))
+  data_ppt$Weight <- ifelse(is.null(resp$Weight_st), 
+                            ifelse(is.null(resp$Weight_kg), NA, resp$Weight_kg), 
+                            convert_stones_to_kg(resp$Weight_st))
   data_ppt$BMI <- data_ppt$Weight / data_ppt$Height^2
 
 

### 2025-02-14 study2/analysis/1_cleaning.qmd
update

--- 2025-02-05 study2/analysis/1_cleaning.qmd
@@
   geom_line() +
-  geom_vline(xintercept=5, linetype="dashed", color="red") +
+  geom_vline(xintercept=10, linetype="dashed", color="red") +
   theme_minimal() +
@@
 ```{r}
-outliers$duration <- as.character(df[df$Experiment_Duration < 5, "Participant"])
+outliers$duration <- as.character(df[df$Experiment_Duration < 10, "Participant"])
 outliers$duration <- outliers$duration[!outliers$duration %in% outliers$attentionchecks]
@@
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 4, "Participant"])
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 3, "Participant"])
 outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
@@
   geom_bar(aes(fill=Outlier), stat="identity") +
-  geom_hline(yintercept = 4, linetype="dashed", color="red") +
+  geom_hline(yintercept = 3, linetype="dashed", color="red") +
   labs(fill = "Status") +
+  scale_fill_manual(values=c("Duration" = "purple", "Failed Attention Checks"="red", "Passed"="grey")) +
   theme_minimal() +
@@
   geom_line() +
-  geom_vline(xintercept=4, linetype="dashed", color="red") +
+  geom_vline(xintercept=3, linetype="dashed", color="red") +
   theme_minimal()
@@
 
-## Imputation
+## Dimension Computation
 
 ```{r}
-#| eval: FALSE
+#| code-fold: true
 
-set.seed(3)
+compute_and_remove <- function(df, name="BodyAwareness", pattern=name, method="mean") {
+  items <- select(df, starts_with(pattern), -contains("AttentionCheck"))
+  df <- df[!names(df) %in% names(items)]
+  if(method == "mean") {
+    df[[name]] <- rowMeans(items, na.rm=TRUE)
+  } else {
+    df[[name]] <- rowSums(items, na.rm=TRUE)
+  }
+  df
+}
+```
 
-d <- datawizard::data_partition(df, proportion = 0.8)
+```{r}
+#| code-fold: false
 
-m1 <- glm(MINT_InteroceptiveFailures_10 ~ .,
-          family = poisson(),
-          data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="IAS", method="sum")
 
-m2 <- parsnip::rand_forest("regression", mtry = 10, trees = 2000) |> 
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="BPQ", pattern="BodyAwareness", method="mean")
 
-m3 <- parsnip::mlp(mode="regression") |> 
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
+df <- compute_and_remove(df, name="MAIA_AttentionRegulation", method="mean")
+df <- compute_and_remove(df, name="MAIA_BodyListening", method="mean")
+df <- compute_and_remove(df, name="MAIA_EmotionalAwareness", method="mean")
+df <- compute_and_remove(df, name="MAIA_NotDistracting", method="mean")
+df <- compute_and_remove(df, name="MAIA_Noticing", method="mean")
+df <- compute_and_remove(df, name="MAIA_NotWorrying", method="mean")
+df <- compute_and_remove(df, name="MAIA_SelfRegulation", method="mean")
+df <- compute_and_remove(df, name="MAIA_Trusting", method="mean")
+```
 
-# m4 <- parsnip::bart(mode="regression") |> 
-#   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+```{r}
+#| code-fold: false
 
-library(baguette)
+df <- compute_and_remove(df, name="PHQ4_Anxiety", method="sum")
+df <- compute_and_remove(df, name="PHQ4_Depression", method="sum")
 
-m5 <- parsnip::bag_mlp(mode="regression") |>
-  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))
+# TODO: check if any reversed items in the following questionnaires
+df <- compute_and_remove(df, name="TAS_EOT", method="mean")
+df <- compute_and_remove(df, name="TAS_DDF", method="mean")
+df <- compute_and_remove(df, name="TAS_DIF", method="mean")
 
-# glmmTMB::glmmTMB(MINT_InteroceptiveFailures_10 ~ .,
-#                  family = poisson(),
-#                  ziformula=~1,
-#                  data = select(df, starts_with("MINT_"), -contains("AttentionCheck")))
+df <- compute_and_remove(df, name="ERS_Arousal", method="mean")
+df <- compute_and_remove(df, name="ERS_Sensitivity", method="mean")
+df <- compute_and_remove(df, name="ERS_Persistence", method="mean")
 
-parsnip::glance(m5)
-parsnip::tidy(m5)
+df <- compute_and_remove(df, name="CERQ_Acceptance", method="mean")
+df <- compute_and_remove(df, name="CERQ_PositiveRefocusing", method="mean")
+df <- compute_and_remove(df, name="CERQ_PositiveReappraisal", method="mean")
+df <- compute_and_remove(df, name="CERQ_SelfBlame", method="mean")
+df <- compute_and_remove(df, name="CERQ_OtherBlame", method="mean")
+df <- compute_and_remove(df, name="CERQ_Rumination", method="mean")
+df <- compute_and_remove(df, name="CERQ_Catastrophizing", method="mean")
+df <- compute_and_remove(df, name="CERQ_RefocusPlanning", method="mean")
+df <- compute_and_remove(df, name="CERQ_Perspective", method="mean")
 
-results <- data.frame(
-  TrueScore = d$test$MINT_InteroceptiveFailures_10,
-  # Poisson = predict(m1, d$test),
-  RandomForest = predict(m2, d$test)$.pred,
-  MLP = predict(m3, d$test)$.pred,
-  BagMLP = predict(m5, d$test)$.pred
-) |> 
-  pivot_longer(-TrueScore)
+df <- compute_and_remove(df, name="CEFSA_Body", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Agency", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Emotion", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Familiarity", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Connection", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Reality", method="mean")
+df <- compute_and_remove(df, name="CEFSA_Self", method="mean")
 
-results |> 
-  ggplot(aes(x=TrueScore, y=value, color=name)) +
-  geom_abline(slope=1) +
-  geom_point()
-
-# Compute R^2
-SS_res <- sum((df$TrueScore - df$PredictedScore)^2)
-SS_tot <- sum((df$TrueScore - mean(df$TrueScore))^2)
-R2 <- 1 - (SS_res / SS_tot)
-
-results |> 
-  summarize(RMSE = sqrt(mean((TrueScore - value)^2)),
-            SS_res = sum((TrueScore - value)^2),
-            SS_tot = sum((TrueScore - mean(value))^2),
-            R2 = 1 - (SS_res / SS_tot),
-            .by="name")
-
-# Compute R2
-
+df[grepl("^PI18.*_R$", names(df))] <- 6 - df[grepl("^PI18.*_R$", names(df))]  # Reverse
+df$PI_Alive <- rowMeans(df[grepl("^PI18.*A_", names(df))], na.rm=TRUE)
+df <- compute_and_remove(df, name="PI_Safe", pattern="PI18_GS", method="mean")
+df <- compute_and_remove(df, name="PI_Enticing", pattern="PI18_GE", method="mean")
+df$PI_Good <- rowMeans(select(df, PI_Safe, PI_Enticing), na.rm=TRUE)
+df <- select(df, -starts_with("PI18_"))
 ```
@@
 The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
+
+Among these, `r sum(is.na(df$MINT_Awareness_RelA_29))` have missing data for the MINT due to a technical error.
 
@@
 ```{r}
-df |> 
+p_bmi <- df |> 
+  filter(!is.na(BMI), Gender != "Other") |> 
   ggplot(aes(x=BMI)) +
   annotate("rect", xmin=10, xmax=18.5, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
-  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.1) +
-  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.1) +
-  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.1) +
+  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.25) +
+  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.25) +
+  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.25) +
   annotate("rect", xmin=40, xmax=Inf, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
-  geom_density(aes(color=Gender, fill=Gender), alpha=0.3, linewidth=1) +
+  geom_density(aes(color=Gender, fill=Gender), alpha=0.5, linewidth=2) +
   labs(title = "BMI distribution") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
   theme_minimal() +
@@
 
-df |> 
+p_bmi_a <- df |> 
+  filter(!is.na(BMI), Gender != "Other") |> 
   ggplot(aes(x=Age, y=BMI, color=Gender)) +
-  geom_point() +
+  geom_point(size=3, alpha=0.5) +
   geom_smooth(aes(fill=Gender), alpha=0.3, method = 'loess', formula = 'y ~ x') +
-  labs(title = "BMI and Age") +
-  theme_minimal() 
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+p_bmi_b <- df |> 
+  filter(!is.na(BMI), Gender != "Other") |> 
+  ggplot(aes(x=Physical_Active, y=BMI)) +
+  geom_jitter(aes(color=Gender), width=0.1, size=3, alpha=0.5) +
+  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
+  labs(x = "Physically Active", y = "") +
+  scale_x_continuous(breaks=0:7) +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none",
+        panel.grid.minor.x = element_blank()) +
+  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
+  ggside::theme_ggside_void()
+
+df$Physical_Workout[df$Physical_Workout > 25] <- NA
+
+p_bmi_c <- df |> 
+  filter(!is.na(BMI) & !is.na(Physical_Workout), Gender != "Other") |> 
+  ggplot(aes(x=Physical_Workout, y=BMI)) +
+  geom_point(aes(color=Gender), size=3, alpha=0.5) +
+  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
+  labs(x = "Hours of Active Workout", y = "") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  theme_minimal() +
+  theme(legend.position = "none") +
+  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
+  ggside::theme_ggside_void()
+
+p_bmi / (p_bmi_a | p_bmi_b | p_bmi_c)
 ```
 
-### Health
+### Mental Health
 
 ```{r}
-df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
+df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "GAD|Bipolar"), TRUE, FALSE)
 df$Disorders_Psychiatric_MoodTreatment <- ifelse(
   df$Disorders_Psychiatric_Mood & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Mood|Antidepressant|Anxiolytic|Psychotherapy"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Anxiety <- ifelse(str_detect(df$Disorders_Psychiatric, "Panic|GAD|Social Phobia|Phobia"), TRUE, FALSE)
+df$Disorders_Psychiatric_AnxietyTreatment <- ifelse(
+  df$Disorders_Psychiatric_Anxiety & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Anxiolytic|Psychotherapy|Mindfulness"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Eating <- ifelse(str_detect(df$Disorders_Psychiatric, "Eating"), TRUE, FALSE)
+df$Disorders_Psychiatric_Addiction <- ifelse(str_detect(df$Disorders_Psychiatric, "Addiction"), TRUE, FALSE)
+df$Disorders_Psychiatric_Borderline <- ifelse(str_detect(df$Disorders_Psychiatric, "BPD"), TRUE, FALSE)
+
+df$Disorders_Psychiatric_Autism <- ifelse(str_detect(df$Disorders_Psychiatric, "ASD"), TRUE, FALSE)
+df$Disorders_Psychiatric_ADHD <- ifelse(str_detect(df$Disorders_Psychiatric, "ADHD"), TRUE, FALSE)
+
 # df$Disorders_Psychiatric_Other <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
 
-p1 <- select(df, Participant, Gender, Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment) |> 
+select(df, Participant, Gender, 
+             Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment,
+             Disorders_Psychiatric_Anxiety, Disorders_Psychiatric_AnxietyTreatment,
+             Disorders_Psychiatric_Eating, Disorders_Psychiatric_Addiction, Disorders_Psychiatric_Borderline,
+             Disorders_Psychiatric_Autism, Disorders_Psychiatric_ADHD) |> 
   pivot_longer(cols = starts_with("Disorders_"), names_to = "Disorder", values_to = "Value") |> 
@@
   labs(title = "Mood Disorders", y = "Number of Participants", subtitle = "Participants per self-declared mood disorder", x="Type") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+```
+
+### Somatic
+
+```{r}
+somatic <- data.frame(
+  Hypermobility = ifelse(str_detect(df$Disorders_Somatic, "Hypermobility Syndrome"), TRUE, FALSE),
+  Fibromyalgia = ifelse(str_detect(df$Disorders_Somatic, "Fibromyalgia"), TRUE, FALSE),
+  ChronicFatigue = ifelse(str_detect(df$Disorders_Somatic, "Chronic Fatigue Syndrome"), TRUE, FALSE),
+  ChronicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pain Syndrome"), TRUE, FALSE),
+  BackPain = ifelse(str_detect(df$Disorders_Somatic, "Back Pain"), TRUE, FALSE),
+  MuscleTension = ifelse(str_detect(df$Disorders_Somatic, "Muscle Tension"), TRUE, FALSE),
+  SkinRashes = ifelse(str_detect(df$Disorders_Somatic, "Skin Rashes"), TRUE, FALSE),
+  Eczema = ifelse(str_detect(df$Disorders_Somatic, "Eczema"), TRUE, FALSE),
+  Psoriasis = ifelse(str_detect(df$Disorders_Somatic, "Psoriasis"), TRUE, FALSE),
+   # Dermatological = ifelse(str_detect(df$Disorders_Somatic, "Other Dermatological"), TRUE, FALSE),
+  # Musculoskeletal = ifelse(str_detect(df$Disorders_Somatic, "Other Musculoskeletal"), TRUE, FALSE),
+  Sjogrens = ifelse(str_detect(df$Disorders_Somatic, "Sjogren"), TRUE, FALSE),
+  ChestPain = ifelse(str_detect(df$Disorders_Somatic, "Chest Pain"), TRUE, FALSE),
+  Arrhythmia = ifelse(str_detect(df$Disorders_Somatic, "Cardiac Arrhythmia"), TRUE, FALSE),
+  Hypertension = ifelse(str_detect(df$Disorders_Somatic, "Hypertension"), TRUE, FALSE),
+  Hypotension = ifelse(str_detect(df$Disorders_Somatic, "Hypotension"), TRUE, FALSE),
+  IBS = ifelse(str_detect(df$Disorders_Somatic, "IBS"), TRUE, FALSE),
+  GERD = ifelse(str_detect(df$Disorders_Somatic, "GERD"), TRUE, FALSE),
+  Crohn = ifelse(str_detect(df$Disorders_Somatic, "Crohn"), TRUE, FALSE),
+  UlcerativeColitis = ifelse(str_detect(df$Disorders_Somatic, "Ulcerative Colitis"), TRUE, FALSE),
+  Celiac = ifelse(str_detect(df$Disorders_Somatic, "Celiac Disease"), TRUE, FALSE),
+  Gluten = ifelse(str_detect(df$Disorders_Somatic, "Gluten"), TRUE, FALSE),
+  Lactose = ifelse(str_detect(df$Disorders_Somatic, "Lactose"), TRUE, FALSE),
+  ShortBreath = ifelse(str_detect(df$Disorders_Somatic, "Shortness of Breath"), TRUE, FALSE),
+  Asthma = ifelse(str_detect(df$Disorders_Somatic, "Asthma"), TRUE, FALSE),
+  COPD = ifelse(str_detect(df$Disorders_Somatic, "COPD"), TRUE, FALSE),
+  SleepApnea = ifelse(str_detect(df$Disorders_Somatic, "Sleep Apnea"), TRUE, FALSE),
+  Bronchitis = ifelse(str_detect(df$Disorders_Somatic, "Chronic Bronchitis"), TRUE, FALSE),
+  Nausea = ifelse(str_detect(df$Disorders_Somatic, "Nausea/Vomiting"), TRUE, FALSE),
+  Dizziness = ifelse(str_detect(df$Disorders_Somatic, "Dizziness/Lightheadedness"), TRUE, FALSE),
+  Migraine = ifelse(str_detect(df$Disorders_Somatic, "Migraine"), TRUE, FALSE),
+  Neuropathy = ifelse(str_detect(df$Disorders_Somatic, "Neuropathy"), TRUE, FALSE),
+  # Epilepsy = ifelse(str_detect(df$Disorders_Somatic, "Epilepsy"), TRUE, FALSE),
+  MS = ifelse(str_detect(df$Disorders_Somatic, "Multiple Sclerosis"), TRUE, FALSE),
+  FrequentUrination = ifelse(str_detect(df$Disorders_Somatic, "Frequent Urination"), TRUE, FALSE),
+  Endometriosis = ifelse(str_detect(df$Disorders_Somatic, "Endometriosis"), TRUE, FALSE),
+  Cystitis = ifelse(str_detect(df$Disorders_Somatic, "Interstitial Cystitis"), TRUE, FALSE),
+  PelvicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pelvic Pain Syndrome"), TRUE, FALSE)
+)
+
+somatic |> 
+  select(where(~n_distinct(.) > 1)) |> 
+  correlation::correlation(redundant = TRUE, p_adjust="none") |>
+  correlation::cor_sort() |> 
+  mutate(label = ifelse(p < .001, "*", ""),
+         label = ifelse(r == 1, "", label)) |> 
+  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
+  geom_tile() +
+  geom_text(aes(label=label), size=3) +
+  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+  labs(title = "Co-occurence Matrix of Somatic Disorders") +
+  theme_minimal()  +
+  theme(axis.text.x = element_text(angle=45, hjust=1),
+        axis.title = element_blank())
+
+# pca <- as.data.frame(prcomp(somatic)$rotation[, 1:5])
+# pca$PC <- colnames(pca)[max.col(pca, ties.method='first')]
+# 
+# pca |> 
+#   rownames_to_column(var="Disorder") |> 
+#   pivot_longer(-c(Disorder, PC)) |> 
+#   filter(PC == name) |> 
+#   arrange(name, desc(value)) |> 
+#   ggplot(aes(x=value, y=Disorder, fill=name)) +
+#   geom_bar(stat = "identity") +
+#   facet_wrap(~name, scale="free_y")
+```
+
+```{r}
+#| fig-keep: "first"
+
+# somatic |> 
+#   select(where(~n_distinct(.) > 1)) |> 
+#   EGAnet::bootEGA(
+#     corr="pearson",
+#     EGA.type = "EGA.fit",
+#     model = "glasso", 
+#     algorithm = "leiden",
+#     seed=42)
+```
+
+```{r}
+# df$Disorders_Somatic_Number <- ifelse(df$Disorders_Somatic == "", 0, str_count(df$Disorders_Somatic, ";")+1)
+
+# 1. Autonomic Dysfunction & Anxiety-Somatic Symptoms
+# Mechanism: Dysregulated autonomic nervous system (e.g., panic disorder, dysautonomia, hyperventilation).
+df$Disorders_Somatic_Autonomic_N <- somatic |> 
+  select(Dizziness, ChestPain, ShortBreath, Arrhythmia, Nausea, Hypotension, Hypertension, MuscleTension) |> 
+  rowSums()
+df$Disorders_Somatic_Autonomic <- ifelse(df$Disorders_Somatic_Autonomic_N >= 1, TRUE, FALSE)
+
+# 2. Functional Somatic Syndromes (Pain, Fatigue, GI Symptoms, and Anxiety)
+# Mechanism: Central sensitization, stress-induced HPA axis dysregulation, visceral hypersensitivity.
+df$Disorders_Somatic_Functional_N <- somatic |> 
+  select(Fibromyalgia, Neuropathy, Migraine, ChronicFatigue, ChronicPain, IBS, BackPain, PelvicPain, FrequentUrination) |> 
+  rowSums()
+df$Disorders_Somatic_Functional <- ifelse(df$Disorders_Somatic_Functional_N >= 1, TRUE, FALSE)
+
+# 3. Hypervigilance, Mast Cell Dysfunction & Multi-System Reactivity
+# Mechanism: Mast cell activation, histamine intolerance, neuroinflammation, heightened interoception.
+df$Disorders_Somatic_Hyperreactivity_N <- somatic |> 
+  select(Migraine, SkinRashes, Nausea, FrequentUrination, Dizziness, MuscleTension, Endometriosis) |> 
+  rowSums()
+df$Disorders_Somatic_Hyperreactivity <- ifelse(df$Disorders_Somatic_Hyperreactivity >= 1, TRUE, FALSE)
+
+# 4. Immune-Inflammatory & Gut-Brain Axis Dysregulation
+# Conditions: Celiac disease, gluten sensitivity, lactose intolerance, MS, neuropathy, eczema, asthma, IBS.
+# Mechanism: Leaky gut, immune activation, microbiome imbalance, chronic low-grade inflammation.
+df$Disorders_Somatic_Immune_N <- somatic |> 
+  select(Celiac, Gluten, Lactose, MS, Eczema, Asthma, IBS) |> 
+  rowSums()
+df$Disorders_Somatic_Immune <- ifelse(df$Disorders_Somatic_Immune_N >= 1, TRUE, FALSE)
+
+# 5. Cardiopulmonary & Stress-Linked Disorders
+# Mechanism: Vascular and respiratory dysregulation, autonomic instability, stress-exacerbated cardiovascular symptoms.
+df$Disorders_Somatic_Cardio_N <- somatic |> 
+  select(Arrhythmia, COPD, ChestPain, ShortBreath, Hypertension, SleepApnea) |> 
+  rowSums()
+df$Disorders_Somatic_Cardio <- ifelse(df$Disorders_Somatic_Cardio_N >= 1, TRUE, FALSE)
+
+# 6. Connective Tissue & Dysautonomia-Linked Disorders
+# Conditions: Hypermobility, Sjogren’s syndrome, hypotension, chronic fatigue, dizziness.
+# Mechanism: Connective tissue laxity affecting autonomic function (e.g., Ehlers-Danlos syndrome, POTS).
+df$Disorders_Somatic_Connective_N <- somatic |> 
+  select(Hypermobility, Hypotension, Sjogrens, Hypotension, ChronicFatigue, Dizziness) |> 
+  rowSums()
+df$Disorders_Somatic_Connective <- ifelse(df$Disorders_Somatic_Connective_N >= 1, TRUE, FALSE)
+
+p2 <- df |> 
+  select(starts_with("Disorders_Somatic_"), Gender, Participant) |> 
+  select(ends_with("_N"), Gender, Participant) |>
+  pivot_longer(starts_with("Disorders_Somatic_")) |> 
+  summarize(n = n(), .by=c("name", "value", "Gender")) |> 
+  mutate(name = str_remove(name, "Disorders_Somatic_"),
+         name = str_remove(name, "_N")) |> 
+  ggplot(aes(x = value, y=n, fill=Gender)) +
+  geom_bar(stat="identity") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Number of Issues") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_wrap(~name)
+p2
+# 
+# p2 <- df |> 
+#   select(starts_with("Disorders_Somatic_"), Gender, Participant) |> 
+#   select(-ends_with("_N"), Gender, Participant) |>
+#   pivot_longer(starts_with("Disorders_Somatic_")) |> 
+#   summarize(n = n(), .by=c("name", "value", "Gender")) |> 
+#   filter(value == TRUE) |> 
+#   ggplot(aes(x = name, y=n, fill=Gender)) +
+#   geom_bar(stat="identity") +
+#   scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
+#   scale_y_continuous(expand = c(0, 0)) +
+#   labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Type") +
+#   theme_minimal() +
+#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+# p2
+```
+
+### Wearables
+
+```{r}
+#| fig-height: 12
+
+p1 <- df |> 
+  ggplot(aes(x = Wearables_Number)) +
+  geom_bar() +
+  scale_x_continuous(breaks = c(0:max(df$Wearables_Number)), expand=c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Number of Wearable Devices", y = "Number of Participants", x="Number Owned") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
 
-df$Disorders_Somatic_Number <- ifelse(df$Disorders_Somatic == "", 0, str_count(df$Disorders_Somatic, ";")+1)
+p2 <- df |> 
+  select(contains("Wearables"), -contains("Importance"), -Wearables_Number) |> 
+  pivot_longer(everything()) |> 
+  summarize(n = n(), .by=c("name", "value")) |> 
+  mutate(value = fct_relevel(value, "Not owning", "Never", "Very rarely", "A few times per week", "Once a day", "A few times per day", "A few times per hour"),
+         name = str_remove(name, "Wearables_")) |> 
+  ggplot(aes(x=value, y=n, fill=name)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Usage frequency", y = "") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-p2 <- df |> 
-  ggplot(aes(x = Disorders_Somatic_Number, fill=Gender)) +
-  geom_bar() +
-  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
-  scale_x_continuous(breaks = c(0:10)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Type") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme_minimal()
+get_databubble <- function(df, var="Heart") {
+  x <- paste0("Wearables_", var)
+  y <- paste0("Wearables_", var, "Importance")
+  dat <- df[df[[x]] != "Not owning", ]
+  dat <- summarize(dat, n = n(), .by = all_of(c(x, y)))
+  lvl <- c("Never", "Very rarely", "A few times per week", "Once a day", "A few times per day", "A few times per hour")
+  dat[[x]] <- factor(dat[[x]], levels=lvl[lvl %in% unique(dat[[x]])])
+  names(dat) <- c("Usage", "Importance", "n")
+  dat$Device <- var
+  dat
+}
 
-p1 / p2
+p3 <- rbind(
+  get_databubble(df, "Heart"),
+  get_databubble(df, "Sleep"),
+  get_databubble(df, "Steps"),
+  get_databubble(df, "Weight"),
+  get_databubble(df, "CalorieIntake"),
+  get_databubble(df, "CaloriesBurnt")
+) |> 
+  filter(!is.na(Importance)) |> 
+  ggplot(aes(x=Usage, y=Importance)) +
+  geom_jitter(aes(size = n, color = Device), width = 0.2, height = 0.2, alpha = 0.5) +
+  geom_smooth(aes(x=as.numeric(Usage), color = Device), method = "lm", se = FALSE, formula = 'y ~ x') +
+  labs(x = "Usage frequency") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "none")
+
+p1 / p2 / p3
 ```
@@
 :::
-
-```{r p_summary}
-#| fig-width: 14
-#| fig-height: 14
-
-(p_age | p_edu) / p_map
-```
 

### 2025-02-14 study2/analysis/2_analysis.qmd
update

@@
 
-df <- read.csv("../data/data_participants.csv")
+df <- read.csv("../data/data_participants.csv") |> 
+  filter(!is.na(MINT_Awareness_ExAc_35))
 ```
@@
 items <- select(df, starts_with("MINT_"))
+names(items) <- str_remove(names(items), "MINT_")
+
+colors <- c(MINT="#00BCD4", MINTi="#00838F", IAS="#F44336", MAIA="#FF9800", MAIAi="#EF6C00", BPQ="#795548")
 ```
-
--   items commneted out - need to decide if keep or not
 
@@
   MINT_Deficit_Olfa_12 = "I often check the smell of my farts",
-  #MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
-  #MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
-  #MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
+  MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
+  MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
+  MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
   # MINT_Awareness_SexA_16 = "I always feel in my body if I am sexually aroused",
@@
 )
+
+cleanlabels <- function(x, qname=FALSE) {
+  is_factor <- FALSE
+  if(is.factor(x)) {
+    is_factor <- TRUE
+    vec <- x
+    x <- levels(x)
+  }
+
+  x <- x |> 
+    str_replace("MINT_", ifelse(qname, "MINT - ", "")) |> 
+    str_replace("MAIA_", ifelse(qname, "MAIA - ", "")) |> 
+    str_replace("_", " (") 
+  x <- ifelse(str_detect(x, "\\("), paste0(x, ")"), x)
+
+  if(is_factor) {
+    levels(vec) <- x
+    return(vec)
+  }
+  x
+}
 ```
@@
 ### Cluster Stability
+
+#### Full
 
@@
   items,
-  na.data = "pairwise",
   EGA.type = "hierEGA",
@@
 
-# EGAnet::dimensionStability(ega)
 itemstability <- EGAnet::itemStability(ega1, IS.plot=FALSE)
 plot(itemstability)
+```
+
+#### Final
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| fig-keep: "first"
+
+items <- items |> 
+  select(-contains("UrSe"))
+```
+
+```{r}
+#| eval: false
+
+ega2 <- bootEGA(
+  items,
+  EGA.type = "hierEGA",
+  model = "glasso",  # BGGM
+  algorithm = "leiden",
+  type="resampling",
+  plot.itemStability=FALSE,
+  typicalStructure=TRUE,
+  plot.typicalGraph=FALSE,
+  iter=500,
+  seed=3, ncores = 4)
+
+save(ega2, file="models/ega2.RData")
+```
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| fig-keep: "first"
+
+load("models/ega2.RData")
+
+# EGAnet::dimensionStability(ega)
+itemstability <- EGAnet::itemStability(ega2, IS.plot=FALSE)
+plot(itemstability)
+```
+
+#### Item Table
+
+```{r}
+#| message: false
 
@@
 
-itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
+dimensions <- list(
+  C08 = "CaCo",       # Cardiorespiratory Confusion
+  C01 = "UrIn",       # Urointestinal Inaccuracy
+  C02 = "Derm",       # Dermatoception
+  C10 = "CaNo",       # Cardiorespiratory Noticing
+  C13 = "Sati",       # Satiety Noticing
 
-# Remove items
-toremove2 <- filter(itemstability_table, Max < 0.8)$Item
-toremove2 <- itemstability_table |> 
-  filter(!Item %in% toremove2) |>
-  mutate(Item, n=n(), .by="Cluster", .keep="used") |> 
-  filter(n < 3) |>  # Remove small clusters
-  pull(Item) |> 
-  c(toremove2)
+  C14 = "SexS",       # Sexual Arousal Sensitivity
+  C07 = "StaS",       # State Specificity
+  C09 = "SexO",       # Sexual Organs Sensitivity
+  C03 = "ExAc",       # Expulsion Accuracy
+  C06 = "RelA",       # Relaxation Awareness
+
+  C05 = "Resp",       # Respiroception
+  C11 = "Card",       # Cardioception
+  C12 = "Gast",       # Gastroception
+  C04 = "Olfa"       # Olfactory Compensation
+
+  # C04 = "SexA",       # Sexual Arousal Awareness
+  # C08 = "UrSe",       # Urointestinal Sensitivity
+  # C12 = "Sign",       # Signalling
+  # C07 = "SexC"        # Sexual Arousal Changes  
+)
+
+higher <- make_loadingtable(t(net.loads(ega2$EGA$higher_order, loading.method="revised")$std))
+cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]
+
+lower <- make_loadingtable(net.loads(ega2$EGA$lower_order, loading.method="revised")$std) |>
+  select(names(higher)) |>
+  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
+  arrange(Cluster, desc(Max))
+
+higher$Item <- paste0("M", higher$Item)
+# higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
+higher$Label <- ""
+# higher$ID  <- ""
+lower <- mutate(lower, Label = labels[paste0("MINT_", Item)], ID=Item, Item = 1:n())
+
+rbind(higher, select(lower, -ID)) |>
+# rbind(higher, lower) |>
+  datawizard::data_relocate("Label", after = "Item") |>
+  datawizard::data_rename(names(dimensions), dimensions) |>
+  select(-Cluster, -Max) |> 
+  mutate(`|` = "") |> 
+  gt::gt() |>
+  gt::tab_row_group(
+    label = "Items",
+    rows = 1:(nrow(lower) + nrow(higher))
+  ) |>
+  gt::tab_row_group(
+    label = "Metaclusters",
+    rows = 1:nrow(higher)
+  ) |>
+  gt::data_color(columns=-Item,
+                 method = "numeric",
+                 palette = c("red", "white", "green"),
+                 domain = c(-1, 1)) |>
+  gt::tab_style(
+    style = gt::cell_text(size="small", style="italic"),
+    locations = gt::cells_body(columns="Label", rows=c(4:45))
+  ) |>
+  gt::tab_style(
+    style = list(gt::cell_text(weight="bold"),
+                 gt::cell_fill(color = "#F5F5F5")),
+    locations = list(
+      gt::cells_row_groups(groups = "Items"),
+      gt::cells_row_groups(groups = "Metaclusters")
+    )
+  ) |>
+  gt::fmt_number(columns=-Item, decimals=2) |>
+  gt::tab_header(
+    title = gt::md("**Item Loadings**"),
+    subtitle = "Node centrality"
+  ) 
 ```
+
+### Score Extraction
+
+```{r}
+df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
+df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
+# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin))
+
+df$MINT_Sensitivity_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
+df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
+df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
+# df$MINT_LackSensitivity <- rowMeans(select(df, MINT_Sensitivity_Derm, MINT_Deficit_Sati, MINT_Deficit_CaNo))
+
+df$MINT_Awareness_SexS <- rowMeans(select(df, starts_with("MINT_Awareness_SexS")), na.rm = TRUE)
+df$MINT_Awareness_StaS <- rowMeans(select(df, starts_with("MINT_Awareness_StaS")), na.rm = TRUE)
+df$MINT_Awareness_SexO <- rowMeans(select(df, starts_with("MINT_Awareness_SexO")), na.rm = TRUE)
+df$MINT_Awareness_ExaC <- rowMeans(select(df, starts_with("MINT_Awareness_ExaC")), na.rm = TRUE)
+df$MINT_Awareness_RelA <- rowMeans(select(df, starts_with("MINT_Awareness_RelA")), na.rm = TRUE)
+df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))
+
+df$MINT_Interoception_Card <- rowMeans(select(df, starts_with("MINT_Sensitivity_Card")), na.rm = TRUE)
+df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
+df$MINT_Interoception_Gast <- rowMeans(select(df, starts_with("MINT_Sensitivity_Gast")), na.rm = TRUE)
+df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
+
+df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)
+# df$MINT_Awareness_UrSe <- rowMeans(select(df, starts_with("MINT_Awareness_UrSe")), na.rm = TRUE)
+
+# df$MINT_Awareness <- rowMeans(select(df, starts_with("MINT_Awareness"), -matches("[[:digit:]]")))
+
+df <- df[names(df)[!grepl("MINT_.*[0-9]$", names(df))]]
+
+minti <- data.frame(
+  # MINT_Deficit = df$MINT_Deficit,
+  MINT_Awareness = df$MINT_Awareness,
+  MINT_Interoception = df$MINT_Interoception
+)
+```
+
+```{r}
+#| warning: false
+
+make_cor <- function(df1, df2=NULL) {
+  df1 |> 
+    correlation::correlation(data2=df2, p_adjust="none", redundant=ifelse(is.null(df2), TRUE, FALSE)) |> 
+    correlation::cor_sort() |>
+    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
+           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
+           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
+    ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
+    geom_tile() +
+    geom_text(aes(label=label), size=3) +
+    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+    theme_minimal() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1),
+          legend.position = "none")
+}
+
+make_cor(select(df, starts_with("MINT"))) +
+  labs(x="", y="", title="Correlation between MINT dimensions") +
+  theme(axis.text.x = element_text(angle = 45, hjust=1, 
+                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
+                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
+                                          "plain", "plain")))
+```
+
+## Convegent Validity
+
+::: panel-tabset
+
+### Interoception
+
+```{r}
+#| warning: false
+
+make_cor <- function(df1, df2) {
+  df1 |> 
+    correlation::correlation(df2, p_adjust="none") |> 
+    correlation::cor_sort() |>
+    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
+           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
+           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
+    ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
+    geom_tile() +
+    geom_text(aes(label=label), size=3) +
+    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
+    theme_minimal() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1),
+          legend.position = "none")
+}
+
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")),
+         select(df, starts_with("MAIA"), IAS, BPQ)) +
+  labs(x="MINT", y="", title="Correlations between the MINT and other Interoception Questionnaires") +
+  theme(axis.text.x = element_text(angle = 45, hjust=1, 
+                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
+                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
+                                          "plain", "plain")))
+```
+
+```{r}
+select(df, starts_with("MINT"), starts_with("MAIA"), IAS, BPQ) |> 
+  parameters::factor_analysis(n=4, rotation="oblimin") |> 
+  plot()
+```
+
+```{r}
+# library(umap)
+# 
+# items_intero <- select(df, starts_with("MINT"), -matches("[[:digit:]]"), starts_with("MAIA"), IAS, BPQ)
+# rez <- umap::umap(datawizard::data_transpose(items_intero[complete.cases(items_intero),]))
+# 
+# rez
+# as.data.frame(rez$layout) |> 
+#   rownames_to_column(var="Variable") |> 
+#   separate(Variable, into=c("Questionnaire", "Dimension", "Sub"), fill="right") |> 
+#   ggplot(aes(x=V1, y=V2, color=Questionnaire)) +
+#   geom_point(size=3) +
+#   scale_color_manual(values=colors)
+```
+
+### Alexithymia
+
+```{r}
+compare_models <- function(outcome="TAS_DIF") {
+
+  # Individual predictors
+  preds <- c("BPQ", "IAS", 
+             names(select(df, starts_with("MINT"), -matches("[[:digit:]]"))),
+             names(select(df, starts_with("MAIA"))))
+
+  models <- list()
+  for(p in preds) {
+    models[[p]] <- lm(as.formula(paste0(outcome, " ~ ", p)), data=df)
+  }
+  perf <- compare_performance(models) |> 
+    arrange(desc(R2))
+
+  best_mint <- perf$Name[str_detect(perf$Name, "MINT_")][1]
+  best_maia <- perf$Name[str_detect(perf$Name, "MAIA")][1]
+
+  models <- list()
+  df_pred <- data.frame()
+  for(p in c(best_mint, best_maia, "BPQ", "IAS")) {
+    models[[p]] <- lm(as.formula(paste0(outcome, " ~ ", p)), data=df)
+    pred <- modelbased::estimate_relation(models[[p]], by=p, length=30) 
+    names(pred)[1] <- "Value"
+    pred$Predictor <- p
+    df_pred <- rbind(df_pred, pred)
+  }
+
+  test <- test_performance(models)
+
+  cols <- colors
+  cols[[best_mint]] <- cols["MINT"]
+  cols[[best_maia]] <- cols["MAIA"]
+
+  p <- df_pred |>
+    mutate(Questionnaire = case_when(
+      str_detect(Predictor, "MINT") ~ "MINT", 
+      str_detect(Predictor, "MAIA") ~ "MAIA",
+      .default = Predictor)) |> 
+    ggplot(aes(x=Value, y=Predicted)) +
+    geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Predictor), alpha=0.3) +
+    geom_line(aes(color=Predictor)) +
+    scale_fill_manual(values=cols) +
+    scale_color_manual(values=cols) +
+    facet_wrap(~Predictor, scales="free_x") +
+    labs(y=outcome, x="Interoception Index")
+
+  # Full Questionnaires
+  m_mint <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) |> 
+    step(direction = "both", trace=0)
+  m_minti <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(minti, df[outcome])) |> 
+    step(direction = "both", trace=0)
+  m_ias <- lm(as.formula(paste0(outcome, " ~ IAS")),
+              data = df)
+  m_maia <- lm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome), starts_with("MAIA"))) |> 
+    step(direction = "both", trace=0)
+  m_maiai <- lm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome), 
+                              starts_with("MAIA"), 
+                              -contains("NotWorrying"),
+                              -contains("NotDistracting"))) |> 
+    step(direction = "both", trace=0)
+  m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
+                data = df)
+
+  test_all <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
+  test_all$Predictors <- c(
+    paste0(cleanlabels(find_predictors(m_mint)$conditional), collapse = ", "),
+    paste0(cleanlabels(find_predictors(m_minti)$conditional), collapse = ", "),
+    "", 
+    paste0(cleanlabels(find_predictors(m_maia)$conditional), collapse = ", "),
+    paste0(cleanlabels(find_predictors(m_maiai)$conditional), collapse = ", "),
+    "")
+
+  list(test=test,  test_all=test_all, p=p)
+}
+
+rez1 <- compare_models("TAS_DIF")
+rez1$test
+rez1$p
+rez1$test_all
+
+rez2 <- compare_models("TAS_DDF")
+rez2$test
+rez2$p
+rez2$test_all
+
+rez3 <- compare_models("TAS_EOT")
+rez3$test
+rez3$p
+rez3$test_all
+```
+
+### Mood
+
+```{r}
+rez <- compare_models("LifeSatisfaction")
+rez$test
+rez$p
+rez$test_all
+
+rez <- compare_models("PHQ4_Anxiety")
+rez$test
+rez$p
+rez$test_all
+
+rez <- compare_models("PHQ4_Depression")
+rez$test
+rez$p
+rez$test_all
+```
+
+### Emotions
+
+```{r}
+rez <- compare_models("ERS_Arousal")
+rez$test
+rez$p
+rez$test_all
+
+rez <- compare_models("ERS_Sensitivity")
+rez$test
+rez$p
+rez$test_all
+
+rez <- compare_models("ERS_Persistence")
+rez$test
+rez$p
+rez$test_all
+```
+
+:::
+
+## Predictive
+
+### Mental Health
+
+::: panel-tabset
+
+#### Mood Disorders
+
+```{r}
+compare_predictive <- function(outcome="Disorders_Psychiatric_Mood") {
+  m_mint <- glm(as.formula(paste0(outcome, " ~ .")),
+              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$")),
+              family = "binomial") |> 
+  step(direction = "both", trace=0)
+
+  m_minti <- glm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(minti, df[outcome]),
+              family = "binomial") |> 
+    step(direction = "both", trace=0)
+
+  m_ias <- glm(as.formula(paste0(outcome, " ~ IAS")),
+              data = df,
+              family = "binomial")
+
+  m_maia <- glm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome), starts_with("MAIA")),
+                family = "binomial") |> 
+    step(direction = "both", trace=0)
+
+  m_maiai <- glm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome), 
+                              starts_with("MAIA"), 
+                              -contains("NotWorrying"),
+                              -contains("NotDistracting")),
+                family = "binomial") |> 
+    step(direction = "both", trace=0)
+
+  m_bpq <- glm(as.formula(paste0(outcome, " ~ BPQ")),
+                data = df,
+                family = "binomial")
+
+  test <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
+
+  get_auc <- function(m) {
+    roc <- as.data.frame(performance_roc(m))
+    auc <- bayestestR::area_under_curve(roc$Specificity, roc$Sensitivity)
+    paste0("AUC = ", insight::format_percent(auc))
+  }
+
+  p <- rbind(
+    mutate(as.data.frame(performance_roc(m_mint)), Predictor = "MINT"),
+    mutate(as.data.frame(performance_roc(m_minti)), Predictor = "MINTi"),
+    mutate(as.data.frame(performance_roc(m_ias)), Predictor = "IAS"),
+    mutate(as.data.frame(performance_roc(m_maia)), Predictor = "MAIA"),
+    mutate(as.data.frame(performance_roc(m_maiai)), Predictor = "MAIAi"),
+    mutate(as.data.frame(performance_roc(m_bpq)), Predictor = "BPQ")
+  ) |> 
+      ggplot(aes(x=Specificity)) +
+      geom_abline(intercept=0, slope=1, color="gray") +
+      geom_line(aes(y=Sensitivity, color=Predictor), linewidth=2, alpha=0.9) +
+      geom_label(data=data.frame(
+        label = c(get_auc(m_mint), get_auc(m_minti), get_auc(m_ias), get_auc(m_maia), get_auc(m_maiai), get_auc(m_bpq)),
+        Predictor = c("MINT", "MINTi", "IAS", "MAIA", "MAIAi", "BPQ"),
+        x = 0.25,
+        y = c(0.65, 0.60, 0.55, 0.45, 0.35, 0.20)), 
+        aes(x=x, y=y, label=label), color=colors) +
+      labs(x= "1 - Specificity (False Positive Rate)", y="Sensitivity (True Positive Rate)",
+           color="Questionnaire Version") +
+      scale_color_manual(values=colors) +
+      scale_x_continuous(labels=scales::percent) +
+      scale_y_continuous(labels=scales::percent) +
+      theme_minimal()
+
+  list(m_mint=m_mint, m_ias=m_ias, m_maia=m_maia, m_maiai=m_maiai, test=test, p=p)
+}
+```
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_Mood")
+rez$p
+```
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_MoodTreatment")
+rez$p
+```
+
+#### Anxiety
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_Anxiety")
+rez$p
+```
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_AnxietyTreatment")
+rez$p
+```
+
+#### Eating
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_Eating")
+rez$p
+```
+
+#### Addiction
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_Addiction")
+rez$p
+```
+
+#### ADHD
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_ADHD")
+rez$p
+```
+
+#### Autism
+
+```{r}
+rez <- compare_predictive("Disorders_Psychiatric_Autism")
+rez$p
+```
+
+#### Borderline
+
+```{r}
+# rez <- compare_predictive("Disorders_Psychiatric_Borderline")
+# rez$p
+```
+
+::::
+
+### Somatic Issues
+
+::: panel-tabset
+
+#### Autonomic
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Autonomic")
+rez$p
+```
+
+#### Functional
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Functional")
+rez$p
+```
+
+#### Hyperreactivity
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Hyperreactivity")
+rez$p
+```
+
+#### Immune
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Immune")
+rez$p
+```
+
+#### Cardio
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Cardio")
+rez$p
+```
+
+#### Connective
+
+```{r}
+rez <- compare_predictive("Disorders_Somatic_Connective")
+rez$p
+```
+
+:::
+
+### Biofeedback Usage
+
+```{r}
+model <- glm(as.formula(paste0("Wearables_Number ~ .")),
+              data = select(df, Wearables_Number, starts_with("MINT"), -matches("[[:digit:]]")),
+              family = "poisson") |> 
+  step(direction = "both", trace=0)
+
+parameters::parameters(model)
+
+model <- glm(as.formula(paste0("Wearables_Heart ~ .")),
+              data = df |>
+              mutate(Wearables_Heart = Wearables_Heart != "Not owning") |> 
+              select(Wearables_Heart, starts_with("MINT"), -matches("[[:digit:]]")),
+              family = "binomial") |> 
+  step(direction = "both", trace=0, k = log(nrow(df)))
+summary(model)
+
+model <- lm(as.formula(paste0("Wearables_HeartImportance ~ .")),
+              data = df |>
+              filter(!is.na(Wearables_HeartImportance)) |> 
+              select(Wearables_HeartImportance, starts_with("MINT"), -matches("[[:digit:]]"))) |> 
+  step(direction = "both", trace=0, k = log(nrow(filter(df, !is.na(Wearables_HeartImportance)))))
+
+parameters::parameters(model)
+```
+
+## Exploratory
+
+### CEFSA
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("CEFSA")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("CEFSA")))
+```
+
+### Emotion Regulation
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("CERQ")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("CERQ")))
+```
+
+### Primals
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("PI")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("PI")))
+```

### 2025-02-14 study2sona/analysis/analysis.qmd
update

---
title: "Data Quality - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(EGAnet)
library(tidygraph)
library(ggraph)

set.seed(42)
```

```{r}
#| code-fold: false

df <- read.csv("../../study2/data/rawdata_participants.csv") |> 
  mutate(Condition = fct_relevel(Condition, "Prolific", "Attention Checks", "Quiz", "Control"))
```

## Attention Checks

```{r}
dfchecks <- df |>
  dplyr::mutate(
    # "I can always accurately answer to the extreme left on this question to show that I am reading it"
    A1 = ifelse(MINT_AttentionCheck_1 == 0, 0, 1),
    # "I notice that I am being asked to respond all the way to the right"
    A2 = ifelse(MAIA_AttentionCheck_1 == 6, 0, 1),
    # "I can always accurately choose the lowest option"
    A3 = ifelse(IAS_AttentionCheck_1 == 1, 0, 1),
    # "Respond all the way to the right."
    A4 = ifelse(BodyAwareness_AttentionCheck_1 == 5, 0, 1),
    # "I am able to respond all the way to the left"
    A5 = ifelse(TAS_AttentionCheck_1 == 1, 0, 1),
    # "On the whole, I know I must press the highest option"
    A6 = ifelse(PI18_AttentionCheck_1 == 5, 0, 1),
    # "I feel that to show I'm being attentive I will press the lowest option"
    A7 = ifelse(CEFSA_AttentionCheck_1 == 0, 0, 1),
    .keep = "none"
  ) 
dfchecks$TotalFailed <- rowSums(dfchecks)
df$TotalFailed <- dfchecks$TotalFailed

dfchecks |>
  mutate(Total = as.factor(paste0(TotalFailed, "/8"))) |> 
  ggplot(aes(x = Total)) +
  geom_bar(aes(fill = Total)) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.title.x = element_blank(),
  )
```

```{r}
df |> 
  mutate(Failed = ifelse(TotalFailed >= 1, 1, 0)) |> 
  summarize(Failed = sum(Failed), N = n(), p = Failed / N, .by="Condition") |> 
  gt::gt()
```

```{r}
m1 <- glm(TotalFailed ~ Condition, data=df, family="poisson")
m2 <- glmmTMB::glmmTMB(TotalFailed ~ Condition,
                      data=df,
                      ziformula=~1,
                      family="poisson")
m3 <- glmmTMB::glmmTMB(TotalFailed ~ Condition,
                      data=df,
                      ziformula=~1,
                      family=glmmTMB::truncated_nbinom2)

compare_performance(m1, m2, m3)
test_performance(m1, m2, m3)

modelbased::estimate_means(m1, by="Condition", backend="emmeans") |> 
  plot()
```

### 2025-02-14 study2/analysis/0_preprocessing.R

@@ -2,10 +2,11 @@ library(jsonlite)
 library(progress)
 
 
-options(warn = 2)  # Stop on warnings
+options(warn = 2) # Stop on warnings
 
-# path <- "C:/Users/maisi/Box/InteroceptionScale/study2"
-path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
+# path <- "C:/Users/maisi/Box/InteroceptionScale/
+# path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
+path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
 # path <- "C:/Users/asf25/Box/InteroceptionScale/"
 
 
@@ -13,10 +14,28 @@ path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
 # Convenience Functions ---------------------------------------------------
 
 convert_feet_to_meters <- function(height) {
-  height[height == "5\"11"] <- "5'11"
+  height[height == "I'm 5ft8"] <- "5'8"
+  height <- gsub("ft ", "'", tolower(height))
+  height <- gsub("ft", "'", tolower(height))
+  height <- gsub(" feet ", "'", tolower(height))
+  height <- gsub(" in ", "", height)
+  height <- gsub("in", "", height)
+  height <- gsub(" inches", "", height)
+  height <- gsub("' ", "'", height)
+  height <- gsub("`", "'", height)
+  height <- gsub("”", "'", height)
+  height <- gsub("\"", "'", height)
+  height[height == "6f 5"] <- "6'5"
+  height[height == "54"] <- "5'4"
+  height[height == "5’qq"] <- "5'11"
   height[height == "511"] <- "5'11"
-  height[height == "5ft2in"] <- "5'12"
-  height[height == "5ft 5 in"] <- "5'5"
+  height[height == "6\"2"] <- "6'2"
+  height[height == "62"] <- "6'2"
+  height[height == "5<1"] <- "5'1"
+  height[height == "5/9"] <- "5'9"
+  height[height == "5.833"] <- "5'8.33"
+
+  if(height=="176") return(1.76)
   # Remove extra spaces and quotes
   height <- trimws(gsub("\"", "", height))
 
@@ -38,8 +57,17 @@ convert_feet_to_meters <- function(height) {
 }
 
[…]

### 2025-02-14 study2sona/analysis/0_preprocessing.R

@@ -1,271 +1,0 @@
-library(jsonlite)
-library(progress)
-
-
-options(warn = 2)  # Stop on warnings
-
-# path <- "C:/Users/domma/Box/Data/InteroceptionScale/study2/"
-path <- "C:/Users/asf25/Box/InteroceptionScale/study2sona/"
-# path <- "C:/Users/aneve/Box/InteroceptionScale/study2sona/"
-
-
-# Convenience Functions ---------------------------------------------------
-
-convert_feet_to_meters <- function(height) {
-  height[height == "5\"11"] <- "5'11"
-  # Remove extra spaces and quotes
-  height <- trimws(gsub("\"", "", height))
-
-  # Handle integer input like "6" (assume feet only, zero inches)
-  if (grepl("^\\d+$", height)) {
-    feet <- as.numeric(height)
-    inches <- 0
-  } else {
-    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " ft "
-    parts <- unlist(strsplit(height, "[ ' .,’\\-]| ft "))
-
-    # Extract feet and inches
-    feet <- as.numeric(parts[1])
-    inches <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
-  }
-
-  # Convert to meters (1 foot = 0.3048 m, 1 inch = 0.0254 m)
-  feet * 0.3048 + inches * 0.0254
-}
-
-convert_stones_to_kg <- function(weight) {
-  weight <- trimws(gsub("\"", "", weight))
-
-  # Handle integer input like "6" (assume stones only, zero pounds)
-  if (grepl("^\\d+$", weight)) {
-    stones <- as.numeric(weight)
-    pounds <- 0
-  } else {
-    # Split input based on common delimiters: ' (apostrophe), space, ., "," or "-", or " st "
-    parts <- unlist(strsplit(weight, "[ ' .,\\-]| st "))
-
-    # Extract stones and pounds
-    stones <- as.numeric(parts[1])
-    pounds <- ifelse(length(parts) > 1, as.numeric(parts[2]), 0)
-  }
-
-  # Convert to kg (1 stone = 6.35029 kg, 1 pound = 0.453592 kg)
-  stones * 6.35029 + pounds * 0.453592
-}
-
-
-# Run loop ----------------------------------------------------------------
-
-
[…]

### 2025-03-09 study2/analysis/1_cleaning.qmd
update 1

@@
 df <- read.csv("../data/rawdata_participants.csv")
+```
+
+## Recruitment History
+
+```{r}
+#| message: false
+
+# Consecutive count of participants per day (as area)
+df |>
+  mutate(Date = as.Date(Experiment_StartDate, format = "%Y-%m-%d %H:%M:%S")) |> 
+  summarize(N = n(), .by=c("Date", "Recruitment")) |> 
+  complete(Date, Recruitment, fill = list(N = 0)) |> 
+  mutate(N = cumsum(N), .by="Recruitment") |>
+  ggplot(aes(x = Date, y = N)) +
+  geom_area(aes(fill=Recruitment)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(
+    title = "Recruitment History",
+    x = "Date",
+    y = "Total Number of Participants"
+  ) +
+  see::theme_modern()
+```
+
+```{r}
+#| message: false
+
+# Table
+summarize(df, N = n(), .by=c("Recruitment")) |> 
+  arrange(desc(N)) |> 
+  gt::gt() |> 
+  gt::opt_stylize() |> 
+  gt::opt_interactive(use_compact_mode = TRUE) |> 
+  gt::tab_header("Number of participants per recruitment source")
 ```
@@
 
+We removed `r sum(is.na(df$MINT_Awareness_RelA_29))` participants with missing data for the MINT due to a technical error.
+
+```{r}
+#| code-fold: false
+
+df <- filter(df, !is.na(df$MINT_Awareness_RelA_29))
+```
+
 The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
-
-Among these, `r sum(is.na(df$MINT_Awareness_RelA_29))` have missing data for the MINT due to a technical error.
 

### 2025-03-09 study2/analysis/2_analysis.qmd
update

@@
 
-df <- read.csv("../data/data_participants.csv") |> 
-  filter(!is.na(MINT_Awareness_ExAc_35))
+df <- read.csv("../data/data_participants.csv")
 ```
@@
 
-items <- select(df, starts_with("MINT_"))
+items <- filter(df, !is.na(MINT_Awareness_ExAc_35)) 
 names(items) <- str_remove(names(items), "MINT_")
 
-colors <- c(MINT="#00BCD4", MINTi="#00838F", IAS="#F44336", MAIA="#FF9800", MAIAi="#EF6C00", BPQ="#795548")
+colors <- c(MINT="#00BCD4", MINTi="#00838F", IAS="#F44336", MAIA="#FF9800", MAIAi="#EF6C00", MAIAmin="#E65100", BPQ="#795548")
 ```
@@
 
+Most correlated dims:
+- CaCo x8
+- Urin x4
+- Rela x4
+- Derm x3
+- Sati
+- Olfa
+- StaS
+- ExaC
+- Resp
+
 ```{r}
@@
 ```{r}
+table_models <- function(models) {
+  test <- test_performance(models)
+  test$Model <- NULL
+  test$Omega2 <- NULL
+  test$p_Omega2 <- NULL
+  test$R2 <- compare_performance(models, metrics="R2")$R2
+
+  preds <- c()
+  for(m in models){
+    x <- names(sort(abs(coef(m)[-1]), decreasing=TRUE))
+    preds <- c(preds, paste0(cleanlabels(x), collapse = ", "))
+  }
+  test$Predictors <- preds
+  format(test, zap_small = TRUE)
+}
+
 compare_models <- function(outcome="TAS_DIF") {
@@
 
-  test <- test_performance(models)
+  test <- table_models(models)
+  test$Predictors <- NULL
 
@@
     step(direction = "both", trace=0)
+  m_maiamin <- lm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome),
+                              MAIA_AttentionRegulation, # remove?
+                              MAIA_SelfRegulation, # remove?
+                              # MAIA_Trusting, # remove?
+                              MAIA_BodyListening, 
+                              MAIA_EmotionalAwareness,
+                              MAIA_Noticing)) |> 
+    step(direction = "both", trace=0)
   m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
@@
 
-  test_all <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
-  test_all$Predictors <- c(
-    paste0(cleanlabels(find_predictors(m_mint)$conditional), collapse = ", "),
-    paste0(cleanlabels(find_predictors(m_minti)$conditional), collapse = ", "),
-    "", 
-    paste0(cleanlabels(find_predictors(m_maia)$conditional), collapse = ", "),
-    paste0(cleanlabels(find_predictors(m_maiai)$conditional), collapse = ", "),
-    "")
+  models_full <- list(m_mint=m_mint, m_minti=m_minti, m_maia=m_maia, m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq)
+  test_all <- table_models(models_full)
 
-  list(test=test,  test_all=test_all, p=p)
+  list(test=test,  test_all=test_all, p=p, models_full=models_full)
 }
@@
 rez1 <- compare_models("TAS_DIF")
-rez1$test
+display(rez1$test, title="DIF")
 rez1$p
-rez1$test_all
+display(rez1$test_all, title="DIF")
 
 rez2 <- compare_models("TAS_DDF")
-rez2$test
+display(rez2$test, title="DDF")
 rez2$p
-rez2$test_all
+display(rez2$test_all, title="DDF")
 
 rez3 <- compare_models("TAS_EOT")
-rez3$test
+display(rez3$test, title="EOT")
 rez3$p
-rez3$test_all
+display(rez3$test_all, title="EOT")
 ```
+
+```{r}
+make_cor(select(df, starts_with("TAS_")),
+         select(df, starts_with("MINT"), -matches("[[:digit:]]"), 
+                starts_with("MAIA"), IAS, BPQ))
+```
+
+CaCo and Sati.
 
@@
 rez <- compare_models("LifeSatisfaction")
-rez$test
+display(rez$test, title="Life Satisfaction") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Life Satisfaction")
 
 rez <- compare_models("PHQ4_Anxiety")
-rez$test
+display(rez$test, title="Anxiety") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Anxiety")
 
 rez <- compare_models("PHQ4_Depression")
-rez$test
+display(rez$test, title="Depression") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Depression")
 ```
+
+```{r}
+make_cor(select(df, LifeSatisfaction, starts_with("PHQ4_")),
+         select(df, starts_with("MINT"), -matches("[[:digit:]]"), 
+                starts_with("MAIA"), IAS, BPQ))
+```
+
+- CaCo and RelA
 
@@
 rez <- compare_models("ERS_Arousal")
-rez$test
+display(rez$test, title="Arousal") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Arousal")
 
 rez <- compare_models("ERS_Sensitivity")
-rez$test
+display(rez$test, title="Sensitivity") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Sensitivity")
 
 rez <- compare_models("ERS_Persistence")
-rez$test
+display(rez$test, title="Persistence") 
 rez$p
-rez$test_all
+display(rez$test_all, title="Persistence")
 ```
+
+```{r}
+make_cor(select(df, starts_with("ERS_")),
+         select(df, starts_with("MINT"), -matches("[[:digit:]]"), 
+                starts_with("MAIA"), IAS, BPQ))
+```
+
+- CaCo
 
@@
 ```{r}
-compare_predictive <- function(outcome="Disorders_Psychiatric_Mood") {
+compare_predictive <- function(outcome="Disorders_Psychiatric_Mood", y = c(0.65, 0.60, 0.50, 0.45, 0.40, 0.30, 0.20)) {
   m_mint <- glm(as.formula(paste0(outcome, " ~ .")),
@@
 
+  m_maiamin <- glm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome),
+                              MAIA_AttentionRegulation, # remove?
+                              MAIA_SelfRegulation, # remove?
+                              # MAIA_Trusting, # remove?
+                              MAIA_BodyListening, 
+                              MAIA_EmotionalAwareness,
+                              MAIA_Noticing),
+                family = "binomial") |> 
+    step(direction = "both", trace=0)
+
   m_bpq <- glm(as.formula(paste0(outcome, " ~ BPQ")),
@@
 
-  test <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
+  test <- table_models(list(m_mint=m_mint, m_minti=m_minti, m_maia=m_maia, m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq))
 
@@
     mutate(as.data.frame(performance_roc(m_minti)), Predictor = "MINTi"),
-    mutate(as.data.frame(performance_roc(m_ias)), Predictor = "IAS"),
     mutate(as.data.frame(performance_roc(m_maia)), Predictor = "MAIA"),
     mutate(as.data.frame(performance_roc(m_maiai)), Predictor = "MAIAi"),
+    mutate(as.data.frame(performance_roc(m_maiamin)), Predictor = "MAIAmin"),
+    mutate(as.data.frame(performance_roc(m_ias)), Predictor = "IAS"),
     mutate(as.data.frame(performance_roc(m_bpq)), Predictor = "BPQ")
   ) |> 
+    mutate(Predictor = fct_relevel(Predictor, "MINT", "MINTi", "MAIA", "MAIAi", "MAIAmin", "IAS", "BPQ")) |> 
       ggplot(aes(x=Specificity)) +
@@
       geom_label(data=data.frame(
-        label = c(get_auc(m_mint), get_auc(m_minti), get_auc(m_ias), get_auc(m_maia), get_auc(m_maiai), get_auc(m_bpq)),
-        Predictor = c("MINT", "MINTi", "IAS", "MAIA", "MAIAi", "BPQ"),
-        x = 0.25,
-        y = c(0.65, 0.60, 0.55, 0.45, 0.35, 0.20)), 
-        aes(x=x, y=y, label=label), color=colors) +
+        label = c(get_auc(m_mint), get_auc(m_minti), get_auc(m_maia), get_auc(m_maiai), get_auc(m_maiamin), get_auc(m_ias), get_auc(m_bpq)),
+        Predictor = c("MINT", "MINTi", "MAIA", "MAIAi", "MAIAmin", "IAS", "BPQ"),
+        x = 0.9,
+        y = y), 
+        aes(x=x, y=y, label=label), color=colors[c("MINT", "MINTi", "MAIA", "MAIAi", "MAIAmin", "IAS", "BPQ")]) +
       labs(x= "1 - Specificity (False Positive Rate)", y="Sensitivity (True Positive Rate)",
@@
 
-  list(m_mint=m_mint, m_ias=m_ias, m_maia=m_maia, m_maiai=m_maiai, test=test, p=p)
+  list(m_mint=m_mint, m_ias=m_ias, m_maia=m_maia, m_maiai=m_maiai, m_maiamin=m_maiamin, test=test, p=p)
 }
@@
 rez$p
+display(rez$test, title="Mood")
 ```
@@
 rez$p
+display(rez$test, title="Mood (with Treatment)")
 ```
@@
   step(direction = "both", trace=0)
-
 parameters::parameters(model)
 
-model <- glm(as.formula(paste0("Wearables_Heart ~ .")),
+# Heart
+m_owns <- glm(as.formula(paste0("Wearables_Heart ~ .")),
               data = df |>
@@
   step(direction = "both", trace=0, k = log(nrow(df)))
-summary(model)
+parameters::parameters(m_owns)
 
@@
   step(direction = "both", trace=0, k = log(nrow(filter(df, !is.na(Wearables_HeartImportance)))))
+parameters::parameters(model)
 
-parameters::parameters(model)
+lm(Wearables_HeartImportance ~ MINT_Interoception_Card, data=df) |> 
+  estimate_relation() |> 
+  plot()
 ```

### 2025-03-09 study2sona/analysis/analysis.qmd
update

@@
 
+```{r}
+
+```
+
 ## Attention Checks
@@
 df$TotalFailed <- dfchecks$TotalFailed
+df$Failed <- ifelse(dfchecks$TotalFailed >= 1, 1, 0)
 
@@
 df |> 
-  mutate(Failed = ifelse(TotalFailed >= 1, 1, 0)) |> 
   summarize(Failed = sum(Failed), N = n(), p = Failed / N, .by="Condition") |> 
@@
 ```
+
+### Failed at least one
+
+```{r}
+m1 <- glm(Failed ~ Prolific, 
+          data=mutate(df, Prolific = ifelse(Condition == "Prolific", "Prolific", "SONA")), 
+          family="binomial")
+# m1 <- brms::brm(Failed ~ Condition, data=df, family="poisson", backend="cmdstanr")
+
+modelbased::estimate_means(m1, by="Prolific", keep_iterations=10) |> 
+  plot()
+
+modelbased::estimate_contrasts(m1)
+```
+
+```{r}
+m1 <- glm(Failed ~ Condition, data=df, family="binomial")
+# m1 <- brms::brm(Failed ~ Condition, data=df, family="poisson", backend="cmdstanr")
+
+modelbased::estimate_means(m1, by="Condition", keep_iterations=10) |> 
+  plot()
+
+modelbased::estimate_contrasts(m1)
+```
+
+### Number
 
@@
                       data=df,
-                      ziformula=~1,
+                      ziformula=~Condition,
                       family="poisson")
@@
                       data=df,
-                      ziformula=~1,
+                      ziformula=~Condition,
                       family=glmmTMB::truncated_nbinom2)
@@
 
-modelbased::estimate_means(m1, by="Condition", backend="emmeans") |> 
+modelbased::estimate_means(m1, by="Condition") |> 
   plot()

### 2025-03-09 study2/analysis/0_preprocessing.R
Update 0_preprocessing.R

@@ -111,6 +111,11 @@ for (file in files) {
     next
   }
 
+  # Deal with other datetime formats
+  if(dat$date == "2/5/2025") {
+    dat$date <- "05/02/2025"
+  }
+
   data_ppt <- data.frame(
     Participant = dat$participantID,
     Recruitment = dat$researcher,
@@ -122,7 +127,6 @@ for (file in files) {
     Screen_Width = dat$screen_width,
     Screen_Height = dat$screen_height
   )
-
 
 
   if (data_ppt$Recruitment == "prolific") {
@@ -168,9 +172,7 @@ for (file in files) {
 
   # BMI
   data_ppt$Height <- ifelse(is.null(resp$Height_ft), resp$Height_cm / 100, convert_feet_to_meters(resp$Height_ft))
-  if ("3y39b5pwby" %in% data_ppt$Participant){
-    data_ppt$Height[data_ppt$Participant == "3y39b5pwby"] <- data_ppt$Height[data_ppt$Participant == "3y39b5pwby"] * 100
-  }
+  if (!is.na(data_ppt$Height) && data_ppt$Height == 0.0165) data_ppt$Height <- 1.65
   if (!is.na(data_ppt$Height) && data_ppt$Height > 2.5) stop("Height too high")
   data_ppt$Weight <- ifelse(is.null(resp$Weight_st),
     ifelse(is.null(resp$Weight_kg), NA, resp$Weight_kg),

### 2025-06-23 paper/manuscript.qmd
bits and bobs

---
title: "**The MInt Scale: A Fresh Validation of the Multidimensional Interoception Questionnaire Outperforms the MAIA, BPQ and IAS**"
shorttitle: "MInt Validation"
author:
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    roles:
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Funding acquisition
      - Investigation
      - Methodology
      - Project administration
      - Resources
      - Software
      - Supervision
      - Validation
      - Visualization
      - Writing – original draft
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
      - name: "University of Sussex"
        department:  "Sussex Centre for Consciousness Science"
  - name: Ana Neves  
    orcid: 0009-0006-0020-7599
    role:
      - Investigation
      - Methodology
      - Project administration
      - Supervision
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - ref: "id1"
  - name: Giulia Poreiro
    orcid: 0000-0002-2343-5109
    role:
      - Investigation
      - Methodology
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - ref: "id1"
author-note:
  status-changes: 
    affiliation-change: ~
    deceased: ~
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
      :::
    study-registration: ~
    data-sharing: ~
    related-report: ~
    conflict-of-interest: ~
    financial-support: ~
    authorship-agreements: ~
abstract: |
  TO DO.
#   **Significance Statement**. TODO.
keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, MInt Validation, Body Awareness"
numbered-lines: false
floatsintext: true
mask: false
bibliography: bibliography.bib
format:
  apaquarto-pdf:
    documentmode: jou
    keep-tex: true
  apaquarto-docx: default
---

# Introduction

TODO: write general intro.

Main issues in existing questionnaires: 
- Either heavily based on theories (e.g., focusing on a specific dimensions), despite shaky evidence for said-theories
- Do not control for context (which leads to variability in interpretation and occurence)
- Often quite narrow in the modalities covered

# Study 1

TODO: write intro.

Goal of study 1: to generate a lot of items, analyze its structure and reduce them to a balanced set of items.

## Methods

### Participants

We recruited 760 English-speaking participants using Prolific\textcopyright. We excluded 191 for failing at least one attention check, and 10 based on measures significantly related to the probability of failing attention checks [namely, the multivariate distance obtained with the OPTICS algorithm, @theriault2024check]. The final sample includes 559 participants (age = 37 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% United Kingdom, 26.65% United States).
This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).

### Item Generation

Based on the two goals outlined for this scale, namely to include different interoceptive modalities, and to explicitly state the context of the interoceptive experience (e.g., whether negative or positive), we generated items following a combinatorial approach, where each item's category was a combination of a specific modality and context (@fig-one).

```{r}
#| label: fig-one
#| fig-cap: "The conceptual grid used to generate the 120 initial items (top-left). Each item belong both to an interoceptive modalitiy and a facet, with the number of each item per category indicated in the circles. The askterisk denotes the additional presence of an attention check item in that category. In the experiment, these items were presented on different pages grouped either by modality (bottom-left), by facet (top-right), or entirely randomly. The Correlation Similarity (bottom-right) analysis suggested that the correlation matrix obtained from the participants assigned to the random-grouping condition was slightly more similar (but non-significantly) to the one obtained in the modality-grouping condition, suggesting that 1) the scale's structure is robust to different presentation conditions; 2) modality-grouping might tend to facilitate the emergence of the underlying item structure (and thus be interpreted as being more natural)." 
#| fig-align: "center"
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

knitr::include_graphics("../study1/analysis/figures/figure1.png")
```

We firstly identified 7 "modalities" (cardiac, respiratory, gastric, genital, skin & temperature, bladder & colon, and a "general state" category corresponding to a holistic and general awareness of an interoceptive state or dimension). Through iterative refinement (e.g., splitting or merging different categories together), we then settled on 6 "facets", which encompass both *contexts* of experience (negative and positive arousal, namely anxious and sexual states), and potential distinct *mechanisms* (nociception & pleasure, sensitivity, accuracy, and confusion).

Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)]. We additionally crafted 8 "attention check" items blending in (and distributed across) each category.

### Procedure

Participants were randomly assigned to one of three conditions, driving how items were grouped on the same page: 1) items grouped by modality (i.e., all cardiac items on the first page, all colon & bladder  items on the second, etc.), 2) items grouped by facet, or 3) items presented fully randomly (but balanced randomly across 6 pages). The order of the item on any given page and the order of the modalities/facets were randomized.
Each participant completed the full set of 120 items, with the attention check items interspersed throughout.
The online experiment was implemented using JsPsych [@de2015jspsych], and item responses were recorded using 7-points Likert scales (0 = Disagree, 6 = Agree).

### Data Analysis

In order to test whether the grouping condition had an effect on the structure (i.e., how items relate to one-another), we compared the correlation matrix obtained in the random condition to the ones obtained in the modality and facet conditions, focusing on 3 indices of correlation matrix similarity - the Procrustes Similarity Index [PSI, @sibson1978studies], the Adjusted RV [Rvadj, @mayer2011exploratory], and the Similarity of Matrices Index [SMI, @indahl2018similarity]. For each index, we bootstrapped the difference between the similarity with the facet and modality conditions to test whether the correlation matrix in the random-grouping condition is significantly more similar to any of the two other conditions.

## Results

The correlation matrix similarity analysis yielded no significant differences between the similarity of the random-grouping condition with the modality-grouping and facet-grouping conditions ($PSI_{\text{Random vs. Facet}} = 0.81$, $PSI_{\text{Random vs. Modality}} = 0.82$, $p = .51$; $RVadj_{\text{Random vs. Facet}} = 0.77$, $RVadj_{\text{Random vs. Modality}} = 0.78$, $p = .78$; $SMI_{\text{Random vs. Facet}} = 0.49$, $SMI_{\text{Random vs. Modality}} = 0.51$, $p = .55$).

## Discussion

Consistent bias across indices in favour of a greater similarity with the modality-grouping condition.

# Study 2

TODO: write intro.
Goal of study 2: to validate the MInt scale against other interoception scales.

# Data Availability

Data, code, and all materials are available at https://github.com/RealityBending/InteroceptionScale.

# Acknowledgements

We would like to thank the dissertation students from the University of Sussex for their help in data collection.
DM would also like to thank ... for the motivation provided to write this paper.

# References

<!-- References will auto-populate in the refs div below -->

::: {#refs}
:::

### 2025-06-23 paper/manuscript.tex
bits and bobs

\documentclass[
  jou,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

\usepackage{amsmath}
\usepackage{amssymb}

\RequirePackage{longtable}
\RequirePackage{threeparttablex}

\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-.5em}%
	{\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-\z@\relax}%
	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
\usepackage{subcaption}

\renewcommand\thesubfigure{\Alph{subfigure}}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

\usepackage{tcolorbox}
\tcbuselibrary{listings,theorems, breakable, skins}
\usepackage{fontawesome5}

\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}

%\newlength\Oldarrayrulewidth
%\newlength\Oldtabcolsep

\usepackage{hyperref}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{newtx}

\defaultfontfeatures{Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

\title{\textbf{The MInt Scale: A Fresh Validation of the
Multidimensional Interoception Questionnaire Outperforms the MAIA, BPQ
and IAS}}

\shorttitle{MInt Validation}

\usepackage{etoolbox}

\authorsnames[{1,2},{1},{1}]{Dominique Makowski,Ana Neves,Giulia
Poreiro}

\authorsaffiliations{
{School of Psychology, University of Sussex},{Sussex Centre for
Consciousness Science, University of Sussex}}

\leftheader{Makowski, Neves and Poreiro}

\abstract{TO DO. }

\keywords{Interoception questionnaire, interoceptive accuracy scale,
MAIA, MInt Validation, Body Awareness}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, opacityback=0, colframe=quarto-callout-note-color-frame, left=2mm, arc=.35mm, colback=white, bottomrule=.15mm, breakable, rightrule=.15mm, leftrule=.75mm]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

\end{tcolorbox}  Author roles were classified using the Contributor Role
Taxonomy (CRediT; https://credit.niso.org/) as follows:  Dominique
Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
acquisition, Investigation, Methodology, Project
administration, Resources, Software, Supervision, Validation, Visualization, Writing
-- original draft; Ana Neves:   Investigation, Methodology, Project
administration, Supervision, Writing -- original draft, Writing --
review \& editing; Giulia Poreiro:   Investigation, Methodology, Writing
-- original draft, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique
Makowski, Email: \href{mailto:D.Makowski@sussex.ac.uk}{D.Makowski@sussex.ac.uk}}
}

\usepackage{pbalance}
% \usepackage{float}
\makeatletter
\let\oldtpt\ThreePartTable
\let\endoldtpt\endThreePartTable
\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
\def\ThreePartTable@i[#1]{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.485\textwidth}
\oldtpt[#1]
}
\def\ThreePartTable@ii{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.48\textwidth}
\oldtpt
}
\def\endThreePartTable{
\endoldtpt
\end{minipage}
\twocolumn
\end{figure}}
\makeatother

\makeatletter
\let\endoldlt\endlongtable		
\def\endlongtable{
\hline
\endoldlt}
\makeatother

\newenvironment{twocolumntable}% environment name
{% begin code
\begin{table*}[!htbp]%
\onecolumn%
}%
{%
\twocolumn%
\end{table*}%
}% end code

\urlstyle{same}

\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

% From https://tex.stackexchange.com/a/645996/211326
%%% apa7 doesn't want to add appendix section titles in the toc
%%% let's make it do it
\makeatletter
\xpatchcmd{\appendix}
  {\par}
  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
  {}{}
\makeatother

%% Disable longtable counter
%% https://tex.stackexchange.com/a/248395/211326

\usepackage{etoolbox}

\makeatletter
\patchcmd{\LT@caption}
  {\bgroup}
  {\bgroup\global\LTpatch@captiontrue}
  {}{}
\patchcmd{\longtable}
  {\par}
  {\par\global\LTpatch@captionfalse}
  {}{}
\apptocmd{\endlongtable}
  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
  {}{}
\newif\ifLTpatch@caption
\makeatother

\begin{document}

\maketitle

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setlength\LTleft{0pt}

\section{Introduction}\label{introduction}

TODO: write general intro.

Main issues in existing questionnaires: - Either heavily based on
theories (e.g., focusing on a specific dimensions), despite shaky
evidence for said-theories - Do not control for context (which leads to
variability in interpretation and occurence) - Often quite narrow in the
modalities covered

\section{Study 1}\label{study-1}

TODO: write intro.

Goal of study 1: to generate a lot of items, analyze its structure and
reduce them to a balanced set of items.

\subsection{Methods}\label{methods}

\subsubsection{Participants}\label{participants}

We recruited 760 English-speaking participants using
Prolific\textcopyright. We excluded 191 for failing at least one
attention check, and 10 based on measures significantly related to the
probability of failing attention checks (namely, the multivariate
distance obtained with the OPTICS algorithm,
\citeproc{ref-theriault2024check}{Thériault et al., 2024}). The final
sample includes 559 participants (age = 37 \(\pm\) 12.2 {[}18, 77{]};
50.8\% women; Country of residence: 63.86\% United Kingdom, 26.65\%
United States). This study was approved by the University of Sussex'
Ethics Committee (\textbf{NUMBER}).

\subsubsection{Item Generation}\label{item-generation}

Based on the two goals outlined for this scale, namely to include
different interoceptive modalities, and to explicitly state the context
of the interoceptive experience (e.g., whether negative or positive), we
generated items following a combinatorial approach, where each item's
category was a combination of a specific modality and context
(Figure~\ref{fig-one}).

\begin{figure*}[!htbp]

{\caption{{The conceptual grid used to generate the 120 initial items
(top-left). Each item belong both to an interoceptive modalitiy and a
facet, with the number of each item per category indicated in the
circles. The askterisk denotes the additional presence of an attention
check item in that category. In the experiment, these items were
presented on different pages grouped either by modality (bottom-left),
by facet (top-right), or entirely randomly. The Correlation Similarity
(bottom-right) analysis suggested that the correlation matrix obtained
from the participants assigned to the random-grouping condition was
slightly more similar (but non-significantly) to the one obtained in the
modality-grouping condition, suggesting that 1) the scale's structure is
robust to different presentation conditions; 2) modality-grouping might
tend to facilitate the emergence of the underlying item structure (and
thus be interpreted as being more natural).}{\label{fig-one}}}}

\begin{center}
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study1/analysis/figures/figure1.png}
\end{center}

\end{figure*}

We firstly identified 7 ``modalities'' (cardiac, respiratory, gastric,
genital, skin \& temperature, bladder \& colon, and a ``general state''
category corresponding to a holistic and general awareness of an
interoceptive state or dimension). Through iterative refinement (e.g.,
splitting or merging different categories together), we then settled on
6 ``facets'', which encompass both \emph{contexts} of experience
(negative and positive arousal, namely anxious and sexual states), and
potential distinct \emph{mechanisms} (nociception \& pleasure,
sensitivity, accuracy, and confusion).

Using this orthogonal 7x6 modality/facet grid as a conceptual
scaffolding, we generated 120 initial items, striving for a balanced
number of items with consistent phrasing within modalities and
facets\footnote{The initial item list at
  \href{https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html}{realitybending.github.io/InteroceptionScale/study1/analysis/2\_analysis.html}}.
We additionally crafted 8 ``attention check'' items blending in (and
distributed across) each category.

\subsubsection{Procedure}\label{procedure}

Participants were randomly assigned to one of three conditions, driving
how items were grouped on the same page: 1) items grouped by modality
(i.e., all cardiac items on the first page, all colon \& bladder items
on the second, etc.), 2) items grouped by facet, or 3) items presented
fully randomly (but balanced randomly across 6 pages). The order of the
item on any given page and the order of the modalities/facets were
randomized. Each participant completed the full set of 120 items, with
the attention check items interspersed throughout. The online experiment
was implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
2015}), and item responses were recorded using 7-points Likert scales (0
= Disagree, 6 = Agree).

\subsubsection{Data Analysis}\label{data-analysis}

In order to test whether the grouping condition had an effect on the
structure (i.e., how items relate to one-another), we compared the
correlation matrix obtained in the random condition to the ones obtained
in the modality and facet conditions, focusing on 3 indices of
correlation matrix similarity - the Procrustes Similarity Index (PSI,
\citeproc{ref-sibson1978studies}{Sibson, 1978}), the Adjusted RV (Rvadj,
\citeproc{ref-mayer2011exploratory}{Mayer et al., 2011}), and the
Similarity of Matrices Index (SMI,
\citeproc{ref-indahl2018similarity}{Indahl et al., 2018}). For each
index, we bootstrapped the difference between the similarity with the
facet and modality conditions to test whether the correlation matrix in
the random-grouping condition is significantly more similar to any of
the two other conditions.

\subsection{Results}\label{results}

The correlation matrix similarity analysis yielded no significant
differences between the similarity of the random-grouping condition with
the modality-grouping and facet-grouping conditions
(\(PSI_{\text{Random vs. Facet}} = 0.81\),
\(PSI_{\text{Random vs. Modality}} = 0.82\), \(p = .51\);
\(RVadj_{\text{Random vs. Facet}} = 0.77\),
\(RVadj_{\text{Random vs. Modality}} = 0.78\), \(p = .78\);
\(SMI_{\text{Random vs. Facet}} = 0.49\),
\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .55\)).

\subsection{Discussion}\label{discussion}

\section{Study 2}\label{study-2}

TODO: write intro. Goal of study 2: to validate the MInt scale against
other interoception scales.

\section{Data Availability}\label{data-availability}

Data, code, and all materials are available at
https://github.com/RealityBending/InteroceptionScale.

\section{Acknowledgements}\label{acknowledgements}

We would like to thank the dissertation students from the University of
Sussex for their help in data collection. DM would also like to thank
\ldots{} for the motivation provided to write this paper.

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-de2015jspsych}
De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
behavioral experiments in a web browser. \emph{Behavior Research
Methods}, \emph{47}, 1--12.

\bibitem[\citeproctext]{ref-indahl2018similarity}
Indahl, U. G., Næs, T., \& Liland, K. H. (2018). A similarity index for
comparing coupled matrices. \emph{Journal of Chemometrics},
\emph{32}(10), e3049.

\bibitem[\citeproctext]{ref-mayer2011exploratory}
Mayer, C.-D., Lorent, J., \& Horgan, G. W. (2011). Exploratory analysis
of multiple omics datasets using the adjusted RV coefficient.
\emph{Statistical Applications in Genetics \& Molecular Biology},
\emph{10}(1).

\bibitem[\citeproctext]{ref-sibson1978studies}
Sibson, R. (1978). Studies in the robustness of multidimensional
scaling: Procrustes statistics. \emph{Journal of the Royal Statistical
Society: Series B (Methodological)}, \emph{40}(2), 234--238.

\bibitem[\citeproctext]{ref-theriault2024check}
Thériault, R., Ben-Shachar, M. S., Patil, I., Lüdecke, D., Wiernik, B.
M., \& Makowski, D. (2024). Check your outliers! An introduction to
identifying statistical outliers in r with easystats. \emph{Behavior
Research Methods}, \emph{56}(4), 4162--4172.

\end{CSLReferences}

\end{document}

### 2025-06-23 study1/analysis/1_cleaning.qmd
bits and bobs

@@
 ```
+
+The initial sample included `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.
 
@@
 
-Mahalanobis distance [@demaesschalck2000] is commonly used to detect multivariate outliers, which are data points with unusual combinations of scores on two or more variables [@filzmoser2016].
-This distance is calculated relative to the centroid—a central point where the means of all variables intersect—with larger distances indicating greater deviation from the center.
-
-This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping items.
-
 We removed `r length(outliers$distance)` (`r insight::format_percent(length(outliers$distance) / nrow(df))`) participants based on multivariate distance.

### 2025-06-23 study1/analysis/2_analysis.qmd
bits and bobs

@@
 ---
-title: "InteroceptionScale - Data Analysis"
+title: "InteroceptionScale - Study 1: Data Analysis"
 editor: source
@@
 ---
+
+## Original Items
+
+```{r}
+#| message: false
+#| warning: false
+#| out-width: "100%"
+
+knitr::include_graphics("figures/table_originalitems.png")
+```
 
@@
 ```{r}
+
+rez[rez$Comparison ==  "Random vs. Facet",  "d_PSI"] |> 
+  pd()
+rez[rez$Comparison ==  "Random vs. Facet" & rez$Sample == "Random",  "d_PSI"] |> 
+  pd()
+
+rez |> 
+  summarize(PSI = mean(PSI),
+            p_PSI = as.numeric(bayestestR::pd(d_PSI, as_p=TRUE)),
+            RVadj = mean(RVadj),
+            p_RVadj = as.numeric(bayestestR::pd(d_RVadj, as_p=TRUE)),
+            SMI = mean(SMI),
+            p_SMI = as.numeric(bayestestR::pd(d_SMI, as_p=TRUE)),
+            .by = "Comparison")
+```
+
+```{r}
 #| fig-width: 10
@@
   filter(Sample == "Random") |>
+  mutate(name = str_remove(name, "d_"), value = -value) |> # Reverse score for figure aesthetics
   ggplot(aes(x=value, y=name)) +
@@
   labs(x="Similarity Difference", y="Indices of pattern difference",
-       title="To which matrix is the random one more similar?",
+       title="Which matrix is the above more similar to?",
        fill="More similar to") +
   theme_minimal() +
-  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))
+  scale_fill_manual(values=c("TRUE"="#4CAF50", "FALSE"="#2196F3"), 
+                    labels = c("By facet", "By modality"),
+                    guide = guide_legend(reverse = TRUE)) +
+  theme(plot.title = element_text(hjust = 0.5, face="italic"))
 
@@
 
-p1 / (p2 | p_sim | p3) +
+fig1 <- p1 / (p3 | p_sim | p2) +
   patchwork::plot_layout(heights=c(3, 1)) +
   patchwork::plot_annotation(
-    title="Effect of Item-presentation Grouping",
+    title="Effect of Item Grouping",
     theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
+fig1
+
+ggsave("figures/fig1_correlations.png", fig1, scale = 1.25, width=2100, height=2100, dpi=300, units = "px")
 ```
@@
 ## Item Selection
+
+### Distributions
+
+```{r}
+items |> 
+  bayestestR::estimate_density(method="kernSmooth") |> 
+  separate(Parameter, into=c("Facet", "Modality", "Item"), sep="_") |>
+  ggplot(aes(x=x, y=y)) +
+  geom_line(aes(color=Facet, group=interaction(Facet, Item)), linewidth=1, alpha=0.9) +
+  facet_wrap(~Modality) +
+  theme_minimal() +
+  scale_color_material_d(palette = "rainbow") +
+  theme(axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+```
 

### 2025-06-23 study2/analysis/1_cleaning.qmd
bits and bobs

@@
                                          method=c("optics"),
-                                         threshold=list(optics=2.5, optics_xi=0.03)) |> 
+                                         threshold=list(optics=2.5, optics_xi=0.01)) |> 
   as.data.frame() |> 
@@
 
-outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 3, "Participant"])
+outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 3.3, "Participant"])
 outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]
@@
   geom_bar(aes(fill=Outlier), stat="identity") +
-  geom_hline(yintercept = 3, linetype="dashed", color="red") +
+  geom_hline(yintercept = 3.3, linetype="dashed", color="red") +
   labs(fill = "Status") +
@@
   geom_line() +
-  geom_vline(xintercept=3, linetype="dashed", color="red") +
+  geom_vline(xintercept=3.3, linetype="dashed", color="red") +
+  geom_hline(yintercept=1/3, linetype="dashed", color="black") +
   theme_minimal()

### 2025-06-23 study2/analysis/2_analysis.qmd
bits and bobs

@@
 
-items <- filter(df, !is.na(MINT_Awareness_ExAc_35)) 
+items <- df |> 
+   filter(!is.na(MINT_Awareness_ExAc_35)) |> 
+  select(starts_with("MINT_")) 
 names(items) <- str_remove(names(items), "MINT_")
@@
 dimensions <- list(
-  C08 = "CaCo",       # Cardiorespiratory Confusion
-  C01 = "UrIn",       # Urointestinal Inaccuracy
-  C02 = "Derm",       # Dermatoception
-  C10 = "CaNo",       # Cardiorespiratory Noticing
-  C13 = "Sati",       # Satiety Noticing
-
-  C14 = "SexS",       # Sexual Arousal Sensitivity
-  C07 = "StaS",       # State Specificity
-  C09 = "SexO",       # Sexual Organs Sensitivity
-  C03 = "ExAc",       # Expulsion Accuracy
-  C06 = "RelA",       # Relaxation Awareness
-
-  C05 = "Resp",       # Respiroception
-  C11 = "Card",       # Cardioception
-  C12 = "Gast",       # Gastroception
-  C04 = "Olfa"       # Olfactory Compensation
-
-  # C04 = "SexA",       # Sexual Arousal Awareness
-  # C08 = "UrSe",       # Urointestinal Sensitivity
-  # C12 = "Sign",       # Signalling
-  # C07 = "SexC"        # Sexual Arousal Changes  
+  C01 = "SexS",       # Sexual Arousal Sensitivity
+  C02 = "SexO",       # Sexual Organs Sensitivity
+  C03 = "Derm",       # Dermatoception
+  C04 = "StaS",       # State Specificity
+  C05 = "Card",       # Cardioception
+  C06 = "Sati",       # Satiety Noticing
+  C07 = "Gast",       # Gastroception
+  C08 = "Olfa",       # Olfactory Compensation
+  C09 = "Resp",       # Respiroception
+  C10 = "RelA",       # Relaxation Awareness
+  C11 = "Urin",       # Urointestinal Inaccuracy
+  C12 = "ExAc",       # Expulsion Accuracy
+  C13 = "CaCo",       # Cardiorespiratory Confusion
+  C14 = "CaNo"        # Cardiorespiratory Noticing
 )
@@
     subtitle = "Node centrality"
+  ) |> 
+  # Metacluster 1
+  gt::tab_style(
+    style = gt::cell_fill(color = "#B39DDB"),
+    locations = list(
+      gt::cells_column_labels(columns = 3),
+      gt::cells_body(columns="Item", rows=c(4:6))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#9FA8DA"),
+    locations = list(
+      gt::cells_column_labels(columns = 4),
+      gt::cells_body(columns="Item", rows=c(7:9))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#90CAF9"),
+    locations = list(
+      gt::cells_column_labels(columns = 5),
+      gt::cells_body(columns="Item", rows=c(1, 10:12))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81D4FA"),
+    locations = list(
+      gt::cells_column_labels(columns = 6),
+      gt::cells_body(columns="Item", rows=c(13:15))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#80DEEA"),
+    locations = list(
+      gt::cells_column_labels(columns = 7),
+      gt::cells_body(columns="Item", rows=c(16:18))
+    )
   ) 
@@
 ```{r}
-df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
-df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
-# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin))
-
-df$MINT_Sensitivity_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
-df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
-df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
-# df$MINT_LackSensitivity <- rowMeans(select(df, MINT_Sensitivity_Derm, MINT_Deficit_Sati, MINT_Deficit_CaNo))
-
 df$MINT_Awareness_SexS <- rowMeans(select(df, starts_with("MINT_Awareness_SexS")), na.rm = TRUE)
@@
 df$MINT_Awareness_RelA <- rowMeans(select(df, starts_with("MINT_Awareness_RelA")), na.rm = TRUE)
-df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))
 
+df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
+df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
+df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
+df$MINT_Deficit_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
+df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
+df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)
+
+df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
 df$MINT_Interoception_Card <- rowMeans(select(df, starts_with("MINT_Sensitivity_Card")), na.rm = TRUE)
-df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
 df$MINT_Interoception_Gast <- rowMeans(select(df, starts_with("MINT_Sensitivity_Gast")), na.rm = TRUE)
-df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
-
-df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)
-# df$MINT_Awareness_UrSe <- rowMeans(select(df, starts_with("MINT_Awareness_UrSe")), na.rm = TRUE)
-
-# df$MINT_Awareness <- rowMeans(select(df, starts_with("MINT_Awareness"), -matches("[[:digit:]]")))
 
 df <- df[names(df)[!grepl("MINT_.*[0-9]$", names(df))]]
-
-minti <- data.frame(
+# df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, 
+#                                      MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))
+# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, 
+#                                    MINT_Deficit_CaNo, MINT_Deficit_Sati, MINT_Sensitivity_Derm))
+# df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, 
+#                                          MINT_Interoception_Gast))
+# 
+# 
+# minti <- data.frame(
 #   MINT_Deficit = df$MINT_Deficit,
-  MINT_Awareness = df$MINT_Awareness,
-  MINT_Interoception = df$MINT_Interoception
-)
+#   MINT_Awareness = df$MINT_Awareness,
+#   MINT_Interoception = df$MINT_Interoception
+# )
 ```
@@
 make_cor(select(df, starts_with("MINT"))) +
-  labs(x="", y="", title="Correlation between MINT dimensions") +
-  theme(axis.text.x = element_text(angle = 45, hjust=1, 
-                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
-                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
-                                          "plain", "plain")))
+  labs(x="", y="", title="Correlation between MINT dimensions") 
+  # theme(axis.text.x = element_text(angle = 45, hjust=1, 
+  #                                  face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
+  #                                         "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
+  #                                         "plain", "plain")))
+```
+
+### Short Version
+
+#### Unicity
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+
+mintg <- data.frame(
+  MINT_Awareness = rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, 
+                                   MINT_Awareness_ExaC, MINT_Awareness_RelA)),
+  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_CaNo, 
+                                 MINT_Deficit_Sati, MINT_Deficit_Derm, MINT_Deficit_Olfa)),
+  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp,
+                                       MINT_Interoception_Gast))
+)
+
+mintmin <- data.frame(
+  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_Sati)),
+  MINT_Awareness = rowMeans(select(df, MINT_Awareness_RelA, MINT_Awareness_ExaC, MINT_Awareness_StaS)),
+  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
+)
+
+mint6 <- data.frame(
+  MINT_Sexs = df$MINT_Awareness_SexS,
+  MINT_Derm = df$MINT_Deficit_Derm,
+  MINT_Olfa = df$MINT_Deficit_Olfa,
+  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_Sati)),
+  MINT_Awareness = rowMeans(select(df, MINT_Awareness_RelA, MINT_Awareness_ExaC, MINT_Awareness_StaS)),
+  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
+)
+
+# fa <- parameters::factor_analysis(features, n = 3, rotation = "oblimin", sort = TRUE) 
+# plot(fa)  
+# 
+# fa |> 
+#   select(Variable, Uniqueness) |> 
+#   arrange(desc(Uniqueness))
 ```
@@
 
-make_cor <- function(df1, df2) {
-  df1 |> 
-    correlation::correlation(df2, p_adjust="none") |> 
-    correlation::cor_sort() |>
-    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
-           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
-           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
-    ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
-    geom_tile() +
-    geom_text(aes(label=label), size=3) +
-    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
-    theme_minimal() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1),
-          legend.position = "none")
-}
-
 make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")),
@@
 
-```{r}
-select(df, starts_with("MINT"), starts_with("MAIA"), IAS, BPQ) |> 
-  parameters::factor_analysis(n=4, rotation="oblimin") |> 
-  plot()
-```
+Most correlated dimensions:
+- IAS: ExAc
+- Trusting: RelA
+- Noticing: Resp
+- Emotional Awareness; Resp
+- Body Listening: Gast
+- SelfRegulation: RelA
+- AttentionRegulation: RelA
+- BPQ: Card
 
@@
 # items_intero <- select(df, starts_with("MINT"), -matches("[[:digit:]]"), starts_with("MAIA"), IAS, BPQ)
-# rez <- umap::umap(datawizard::data_transpose(items_intero[complete.cases(items_intero),]))
+# rez <- umap::umap(t(items_intero[complete.cases(items_intero),]))
 # 
@@
   }
-  test$Predictors <- preds
+  # test$Predictors <- preds
   format(test, zap_small = TRUE)
@@
   m_mint <- lm(as.formula(paste0(outcome, " ~ .")),
-              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) |> 
-    step(direction = "both", trace=0)
-  m_minti <- lm(as.formula(paste0(outcome, " ~ .")),
-              data = cbind(minti, df[outcome])) |> 
-    step(direction = "both", trace=0)
+              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) # |> 
+    # step(direction = "both", trace=0)
+  m_mintg <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(mintg, df[outcome])) # |> 
+    # step(direction = "both", trace=0)
+  m_mintmin <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(mintmin, df[outcome])) # |> 
+    # step(direction = "both", trace=0)
+  m_mint6 <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(mint6, df[outcome])) # |> 
+    # step(direction = "both", trace=0)
   m_ias <- lm(as.formula(paste0(outcome, " ~ IAS")),
@@
   m_maia <- lm(as.formula(paste0(outcome, " ~ .")),
-                data = select(df, all_of(outcome), starts_with("MAIA"))) |> 
-    step(direction = "both", trace=0)
+                data = select(df, all_of(outcome), starts_with("MAIA"))) # |> 
+    # step(direction = "both", trace=0)
   m_maiai <- lm(as.formula(paste0(outcome, " ~ .")),
@@
                               -contains("NotWorrying"),
-                              -contains("NotDistracting"))) |> 
-    step(direction = "both", trace=0)
+                              -contains("NotDistracting"))) # |> 
+    # step(direction = "both", trace=0)
   m_maiamin <- lm(as.formula(paste0(outcome, " ~ .")),
                 data = select(df, all_of(outcome),
-                              MAIA_AttentionRegulation, # remove?
-                              MAIA_SelfRegulation, # remove?
+                              # MAIA_AttentionRegulation, # remove?
+                              # MAIA_SelfRegulation, # remove?
                               # MAIA_Trusting, # remove?
@@
                               MAIA_EmotionalAwareness,
-                              MAIA_Noticing)) |> 
-    step(direction = "both", trace=0)
+                              MAIA_Noticing)) # s|> 
+    # step(direction = "both", trace=0)
   m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
@@
 
-  models_full <- list(m_mint=m_mint, m_minti=m_minti, m_maia=m_maia, m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq)
+  models_full <- list(m_mint=m_mint, m_mintg=m_mintg, m_mintmin=m_mintmin, m_mint6=m_mint6, m_maia=m_maia, 
+                      m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq)
   test_all <- table_models(models_full)

### 2025-06-23 study2/analysis/0_preprocessing.R

@@ -6,8 +6,8 @@ options(warn = 2) # Stop on warnings
 
 # path <- "C:/Users/maisi/Box/InteroceptionScale/
 # path <- "C:/Users/dmm56/Box/Data/InteroceptionScale/"
-# path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
-path <- "C:/Users/asf25/Box/InteroceptionScale/"
+path <- "C:/Users/domma/Box/Data/InteroceptionScale/"
+# path <- "C:/Users/asf25/Box/InteroceptionScale/"
 
 
 
@@ -15,6 +15,7 @@ path <- "C:/Users/asf25/Box/InteroceptionScale/"
 
 convert_feet_to_meters <- function(height) {
   height[height == "I'm 5ft8"] <- "5'8"
+  height[height == "5 feet 9inch"] <- "5'9"
   height <- gsub("ft ", "'", tolower(height))
   height <- gsub("ft", "'", tolower(height))
   height <- gsub(" feet ", "'", tolower(height))
@@ -156,7 +157,8 @@ for (file in files) {
   # Detect "equivalent to a Bachelors" and "HND (college)" and convert to "Bachelor" and "High school"
   data_ppt$Education <- ifelse(stringr::str_detect(data_ppt$Education, "equivalent to a Bachelors"), "Bachelor", data_ppt$Education)
   data_ppt$Education <- ifelse(data_ppt$Education %in% c("3rd year BSc", "Bachelor non-university", "graduate certificate (Certificate IV)"), "Bachelor", data_ppt$Education)
-  data_ppt$Education <- ifelse(data_ppt$Education %in% c("NVQ 4", "Professional", "Vocational degree.", "level 3 nvq's", "tech college", "College - HND"), "High school", data_ppt$Education)
+  data_ppt$Education <- ifelse(data_ppt$Education %in% c("NVQ 4", "Professional", "Vocational degree.", "level 3 nvq's",
+                                                         "tech college", "College - HND", "Vocational diploma", "Vocational Qualification"), "High school", data_ppt$Education)
 
   data_ppt$Student <- ifelse(!is.null(resp$Student), resp$Student, NA)
   data_ppt$Country <- ifelse(!is.null(resp$Country), resp$Country, NA)
@@ -164,7 +166,7 @@ for (file in files) {
   # Ethnicity
[…]

### 2025-07-01 paper/manuscript.qmd
lesgoo

@@
 ---
-title: "**The MInt Scale: A Fresh Validation of the Multidimensional Interoception Questionnaire Outperforms the MAIA, BPQ and IAS**"
-shorttitle: "MInt Validation"
+title: "**The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS**"
+shorttitle: "Mint Validation"
 author:
@@
 #   **Significance Statement**. TODO.
-keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, MInt Validation, Body Awareness"
+keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, Mint Validation, Body Awareness"
 numbered-lines: false
@@
 
-# Study 1
+# Study 1: Item Selection
 
@@
 We excluded 191 for failing at least one attention check, and 10 based on measures significantly related to the probability of failing attention checks [namely, the multivariate distance obtained with the OPTICS algorithm, @theriault2024check].
-The final sample includes 559 participants (age = 37 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% United Kingdom, 26.65% United States).
+The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% UK, 26.65% USA).
 This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).
@@
 
-Based on the two goals outlined for this scale, namely to include different interoceptive modalities, and to explicitly state the context of the interoceptive experience (e.g., whether negative or positive), we generated items following a combinatorial approach, where each item's category was a combination of a specific modality and context (@fig-one).
+Based on the two goals outlined for this scale, namely to include different interoceptive modalities, and to explicitly state the context of the interoceptive experience (e.g., whether negative or positive), we generated items in a systematic way following a combinatory approach, where each item's category corresponds to the combination of a specific modality and context (@fig-one).
 
@@
 
-We firstly identified 7 "modalities" (cardiac, respiratory, gastric, genital, skin & temperature, bladder & colon, and a "general state" category corresponding to a holistic and general awareness of an interoceptive state or dimension).
-Through iterative refinement (e.g., splitting or merging different categories together), we then settled on 6 "facets", which encompass both *contexts* of experience (negative and positive arousal, namely anxious and sexual states), and potential distinct *mechanisms* (nociception & pleasure, sensitivity, accuracy, and confusion).
+We identified 7 "modalities" (cardiac, respiratory, gastric, genital, skin & temperature, bladder & colon, and a "general state" category corresponding to a holistic and general awareness of an interoceptive state or dimension).
+Through iterative refinement (e.g., splitting or merging different categories together), we settled on 6 "facets", which encompass both *contexts* of experience (negative and positive arousal, namely anxious and sexual states), and potential distinct *mechanisms* (nociception & pleasure, sensitivity, accuracy, and confusion).
 
-Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)].
+Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)].
 We additionally crafted 8 "attention check" items blending in (and distributed across) each category.
@@
 
+To avoid presenting all the 120 items on a single long and discouraging page, we split them into different pages.
 Participants were randomly assigned to one of three conditions, driving how items were grouped on the same page: 1) items grouped by modality (i.e., all cardiac items on the first page, all colon & bladder  items on the second, etc.), 2) items grouped by facet, or 3) items presented fully randomly (but balanced randomly across 6 pages).
 The order of the item on any given page and the order of the modalities/facets were randomized.
-Each participant completed the full set of 120 items, with the attention check items interspersed throughout.
+Each participant completed the full set of 120 items, with the 8 attention check items interspersed throughout.
 The online experiment was implemented using JsPsych [@de2015jspsych], and item responses were recorded using 7-points Likert scales (0 = Disagree, 6 = Agree).
@@
 
+Items deemed "redundant" (which can distort the item structure estimation by introducing multicollinearity or local dependencies) will be identified (using the recommended threshold of 0.25) using Unique Variable Analysis [UVA, @christensen2023unique], a novel and principled method derived from network psychometrics.
+
+The structure of the items will be analyzed using the recently-developed Exploratory Graph Analysis [EGA, @golino2017exploratory] framework, which allows to jointly estimate the number of dimensions (i.e., clusters of items), the structure, as well as its stability using bootstrapping [@golino2020investigating].
+At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them.
+Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, issues in estimation of the optimal factor numbers, and poor performance in complex population structures, while remaining comparable and interpretable [@christensen2021equivalency; @jimenez2023dimensionality].
+In particular, nodes communities (i.e., clusters of items) can be in practice interpreted as distinct "dimensions", similarly to traditional latent factors - but without explicitly assuming their existence [@christensen2021equivalency].
+
+After removing redundant items using UVA, we will iteratively fit hierarchical EGA models (which additionally estimates higher-order "meta" clusters) using "glasso" [**REF**] and the "leiden" algorithm [**REF**] for community detection, refining the item pool at each step.
+We will start by removing items with a low (< 80%) cluster stability (i.e., volatile items which jump between clusters across bootstrapped samples), followed by odd items belonging to no clusters or pairs of items (i.e., we keep items belonging to clusters of more than 2 items).
+Finally, for each lower-level cluster, we will select the 3 items with the highest node centrality (i.e., the highest loading in the cluster).
+
 ## Results
@@
 Facet}} = 0.81$, $PSI_{\text{Random vs.
-Modality}} = 0.82$, $p = .51$; $RVadj_{\text{Random vs.
+Modality}} = 0.82$, $p = .45$; $RVadj_{\text{Random vs.
 Facet}} = 0.77$, $RVadj_{\text{Random vs.
-Modality}} = 0.78$, $p = .78$; $SMI_{\text{Random vs.
+Modality}} = 0.78$, $p = .74$; $SMI_{\text{Random vs.
 Facet}} = 0.49$, $SMI_{\text{Random vs.
-Modality}} = 0.51$, $p = .55$).
+Modality}} = 0.51$, $p = .52$).
+
+From the 120 initial items, UVA flagged 4 redundant items that we removed.
+We then removed 40 items that showed low cluster stability, and 9 items that were part of clusters with less than 3 items.
+Finally, We kept the 3 items with the highest loading in their lower-level structure (removing 13 items in the process), resulting in 54 items in the final item pool.
+
+The final hierarchical EGA model (Generalized Total Entropy Fit Index = -119.18) - in which all 54 items yielded a high cluster stability (> 90%) suggested 3 metaclusters and 15 lower-level clusters (each containing 3 items): "Interoceptive Deficits" (containing 5 clusters: *Urointestinal Inaccuracy* - UrIn; *Cardiorespiratory Confusion* - CaCo; *Cardiorespiratory Noticing* - CaNo; *Olfactory Compensation* - Olfa; *Satiety Noticing* - Sati), "Interoceptive Awareness" (containing 7 clusters: *Sexual Arousal Awareness* - SexA; *Sexual Arousal Sensitivity* - SexS; *Sexual Organs Sensitivity* - SexO; *Urointestinal Sensitivity* - UrSe; *Relaxation Awareness* - RelA; *State Specificity* - StaS; *Expulsion Accuracy* - ExAc), and "Interoceptive Sensitivity" (containing 6 clusters: *Cardioception* - Card; *Respiroception* - Resp; *Signalling* - Sign; *Gastroception* - Gast; *Dermal Hypersensitivity* - Derm; *Sexual Arousal Changes* - SexC).
+
+To further reduce and balance the remaining items, we collectively decided on removing the lower-level clusters *Sexual Arousal Awareness* (too general and overlapping with the other more specific sex-related items), *Signalling* (which items started with "when something important is happening in my life", which meaning we deemed too much open to interpretation), and *Sexual Arousal Changes* (low fit with the other modality-focused clusters of its group).
+The final set included 45 items.
+
+<!-- Interoceptive Deficits -->
+<!--   C01 = "UrIn",       # Urointestinal Inaccuracy -->
+<!--   C09 = "CaCo",       # Cardiorespiratory Confusion -->
+<!--   C13 = "CaNo",       # Cardiorespiratory Noticing -->
+<!--   C18 = "Olfa",       # Olfactory Compensation -->
+<!--   C03 = "Sati",       # Satiety Noticing -->
+<!-- Interoceptive Awareness -->
+<!--   C04 = "SexA",       # Sexual Arousal Awareness -->
+<!--   C06 = "SexS",       # Sexual Arousal Sensitivity -->
+<!--   C15 = "SexO",       # Sexual Organs Sensitivity -->
+<!--   C08 = "UrSe",       # Urointestinal Sensitivity -->
+<!--   C10 = "RelA",       # Relaxation Awareness -->
+<!--   C05 = "StaS",       # State Specificity -->
+<!--   C02 = "ExAc",       # Expulsion Accuracy -->
+<!-- Interoceptive Sensitivity -->
+<!--   C17 = "Card",       # Cardioception -->
+<!--   C14 = "Resp",       # Respiroception -->
+<!--   C12 = "Sign",       # Signalling -->
+<!--   C16 = "Gast",       # Gastroception -->
+<!--   C11 = "Derm",       # Dermal Hypersensitivity -->
+<!--   C07 = "SexC"        # Sexual Arousal Changes -->
+<!-- ) -->
 
@@
 
-Consistent bias across indices in favour of a greater similarity with the modality-grouping condition.
+Possible (although not at all significant) bias consistent across indices in favour of a greater similarity with the modality-grouping condition.
 
-# Study 2
+# Study 2: Validation
 
 TODO: write intro.
-Goal of study 2: to validate the MInt scale against other interoception scales.
+Goal of study 2: to validate the Mint scale against other interoception scales.
+
+## Methods
+
+### Participants
+
+We recruited 921 English-speaking participants via Prolific\textcopyright and SONA, from which 118 were excluded for failing at least one attention check and 6 based on multivariate distance (using the same procedure as for study 1).
+60 participants were further excluded due to missing data following a technical error.
+The final sample includes 737 participants (age = 36.8 $\pm$ 14.7 [18, 87]; 57.3\% women; Country of residence: 75.17% United Kingdom, 24.83% other).
+This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).
+
+### Procedure
+
+The experiment included the following questionnaires.
+
+#### Interoception Questionnaires
+
+##### The Multimodal Interoception Questionnaire (Mint)
+
+The 45 items of the Mint scale were presented in a random order, with the same 7-point Likert scale as in study 1 (0 = Disagree, 6 = Agree).
+
+##### Multidimensional Assessment of Interoceptive Awareness (MAIA)
+
+The X items of the MAIA...
+
+##### The Body Perception Questionnaire (BPQ)
+
+**TODO**
+
+##### The Interoceptive Awareness Scale (IAS)
+
+**TODO**
+
+#### Emotions and Cognition
+
+##### Toronto Alexithymia Scale (TAS-20)
+
+**TODO**
+
+##### Emotion Reactivity Scale (ERS)
+
+**TODO**
+
+##### Cognitive Emotion Regulation Questionnaire (CERQ)
+
+**TODO**
+
+##### TODO (CEFSA)
+
+**TODO**
+
+##### Primal World Beliefs (PI-18)
+
+**TODO**
+
+#### Health and Wellbeing
+
+##### Life Satisfaction, Depression and Anxiety (PHQ-4)
+
+**TODO**
+
+<!-- PHQ-4 + LS: presented together -->
+
+##### Mental Health
+
+Participants were asked to self-report any current, medically diagnosed psychiatric disorders using a checklist based on DSM-5 categories.
+If one or more conditions were endorsed, participants were asked to indicate any current treatments, including pharmacological (e.g., antidepressants, anxiolytics, antipsychotics, mood stabilizers), psychological (e.g., psychotherapy, mindfulness), or lifestyle interventions.
+Binary variables (0 = absent, 1 = present) were created to identify participants reporting mood disorders (MDD, GAD, Bipolar Disorder; with a stricter subgroup of participants undergoing a pharma- or psychological treatment), anxiety-centred disorders (GAD, Panic Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders, addiction-related disorders, borderline personality disorder, autism spectrum disorder (ASD), and ADHD.
+
+##### Somatic Health
+
+Participants were asked to select somatic symptoms or conditions they experienced from a list of 36 options.
+To facilitate mechanistic interpretation and reduce redundancy, answers were grouped into four non-overlapping clusters based on shared physiological pathways and known etiological mechanisms.
+The *Afferent Sensitivity* cluster included conditions associated with heightened interoceptive awareness and neurogenic excitability, such as migraine, neuropathy, dizziness, nausea, muscle tension, epilepsy, and frequent urination.
+The *Central Sensitization* cluster comprised syndromes characterized by chronic pain and fatigue, likely reflecting central amplification of sensory signals and HPA-axis dysregulation, such as fibromyalgia, chronic fatigue syndrome, chronic pain, back pain, pelvic pain, irritable bowel syndrome (IBS).
+The *Autonomic Dysfunction* cluster captured disorders linked to dysregulation of the autonomic and cardiopulmonary systems, including joint hypermobility, cardiac arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep apnea, chronic obstructive pulmonary disease (COPD), and chronic bronchitis.
+Finally, the *Immune-Inflammatory* cluster encompassed conditions associated with immune dysregulation, barrier dysfunction, and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes, asthma, celiac disease, gluten and lactose sensitivity, inflammatory bowel diseases (Crohn’s disease and ulcerative colitis), gastroesophageal reflux disease (GERD), multiple sclerosis, and Sjögren’s syndrome.
+<!-- Each symptom was assigned to a single cluster to preserve orthogonality and support subsequent analyses linking symptom profiles to interoceptive processes. -->
+We scored each cluster as a binary variable based on whether the participant selected at least one symptom from that cluster.
+
+#### Lifestyle
+
+**TODO**
+
+Physical activity.
+
+Wearables.
+
+#### Randomization
+
+In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned them into three groups (and randomized their order within them): (1) interoception questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18), and (3) pathology (somatic health, mental health, LS + PHQ-4, CEFSA).
+After completing demographic questions, participants always started with the Mint scale, and each following interoception questionnaire was interspersed with two questionnaires from the emotions and pathology groups.
+In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on https://github.com/RealityBending/InteroceptionScale].
+
+### Data Analysis
+
+We will start by confirming and further refining the structure of the Mint scale using the same EGA model as in Study 1.
+The convergent validity of the final set of items will be assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
+Then, we will test the predictive power of the Mint scale (relative to the other interoception questionnaires) on various measures.
+We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary
+
+```{r}
+#| label: fig-two
+#| fig-cap: "TODO." 
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/fig1.png")
+```
+
+##  Results
+
+```{r}
+#| label: fig-three
+#| fig-cap: "TODO." 
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/table1.png")
+```
+
+```{r}
+#| label: fig-four
+#| fig-cap: "TODO." 
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/fig2.png")
+```
+
+```{r}
+#| label: fig-five
+#| fig-cap: "TODO." 
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/fig3.png")
+```
+
+```{r}
+#| label: fig-six
+#| fig-cap: "TODO." 
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/table2.png")
+```
+
+## Discussion
+
+# General Discussion
 

### 2025-07-01 paper/manuscript.tex
lesgoo

@@
 
-\title{\textbf{The MInt Scale: A Fresh Validation of the
-Multidimensional Interoception Questionnaire Outperforms the MAIA, BPQ
-and IAS}}
+\title{\textbf{The Mint Scale: A Fresh Validation of the Multimodal
+Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS}}
 
-\shorttitle{MInt Validation}
+\shorttitle{Mint Validation}
 
@@
 \keywords{Interoception questionnaire, interoceptive accuracy scale,
-MAIA, MInt Validation, Body Awareness}
+MAIA, Mint Validation, Body Awareness}
 
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, opacityback=0, colframe=quarto-callout-note-color-frame, left=2mm, arc=.35mm, colback=white, bottomrule=.15mm, breakable, rightrule=.15mm, leftrule=.75mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, toprule=.15mm, arc=.35mm, left=2mm, breakable, colback=white, rightrule=.15mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]
 
@@
 
-\section{Study 1}\label{study-1}
+\section{Study 1: Item Selection}\label{study-1-item-selection}
 
@@
 \citeproc{ref-theriault2024check}{Thériault et al., 2024}). The final
-sample includes 559 participants (age = 37 \(\pm\) 12.2 {[}18, 77{]};
-50.8\% women; Country of residence: 63.86\% United Kingdom, 26.65\%
-United States). This study was approved by the University of Sussex'
-Ethics Committee (\textbf{NUMBER}).
+sample includes 559 participants (age = 37.0 \(\pm\) 12.2 {[}18, 77{]};
+50.8\% women; Country of residence: 63.86\% UK, 26.65\% USA). This study
+was approved by the University of Sussex' Ethics Committee
+(\textbf{NUMBER}).
 
@@
 of the interoceptive experience (e.g., whether negative or positive), we
-generated items following a combinatorial approach, where each item's
-category was a combination of a specific modality and context
-(Figure~\ref{fig-one}).
+generated items in a systematic way following a combinatorial approach,
+where each item's category was a combination of a specific modality and
+context (Figure~\ref{fig-one}).
 
@@
 
-Participants were randomly assigned to one of three conditions, driving
-how items were grouped on the same page: 1) items grouped by modality
-(i.e., all cardiac items on the first page, all colon \& bladder items
-on the second, etc.), 2) items grouped by facet, or 3) items presented
-fully randomly (but balanced randomly across 6 pages). The order of the
-item on any given page and the order of the modalities/facets were
-randomized. Each participant completed the full set of 120 items, with
-the attention check items interspersed throughout. The online experiment
-was implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
+To avoid presenting all the 120 items on a single long and discouraging
+page, we split them into different pages. Participants were randomly
+assigned to one of three conditions, driving how items were grouped on
+the same page: 1) items grouped by modality (i.e., all cardiac items on
+the first page, all colon \& bladder items on the second, etc.), 2)
+items grouped by facet, or 3) items presented fully randomly (but
+balanced randomly across 6 pages). The order of the item on any given
+page and the order of the modalities/facets were randomized. Each
+participant completed the full set of 120 items, with the attention
+check items interspersed throughout. The online experiment was
+implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
 2015}), and item responses were recorded using 7-points Likert scales (0
@@
 
+Items deemed ``redundant'' (which can distort the item structure
+estimation by introducing multicollinearity or local dependencies) will
+be identified (using the recommended threshold of 0.25) using Unique
+Variable Analysis (UVA, \citeproc{ref-christensen2023unique}{Christensen
+et al., 2023}), a novel and principled method derived from network
+psychometrics.
+
+The structure of the items will be analyzed using the recently-developed
+Exploratory Graph Analysis (EGA, \citeproc{ref-golino2017exploratory}{H.
+F. Golino \& Epskamp, 2017}) framework, which allows to jointly estimate
+the number of dimensions (i.e., clusters of items), the structure, as
+well as its stability using bootstrapping
+(\citeproc{ref-golino2020investigating}{H. Golino et al., 2020}). At a
+fundamental level, EGA conceptualizes variables as nodes in a network,
+with connections (edges) reflecting associations between them. Evidence
+has underlined its suitability as an alternative to traditional factor
+analysis, addressing some of its limitations such as the assumption of a
+``latent'' source of variability, issues in estimation of the optimal
+factor numbers, and poor performance in complex population structures,
+while remaining comparable and interpretable
+(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino, 2021};
+\citeproc{ref-jimenez2023dimensionality}{Jiménez et al., 2023}). In
+particular, nodes communities (i.e., clusters of items) can be in
+practice interpreted as distinct ``dimensions'', similarly to
+traditional latent factors - but without explicitly assuming their
+existence (\citeproc{ref-christensen2021equivalency}{Christensen \&
+Golino, 2021}).
+
+After removing redundant items using UVA, we will iteratively fit
+hierarchical EGA models (which additionally estimates higher-order
+``meta'' clusters) using ``glasso'' {[}\textbf{REF}{]} and the
+``leiden'' algorithm {[}\textbf{REF}{]} for community detection,
+refining the item pool at each step. We will start by removing items
+with a low (\textless{} 80\%) cluster stability (i.e., volatile items
+which jump between clusters across bootstrapped samples), followed by
+odd items belonging to no clusters or pairs of items (i.e., we keep
+items belonging to clusters of more than 2 items). Finally, for each
+lower-level cluster, we will select the 3 items with the highest node
+centrality (i.e., the highest loading in the cluster).
+
 \subsection{Results}\label{results}
@@
 (\(PSI_{\text{Random vs. Facet}} = 0.81\),
-\(PSI_{\text{Random vs. Modality}} = 0.82\), \(p = .51\);
+\(PSI_{\text{Random vs. Modality}} = 0.82\), \(p = .45\);
 \(RVadj_{\text{Random vs. Facet}} = 0.77\),
-\(RVadj_{\text{Random vs. Modality}} = 0.78\), \(p = .78\);
+\(RVadj_{\text{Random vs. Modality}} = 0.78\), \(p = .74\);
 \(SMI_{\text{Random vs. Facet}} = 0.49\),
-\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .55\)).
+\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .52\)).
+
+From the 120 initial items, UVA flagged 4 redundant items that we
+removed. We then removed 40 items that showed low cluster stability, and
+9 items that were part of clusters with less than 3 items. Finally, We
+kept the 3 items with the highest loading in their lower-level structure
+(removing 13 items in the process), resulting in 54 items in the final
+item pool.
+
+The final hierarchical EGA model (Generalized Total Entropy Fit Index =
+-119.18) - in which all 54 items yielded a high cluster stability
+(\textgreater{} 90\%) suggested 3 metaclusters and 15 lower-level
+clusters (each containing 3 items): ``Interoceptive Deficits''
+(containing 5 clusters: \emph{Urointestinal Inaccuracy} - UrIn;
+\emph{Cardiorespiratory Confusion} - CaCo; \emph{Cardiorespiratory
+Noticing} - CaNo; \emph{Olfactory Compensation} - Olfa; \emph{Satiety
+Noticing} - Sati), ``Interoceptive Awareness'' (containing 7 clusters:
+\emph{Sexual Arousal Awareness} - SexA; \emph{Sexual Arousal
+Sensitivity} - SexS; \emph{Sexual Organs Sensitivity} - SexO;
+\emph{Urointestinal Sensitivity} - UrSe; \emph{Relaxation Awareness} -
+RelA; \emph{State Specificity} - StaS; \emph{Expulsion Accuracy} -
+ExAc), and ``Interoceptive Sensitivity'' (containing 6 clusters:
+\emph{Cardioception} - Card; \emph{Respiroception} - Resp;
+\emph{Signalling} - Sign; \emph{Gastroception} - Gast; \emph{Dermal
+Hypersensitivity} - Derm; \emph{Sexual Arousal Changes} - SexC).
+
+To further reduce and balance the remaining items, we collectively
+decided on removing the lower-level clusters \emph{Sexual Arousal
+Awareness} (too general and overlapping with the other more specific
+sex-related items), \emph{Signalling} (which items started with ``when
+something important is happening in my life'', which meaning we deemed
+too much open to interpretation), and \emph{Sexual Arousal Changes} (low
+fit with the other modality-focused clusters of its group). The final
+set included 45 items.
 
@@
 
-\section{Study 2}\label{study-2}
+Possible (although not at all significant) bias consistent across
+indices in favour of a greater similarity with the modality-grouping
+condition.
 
-TODO: write intro. Goal of study 2: to validate the MInt scale against
+\section{Study 2: Validation}\label{study-2-validation}
+
+TODO: write intro. Goal of study 2: to validate the Mint scale against
 other interoception scales.
+
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Participants}\label{participants-1}
+
+We recruited 921 English-speaking participants via
+Prolific\textcopyright and SONA, from which 118 were excluded for
+failing at least one attention check and 6 based on multivariate
+distance (using the same procedure as for study 1). 60 participants were
+further excluded due to missing data following a technical error. The
+final sample includes 737 participants (age = 36.8 \(\pm\) 14.7 {[}18,
+87{]}; 57.3\% women; Country of residence: 75.17\% United Kingdom,
+24.83\% other). This study was approved by the University of Sussex'
+Ethics Committee (\textbf{NUMBER}).
+
+\subsubsection{Procedure}\label{procedure-1}
+
+The experiment included the following questionnaires.
+
+\paragraph{Interoception
+Questionnaires.}\label{interoception-questionnaires}
+
+\subparagraph{The Multimodal Interoception Questionnaire
+(Mint).}\label{the-multimodal-interoception-questionnaire-mint}
+
+The 45 items of the Mint scale were presented in a random order, with
+the same 7-point Likert scale as in study 1 (0 = Disagree, 6 = Agree).
+
+\subparagraph{Multidimensional Assessment of Interoceptive Awareness
+(MAIA).}\label{multidimensional-assessment-of-interoceptive-awareness-maia}
+
+The X items of the MAIA\ldots{}
+
+\subparagraph{The Body Perception Questionnaire
+(BPQ).}\label{the-body-perception-questionnaire-bpq}
+
+\textbf{TODO}
+
+\subparagraph{The Interoceptive Awareness Scale
+(IAS).}\label{the-interoceptive-awareness-scale-ias}
+
+\textbf{TODO}
+
+\paragraph{Emotions and Cognition.}\label{emotions-and-cognition}
+
+\subparagraph{Toronto Alexithymia Scale
+(TAS-20).}\label{toronto-alexithymia-scale-tas-20}
+
+\textbf{TODO}
+
+\subparagraph{Emotion Reactivity Scale
+(ERS).}\label{emotion-reactivity-scale-ers}
+
+\textbf{TODO}
+
+\subparagraph{Cognitive Emotion Regulation Questionnaire
+(CERQ).}\label{cognitive-emotion-regulation-questionnaire-cerq}
+
+\textbf{TODO}
+
+\subparagraph{TODO (CEFSA).}\label{todo-cefsa}
+
+\textbf{TODO}
+
+\subparagraph{Primal World Beliefs
+(PI-18).}\label{primal-world-beliefs-pi-18}
+
+\textbf{TODO}
+
+\paragraph{Health and Wellbeing.}\label{health-and-wellbeing}
+
+\subparagraph{Life Satisfaction, Depression and Anxiety
+(PHQ-4).}\label{life-satisfaction-depression-and-anxiety-phq-4}
+
+\textbf{TODO}
+
+\subparagraph{Mental Health.}\label{mental-health}
+
+Participants were asked to self-report any current, medically diagnosed
+psychiatric disorders using a checklist based on DSM-5 categories. If
+one or more conditions were endorsed, participants were asked to
+indicate any current treatments, including pharmacological (e.g.,
+antidepressants, anxiolytics, antipsychotics, mood stabilizers),
+psychological (e.g., psychotherapy, mindfulness), or lifestyle
+interventions. Binary variables (0 = absent, 1 = present) were created
+to identify participants reporting mood disorders (MDD, GAD, Bipolar
+Disorder; with a stricter subgroup of participants undergoing a pharma-
+or psychological treatment), anxiety-centred disorders (GAD, Panic
+Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders,
+addiction-related disorders, borderline personality disorder, autism
+spectrum disorder (ASD), and ADHD.
+
+\subparagraph{Somatic Health.}\label{somatic-health}
+
+Participants were asked to select somatic symptoms or conditions they
+experienced from a list of 36 options. To facilitate mechanistic
+interpretation and reduce redundancy, answers were grouped into four
+non-overlapping clusters based on shared physiological pathways and
+known etiological mechanisms. The \emph{Afferent Sensitivity} cluster
+included conditions associated with heightened interoceptive awareness
+and neurogenic excitability, such as migraine, neuropathy, dizziness,
+nausea, muscle tension, epilepsy, and frequent urination. The
+\emph{Central Sensitization} cluster comprised syndromes characterized
+by chronic pain and fatigue, likely reflecting central amplification of
+sensory signals and HPA-axis dysregulation, such as fibromyalgia,
+chronic fatigue syndrome, chronic pain, back pain, pelvic pain,
+irritable bowel syndrome (IBS). The \emph{Autonomic Dysfunction} cluster
+captured disorders linked to dysregulation of the autonomic and
+cardiopulmonary systems, including joint hypermobility, cardiac
+arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep
+apnea, chronic obstructive pulmonary disease (COPD), and chronic
+bronchitis. Finally, the \emph{Immune-Inflammatory} cluster encompassed
+conditions associated with immune dysregulation, barrier dysfunction,
+and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes,
+asthma, celiac disease, gluten and lactose sensitivity, inflammatory
+bowel diseases (Crohn's disease and ulcerative colitis),
+gastroesophageal reflux disease (GERD), multiple sclerosis, and
+Sjögren's syndrome. We scored each cluster as a binary variable based on
+whether the participant selected at least one symptom from that cluster.
+
+\paragraph{Lifestyle.}\label{lifestyle}
+
+\textbf{TODO}
+
+Physical activity.
+
+Wearables.
+
+\paragraph{Randomization.}\label{randomization}
+
+In order to avoid the repetition of similar types of questions and and
+balance longer and shorter questionnaires, we partitioned them into
+three groups (and randomized their order within them): (1) interoception
+questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18),
+and (3) pathology (somatic health, mental health, LS + PHQ-4, CEFSA).
+After completing demographic questions, participants always started with
+the Mint scale, and each following interoception questionnaire was
+interspersed with two questionnaires from the emotions and pathology
+groups. In order to make the experiment more enjoyable, the experiment
+ended with a radar chart summarizing the participants' responses to the
+Mint scale\footnote{The experiment can be tested by following the link
+  on https://github.com/RealityBending/InteroceptionScale}.
+
+\subsubsection{Data Analysis}\label{data-analysis-1}
+
+We will start by confirming and further refining the structure of the
+Mint scale using the same EGA model as in Study 1. The convergent
+validity of the final set of items will be assessed by computing the
+correlations between the Mint scale and the other interoception
+questionnaires (MAIA, BPQ, IAS). Then, we will test the predictive power
+of the Mint scale (relative to the other interoception questionnaires)
+on various measures. We will start by fitting regression (linear for
+continuous measures - e.g., depression score - and logistic for binary
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-two}}}}
+
+\begin{center}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig1.png}
+\end{center}
+
+\end{figure*}
+
+\subsection{Results}\label{results-1}
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-three}}}}
+
+\begin{center}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table1.png}
+\end{center}
+
+\end{figure*}
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-four}}}}
+
+\begin{center}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig2.png}
+\end{center}
+
+\end{figure*}
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-five}}}}
+
+\begin{center}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig3.png}
+\end{center}
+
+\end{figure*}
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-six}}}}
+
+\begin{center}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table2.png}
+\end{center}
+
+\end{figure*}
+
+\subsection{Discussion}\label{discussion-1}
+
+\section{General Discussion}\label{general-discussion}
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-christensen2023unique}
+Christensen, A. P., Garrido, L. E., \& Golino, H. (2023). Unique
+variable analysis: A network psychometrics method to detect local
+dependence. \emph{Multivariate Behavioral Research}, \emph{58}(6),
+1165--1182.
+
+\bibitem[\citeproctext]{ref-christensen2021equivalency}
+Christensen, A. P., \& Golino, H. (2021). On the equivalency of factor
+and network loadings. \emph{Behavior Research Methods}, \emph{53}(4),
+1563--1580.
+
 \bibitem[\citeproctext]{ref-de2015jspsych}
@@
 
+\bibitem[\citeproctext]{ref-golino2017exploratory}
+Golino, H. F., \& Epskamp, S. (2017). Exploratory graph analysis: A new
+approach for estimating the number of dimensions in psychological
+research. \emph{PloS One}, \emph{12}(6), e0174035.
+
+\bibitem[\citeproctext]{ref-golino2020investigating}
+Golino, H., Shi, D., Christensen, A. P., Garrido, L. E., Nieto, M. D.,
+Sadana, R., Thiyagarajan, J. A., \& Martinez-Molina, A. (2020).
+Investigating the performance of exploratory graph analysis and
+traditional techniques to identify the number of latent factors: A
+simulation and tutorial. \emph{Psychological Methods}, \emph{25}(3),
+292.
+
 \bibitem[\citeproctext]{ref-indahl2018similarity}
@@
 \emph{32}(10), e3049.
+
+\bibitem[\citeproctext]{ref-jimenez2023dimensionality}
+Jiménez, M., Abad, F. J., Garcia-Garzon, E., Golino, H., Christensen, A.
+P., \& Garrido, L. E. (2023). Dimensionality assessment in bifactor
+structures with multiple general factors: A network psychometrics
+approach. \emph{Psychological Methods}.
 

### 2025-07-01 study1/analysis/1_cleaning.qmd
lesgoo

@@
          .by="Condition") |>
+  mutate(Condition = str_replace(Condition, "Domains", "By Modality"),
+         Condition = str_replace(Condition, "Dimensions", "By Facet"),
+         Condition = str_replace(Condition, "Random", "Randomly")) |>
   ggplot(aes(y = Condition, x = n, fill = Experiment_Enjoyment)) +
@@
   labs(title="Experiment Enjoyment",
-       subtitle="Proportion of participants by condition") + 
+       subtitle="Proportion of participants by condition", 
+       y = "Items presented grouped...") + 
   guides(fill = guide_legend(reverse=TRUE)) +

### 2025-07-01 study1/analysis/2_analysis.qmd
lesgoo

@@
 set.seed(42)
+
+Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
 ```
@@
   rez <- data.frame()
-  for(i in 1:200) {
+  for(i in 1:500) {
     idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
@@
 ```{r}
-
-rez[rez$Comparison ==  "Random vs. Facet",  "d_PSI"] |> 
-  pd()
-rez[rez$Comparison ==  "Random vs. Facet" & rez$Sample == "Random",  "d_PSI"] |> 
-  pd()
-
 rez |> 
@@
   patchwork::plot_annotation(
-    title="Effect of Item Grouping",
+    title="Item Correlation Matrix Similarity",
     theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
@@
 ```
+
+We removed `r length(toremove1)` items (`r paste(toremove1, collapse=", ")`) based on Unique Variable Analysis (UVA).
 
@@
 toremove2 <- filter(itemstability_table, Max < 0.8)$Item
-toremove2 <- itemstability_table |> 
+```
+
+We removed `r length(toremove2)` items (`r paste(toremove2, collapse=", ")`) that had a low stability (< 0.8).
+
+```{r}
+toremove2b <- itemstability_table |> 
   filter(!Item %in% toremove2) |>
@@
   filter(n < 3) |>  # Remove small clusters
-  pull(Item) |> 
-  c(toremove2)
-```
+  pull(Item)
+
+toremove2 <- c(toremove2, toremove2b)
+```
+
+We removed `r length(toremove2b)` items (`r paste(toremove2b, collapse=", ")`) that were in clusters with less than 3 items after the first removal.
 
@@
 
-## Structure Analysis
+We kept the 3 items with the highest loading in their lower-level structure, removing `r length(toremove3)` items (`r paste(toremove3, collapse=", ")`).
+
+## Structure Analysis (Final Selection)
+
+### EGA
 
@@
 
+```{r}
+EGAnet::genTEFI(ega3$EGA)
+# cfa <- EGAnet::CFA(ega3$EGA, 
+#             items[colnames(ega3$lower_order$boot.wc)],
+#             estimator = "WLSMV")
+```
+
 ### Item Table
@@
 ```{r}
-#| message: false
+#| code-fold: false
 
@@
 
+``` 
+```{r}
+#| message: false
+
 higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order, loading.method="revised")$std))
@@
 
-gt::gtsave(gt::cols_hide(tab1, `|`), "table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
-
-Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
-
-gt::gtsave(tab1, "table1.png", vwidth=1660, expand=0, quiet=TRUE)
+gt::gtsave(gt::cols_hide(tab1, `|`), "figures/table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal
+
+gt::gtsave(tab1, "figures/table1.png", vwidth=1660, expand=0, quiet=TRUE)
 ```
@@
 # EGAnet::EGM(items[, 1:60])
-EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
-rez <- EGAnet::network.compare(byfacet, bymodality, model = "glasso", seed=3)
+# EGAnet::EGM.compare(items, model = "glasso", algorithm = "leiden")
+rez <- EGAnet::network.compare(byfacet[colnames(ega3$lower_order$boot.wc)], 
+                               bymodality[colnames(ega3$lower_order$boot.wc)], 
+                               model = "glasso", seed=3)
 

### 2025-07-01 study2/analysis/1_cleaning.qmd
lesgoo

@@
   gt::gt() |> 
-  gt::opt_stylize() |> 
-  gt::opt_interactive(use_compact_mode = TRUE) |> 
+  gt::grand_summary_rows(columns = "N", fns = Total ~ sum(.)) |> 
+  gt::opt_stylize(style = 2, color = "gray") |> 
   gt::tab_header("Number of participants per recruitment source") 
@@
 
-::: panel-tabset
+::: {.panel-tabset}
 
@@
 ```{r}
-df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "GAD|Bipolar"), TRUE, FALSE)
+df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
 df$Disorders_Psychiatric_MoodTreatment <- ifelse(
@@
   Neuropathy = ifelse(str_detect(df$Disorders_Somatic, "Neuropathy"), TRUE, FALSE),
-  # Epilepsy = ifelse(str_detect(df$Disorders_Somatic, "Epilepsy"), TRUE, FALSE),
+  Epilepsy = ifelse(str_detect(df$Disorders_Somatic, "Epilepsy"), TRUE, FALSE),
   MS = ifelse(str_detect(df$Disorders_Somatic, "Multiple Sclerosis"), TRUE, FALSE),
@@
 
+To facilitate mechanistic interpretation and reduce redundancy, self-reported somatic symptoms were grouped into four non-overlapping clusters based on shared physiological pathways and known etiological mechanisms.
+The **Afferent Sensitivity** cluster included conditions associated with heightened interoceptive awareness and neurogenic excitability, such as migraine, neuropathy, dizziness, nausea, muscle tension, epilepsy, and frequent urination.
+The **Central Sensitization** cluster comprised syndromes characterized by chronic pain and fatigue, likely reflecting central amplification of sensory signals and HPA-axis dysregulation; this included fibromyalgia, chronic fatigue syndrome, chronic pain, back pain, pelvic pain, endometriosis, irritable bowel syndrome (IBS), and interstitial cystitis.
+The **Autonomic Dysfunction** cluster captured disorders linked to dysregulation of the autonomic and cardiopulmonary systems, including joint hypermobility, cardiac arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep apnea, chronic obstructive pulmonary disease (COPD), and chronic bronchitis.
+Finally, the **Immune-Inflammatory** cluster encompassed conditions associated with immune dysregulation, barrier dysfunction, and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes, asthma, celiac disease, gluten and lactose sensitivity, inflammatory bowel diseases (Crohn’s disease and ulcerative colitis), gastroesophageal reflux disease (GERD), multiple sclerosis, and Sjögren’s syndrome.
+Each symptom was assigned to a single cluster to preserve orthogonality and support subsequent analyses linking symptom profiles to interoceptive processes.
+
 ```{r}
@@
 
-# 1. Autonomic Dysfunction & Anxiety-Somatic Symptoms
-# Mechanism: Dysregulated autonomic nervous system (e.g., panic disorder, dysautonomia, hyperventilation).
-df$Disorders_Somatic_Autonomic_N <- somatic |> 
-  select(Dizziness, ChestPain, ShortBreath, Arrhythmia, Nausea, Hypotension, Hypertension, MuscleTension) |> 
-  rowSums()
-df$Disorders_Somatic_Autonomic <- ifelse(df$Disorders_Somatic_Autonomic_N >= 1, TRUE, FALSE)
+# Cluster A: Afferent Sensitivity (neurogenic excitability, interoceptive hypervigilance)
+df$Disorders_Somatic_AfferentSensitivity_N <- rowSums(somatic[, c(
+  "Migraine", "Neuropathy", "MuscleTension", "Dizziness", 
+  "Nausea", "Epilepsy", "FrequentUrination"
+)])
+df$Disorders_Somatic_AfferentSensitivity <- df$Disorders_Somatic_AfferentSensitivity_N >= 1
 
-# 2. Functional Somatic Syndromes (Pain, Fatigue, GI Symptoms, and Anxiety)
-# Mechanism: Central sensitization, stress-induced HPA axis dysregulation, visceral hypersensitivity.
-df$Disorders_Somatic_Functional_N <- somatic |> 
-  select(Fibromyalgia, Neuropathy, Migraine, ChronicFatigue, ChronicPain, IBS, BackPain, PelvicPain, FrequentUrination) |> 
-  rowSums()
-df$Disorders_Somatic_Functional <- ifelse(df$Disorders_Somatic_Functional_N >= 1, TRUE, FALSE)
+# Cluster B: Central Sensitization (pain and fatigue syndromes)
+df$Disorders_Somatic_CentralSensitization_N <- rowSums(somatic[, c(
+  "Fibromyalgia", "ChronicPain", "ChronicFatigue", "BackPain", 
+  "PelvicPain", "Endometriosis", "IBS", "Cystitis"
+)])
+df$Disorders_Somatic_CentralSensitization <- df$Disorders_Somatic_CentralSensitization_N >= 1
 
-# 3. Hypervigilance, Mast Cell Dysfunction & Multi-System Reactivity
-# Mechanism: Mast cell activation, histamine intolerance, neuroinflammation, heightened interoception.
-df$Disorders_Somatic_Hyperreactivity_N <- somatic |> 
-  select(Migraine, SkinRashes, Nausea, FrequentUrination, Dizziness, MuscleTension, Endometriosis) |> 
-  rowSums()
-df$Disorders_Somatic_Hyperreactivity <- ifelse(df$Disorders_Somatic_Hyperreactivity >= 1, TRUE, FALSE)
+# Cluster C: Autonomic Dysfunction (dysautonomia and cardiorespiratory instability)
+df$Disorders_Somatic_AutonomicDysfunction_N <- rowSums(somatic[, c(
+  "Hypermobility", "Arrhythmia", "ChestPain", "ShortBreath", 
+  "Hypotension", "Hypertension", "SleepApnea", "COPD", "Bronchitis"
+)])
+df$Disorders_Somatic_AutonomicDysfunction <- df$Disorders_Somatic_AutonomicDysfunction_N >= 1
 
-# 4. Immune-Inflammatory & Gut-Brain Axis Dysregulation
-# Conditions: Celiac disease, gluten sensitivity, lactose intolerance, MS, neuropathy, eczema, asthma, IBS.
-# Mechanism: Leaky gut, immune activation, microbiome imbalance, chronic low-grade inflammation.
-df$Disorders_Somatic_Immune_N <- somatic |> 
-  select(Celiac, Gluten, Lactose, MS, Eczema, Asthma, IBS) |> 
-  rowSums()
-df$Disorders_Somatic_Immune <- ifelse(df$Disorders_Somatic_Immune_N >= 1, TRUE, FALSE)
-
-# 5. Cardiopulmonary & Stress-Linked Disorders
-# Mechanism: Vascular and respiratory dysregulation, autonomic instability, stress-exacerbated cardiovascular symptoms.
-df$Disorders_Somatic_Cardio_N <- somatic |> 
-  select(Arrhythmia, COPD, ChestPain, ShortBreath, Hypertension, SleepApnea) |> 
-  rowSums()
-df$Disorders_Somatic_Cardio <- ifelse(df$Disorders_Somatic_Cardio_N >= 1, TRUE, FALSE)
-
-# 6. Connective Tissue & Dysautonomia-Linked Disorders
-# Conditions: Hypermobility, Sjogren’s syndrome, hypotension, chronic fatigue, dizziness.
-# Mechanism: Connective tissue laxity affecting autonomic function (e.g., Ehlers-Danlos syndrome, POTS).
-df$Disorders_Somatic_Connective_N <- somatic |> 
-  select(Hypermobility, Hypotension, Sjogrens, Hypotension, ChronicFatigue, Dizziness) |> 
-  rowSums()
-df$Disorders_Somatic_Connective <- ifelse(df$Disorders_Somatic_Connective_N >= 1, TRUE, FALSE)
+# Cluster D: Immune-Inflammatory (gut-brain axis, autoimmune and barrier-related conditions)
+df$Disorders_Somatic_ImmuneInflammatory_N <- rowSums(somatic[, c(
+  "SkinRashes", "Eczema", "Psoriasis", "Sjogrens", "Asthma", 
+  "Celiac", "Gluten", "Lactose", "Crohn", "UlcerativeColitis", 
+  "GERD", "MS"
+)])
+df$Disorders_Somatic_ImmuneInflammatory <- df$Disorders_Somatic_ImmuneInflammatory_N >= 1
 

### 2025-07-01 study2/analysis/2_analysis.qmd
lesgoo

--- 2025-02-14 study2/analysis/2_analysis.qmd
@@
 set.seed(42)
-```
-
-```{r}
-#| code-fold: false
+
+Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
+```
+
+```{r}
+#| code-fold: true
 
 df <- read.csv("../data/data_participants.csv") |> 
-  filter(!is.na(MINT_Awareness_ExAc_35))
+  rename(MINT_Urin_1 = MINT_Deficit_Urin_1,
+         MINT_Urin_2 = MINT_Deficit_Urin_2,
+         MINT_Urin_3 = MINT_Deficit_Urin_3,
+         MINT_CaCo_1 = MINT_Deficit_CaCo_4,
+         MINT_CaCo_2 = MINT_Deficit_CaCo_5,
+         MINT_CaCo_3 = MINT_Deficit_CaCo_6,
+         MINT_CaNo_1 = MINT_Deficit_CaNo_7,
+         MINT_CaNo_2 = MINT_Deficit_CaNo_8,
+         MINT_CaNo_3 = MINT_Deficit_CaNo_9,
+         MINT_Olfa_1 = MINT_Deficit_Olfa_10,
+         MINT_Olfa_2 = MINT_Deficit_Olfa_11,
+         MINT_Olfa_3 = MINT_Deficit_Olfa_12,
+         MINT_Sati_1 = MINT_Deficit_Sati_13,
+         MINT_Sati_2 = MINT_Deficit_Sati_14,
+         MINT_Sati_3 = MINT_Deficit_Sati_15,
+         MINT_SexS_1 = MINT_Awareness_SexS_19,
+         MINT_SexS_2 = MINT_Awareness_SexS_20,
+         MINT_SexS_3 = MINT_Awareness_SexS_21,
+         MINT_SexO_1 = MINT_Awareness_SexO_22,
+         MINT_SexO_2 = MINT_Awareness_SexO_23,
+         MINT_SexO_3 = MINT_Awareness_SexO_24,
+         MINT_UrSe_1 = MINT_Awareness_UrSe_25,
+         MINT_UrSe_2 = MINT_Awareness_UrSe_26,
+         MINT_UrSe_3 = MINT_Awareness_UrSe_27,
+         MINT_RelA_1 = MINT_Awareness_RelA_28,
+         MINT_RelA_2 = MINT_Awareness_RelA_29,
+         MINT_RelA_3 = MINT_Awareness_RelA_30,
+         MINT_StaS_1 = MINT_Awareness_StaS_31,
+         MINT_StaS_2 = MINT_Awareness_StaS_32,
+         MINT_StaS_3 = MINT_Awareness_StaS_33,
+         MINT_ExAc_1 = MINT_Awareness_ExAc_34,
+         MINT_ExAc_2 = MINT_Awareness_ExAc_35,
+         MINT_ExAc_3 = MINT_Awareness_ExAc_36,
+         MINT_Card_1 = MINT_Sensitivity_Card_37,
+         MINT_Card_2 = MINT_Sensitivity_Card_38,
+         MINT_Card_3 = MINT_Sensitivity_Card_39,
+         MINT_Resp_1 = MINT_Sensitivity_Resp_40,
+         MINT_Resp_2 = MINT_Sensitivity_Resp_41,
+         MINT_Resp_3 = MINT_Sensitivity_Resp_42,
+         MINT_Gast_1 = MINT_Sensitivity_Gast_46,
+         MINT_Gast_2 = MINT_Sensitivity_Gast_47,
+         MINT_Gast_3 = MINT_Sensitivity_Gast_48,
+         MINT_Derm_1 = MINT_Sensitivity_Derm_49,
+         MINT_Derm_2 = MINT_Sensitivity_Derm_50,
+         MINT_Derm_3 = MINT_Sensitivity_Derm_51)
+
+colors <- c(Mint="#00BCD4", metaMint="#673AB7", miniMint="#26A36C", microMint="#8BC34A", 
+            IAS="#F44336", MAIA="#FFAD04",  iMAIA="#FF7811", BPQ="#795548")
 ```
@@
 names(items) <- str_remove(names(items), "MINT_")
-
-colors <- c(MINT="#00BCD4", MINTi="#00838F", IAS="#F44336", MAIA="#FF9800", MAIAi="#EF6C00", BPQ="#795548")
 ```
@@
 labels <- list(
-  MINT_Deficit_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
-  MINT_Deficit_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
-  MINT_Deficit_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
-  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
-  MINT_Deficit_CaCo_5 = "I often feel like I can't get enough oxygen by breathing normally",
-  MINT_Deficit_CaCo_6 = "Sometimes my heart starts racing and I often don't know why",
-  MINT_Deficit_CaNo_7 = "I often only notice how I am breathing when it becomes loud",
-  MINT_Deficit_CaNo_8 = "I only notice my heart when it is thumping in my chest",
-  MINT_Deficit_CaNo_9 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
-  MINT_Deficit_Olfa_10 = "I often check the smell of my armpits",
-  MINT_Deficit_Olfa_11 = "I often check the smell of my own breath",
-  MINT_Deficit_Olfa_12 = "I often check the smell of my farts",
-  MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
-  MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
-  MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
-  # MINT_Awareness_SexA_16 = "I always feel in my body if I am sexually aroused",
-  # MINT_Awareness_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
-  # MINT_Awareness_SexA_18 = "I always know when I am sexually aroused",
-  MINT_Awareness_SexS_19 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
-  MINT_Awareness_SexS_20 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
-  MINT_Awareness_SexS_21 = "My genital organs are very sensitive to pleasant stimulations",
-  MINT_Awareness_SexO_22 = "In general, I am very sensitive to changes in my genital organs",
-  MINT_Awareness_SexO_23 = "I can notice even very subtle changes in the state of my genital organs",
-  MINT_Awareness_SexO_24 = "I am always very aware of the state of my genital organs, even when I am calm",
-  MINT_Awareness_UrSe_25 = "In general, I am very aware of the sensations that are happening when I am urinating",
-  MINT_Awareness_UrSe_26 = "In general, I am very aware of the sensations that are happening when I am defecating",
-  MINT_Awareness_UrSe_27 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
-  MINT_Awareness_RelA_28 = "I always know when I am relaxed",
-  MINT_Awareness_RelA_29 = "I always feel in my body if I am relaxed",
-  MINT_Awareness_RelA_30 = "My body is always in the same specific state when I am relaxed",
-  MINT_Awareness_StaS_31 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
-  MINT_Awareness_StaS_32 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
-  MINT_Awareness_StaS_33 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
-  MINT_Awareness_ExAc_34 = "I can always accurately feel when I am about to burp",
-  MINT_Awareness_ExAc_35 = "I can always accurately feel when I am about to fart",
-  MINT_Awareness_ExAc_36 = "I can always accurately feel when I am about to sneeze",
-  MINT_Sensitivity_Card_37 = "In general, I am very sensitive to changes in my heart rate",
-  MINT_Sensitivity_Card_38 = "I can notice even very subtle changes in the way my heart beats",
-  MINT_Sensitivity_Card_39 = "I often notice changes in my heart rate",
-  MINT_Sensitivity_Resp_40 = "I can notice even very subtle changes in my breathing",
-  MINT_Sensitivity_Resp_41 = "I am always very aware of how I am breathing, even when I am calm",
-  MINT_Sensitivity_Resp_42 = "In general, I am very sensitive to changes in my breathing",
-  # MINT_Sensitivity_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
-  # MINT_Sensitivity_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
-  # MINT_Sensitivity_Sign_45 = "When something important is happening in my life, I can feel it in my body",
-  MINT_Sensitivity_Gast_46 = "I can notice even very subtle changes in what my stomach is doing",
-  MINT_Sensitivity_Gast_47 = "In general, I am very sensitive to what my stomach is doing",
-  MINT_Sensitivity_Gast_48 = "I am always very aware of what my stomach is doing, even when I am calm",
-  MINT_Sensitivity_Derm_49 = "In general, my skin is very sensitive",
-  MINT_Sensitivity_Derm_50 = "My skin is susceptible to itchy fabrics and materials",
-  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"
-  # MINT_Sensitivity_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
-  # MINT_Sensitivity_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
-  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"
+  MINT_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
+  MINT_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
+  MINT_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
+  MINT_CaCo_1 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
+  MINT_CaCo_2 = "I often feel like I can't get enough oxygen by breathing normally",
+  MINT_CaCo_3 = "Sometimes my heart starts racing and I often don't know why",
+  MINT_CaNo_1 = "I often only notice how I am breathing when it becomes loud",
+  MINT_CaNo_2 = "I only notice my heart when it is thumping in my chest",
+  MINT_CaNo_3 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
+  MINT_Olfa_1 = "I often check the smell of my armpits",
+  MINT_Olfa_2 = "I often check the smell of my own breath",
+  MINT_Olfa_3 = "I often check the smell of my farts",
+  MINT_Sati_1 = "I don't always feel the need to eat until I am really hungry",
+  MINT_Sati_2 = "Sometimes I don't realise I was hungry until I ate something",
+  MINT_Sati_3 = "I don't always feel the need to drink until I am really thirsty",
+  # MINT_SexA_16 = "I always feel in my body if I am sexually aroused",
+  # MINT_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
+  # MINT_SexA_18 = "I always know when I am sexually aroused",
+  MINT_SexS_1 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
+  MINT_SexS_2 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
+  MINT_SexS_3 = "My genital organs are very sensitive to pleasant stimulations",
+  MINT_SexO_1 = "In general, I am very sensitive to changes in my genital organs",
+  MINT_SexO_2 = "I can notice even very subtle changes in the state of my genital organs",
+  MINT_SexO_3 = "I am always very aware of the state of my genital organs, even when I am calm",
+  MINT_UrSe_1 = "In general, I am very aware of the sensations that are happening when I am urinating",
+  MINT_UrSe_2 = "In general, I am very aware of the sensations that are happening when I am defecating",
+  MINT_UrSe_3 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
+  MINT_RelA_1 = "I always know when I am relaxed",
+  MINT_RelA_2 = "I always feel in my body if I am relaxed",
+  MINT_RelA_3 = "My body is always in the same specific state when I am relaxed",
+  MINT_StaS_1 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
+  MINT_StaS_2 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
+  MINT_StaS_3 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
+  MINT_ExAc_1 = "I can always accurately feel when I am about to burp",
+  MINT_ExAc_2 = "I can always accurately feel when I am about to fart",
+  MINT_ExAc_3 = "I can always accurately feel when I am about to sneeze",
+  MINT_Card_1 = "In general, I am very sensitive to changes in my heart rate",
+  MINT_Card_2 = "I can notice even very subtle changes in the way my heart beats",
+  MINT_Card_3 = "I often notice changes in my heart rate",
+  MINT_Resp_1 = "I can notice even very subtle changes in my breathing",
+  MINT_Resp_2 = "I am always very aware of how I am breathing, even when I am calm",
+  MINT_Resp_3 = "In general, I am very sensitive to changes in my breathing",
+  # MINT_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
+  # MINT_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
+  # MINT_Sign_45 = "When something important is happening in my life, I can feel it in my body",
+  MINT_Gast_1 = "I can notice even very subtle changes in what my stomach is doing",
+  MINT_Gast_2 = "In general, I am very sensitive to what my stomach is doing",
+  MINT_Gast_3 = "I am always very aware of what my stomach is doing, even when I am calm",
+  MINT_Derm_1 = "In general, my skin is very sensitive",
+  MINT_Derm_2 = "My skin is susceptible to itchy fabrics and materials",
+  MINT_Derm_3 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"
+  # MINT_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
+  # MINT_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
+  # MINT_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"
 )
@@
     str_replace("MAIA_", ifelse(qname, "MAIA - ", "")) |> 
-    str_replace("_", " (") 
-  x <- ifelse(str_detect(x, "\\("), paste0(x, ")"), x)
+    str_replace("_", " - ")
 
@@
 
-### Cluster Stability
-
-#### Full
+### Full
+
+#### EGA
 
@@
   algorithm = "leiden",
+  allow.singleton = TRUE,
   type="resampling",
@@
 
-#### Final
+#### Hierarchical Clustering
 
@@
 #| fig-height: 14
+#| warning: false
+
+hclust <- pvclust::pvclust(items,
+                 method.hclust = "ward.D2",
+                 method.dist = "correlation",
+                 nboot = 1000, quiet=TRUE, parallel=TRUE)
+plot(hclust, hang = -1, cex = 0.5)
+pvclust::pvrect(hclust, alpha=0.95, max.only=TRUE)
+```
+
+### Item Reduction
+
+::: {.panel-tabset}
+
+```{r}
+features <- data.frame(
+  SexS = rowMeans(select(df, starts_with("MINT_SexS_")), na.rm = TRUE),
+  StaS = rowMeans(select(df, starts_with("MINT_StaS_")), na.rm = TRUE),
+  SexO = rowMeans(select(df, starts_with("MINT_SexO_")), na.rm = TRUE),
+  ExaC = rowMeans(select(df, starts_with("MINT_ExAc_")), na.rm = TRUE),
+  RelA = rowMeans(select(df, starts_with("MINT_RelA_")), na.rm = TRUE),
+  UrSe = rowMeans(select(df, starts_with("MINT_UrSe_")), na.rm = TRUE),
+  CaCo = rowMeans(select(df, starts_with("MINT_CaCo_")), na.rm = TRUE),
+  Urin = rowMeans(select(df, starts_with("MINT_Urin_")), na.rm = TRUE),
+  Sati = rowMeans(select(df, starts_with("MINT_Sati_")), na.rm = TRUE),
+  Derm = rowMeans(select(df, starts_with("MINT_Derm_")), na.rm = TRUE),
+  CaNo = rowMeans(select(df, starts_with("MINT_CaNo_")), na.rm = TRUE),
+  Olfa = rowMeans(select(df, starts_with("MINT_Olfa_")), na.rm = TRUE),
+  Resp = rowMeans(select(df, starts_with("MINT_Resp_")), na.rm = TRUE),
+  Card = rowMeans(select(df, starts_with("MINT_Card_")), na.rm = TRUE),
+  Gast = rowMeans(select(df, starts_with("MINT_Gast_")), na.rm = TRUE)
+)
+
+features$CardGast = rowMeans(select(features, Card, Gast), na.rm = TRUE)
+features$CardResp = rowMeans(select(features, Card, Resp), na.rm = TRUE)
+features$CardRespGast = rowMeans(select(features, Card, Resp, Gast), na.rm = TRUE)
+
+rez <- data.frame()
+for(outcome_group in c("Interoception", "Alexithymia", "Mood", "Mental", "Physical", "Biofeedback", "Dissociative", "ER", "Primals", "Lifestyle")) {
+  if(outcome_group == "Interoception") {
+    outcomes <- c("IAS", "BPQ", "MAIA_EmotionalAwareness", 
+                  "MAIA_BodyListening", "MAIA_SelfRegulation",
+                  "MAIA_AttentionRegulation", "MAIA_Trusting")
+  } else if(outcome_group == "Alexithymia") {
+    outcomes <- c("TAS_EOT", "TAS_DDF", "TAS_DIF")
+  } else if(outcome_group == "Mood") {
+    outcomes <- c("LifeSatisfaction", "PHQ4_Anxiety", "PHQ4_Depression", "ERS_Arousal", "ERS_Sensitivity", "ERS_Persistence")
+  } else if (outcome_group == "Mental") {
+    outcomes <- c("Disorders_Psychiatric_MoodTreatment", "Disorders_Psychiatric_AnxietyTreatment",
+                  "Disorders_Psychiatric_Eating", "Disorders_Psychiatric_Addiction",
+                  "Disorders_Psychiatric_Borderline", "Disorders_Psychiatric_Autism",
+                  "Disorders_Psychiatric_ADHD")
+  } else if (outcome_group == "Physical") {
+    outcomes <- c("Disorders_Somatic_AfferentSensitivity", "Disorders_Somatic_CentralSensitization_N",
+                  "Disorders_Somatic_AutonomicDysfunction", "Disorders_Somatic_ImmuneInflammatory")
+  } else if (outcome_group == "Biofeedback") {
+    outcomes <- c("Wearables_HeartImportance", "Wearables_StepsImportance", 
+                  "Wearables_SleepImportance", "Wearables_CalorieIntakeImportance",
+                  "Wearables_WeightImportance")
+  } else if (outcome_group == "Dissociative") {
+    outcomes <- names(select(df, starts_with("CEFSA_")))
+  } else if (outcome_group == "ER") {
+    outcomes <- names(select(df, starts_with("CERQ_"))) 
+  } else if (outcome_group == "Primals") {
+    outcomes <- names(select(df, starts_with("PI_")))
+  } else if (outcome_group == "Lifestyle") {
+    outcomes <- c("Physical_Active", "BMI")
+  }
+
+  out_group <- data.frame()
+  for(outcome in outcomes) {
+
+    out <- data.frame()
+    for(feature in names(features)) {
+
+      dat <- data.frame(Participant = df$Participant)
+      dat[[outcome]] <- df[[outcome]]
+      dat[[feature]] <- features[[feature]]
+      dat <- dat[!is.na(dat[[outcome]]) & !is.na(dat[[feature]]), ]
+
+      f <- as.formula(paste0(outcome, " ~ ", feature))
+      if(length(unique(dat[[outcome]])) > 2) {
+        m <- lm(f, data = dat)
+      } else {
+        m <- glm(f, data = dat, family = "binomial")
+      }
+      out <- rbind(out, data.frame(
+        Group = outcome_group,
+        Outcome = outcome,
+        Dimension = feature,
+        R2 = as.numeric(r2(m))[1]
+      ))
+    }
+
+    out$R2 <- as.numeric(normalize(out$R2))
+    out$Rank <- datawizard::ranktransform(1 - out$R2)
+    out_group <- rbind(out_group, out)
+  }
+
+  ave <- summarize(out_group, R2 = median(R2), Rank = min(Rank), .by="Dimension") |> 
+    mutate(Group = outcome_group, Outcome = outcome_group)
+
+  rez <- rbind(rez, out_group, ave)
+}
+
+grandave <- rez |> 
+  filter(Group != Outcome) |> 
+  summarize(R2 = mean(R2), Rank = min(Rank), .by="Dimension") |> 
+  mutate(Group = "Average", Outcome = "Average")
+```
+
+#### R2
+
+```{r}
+rbind(rez, grandave) |> 
+  select(-Group, -Rank) |> 
+  pivot_wider(names_from = "Outcome", values_from = "R2") |> 
+  mutate(Group = case_when(
+    Dimension %in% c("Card", "Resp", "Gast", "CardRespGast", "CardResp", "CardGast") ~ "Visceral", 
+    Dimension %in% c("RelA", "SexS", "ExaC", "StaS", "SexO", "UrSe") ~ "sensitivity", 
+    Dimension %in% c("CaCo", "Urin", "Derm", "Olfa", "Sati", "CaNo") ~ "Deficit", 
+    .default = "Other")) |> 
+  select(Group, Dimension, Average, Interoception, Biofeedback, ER, 
+         Primals, Alexithymia, Dissociative, Mood, 
+         Physical, Mental, Lifestyle) |>
+  arrange(Group, desc(Average)) |> 
+  # select(-Group) |> 
+  gt::gt() |> 
+  gt::data_color(
+    columns = -c(Dimension, Group),
+    palette = c("white", "green"),
+    domain = c(0, 1)
+  ) |>
+  gt::fmt_number() |>
+  gt::tab_header(
+    title = "Variable Importance",
+    subtitle = "Normalized Predictive Power (R2)"
+  ) |> 
+  gt::tab_row_group(
+    label = "Sensitivity",
+    rows = Group == "sensitivity"
+  )  |> 
+  gt::tab_row_group(
+    label = "Interoception",
+    rows = Group == "Visceral"
+  ) |> 
+  gt::tab_row_group(
+    label = "Deficit",
+    rows = Group == "Deficit"
+  ) |> 
+  gt::cols_hide(Group)
+```
+
+#### Rank
+
+```{r}
+rbind(rez, grandave) |> 
+  select(-Group, -R2) |> 
+  pivot_wider(names_from = "Outcome", values_from = "Rank") |> 
+  mutate(Group = case_when(
+    Dimension %in% c("Card", "Resp", "Gast", "CardRespGast", "CardResp", "CardGast") ~ "Visceral", 
+    Dimension %in% c("RelA", "SexS", "ExaC", "StaS", "SexO", "UrSe") ~ "sensitivity", 
+    Dimension %in% c("CaCo", "Urin", "Derm", "Olfa", "Sati", "CaNo") ~ "Deficit", 
+    .default = "Other")) |> 
+  datawizard::data_relocate(select=c("Group", "Dimension", "Average", "Interoception")) |>
+  arrange(Group, Average) |> 
+  gt::gt() |> 
+  # gt::fmt_number(columns = "Average") |>
+  gt::data_color(
+    columns = -c(Dimension, Group),
+    palette = c("green", "white"),
+    domain = c(1, 18)
+  ) |> 
+  gt::opt_interactive(page_size_default=20)
+```
+
+#### Clusters
+
+```{r}
+hclust2 <- rez |>
+  filter(Group != Outcome) |>
+  select(-Group, -Rank) |>
+  pivot_wider(names_from = "Dimension", values_from = "R2") |>
+  select(-Outcome) |>
+  pvclust::pvclust(
+     method.hclust = "average",
+     method.dist = "correlation",
+     nboot = 1000, quiet=TRUE, parallel=TRUE)
+
+plot(hclust2, hang = -1, cex = 0.5)
+pvclust::pvrect(hclust2, alpha=0.95, max.only=TRUE)
+```
+
+:::
+
+### Final
+
+```{r}
+#| fig-width: 10
+#| fig-height: 8
 #| fig-keep: "first"
+#| code-fold: false
 
 items <- items |> 
-  select(-contains("UrSe"))
-```
+  select(
+    -contains("UrSe"), # Unstable item
+    -contains("StaS"), # Too vague and overlapping
+    -contains("SexO"), # Overalapping with SexS
+
+    -contains("CaNo") # Overlap with CaCo
+    # -contains("Olfa"), # Unstable metacluster
+    # -contains("Sati")
+  )
+```
+
+::: {.panel-tabset}
+
+#### EGA
 
@@
   algorithm = "leiden",
+  # consensus.method = "lowest_tefi",
+  allow.singleton = TRUE,
   type="resampling",
@@
 itemstability <- EGAnet::itemStability(ega2, IS.plot=FALSE)
-plot(itemstability)
+p_stab <- plot(itemstability)
+p_stab
 ```
@@
 dimensions <- list(
-  C08 = "CaCo",       # Cardiorespiratory Confusion
-  C01 = "UrIn",       # Urointestinal Inaccuracy
-  C02 = "Derm",       # Dermatoception
-  C10 = "CaNo",       # Cardiorespiratory Noticing
-  C13 = "Sati",       # Satiety Noticing
-
-  C14 = "SexS",       # Sexual Arousal Sensitivity
-  C07 = "StaS",       # State Specificity
-  C09 = "SexO",       # Sexual Organs Sensitivity
-  C03 = "ExAc",       # Expulsion Accuracy
-  C06 = "RelA",       # Relaxation Awareness
-
-  C05 = "Resp",       # Respiroception
-  C11 = "Card",       # Cardioception
-  C12 = "Gast",       # Gastroception
-  C04 = "Olfa"       # Olfactory Compensation
-
-  # C04 = "SexA",       # Sexual Arousal Awareness
-  # C08 = "UrSe",       # Urointestinal Sensitivity
-  # C12 = "Sign",       # Signalling
-  # C07 = "SexC"        # Sexual Arousal Changes  
-)
-
-higher <- make_loadingtable(t(net.loads(ega2$EGA$higher_order, loading.method="revised")$std))
+  C01 = "SexS",       # Sexual Arousal Sensitivity
+  C02 = "Derm",       # Dermal Hypersensitivity
+  C03 = "Card",       # Cardioception
+  C04 = "Sati",       # Satiety Awareness
+  C05 = "Gast",       # Gastroception
+  C06 = "Olfa",       # Olfactory Compensation
+  C07 = "Resp",       # Respiroception
+  C08 = "RelA",       # Relaxation Awareness
+  C09 = "Urin",       # Urointestinal Inaccuracy
+  C10 = "ExAc",       # Expulsion Accuracy
+  C11 = "CaCo"       # Cardiorespiratory Confusion
+  # C01 = "C01",
+  # C02 = "C02",
+  # C03 = "C03",
+  # C04 = "C04",
+  # C05 = "C05",
+  # C06 = "C06",
+  # C07 = "C07",
+  # C08 = "C08",
+  # C09 = "C09",
+  # C10 = "C10",
+  # C11 = "C11",
+  # C12 = "C12"
+)
+
+higher <- make_loadingtable(t(net.loads(ega2$EGA$higher_order, loading.method="revised")$std)) |> 
+  arrange(Item)
 cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]
@@
   arrange(Cluster, desc(Max))
+dimensions <- dimensions[names(dimensions) %in% names(lower)]
 
@@
 # higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
-higher$Label <- ""
-# higher$ID  <- ""
+higher$Label <- c("Interoceptive Awareness", "Interoceptive Deficit", "Visceroception")
+higher$ID  <- ""
+
 lower <- mutate(lower, Label = labels[paste0("MINT_", Item)], ID=Item, Item = 1:n())
 
-rbind(higher, select(lower, -ID)) |>
-# rbind(higher, lower) |>
+tab1 <- rbind(higher, lower) |>
+  select(-ID) |>
   datawizard::data_relocate("Label", after = "Item") |>
-  datawizard::data_rename(names(dimensions), dimensions) |>
+  datawizard::data_rename(names(dimensions), dimensions[names(dimensions)]) |>
   select(-Cluster, -Max) |> 
@@
     style = gt::cell_text(size="small", style="italic"),
-    locations = gt::cells_body(columns="Label", rows=c(4:45))
+    locations = gt::cells_body(columns="Label", rows=c(4:36))
   ) |>
@@
     subtitle = "Node centrality"
-  ) 
-```
+  ) |> 
+  # Metacluster 1
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81C784"),
+    locations = list(
+      gt::cells_body(columns="Item", rows=c(1))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81C784"),
+    locations = list(
+      gt::cells_column_labels(columns = 3),
+      gt::cells_body(columns="Item", rows=c(4:6))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#AED581"),
+    locations = list(
+      gt::cells_column_labels(columns = 4),
+      gt::cells_body(columns="Item", rows=c(7:9))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#DCE775"),
+    locations = list(
+      gt::cells_column_labels(columns = 5),
+      gt::cells_body(columns="Item", rows=c(10:12))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#BA68C8"),
+    locations = list(
+      gt::cells_body(columns="Item", rows=c(2))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#BA68C8"),
+    locations = list(
+      gt::cells_column_labels(columns = 6),
+      gt::cells_body(columns="Item", rows=c(13:15))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#9575CD"),
+    locations = list(
+      gt::cells_column_labels(columns = 7),
+      gt::cells_body(columns="Item", rows=c(16:18))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#7986CB"),
+    locations = list(
+      gt::cells_column_labels(columns = 8),
+      gt::cells_body(columns="Item", rows=c(19:21))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#64B5F6"),
+    locations = list(
+      gt::cells_column_labels(columns = 9),
+      gt::cells_body(columns="Item", rows=c(22:24))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#4DD0E1"),
+    locations = list(
+      gt::cells_column_labels(columns = 10),
+      gt::cells_body(columns="Item", rows=c(25:27))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FF7811"),
+    locations = list(
+      gt::cells_body(columns="Item", rows=c(3))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFB74D"),
+    locations = list(
+      gt::cells_column_labels(columns = 11),
+      gt::cells_body(columns="Item", rows=c(28:30))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#E57373"),
+    locations = list(
+      gt::cells_column_labels(columns = 12),
+      gt::cells_body(columns="Item", rows=c(31:33))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#A1887F"),
+    locations = list(
+      gt::cells_column_labels(columns = 13),
+      gt::cells_body(columns="Item", rows=c(34:36))
+    )
+  ) 
+tab1
+```
+
+```{r}
+#| eva: false
+
+gt::gtsave(tab1, "figures/table1.png", vwidth=1660, expand=0, quiet=TRUE)
+```
+
+#### Hierarchical Clustering
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| warning: false
+
+rez <- pvclust::pvclust(items,
+                 method.hclust = "ward.D2",
+                 method.dist = "correlation",
+                 nboot = 1000, quiet=TRUE, parallel=TRUE)
+plot(rez, hang = -1, cex = 0.5)
+pvclust::pvrect(rez, alpha=0.95, max.only=FALSE)
+```
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+#| warning: false
+
+dendrogram <- as.dist(1 - cor(items, use = "pairwise.complete.obs")) |> 
+  hclust(method = "ward.D2") |> 
+  tidygraph::as_tbl_graph()
+
+# Process Nodes
+nodes <- as.list(dendrogram)$nodes |> 
+  mutate(Group = case_when(str_detect(label, "Card") ~ "Card", 
+                           str_detect(label, "Resp") ~ "Resp",
+                           str_detect(label, "Gast") ~ "Gast",
+                           str_detect(label, "SexS") ~ "SexS",
+                           str_detect(label, "RelA") ~ "RelA",
+                           str_detect(label, "ExAc") ~ "ExAc",
+                           str_detect(label, "Urin") ~ "Urin",
+                           str_detect(label, "CaCo") ~ "CaCo",
+                           str_detect(label, "Derm") ~ "Derm",
+                           str_detect(label, "Olfa") ~ "Olfa",
+                           str_detect(label, "Sati") ~ "Sati",
+                           label == "" ~ "NA",
+                           .default = "Other"),
+         Size = setNames(lower$Max, lower$ID)[label],
+         item = label)
+nodes$idx <- 1:nrow(nodes)
+
+# Rename accoring to table
+items_newnames <- lower |>
+  separate(ID, into = c("Group", "Item"), sep = "_", remove = FALSE) |>
+  mutate(Name = paste0(Group, "-", 1:nrow(lower)))
+items_newnames <- setNames(items_newnames$Name, items_newnames$ID)
+
+nodes$label <- items_newnames[nodes$label]
+nodes$label <- ifelse(is.na(nodes$label), "", nodes$label)
+
+# Central node 
+max_size  <- max(nodes$Size, na.rm = TRUE)
+nodes[nodes$height == max(nodes$height), c("Group", "Size")] <- data.frame(Group="Central", Size=2 * max_size)
+# Metaclusters
+nodes[17, c("Group", "Size")] <- data.frame(Group="Awareness", Size=1.5 * max_size)
+nodes[34, c("Group", "Size")] <- data.frame(Group="Visceroception", Size=1.5 * max_size)
+nodes[63, c("Group", "Size")] <- data.frame(Group="Deficit", Size=1.5 * max_size)
+
+# Process Edges
+edges <- as.list(dendrogram)$edges
+edges$linewidth = datawizard::rescale(nodes[edges$from, ]$height, to = c(0.1, 1))
+
+p_hclust <- tbl_graph(nodes = nodes, edges = edges) |> 
+  ggraph(layout = "dendrogram", circular = TRUE) +
+  # geom_edge_diagonal(strength = 0.7, linewidth = 1) +
+  geom_edge_elbow2(aes(edge_width=linewidth), color="darkgrey") +
+  geom_node_point(aes(filter=Group %in% c("Central"), size = Size), color="darkgrey") +
+  geom_node_point(aes(filter=Group %in% c("Visceroception", "Awareness", "Deficit"), color=Group, size = Size)) +
+  geom_node_text(aes(
+    label = ifelse(label != "NA", label, NA),
+    x = x * 1.05,
+    y = y * 1.05,
+    filter = label != "",
+    angle = ifelse(
+      x >= 0,
+      asin(y) * 360 / 2 / pi,
+      360 - asin(y) * 360 / 2 / pi
+    ),
+    hjust = ifelse(
+      x >= 0, 0, 1
+    ))) +
+  geom_node_point(aes(filter = label != "", color=Group, size=Size), alpha = 1) +
+  # geom_node_text(aes(label=idx)) +  # Debug
+  scale_edge_width_continuous(range=c(1, 3), guide = "none") +
+  scale_size_continuous(range=c(3, 11), guide = "none") +
+  scale_color_manual(values = c(
+    "Visceroception" = "#FF7811", "Card" = "#F44336", "Resp"="#FF9800", "Gast"="#795548",
+    "Awareness" = "#4CAF50", "ExAc"="#4CAF50", "RelA"="#8BC34A", "SexS" = "#CDDC39",
+    "Deficit" = "#9C27B0", "CaCo"="#9C27B0", "Urin" = "#673AB7", "Derm"="#3F51B5",
+    "Sati" = "#2196F3", "Olfa" = "#00BCD4"),
+                     breaks = c(
+                       "Awareness", "ExAc", "RelA", "SexS",
+                       "Deficit", "CaCo", "Urin", "Derm", "Sati", "Olfa",
+                       "Visceroception", "Resp", "Card", "Gast"
+                       ),
+                     labels=c(
+                       "***Awareness***", "ExAc", "RelA", "SexS",
+                       "***Deficit***", "CaCo", "Urin", "Derm", "Sati", "Olfa",
+                       "***Visceroception***", "Resp", "Card", "Gast"
+                       )) +
+  ggtitle("Hierarchical Clustering", subtitle = "Method = Correlation") +
+  coord_equal(clip = "off", xlim = c(-1.25, 1.25), ylim = c(-1.25, 1.25)) +
+  theme_void() + 
+  guides(color = guide_legend(override.aes = list(size = c(7.5, 5, 5, 3.5, 7.5, 5, 5, 3.5, 3.5, 3.5, 7.5, 5, 5, 3.5)))) +
+  theme(legend.text = ggtext::element_markdown(),
+        legend.title = element_blank(),
+        plot.title = element_blank(),  #element_text(face="bold")
+        plot.subtitle = element_blank())
+p_hclust
+```
+
+```{r}
+#| eval: FALSE
+
+ggsave("figures/fig1a.png", p_stab, width=10, height=10*0.8, dpi=300)
+ggsave("figures/fig1b.png", p_hclust, width=12, height=8, dpi=300)
+```
+
+#### EFA
+
+```{r}
+#| fig-width: 12
+#| fig-height: 14
+
+n <- parameters::n_factors(items)
+plot(n)
+
+fa <- parameters::factor_analysis(items, n = 9, rotation = "varimax", sort = TRUE)
+plot(fa)
+
+# fa |>
+#   select(Variable, Uniqueness) |>
+#   mutate(Group = str_extract(Variable, "^[A-Z][a-z]+")) |>
+#   mutate(Average = mean(Uniqueness), .by = "Group") |> 
+#   arrange(desc(Average), desc(Uniqueness)) |> 
+#   select(-Average, -Group) |> 
+#   gt::gt() |> 
+#   gt::data_color(
+#     columns = "Uniqueness",
+#     palette = c("red", "white", "green"),
+#     domain = c(0, 1) 
+#   ) 
+```
+
+:::
 
@@
 ```{r}
-df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
-df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
-# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin))
-
-df$MINT_Sensitivity_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
-df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
-df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
-# df$MINT_LackSensitivity <- rowMeans(select(df, MINT_Sensitivity_Derm, MINT_Deficit_Sati, MINT_Deficit_CaNo))
-
-df$MINT_Awareness_SexS <- rowMeans(select(df, starts_with("MINT_Awareness_SexS")), na.rm = TRUE)
-df$MINT_Awareness_StaS <- rowMeans(select(df, starts_with("MINT_Awareness_StaS")), na.rm = TRUE)
-df$MINT_Awareness_SexO <- rowMeans(select(df, starts_with("MINT_Awareness_SexO")), na.rm = TRUE)
-df$MINT_Awareness_ExaC <- rowMeans(select(df, starts_with("MINT_Awareness_ExaC")), na.rm = TRUE)
-df$MINT_Awareness_RelA <- rowMeans(select(df, starts_with("MINT_Awareness_RelA")), na.rm = TRUE)
-df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))
-
-df$MINT_Interoception_Card <- rowMeans(select(df, starts_with("MINT_Sensitivity_Card")), na.rm = TRUE)
-df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
-df$MINT_Interoception_Gast <- rowMeans(select(df, starts_with("MINT_Sensitivity_Gast")), na.rm = TRUE)
-df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
-
-df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)
-# df$MINT_Awareness_UrSe <- rowMeans(select(df, starts_with("MINT_Awareness_UrSe")), na.rm = TRUE)
-
-# df$MINT_Awareness <- rowMeans(select(df, starts_with("MINT_Awareness"), -matches("[[:digit:]]")))
+# Awareness
+df$MINT_SexS <- rowMeans(select(df, starts_with("MINT_SexS_")), na.rm = TRUE)
+df$MINT_ExaC <- rowMeans(select(df, starts_with("MINT_ExaC_")), na.rm = TRUE)
+df$MINT_RelA <- rowMeans(select(df, starts_with("MINT_RelA_")), na.rm = TRUE)
+# df$MINT_StaS <- rowMeans(select(df, starts_with("MINT_StaS_")), na.rm = TRUE)
+# df$MINT_SexO <- rowMeans(select(df, starts_with("MINT_SexO_")), na.rm = TRUE)
+# df$MINT_UrSe <- rowMeans(select(df, starts_with("MINT_UrSe_")), na.rm = TRUE)
+
+# Deficit
+df$MINT_Urin <- rowMeans(select(df, starts_with("MINT_Urin_")), na.rm = TRUE)
+df$MINT_CaCo <- rowMeans(select(df, starts_with("MINT_CaCo_")), na.rm = TRUE)
+df$MINT_Derm <- rowMeans(select(df, starts_with("MINT_Derm_")), na.rm = TRUE)
+# df$MINT_CaNo <- rowMeans(select(df, starts_with("MINT_CaNo_")), na.rm = TRUE)
+
+df$MINT_Sati <- rowMeans(select(df, starts_with("MINT_Sati_")), na.rm = TRUE)
+df$MINT_Olfa <- rowMeans(select(df, starts_with("MINT_Olfa_")), na.rm = TRUE)
+
+# Visceral
+df$MINT_Resp <- rowMeans(select(df, starts_with("MINT_Resp_")), na.rm = TRUE)
+df$MINT_Card <- rowMeans(select(df, starts_with("MINT_Card_")), na.rm = TRUE)
+df$MINT_Gast <- rowMeans(select(df, starts_with("MINT_Gast_")), na.rm = TRUE)
 
 df <- df[names(df)[!grepl("MINT_.*[0-9]$", names(df))]]
-
-minti <- data.frame(
-  # MINT_Deficit = df$MINT_Deficit,
-  MINT_Awareness = df$MINT_Awareness,
-  MINT_Interoception = df$MINT_Interoception
+```
+
+### Mini Versions
+
+```{r}
+mint <- select(df, starts_with("MINT_"))
+
+metamint <- data.frame(
+  MINT_Awareness = rowMeans(select(df, MINT_SexS, MINT_ExaC, MINT_RelA)),
+  MINT_Deficit = rowMeans(select(df, MINT_CaCo, MINT_Urin, MINT_Derm, MINT_Sati, MINT_Olfa)),
+  MINT_Visceroception = rowMeans(select(df, MINT_Card, MINT_Resp, MINT_Gast))
+)
+
+minimint <- data.frame(
+  MINT_Awareness = rowMeans(select(df, MINT_ExaC, MINT_RelA)),
+  MINT_Deficit = rowMeans(select(df, MINT_CaCo, MINT_Urin)),
+  MINT_Visceroception = rowMeans(select(df, MINT_Resp, MINT_Card))
+)
+
+micromint <- data.frame(
+  MINT_ExaC = df$MINT_ExaC,
+  MINT_CaCo = df$MINT_CaCo,
+  MINT_Resp = df$MINT_Resp
 )
@@
 
-make_cor <- function(df1, df2=NULL) {
-  df1 |> 
+make_cor <- function(df1, df2=NULL, qname_x=TRUE, qname_y=TRUE, textsize = 2.9, xcol = "#424242", ycol="#424242") {
+
+  r <- df1 |> 
     correlation::correlation(data2=df2, p_adjust="none", redundant=ifelse(is.null(df2), TRUE, FALSE)) |> 
@@
     mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
-           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
-           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
+           Parameter1 = cleanlabels(Parameter1, qname=qname_x),
+           Parameter2 = cleanlabels(Parameter2, qname=qname_y))
+  r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""
+
+  xnames <- levels(r$Parameter1)
+  ynames <- levels(r$Parameter2)
+
+  xcol <- case_when(
+    str_detect(xnames, "MINT") ~ "#00838F",
+    str_detect(xnames, "MAIA") ~ "#EF6C00",
+    str_detect(xnames, "IAS") ~ "#C62828",
+    str_detect(xnames, "BPQ") ~ "#795548",
+    .default = xcol
+  )
+  ycol <- case_when(
+    str_detect(ynames, "MINT") ~ "#00838F",
+    str_detect(ynames, "MAIA") ~ "#EF6C00",
+    str_detect(ynames, "IAS") ~ "#C62828",
+    str_detect(ynames, "BPQ") ~ "#795548",
+    .default = ycol
+  )
+  xbold <- case_when(
+    xnames %in% c("Awareness", "MINT - Awareness") ~ "bold",
+    str_detect(xnames, "Visceroception") ~ "bold",
+    str_detect(xnames, "Deficit") ~ "bold",
+    .default = "plain"
+  )
+  ybold <- case_when(
+    ynames %in% c("Awareness", "MINT - Awareness") ~ "bold",
+    str_detect(ynames, "Visceroception") ~ "bold",
+    str_detect(ynames, "Deficit") ~ "bold",
+    .default = "plain"
+  )
+
+  r |> 
     ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
     geom_tile() +
-    geom_text(aes(label=label), size=3) +
+    geom_text(aes(label=label), size=textsize) +
     scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
     theme_minimal() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1),
-          legend.position = "none")
-}
-
-make_cor(select(df, starts_with("MINT"))) +
-  labs(x="", y="", title="Correlation between MINT dimensions") +
-  theme(axis.text.x = element_text(angle = 45, hjust=1, 
-                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
-                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
-                                          "plain", "plain")))
+    theme(axis.text.x = element_text(angle = 45, hjust=1, color = xcol, face = xbold),
+          axis.text.y = element_text(color = ycol, face = ybold),
+          legend.position = "none",
+          axis.title = element_blank())
+}
+
+p_cormint <- make_cor(cbind(mint, metamint), qname_x = FALSE, qname_y = FALSE, textsize = 2.5,
+                      xcol = "#00838F", ycol = "#00838F") +
+  labs(title="Correlations between MINT dimensions") +
+  theme(axis.title = element_blank())
+
+p_cormint
 ```
@@
 
-make_cor <- function(df1, df2) {
-  df1 |> 
-    correlation::correlation(df2, p_adjust="none") |> 
-    correlation::cor_sort() |>
-    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
-           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
-           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
-    ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
-    geom_tile() +
-    geom_text(aes(label=label), size=3) +
-    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
-    theme_minimal() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1),
-          legend.position = "none")
-}
-
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")),
-         select(df, starts_with("MAIA"), IAS, BPQ)) +
-  labs(x="MINT", y="", title="Correlations between the MINT and other Interoception Questionnaires") +
-  theme(axis.text.x = element_text(angle = 45, hjust=1, 
-                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
-                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
-                                          "plain", "plain")))
-```
-
-```{r}
-select(df, starts_with("MINT"), starts_with("MAIA"), IAS, BPQ) |> 
-  parameters::factor_analysis(n=4, rotation="oblimin") |> 
-  plot()
-```
-
-```{r}
-# library(umap)
-# 
-# items_intero <- select(df, starts_with("MINT"), -matches("[[:digit:]]"), starts_with("MAIA"), IAS, BPQ)
-# rez <- umap::umap(datawizard::data_transpose(items_intero[complete.cases(items_intero),]))
-# 
-# rez
-# as.data.frame(rez$layout) |> 
-#   rownames_to_column(var="Variable") |> 
-#   separate(Variable, into=c("Questionnaire", "Dimension", "Sub"), fill="right") |> 
-#   ggplot(aes(x=V1, y=V2, color=Questionnaire)) +
-#   geom_point(size=3) +
-#   scale_color_manual(values=colors)
-```
+p_corintero <- make_cor(select(df, starts_with("MAIA"), IAS, BPQ),
+                        cbind(mint, metamint), qname_y = FALSE, textsize = 2.5,
+                        ycol = "#00838F") +
+  labs(title="MINT vs. Other Interoception Questionnaires") +
+  theme(axis.title = element_blank())
+p_corintero
+```
+
+Most correlated dimensions:
+- IAS: ExAc
+- Trusting: RelA
+- Noticing: Resp
+- Emotional Awareness: Resp
+- Body Listening: Gast
+- SelfRegulation: RelA
+- AttentionRegulation: RelA
+- BPQ: Card
 
@@
 ```{r}
-compare_models <- function(outcome="TAS_DIF") {
-
-  # Individual predictors
+table_models <- function(models) {
+  test <- test_performance(models)
+  table <- compare_performance(models, metrics=c("R2", "BIC"))
+  test$Model <- NULL
+  test$Omega2 <- NULL
+  test$p_Omega2 <- NULL
+  test$R2 <- table$R2
+  test$BIC <- table$BIC
+
+  preds <- c()
+  coefs <- c()
+  for(m in models){
+    x <- names(sort(abs(coef(m)[-1]), decreasing=TRUE))
+    preds <- c(preds, paste0(cleanlabels(x), collapse = ", "))
+    if(length(coef(m)) == 2) {
+      coefs <- c(coefs, coef(m)[2])
+    }
+  }
+
+  if(length(coefs) == length(models)) test$Coefficient <- coefs
+  format(test, zap_small = TRUE)
+}
+
+# Individual predictors ------------------------------------------------------
+
+compare_predictors <- function(outcome="TAS_DIF", family = "linear") {
+
   preds <- c("BPQ", "IAS", 
              names(select(df, starts_with("MINT"), -matches("[[:digit:]]"))),
-             names(select(df, starts_with("MAIA"))))
+             names(select(df, starts_with("MAIA"))),
+             names(metamint))
 
@@
   for(p in preds) {
-    models[[p]] <- lm(as.formula(paste0(outcome, " ~ ", p)), data=df)
+    if(length(unique(df[[outcome]])) > 2) {
+      if (family == "linear") {
+        models[[p]] <- lm(as.formula(paste0(outcome, " ~ ", p)), data=cbind(df, metamint))
+      } else {
+        models[[p]] <- glm(as.formula(paste0(outcome, " ~ ", p)), data=cbind(df, metamint), family=family)
+      }
+    } else {
+      models[[p]] <- glm(as.formula(paste0(outcome, " ~ ", p)), data=standardize(cbind(df, metamint), exclude=outcome), family="binomial")
+    }
   }
   perf <- compare_performance(models) |> 
-    arrange(desc(R2))
+    arrange(AIC)
 
@@
 
-  models <- list()
+  table <- table_models(models[c(best_mint, best_maia, "BPQ", "IAS")])
+
+  # Make plots --------------------------------------------------
   df_pred <- data.frame()
   for(p in c(best_mint, best_maia, "BPQ", "IAS")) {
-    models[[p]] <- lm(as.formula(paste0(outcome, " ~ ", p)), data=df)
     pred <- modelbased::estimate_relation(models[[p]], by=p, length=30) 
@@
 
-  test <- test_performance(models)
-
   cols <- colors
-  cols[[best_mint]] <- cols["MINT"]
+  cols[[best_mint]] <- cols["Mint"]
   cols[[best_maia]] <- cols["MAIA"]
@@
   p <- df_pred |>
-    mutate(Questionnaire = case_when(
-      str_detect(Predictor, "MINT") ~ "MINT", 
-      str_detect(Predictor, "MAIA") ~ "MAIA",
-      .default = Predictor)) |> 
+    mutate(Predictor = fct_rev(Predictor)) |> 
     ggplot(aes(x=Value, y=Predicted)) +
@@
 
+  list(table=table, p=p, outcome=outcome)
+}
+
+# Full Models ------------------------------------------------------
+
+compare_models_lm <- function(outcome="TAS_DIF") {
+
   # Full Questionnaires
   m_mint <- lm(as.formula(paste0(outcome, " ~ .")),
-              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) |> 
-    step(direction = "both", trace=0)
-  m_minti <- lm(as.formula(paste0(outcome, " ~ .")),
-              data = cbind(minti, df[outcome])) |> 
-    step(direction = "both", trace=0)
+              data = cbind(mint, df[outcome]))
+  m_metamint <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(metamint, df[outcome])) 
+  m_minimint <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(minimint, df[outcome])) 
+  m_micromint <- lm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(micromint, df[outcome])) 
   m_ias <- lm(as.formula(paste0(outcome, " ~ IAS")),
@@
   m_maia <- lm(as.formula(paste0(outcome, " ~ .")),
-                data = select(df, all_of(outcome), starts_with("MAIA"))) |> 
-    step(direction = "both", trace=0)
-  m_maiai <- lm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome), starts_with("MAIA"))) 
+  m_imaia <- lm(as.formula(paste0(outcome, " ~ .")),
                 data = select(df, all_of(outcome), 
@@
                               -contains("NotWorrying"),
-                              -contains("NotDistracting"))) |> 
-    step(direction = "both", trace=0)
+                              -contains("NotDistracting"))) 
+  m_imaia <- lm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome),
+                              # MAIA_AttentionRegulation, # remove?
+                              # MAIA_SelfRegulation, # remove?
+                              # MAIA_Trusting, # remove?
+                              MAIA_BodyListening, 
+                              MAIA_EmotionalAwareness,
+                              MAIA_Noticing))
   m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
@@
 
-  test_all <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
-  test_all$Predictors <- c(
-    paste0(cleanlabels(find_predictors(m_mint)$conditional), collapse = ", "),
-    paste0(cleanlabels(find_predictors(m_minti)$conditional), collapse = ", "),
-    "", 
-    paste0(cleanlabels(find_predictors(m_maia)$conditional), collapse = ", "),
-    paste0(cleanlabels(find_predictors(m_maiai)$conditional), collapse = ", "),
-    "")
-
-  list(test=test,  test_all=test_all, p=p)
-}
-
-rez1 <- compare_models("TAS_DIF")
-rez1$test
-rez1$p
-rez1$test_all
-
-rez2 <- compare_models("TAS_DDF")
-rez2$test
-rez2$p
-rez2$test_all
-
-rez3 <- compare_models("TAS_EOT")
-rez3$test
-rez3$p
-rez3$test_all
+  models_full <- list(m_mint=m_mint, m_metamint=m_metamint,
+                      m_minimint=m_minimint, m_micromint=m_micromint, 
+                      m_maia=m_maia, m_imaia=m_imaia, 
+                      m_ias=m_ias, m_bpq=m_bpq)
+  table_models(models_full)
+}
+```
+
+```{r}
+preds_dif <- compare_predictors("TAS_DIF")
+display(preds_dif$table, title="DIF")
+preds_dif$p
+mods_dif <- compare_models_lm("TAS_DIF")
+display(mods_dif, title="DIF")
+
+preds_ddf <- compare_predictors("TAS_DDF")
+display(preds_ddf$table, title="DDF")
+preds_ddf$p
+mods_ddf <- compare_models_lm("TAS_DDF")
+display(mods_ddf, title="DDF")
+
+preds_eot <- compare_predictors("TAS_EOT")
+display(preds_eot$table, title="EOT")
+preds_eot$p
+mods_eot <- compare_models_lm("TAS_EOT")
+display(mods_eot, title="EOT")
+```
+
+```{r}
+make_cor(select(df, starts_with("TAS_")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
 ```
@@
 ```{r}
-rez <- compare_models("LifeSatisfaction")
-rez$test
-rez$p
-rez$test_all
-
-rez <- compare_models("PHQ4_Anxiety")
-rez$test
-rez$p
-rez$test_all
-
-rez <- compare_models("PHQ4_Depression")
-rez$test
-rez$p
-rez$test_all
-```
+preds_ls <- compare_predictors("LifeSatisfaction")
+display(preds_ls$table, title="Life Satisfaction")
+preds_ls$p
+mods_ls <- compare_models_lm("LifeSatisfaction")
+display(mods_ls, title="Life Satisfaction")
+
+preds_anx <- compare_predictors("PHQ4_Anxiety")
+display(preds_anx$table, title="PHQ4 Anxiety")
+preds_anx$p
+mods_anx <- compare_models_lm("PHQ4_Anxiety")
+display(mods_anx, title="PHQ4 Anxiety")
+
+preds_dep <- compare_predictors("PHQ4_Depression")
+display(preds_dep$table, title="PHQ4 Depression")
+preds_dep$p
+mods_dep <- compare_models_lm("PHQ4_Depression")
+display(mods_dep, title="PHQ4 Depression")
+```
+
+```{r}
+make_cor(select(df, LifeSatisfaction, starts_with("PHQ4_")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
+```
+
+- CaCo and RelA
 
@@
 ```{r}
-rez <- compare_models("ERS_Arousal")
-rez$test
-rez$p
-rez$test_all
-
-rez <- compare_models("ERS_Sensitivity")
-rez$test
-rez$p
-rez$test_all
-
-rez <- compare_models("ERS_Persistence")
-rez$test
-rez$p
-rez$test_all
-```
+preds_arou <- compare_predictors("ERS_Arousal")
+display(preds_arou$table, title="ERS Arousal")
+preds_arou$p
+mods_arou <- compare_models_lm("ERS_Arousal")
+display(mods_arou, title="ERS Arousal")
+
+preds_sens <- compare_predictors("ERS_Sensitivity")
+display(preds_sens$table, title="ERS Sensitivity")
+preds_sens$p
+mods_sens <- compare_models_lm("ERS_Sensitivity")
+display(mods_sens, title="ERS Sensitivity")
+
+preds_pers <- compare_predictors("ERS_Persistence")
+display(preds_pers$table, title="ERS Persistence")
+preds_pers$p
+mods_pers <- compare_models_lm("ERS_Persistence")
+display(mods_pers, title="ERS Persistence")
+```
+
+```{r}
+make_cor(select(df, starts_with("ERS_")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
+```
+
+- CaCo
 
@@
 
+## Exploratory
+
+::: {.panel-tabset}
+
+### CEFSA
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("CEFSA")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("CEFSA")))
+```
+
+```{r}
+preds_cefsabody <- compare_predictors("CEFSA_Body")
+display(preds_cefsabody$table, title="CEFSA - Body")
+preds_cefsabody$p
+mods_cefsabody <- compare_models_lm("CEFSA_Body")
+display(mods_cefsabody, title="CEFSA - Body")
+
+preds_cefsaself <- compare_predictors("CEFSA_Self")
+display(preds_cefsaself$table, title="CEFSA - Self")
+preds_cefsaself$p
+mods_cefsaself <- compare_models_lm("CEFSA_Self")
+display(mods_cefsaself, title="CEFSA - Self")
+
+preds_cefsaemo <- compare_predictors("CEFSA_Emotion")
+display(preds_cefsaemo$table, title="CEFSA - Emotion")
+preds_cefsaemo$p
+mods_cefsaemo <- compare_models_lm("CEFSA_Emotion")
+display(mods_cefsaemo, title="CEFSA - Emotion")
+
+preds_cefsareal <- compare_predictors("CEFSA_Reality")
+display(preds_cefsareal$table, title="CEFSA - Reality")
+preds_cefsareal$p
+mods_cefsareal <- compare_models_lm("CEFSA_Reality")
+display(mods_cefsareal, title="CEFSA - Reality")
+
+preds_cefsacon <- compare_predictors("CEFSA_Connection")
+display(preds_cefsacon$table, title="CEFSA - Connection")
+preds_cefsacon$p
+mods_cefsacon <- compare_models_lm("CEFSA_Connection")
+display(mods_cefsacon, title="CEFSA - Connection")
+
+preds_cefsagency <- compare_predictors("CEFSA_Agency")
+display(preds_cefsagency$table, title="CEFSA - Agency")
+preds_cefsagency$p
+mods_cefsagency <- compare_models_lm("CEFSA_Agency")
+display(mods_cefsagency, title="CEFSA - Agency")
+```
+
+### Emotion Regulation
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("CERQ")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("CERQ")))
+```
+
+```{r}
+preds_cerqreapp <- compare_predictors("CERQ_PositiveReappraisal")
+display(preds_cerqreapp$table, title="CERQ - Positive Reappraisal")
+preds_cerqreapp$p
+mods_cerqreapp <- compare_models_lm("CERQ_PositiveReappraisal")
+display(mods_cerqreapp, title="CERQ - Positive Reappraisal")
+
+preds_cerqrefocus <- compare_predictors("CERQ_PositiveRefocusing")
+display(preds_cerqrefocus$table, title="CERQ - Positive Refocusing")
+preds_cerqrefocus$p
+mods_cerqrefocus <- compare_models_lm("CERQ_PositiveRefocusing")
+display(mods_cerqrefocus, title="CERQ - Positive Refocusing")
+
+preds_cerqpersp <- compare_predictors("CERQ_Perspective")
+display(preds_cerqpersp$table, title="CERQ - Perspective")
+preds_cerqpersp$p
+mods_cerqpersp <- compare_models_lm("CERQ_Perspective")
+display(mods_cerqpersp, title="CERQ - Perspective")
+
+preds_cerqacceptance <- compare_predictors("CERQ_Acceptance")
+display(preds_cerqacceptance$table, title="CERQ - Acceptance")
+preds_cerqacceptance$p
+mods_cerqacceptance <- compare_models_lm("CERQ_Acceptance")
+display(mods_cerqacceptance, title="CERQ - Acceptance")
+```
+
+### Primals
+
+```{r}
+make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
+         select(df, starts_with("PI")))
+
+make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
+         select(df, starts_with("PI")))
+```
+
+```{r}
+preds_pialive <- compare_predictors("PI_Alive")
+display(preds_pialive$table, title="Primals - Alive")
+preds_pialive$p
+mods_pialive <- compare_models_lm("PI_Alive")
+display(mods_pialive, title="Primals - Alive")
+
+preds_pisafe <- compare_predictors("PI_Safe")
+display(preds_pisafe$table, title="Primals - Safe")
+preds_pisafe$p
+mods_pisafe <- compare_models_lm("PI_Safe")
+display(mods_pisafe, title="Primals - Safe")
+
+preds_pient <- compare_predictors("PI_Enticing")
+display(preds_pient$table, title="Primals - Enticing")
+preds_pient$p
+mods_pient <- compare_models_lm("PI_Enticing")
+display(mods_pient, title="Primals - Enticing")
+
+preds_pigood <- compare_predictors("PI_Good")
+display(preds_pigood$table, title="Primals - Good")
+preds_pigood$p
+mods_pigood <- compare_models_lm("PI_Good")
+display(mods_pigood, title="Primals - Good")
+```
+
+:::
+
 ## Predictive
@@
 ```{r}
-compare_predictive <- function(outcome="Disorders_Psychiatric_Mood") {
+compare_models_glm <- function(outcome="Disorders_Psychiatric_Mood", title="", subtitle = "") {
+
+  # Full Questionnaires
   m_mint <- glm(as.formula(paste0(outcome, " ~ .")),
-              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$")),
-              family = "binomial") |> 
-  step(direction = "both", trace=0)
-
-  m_minti <- glm(as.formula(paste0(outcome, " ~ .")),
-              data = cbind(minti, df[outcome]),
-              family = "binomial") |> 
-    step(direction = "both", trace=0)
-
+              data = cbind(mint, df[outcome]),
+              family = "binomial")
+  m_metamint <- glm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(metamint, df[outcome]),
+              family = "binomial")
+  m_minimint <- glm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(minimint, df[outcome]),
+              family = "binomial") 
+  m_micromint <- glm(as.formula(paste0(outcome, " ~ .")),
+              data = cbind(micromint, df[outcome]),
+              family = "binomial") 
   m_ias <- glm(as.formula(paste0(outcome, " ~ IAS")),
@@
               family = "binomial")
-
   m_maia <- glm(as.formula(paste0(outcome, " ~ .")),
                 data = select(df, all_of(outcome), starts_with("MAIA")),
-                family = "binomial") |> 
-    step(direction = "both", trace=0)
-
-  m_maiai <- glm(as.formula(paste0(outcome, " ~ .")),
+              family = "binomial") 
+  m_imaia <- glm(as.formula(paste0(outcome, " ~ .")),
                 data = select(df, all_of(outcome), 
@@
                               -contains("NotDistracting")),
-                family = "binomial") |> 
-    step(direction = "both", trace=0)
-
+              family = "binomial")
+  m_imaia <- glm(as.formula(paste0(outcome, " ~ .")),
+                data = select(df, all_of(outcome),
+                              # MAIA_AttentionRegulation, # remove?
+                              # MAIA_SelfRegulation, # remove?
+                              # MAIA_Trusting, # remove?
+                              MAIA_BodyListening, 
+                              MAIA_EmotionalAwareness,
+                              MAIA_Noticing),
+              family = "binomial")
   m_bpq <- glm(as.formula(paste0(outcome, " ~ BPQ")),
@@
 
-  test <- test_performance(m_mint, m_minti, m_ias, m_maia, m_maiai, m_bpq)
+  models_full <- list(m_mint=m_mint, m_metamint=m_metamint, 
+                      m_minimint=m_minimint, m_micromint=m_micromint,
+                      m_maia=m_maia, m_imaia=m_imaia, 
+                      m_ias=m_ias, m_bpq=m_bpq)
+
+  table <- table_models(models_full)
 
@@
 
+  mods_order <- c("Mint", "metaMint", "miniMint", "microMint", "MAIA", "iMAIA", "IAS", "BPQ")
+
   p <- rbind(
-    mutate(as.data.frame(performance_roc(m_mint)), Predictor = "MINT"),
-    mutate(as.data.frame(performance_roc(m_minti)), Predictor = "MINTi"),
+    mutate(as.data.frame(performance_roc(m_mint)), Predictor = "Mint"),
+    mutate(as.data.frame(performance_roc(m_metamint)), Predictor = "metaMint"),
+    mutate(as.data.frame(performance_roc(m_minimint)), Predictor = "miniMint"),
+    mutate(as.data.frame(performance_roc(m_micromint)), Predictor = "microMint"),
+    mutate(as.data.frame(performance_roc(m_maia)), Predictor = "MAIA"),
+    mutate(as.data.frame(performance_roc(m_imaia)), Predictor = "iMAIA"),
     mutate(as.data.frame(performance_roc(m_ias)), Predictor = "IAS"),
-    mutate(as.data.frame(performance_roc(m_maia)), Predictor = "MAIA"),
-    mutate(as.data.frame(performance_roc(m_maiai)), Predictor = "MAIAi"),
     mutate(as.data.frame(performance_roc(m_bpq)), Predictor = "BPQ")
   ) |>
+    mutate(Predictor = fct_relevel(Predictor, mods_order)) |>
     ggplot(aes(x=Specificity)) +
-      geom_abline(intercept=0, slope=1, color="gray") +
-      geom_line(aes(y=Sensitivity, color=Predictor), linewidth=2, alpha=0.9) +
+    geom_abline(intercept=0, slope=1, color="gray", linewidth=1) +
+    geom_line(aes(y=Sensitivity, color=Predictor), linewidth=1.5, alpha=0.9) +
     geom_label(data=data.frame(
-        label = c(get_auc(m_mint), get_auc(m_minti), get_auc(m_ias), get_auc(m_maia), get_auc(m_maiai), get_auc(m_bpq)),
-        Predictor = c("MINT", "MINTi", "IAS", "MAIA", "MAIAi", "BPQ"),
-        x = 0.25,
-        y = c(0.65, 0.60, 0.55, 0.45, 0.35, 0.20)), 
-        aes(x=x, y=y, label=label), color=colors) +
+      label = c(get_auc(m_mint), get_auc(m_metamint), 
+                get_auc(m_minimint), get_auc(m_micromint), 
+                get_auc(m_maia), get_auc(m_imaia), get_auc(m_ias), get_auc(m_bpq)),
+      Predictor = mods_order,
+      x = 0.8,
+      y = c(0.55, 0.475, 0.425, 0.375, 0.30, 0.25, 0.20, 0.15)),
+      aes(x=x, y=y, label=label), color=colors[mods_order], size=3) +
     labs(x= "1 - Specificity (False Positive Rate)", y="Sensitivity (True Positive Rate)",
-           color="Questionnaire Version") +
+         color="Questionnaire", title = title, subtitle=subtitle) +
     scale_color_manual(values=colors) +
@@
     scale_y_continuous(labels=scales::percent) +
-      theme_minimal()
-
-  list(m_mint=m_mint, m_ias=m_ias, m_maia=m_maia, m_maiai=m_maiai, test=test, p=p)
-}
-```
-
-```{r}
-rez <- compare_predictive("Disorders_Psychiatric_Mood")
-rez$p
-```
-
-```{r}
-rez <- compare_predictive("Disorders_Psychiatric_MoodTreatment")
-rez$p
+    theme_minimal() +
+    theme(plot.title = element_text(face="bold"))
+
+  list(table=table, p=p)
+}
+```
+
+```{r}
+preds_mood <- compare_predictors("Disorders_Psychiatric_Mood")
+display(preds_mood$table, title="Mood Disorders")
+preds_mood$p
+mods_mood <- compare_models_glm("Disorders_Psychiatric_Mood")
+display(mods_mood$table, title="Mood Disorders")
+mods_mood$p
+```
+
+```{r}
+preds_moodt <- compare_predictors("Disorders_Psychiatric_MoodTreatment")
+display(preds_moodt$table, title="Mood Disorders (with Treatment)")
+preds_moodt$p
+mods_moodt <- compare_models_glm("Disorders_Psychiatric_MoodTreatment",
+                                 title="Mood Disorders", subtitle = "MDD, GAD, Bipolar (with Treatment)")
+display(mods_moodt$table, title="Mood Disorders (with Treatment)")
+mods_moodt$p
 ```
@@
 ```{r}
-rez <- compare_predictive("Disorders_Psychiatric_Anxiety")
-rez$p
-```
-
-```{r}
-rez <- compare_predictive("Disorders_Psychiatric_AnxietyTreatment")
-rez$p
+preds_anxdis <- compare_predictors("Disorders_Psychiatric_Anxiety")
+display(preds_anxdis$table, title="Anxiety Disorders")
+preds_anxdis$p
+mods_anxdis <- compare_models_glm("Disorders_Psychiatric_Anxiety")
+display(mods_anxdis$table, title="Anxiety Disorders")
+mods_anxdis$p
+```
+
+```{r}
+preds_anxdist <- compare_predictors("Disorders_Psychiatric_AnxietyTreatment")
+display(preds_anxdist$table, title="Anxiety Disorders (with Treatment)")
+preds_anxdist$p
+mods_anxdist <- compare_models_glm("Disorders_Psychiatric_AnxietyTreatment")
+display(mods_anxdist$table, title="Anxiety Disorders (with Treatment)")
+mods_anxdist$p
 ```
@@
 ```{r}
-rez <- compare_predictive("Disorders_Psychiatric_Eating")
-rez$p
+preds_eat <- compare_predictors("Disorders_Psychiatric_Eating")
+display(preds_eat$table, title="Eating Disorders")
+preds_eat$p
+mods_eat <- compare_models_glm("Disorders_Psychiatric_Eating")
+display(mods_eat$table, title="Eating Disorders")
+mods_eat$p
 ```
@@
 ```{r}
-rez <- compare_predictive("Disorders_Psychiatric_Addiction")
-rez$p
+preds_addict <- compare_predictors("Disorders_Psychiatric_Addiction")
+display(preds_addict$table, title="Addiction")
+preds_addict$p
+mods_addict <- compare_models_glm("Disorders_Psychiatric_Addiction")
+display(mods_addict$table, title="Addiction")
+mods_addict$p
 ```
@@
 ```{r}
-rez <- compare_predictive("Disorders_Psychiatric_ADHD")
-rez$p
+preds_adhd <- compare_predictors("Disorders_Psychiatric_ADHD")
+display(preds_adhd$table, title="ADHD")
+preds_adhd$p
+mods_adhd <- compare_models_glm("Disorders_Psychiatric_ADHD",
+                                title = "ADHD", subtitle = "Attention Deficit/Hyperactivity Disorder")
+display(mods_adhd$table, title="ADHD")
+mods_adhd$p
 ```
@@
 ```{r}
-rez <- compare_predictive("Disorders_Psychiatric_Autism")
-rez$p
+preds_asd <- compare_predictors("Disorders_Psychiatric_Autism")
+display(preds_asd$table, title="Autism")
+preds_asd$p
+mods_asd <- compare_models_glm("Disorders_Psychiatric_Autism",
+                                title = "ASD", subtitle = "Autism Spectrum Disorder")
+display(mods_asd$table, title="Autism")
+mods_asd$p
 ```
@@
 ```{r}
-# rez <- compare_predictive("Disorders_Psychiatric_Borderline")
-# rez$p
+preds_bpd <- compare_predictors("Disorders_Psychiatric_Borderline")
+display(preds_bpd$table, title="Borderline Personality Disorder")
+preds_bpd$p
+mods_bpd <- compare_models_glm("Disorders_Psychiatric_Borderline")
+display(mods_bpd$table, title="Borderline Personality Disorder")
+mods_bpd$p
 ```
@@
 
-#### Autonomic
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Autonomic")
-rez$p
-```
-
-#### Functional
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Functional")
-rez$p
-```
-
-#### Hyperreactivity
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Hyperreactivity")
-rez$p
-```
-
-#### Immune
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Immune")
-rez$p
-```
-
-#### Cardio
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Cardio")
-rez$p
-```
-
-#### Connective
-
-```{r}
-rez <- compare_predictive("Disorders_Somatic_Connective")
-rez$p
+#### Afferent Sensitivity
+
+```{r}
+preds_afferent <- compare_predictors("Disorders_Somatic_AfferentSensitivity")
+display(preds_afferent$table, title="Afferent Sensitivity Symptoms")
+preds_afferent$p
+mods_afferent <- compare_models_glm("Disorders_Somatic_AfferentSensitivity",
+                                    title="Afferent Sensitivity Symptoms",
+                                    subtitle = "Migraine, neuropathy, muscle tension, dizziness, ...")
+display(mods_afferent$table, title="Afferent Sensitivity Symptoms")
+mods_afferent$p
+```
+
+#### Central Sensitization
+
+```{r}
+preds_central <- compare_predictors("Disorders_Somatic_CentralSensitization")
+display(preds_central$table, title="Central Sensitization Symptoms")
+preds_central$p
+mods_central <- compare_models_glm("Disorders_Somatic_CentralSensitization",
+                                   title="Central Sensitization Symptoms",
+                                   subtitle = "Fibromyalgia, chronic fatigue, back pain, IBS, ...")
+display(mods_central$table, title="Central Sensitization Symptoms")
+mods_central$p
+```
+
+#### Autonomic Dysfunction
+
+```{r}
+preds_autonomic <- compare_predictors("Disorders_Somatic_AutonomicDysfunction")
+display(preds_autonomic$table, title="Autonomic Dysfunction")
+preds_autonomic$p
+mods_autonomic <- compare_models_glm("Disorders_Somatic_AutonomicDysfunction",
+                                     title="Autonomic Dysfunction",
+                                     subtitle = "Hypermobility, chest pain, hypo/hypertension, ....")
+display(mods_autonomic$table, title="Autonomic Dysfunction")
+mods_autonomic$p
+```
+
+#### Immune-Inflammatory
+
+```{r}
+preds_immune <- compare_predictors("Disorders_Somatic_ImmuneInflammatory")
+display(preds_immune$table, title="Immune-Inflammatory Symptoms")
+preds_immune$p
+mods_immune <- compare_models_glm("Disorders_Somatic_ImmuneInflammatory",
+                                  title="Immune-Inflammatory Symptoms",
+                                  subtitle = "Allergies, asthma, eczema, autoimmune, ...")
+display(mods_immune$table, title="Immune-Inflammatory Symptoms")
+mods_immune$p
 ```
@@
 
-### Biofeedback Usage
-
-```{r}
-model <- glm(as.formula(paste0("Wearables_Number ~ .")),
-              data = select(df, Wearables_Number, starts_with("MINT"), -matches("[[:digit:]]")),
-              family = "poisson") |> 
-  step(direction = "both", trace=0)
-
-parameters::parameters(model)
-
-model <- glm(as.formula(paste0("Wearables_Heart ~ .")),
-              data = df |>
-              mutate(Wearables_Heart = Wearables_Heart != "Not owning") |> 
-              select(Wearables_Heart, starts_with("MINT"), -matches("[[:digit:]]")),
-              family = "binomial") |> 
-  step(direction = "both", trace=0, k = log(nrow(df)))
-summary(model)
-
-model <- lm(as.formula(paste0("Wearables_HeartImportance ~ .")),
-              data = df |>
-              filter(!is.na(Wearables_HeartImportance)) |> 
-              select(Wearables_HeartImportance, starts_with("MINT"), -matches("[[:digit:]]"))) |> 
-  step(direction = "both", trace=0, k = log(nrow(filter(df, !is.na(Wearables_HeartImportance)))))
-
-parameters::parameters(model)
-```
-
-## Exploratory
-
-### CEFSA
-
-```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("CEFSA")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("CEFSA")))
-```
-
-### Emotion Regulation
-
-```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("CERQ")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("CERQ")))
-```
-
-### Primals
-
-```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("PI")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("PI")))
-```
+### Lifestyle and Demographic
+
+::: {.panel-tabset}
+
+#### Age
+
+```{r}
+preds_age <- compare_predictors("Age")
+display(preds_age$table, title="Age")
+preds_age$p
+mods_age <- compare_models_lm("Age")
+display(mods_age, title="Age")
+```
+
+#### Sex
+
+```{r}
+df$Sex <- ifelse(df$Gender == "Female", 1, ifelse(df$Gender == "Male", 0, NA))
+
+preds_sex <- compare_predictors("Sex")
+display(preds_sex$table, title="Sex")
+preds_sex$p
+mods_sex <- compare_models_glm("Sex")
+display(mods_sex$table, title="Sex")
+mods_sex$p
+```
+
+#### BMI
+
+```{r}
+preds_bmi <- compare_predictors("BMI")
+display(preds_bmi$table, title="BMI")
+preds_bmi$p
+mods_bmi <- compare_models_lm("BMI")
+display(mods_bmi, title="BMI")
+```
+
+#### Physical Activity
+
+```{r}
+preds_physactiv <- compare_predictors("Physical_Active")
+display(preds_physactiv$table, title="Physical Activity")
+preds_physactiv$p
+mods_physactiv <- compare_models_lm("Physical_Active")
+display(mods_physactiv, title="Physical Activity")
+```
+
+:::
+
+### Biofeedback Usage (Wearables)
+
+::: {.panel-tabset}
+
+#### Number of Wearables
+
+```{r}
+preds_wearN <- compare_predictors("Wearables_Number", family = "poisson")
+display(preds_wearN$table, title="Wearables Number")
+preds_wearN$p
+```
+
+#### Heart
+
+```{r}
+df$Wearables_HeartOwn <- ifelse(df$Wearables_Heart == "Not owning", 0, 1) 
+preds_wearHeartOwn <- compare_predictors("Wearables_HeartOwn")
+display(preds_wearHeartOwn$table, title="Wearables Heart Ownership")
+preds_wearHeartOwn$p
+mods_wearHeartOwn <- compare_models_glm("Wearables_HeartOwn")
+display(mods_wearHeartOwn$table, title="Wearables Heart Ownership")
+mods_wearHeartOwn$p
+
+preds_wearHeartImp <- compare_predictors("Wearables_HeartImportance")
+display(preds_wearHeartImp$table, title="Wearables Heart Importance")
+preds_wearHeartImp$p
+mods_wearHeartImp <- compare_models_lm("Wearables_HeartImportance")
+display(mods_wearHeartImp, title="Wearables Heart Importance")
+```
+
+#### Sleep
+
+```{r}
+df$Wearables_SleepOwn <- ifelse(df$Wearables_Sleep == "Not owning", 0, 1)
+preds_wearSleepOwn <- compare_predictors("Wearables_SleepOwn")
+display(preds_wearSleepOwn$table, title="Wearables Sleep Ownership")
+preds_wearSleepOwn$p
+mods_wearSleepOwn <- compare_models_glm("Wearables_SleepOwn")
+display(mods_wearSleepOwn$table, title="Wearables Sleep Ownership")
+
+preds_wearSleepImp <- compare_predictors("Wearables_SleepImportance")
+display(preds_wearSleepImp$table, title="Wearables Sleep Importance")
+preds_wearSleepImp$p
+mods_wearSleepImp <- compare_models_lm("Wearables_SleepImportance")
+display(mods_wearSleepImp, title="Wearables Sleep Importance")
+```
+
+#### Steps
+
+```{r}
+df$Wearables_StepsOwn <- ifelse(df$Wearables_Steps == "Not owning", 0, 1)
+preds_wearStepsOwn <- compare_predictors("Wearables_StepsOwn")
+display(preds_wearStepsOwn$table, title="Wearables Steps Ownership")
+preds_wearStepsOwn$p
+mods_wearStepsOwn <- compare_models_glm("Wearables_StepsOwn")
+display(mods_wearStepsOwn$table, title="Wearables Steps Ownership")
+
+preds_wearStepsImp <- compare_predictors("Wearables_StepsImportance")
+display(preds_wearStepsImp$table, title="Wearables Steps Importance")
+preds_wearStepsImp$p
+mods_wearStepsImp <- compare_models_lm("Wearables_StepsImportance")
+display(mods_wearStepsImp, title="Wearables Steps Importance")
+```
+
+#### Weight
+
+```{r}
+df$Wearables_WeightOwn <- ifelse(df$Wearables_Weight == "Not owning", 0, 1)
+preds_wearWeightOwn <- compare_predictors("Wearables_WeightOwn")
+display(preds_wearWeightOwn$table, title="Wearables Weight Ownership")
+preds_wearWeightOwn$p
+mods_wearWeightOwn <- compare_models_glm("Wearables_WeightOwn")
+display(mods_wearWeightOwn$table, title="Wearables Weight Ownership")
+
+preds_wearWeightImp <- compare_predictors("Wearables_WeightImportance")
+display(preds_wearWeightImp$table, title="Wearables Weight Importance")
+preds_wearWeightImp$p
+mods_wearWeightImp <- compare_models_lm("Wearables_WeightImportance")
+display(mods_wearWeightImp, title="Wearables Weight Importance")
+```
+
+:::
+
+## Summary Table
+
+```{r}
+make_table1 <- function(preds=preds_dif, mods=mods_dif, group = "Alexithymia", outcome = "TAS - DIF") {
+  yvar <- preds$outcome
+  preds <- preds$table
+
+  best_pred_mint <- preds[str_detect(preds$Name, "MINT"), ]
+  best_pred_nonmint <- preds[!str_detect(preds$Name, "MINT"), ]
+  best_pred_nonmint <- best_pred_nonmint[best_pred_nonmint$R2 == max(best_pred_nonmint$R2), ][1,]
+  best_models_R2 <- str_remove(arrange(mods, desc(as.numeric(R2)))$Name, "m_")
+  best_model_BIC <- str_remove(arrange(mods, as.numeric(BIC))$Name, "m_")
+
+  if(length(unique(df[[yvar]])) > 2) {
+    # LMs - display correlation
+    r_mint <- cor.test(cbind(df, metamint)[[best_pred_mint$Name[1]]], df[[yvar]])
+    r_mint <- paste0(insight::format_value(r_mint$estimate, zap_small = TRUE))
+    r_nonmint <- cor.test(df[[best_pred_nonmint$Name[1]]], df[[yvar]])
+    r_nonmint <- paste0(insight::format_value(r_nonmint$estimate, zap_small = TRUE))
+  } else {
+    # GLMs - display log-odds
+    r_mint <- best_pred_mint$Coefficient
+    r_nonmint <- best_pred_nonmint$Coefficient
+  }
+
+  # Format
+  best_models_R2[str_detect(best_models_R2, "mint")] <- paste0("<b>", best_models_R2[str_detect(best_models_R2, "mint")], "</b>")
+  best_model_BIC[str_detect(best_model_BIC, "mint")] <- paste0("<b>", best_model_BIC[str_detect(best_model_BIC, "mint")], "</b>")
+  best_models_R2 <- paste0("<small>", paste0(best_models_R2, collapse = " > "), "</small>")
+  best_model_BIC <- paste0("<small>", paste0(best_model_BIC, collapse = " > "), "</small>")
+
+  data.frame(
+    Group = group,
+    Outcome = outcome, 
+    Best_MINT_Predictor = paste0(str_remove(best_pred_mint$Name[1], "MINT_"), "<br><small><i>(", r_mint, ")</i></small>"),
+    Best_NonMINT_Predictor = paste0(str_replace(best_pred_nonmint$Name[1], "_", " - "), "<br><small><i>(",  r_nonmint, ")</i></small>"),
+    Best_Models_R2 = best_models_R2,
+    Best_Models_BIC = best_model_BIC
+    )
+}
+
+rez <- rbind(
+  make_table1(preds_dif, mods_dif, group = "Alexithymia", outcome = "Difficulty Identifying Feelings (DIF)<small><p align='right'><i>TAS-20</i></small><p>"),
+  make_table1(preds_ddf, mods_ddf, group = "Alexithymia", outcome = "Difficulty Describing Feelings (DDF)<small><p align='right'><i>TAS-20</i></small><p>"),
+  make_table1(preds_eot, mods_eot, group = "Alexithymia", outcome = "Externally Oriented Thinking (EOT)<small><p align='right'><i>TAS-20</i></small><p>"),
+
+  make_table1(preds_arou, mods_arou, group = "Emotion Reactivity", outcome = "Arousal<small><p align='right'><i>ERS</i></small><p>"),
+  make_table1(preds_sens, mods_sens, group = "Emotion Reactivity", outcome = "Sensitivity<small><p align='right'><i>ERS</i></small><p>"),
+  make_table1(preds_pers, mods_pers, group = "Emotion Reactivity", outcome = "Persistence<small><p align='right'><i>ERS</i></small><p>"),
+
+  make_table1(preds_ls, mods_ls, group = "Mood", outcome = "Life Satisfaction"),
+  make_table1(preds_anx, mods_anx, group = "Mood", outcome = "Anxiety<small><p align='right'><i>PHQ-4</i></small><p>"),
+  make_table1(preds_dep, mods_dep, group = "Mood", outcome = "Depression<small><p align='right'><i>PHQ-4</i></small><p>"),
+
+  make_table1(preds_moodt, mods_moodt$table, group = "Mental Health", outcome = "Mood Disorder"),
+  make_table1(preds_adhd, mods_adhd$table, group = "Mental Health", outcome = "ADHD"),
+  make_table1(preds_asd, mods_asd$table, group = "Mental Health", outcome = "Autism"),
+
+  make_table1(preds_afferent, mods_afferent$table, group = "Somatic Health", outcome = "Afferent Sensitivity<small><small><p align='right'><i>Migraine, neuropathy, muscle tension, dizziness, ...</i></small></small><p>"),
+  make_table1(preds_central, mods_central$table, group = "Somatic Health", outcome = "Central Sensitization<small><small><p align='right'><i>Fibromyalgia, chronic fatigue, back pain, IBS, ...</i></small></small><p>"),
+  make_table1(preds_autonomic, mods_autonomic$table, group = "Somatic Health", outcome = "Autonomic Dysfunction<small><small><p align='right'><i>Hypermobility, chest pain, hypo/hypertension, ...</i></small></small><p>"),
+  make_table1(preds_immune, mods_immune$table, group = "Somatic Health", outcome = "Immune-Inflammatory<small><small><p align='right'><i>Allergies, eczema, autoimmune, ...</i></small></small><p>"),
+
+  make_table1(preds_cefsabody, mods_cefsabody, group = "Dissociative Symptoms", outcome = "Body<small><p align='right'><i>CEFSA</i></small><p>"),
+  make_table1(preds_cefsaself, mods_cefsaself, group = "Dissociative Symptoms", outcome = "Self<small><p align='right'><i>CEFSA</i></small><p>"),
+  make_table1(preds_cefsaemo, mods_cefsaemo, group = "Dissociative Symptoms", outcome = "Emotions<small><p align='right'><i>CEFSA</i></small><p>"),
+  make_table1(preds_cefsareal, mods_cefsareal, group = "Dissociative Symptoms", outcome = "Reality<small><p align='right'><i>CEFSA</i></small><p>"),
+
+  # make_table1(preds_pialive, mods_pialive, group = "Primals", outcome = "Alive<small><p align='right'><i>PI-18</i></small><p>"),
+  # make_table1(preds_pisafe, mods_pisafe, group = "Primals", outcome = "Safe<small><p align='right'><i>PI-18</i></small><p>"),
+  # make_table1(preds_pient, mods_pient, group = "Primals", outcome = "Enticing<small><p align='right'><i>PI-18</i></small><p>"),
+  # make_table1(preds_pigood, mods_pigood, group = "Primals", outcome = "Good<small><p align='right'><i>PI-18</i></small><p>")
+
+  make_table1(preds_bmi, mods_bmi, group = "Lifestyle", outcome = "BMI"),
+  make_table1(preds_physactiv, mods_physactiv, group = "Lifestyle", outcome = "Physical Activity"),
+  # make_table1(preds_age, mods_age, group = "Lifestyle", outcome = "Age"),
+  make_table1(preds_wearHeartImp, mods_wearHeartImp, group = "Lifestyle", outcome = "Cardiac Monitoring"),
+  make_table1(preds_wearSleepImp, mods_wearSleepImp, group = "Lifestyle", outcome = "Sleep Monitoring"),
+  make_table1(preds_wearStepsImp, mods_wearStepsImp, group = "Lifestyle", outcome = "Steps Monitoring")
+  # make_table1(preds_wearWeightImp, mods_wearWeightImp, group = "Lifestyle", outcome = "Weight Monitoring")
+)
+
+tab2 <- rez |> 
+  gt::gt() |> 
+  gt::tab_header(
+    title = gt::md("**Interoceptive Questionnaires Comparison**"),
+    subtitle = "MINT vs. MAIA, IAS, BPQ"
+  ) |> 
+  gt::cols_width(
+    Outcome ~ gt::pct(23),
+    Best_MINT_Predictor ~ gt::pct(12),
+    Best_NonMINT_Predictor ~ gt::pct(15),
+    Best_Models_R2 ~ gt::pct(25),
+    Best_Models_BIC ~ gt::pct(25)
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_text(weight="bold", v_align = "middle"),
+    locations = gt::cells_column_labels()
+  )  |>
+  gt::tab_style(
+    style = gt::cell_text(align = "center", v_align = "middle"),
+    locations = gt::cells_body(columns=c("Best_MINT_Predictor", "Best_NonMINT_Predictor"))
+  )  |>
+  gt::tab_row_group(
+    label = "Lifestyle",
+    rows = Group == "Lifestyle"
+  ) |> 
+  gt::tab_row_group(
+    label = "Dissociative Symptoms",
+    rows = Group == "Dissociative Symptoms"
+  ) |> 
+  gt::tab_row_group(
+    label = "Primal World Beliefs",
+    rows = Group == "Primals"
+  ) |> 
+  gt::tab_row_group(
+    label = "Somatic Health",
+    rows = Group == "Somatic Health"
+  ) |> 
+  gt::tab_row_group(
+    label = "Mental Health",
+    rows = Group == "Mental Health"
+  ) |>
+  gt::tab_row_group(
+    label = "Mood",
+    rows = Group == "Mood"
+  ) |> 
+  gt::tab_row_group(
+    label = "Emotional Reactivity",
+    rows = Group == "Emotion Reactivity"
+  ) |> 
+  gt::tab_row_group(
+    label = "Alexithymia",
+    rows = Group == "Alexithymia"
+  ) |> 
+  gt::tab_style(
+    style = list(
+      gt::cell_fill(color = "gray85"),
+      gt::cell_text(weight="bold", style="italic")),
+    locations = gt::cells_row_groups()
+  )  |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81C784"),
+    locations = list(
+      gt::cells_body(columns="Best_MINT_Predictor", rows=c(1:4, 11:18, 20:21, 24))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFB74D"),
+    locations = list(
+      gt::cells_body(columns="Best_MINT_Predictor", rows=c(5:9, 10, 19, 22))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#EF9A9A"),
+    locations = list(
+      gt::cells_body(columns="Best_MINT_Predictor", rows=c(23, 25))
+    )
+  ) |> 
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81C784"),
+    locations = list(
+      gt::cells_body(columns="Best_Models_R2", rows=c(1:3, 11:13, 15:21, 23:25))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFB74D"),
+    locations = list(
+      gt::cells_body(columns="Best_Models_R2", rows=c(4:10, 14, 22))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#81C784"),
+    locations = list(
+      gt::cells_body(columns="Best_Models_BIC", rows=c(1:3, 11:20, 25))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#FFB74D"),
+    locations = list(
+      gt::cells_body(columns="Best_Models_BIC", rows=c(4:10, 22))
+    )
+  ) |>
+  gt::tab_style(
+    style = gt::cell_fill(color = "#EF9A9A"),
+    locations = list(
+      gt::cells_body(columns="Best_Models_BIC", rows=c(21, 23, 24))
+    )
+  ) |>
+  gt::cols_label(
+    Best_MINT_Predictor = "Best Predictor\n(MINT)",
+    Best_NonMINT_Predictor = "Best Predictor\n(Non-MINT)",
+    Best_Models_R2 = "Best Models (R2)",
+    Best_Models_BIC = "Best Models (BIC)"
+  ) |> 
+  gt::cols_hide(Group) |> 
+  gt::fmt_markdown() |> 
+  gt::tab_options(
+    table.font.size = gt::pct(125)
+  )
+
+tab2 |> 
+  gt::tab_options(
+    table.font.size = gt::pct(50)
+  ) |> 
+  gt::opt_interactive()
+
+gt::gtsave(tab2, "figures/table2.png", vwidth=1400, expand=0, quiet=TRUE)
+```
+
+## Figures
+
+```{r}
+#| warning: false
+#| eval: false
+
+fig1a <- patchwork::wrap_elements(
+  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/fig1a.png"))) +
+  patchwork::plot_annotation(title = "Exploratory Graphical Analysis (EGA)",
+                             subtitle = "Bootstrapped replication of hierarchical clusters (Methhod = leiden)",
+                             theme = theme(plot.title = element_text(face="bold", hjust = 0, size = rel(1.4)),
+                                           plot.subtitle = element_text(hjust = 0, size = rel(1)))))
+fig1b <- patchwork::wrap_elements(
+  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/fig1b.png"))) +
+  patchwork::plot_annotation(title = "Hierarchical Clustering",
+                             subtitle = "Method = Correlation",
+                             theme = theme(plot.title = element_text(face="bold", hjust = 0, size = rel(1.4)),
+                                           plot.subtitle = element_text(hjust = 0, size = rel(1)))))
+ggsave("figures/fig1.png", fig1a / fig1b, width=8, height=12, dpi=300)
+
+p_cor <- df |> 
+  select(starts_with("TAS_"), LifeSatisfaction, starts_with("PHQ4_"), starts_with("CEFSA"), starts_with("PI"), starts_with("ERS_")) |> 
+  mutate(LifeSatisfaction = datawizard::reverse_scale(LifeSatisfaction),
+         PI_Safe = datawizard::reverse_scale(PI_Safe),
+         PI_Good = datawizard::reverse_scale(PI_Good),
+         PI_Enticing = datawizard::reverse_scale(PI_Enticing)) |>
+  rename(`Life Satisfaction*` = LifeSatisfaction,
+         `Primals - Alive` = PI_Alive,
+         `Primals - Safe*` = PI_Safe,
+         `Primals - Good*` = PI_Good,
+         `Primals - Enticing*` = PI_Enticing) |>
+  make_cor(cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ))) +
+  labs(title="Correlates of Interoception") 
+p_cor
+
+fig2 <- (p_cormint | p_corintero) / p_cor + plot_layout(heights = c(0.4, 0.6))
+ggsave("figures/fig2.png", fig2, width=10, height=12, dpi=300)
+
+fig3 <- (mods_moodt$p + theme(axis.text.x = element_blank(), axis.title.x = element_blank()) | 
+    mods_adhd$p + theme(axis.text.x = element_blank(), axis.title.x = element_blank()) | 
+    mods_asd$p + theme(axis.text.x = element_blank(), axis.title.x = element_blank())) / 
+  (mods_central$p | mods_autonomic$p | mods_immune$p) +
+  plot_layout(guides = "collect") +
+  plot_annotation(title = "Predictive Performance of Interoceptive Questionnaires", 
+       subtitle = "ROC Curves",
+       theme = theme(plot.title = element_text(face="bold", hjust = 0.5, size = rel(1.4)),
+                     plot.subtitle = element_text(hjust = 0.5, size = rel(1.25))))
+fig3
+ggsave("figures/fig3.png", fig3, width=13, height=9, dpi=300)
+```

### 2025-07-01 study2sona/analysis/analysis.qmd
bits and bobs
lesgoo

@@
 df <- read.csv("../../study2/data/rawdata_participants.csv") |> 
-  mutate(Condition = fct_relevel(Condition, "Prolific", "Attention Checks", "Quiz", "Control"))
+  mutate(Prolific = ifelse(Condition == "Prolific", "Prolific", "SONA"))
 ```
 
+## Enjoyment
+
 ```{r}
+df |> 
+  summarise(n = n(), .by=c("Prolific", "Experiment_Enjoyment")) |>
+  filter(!is.na(Experiment_Enjoyment)) |> 
+  mutate(n = n / sum(n),
+         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
+         .by="Prolific") |>
+  ggplot(aes(y = Prolific, x = n, fill = Experiment_Enjoyment)) +
+  geom_bar(stat="identity", position="stack") +
+  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
+  scale_x_continuous(expand=c(0, 0))  +
+  labs(title="Experiment Enjoyment",
+       subtitle="Proportion of participants by condition") + 
+  guides(fill = guide_legend(reverse=TRUE)) +
+  theme_minimal() +
+  theme(axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.x = element_blank(),
+        legend.position = "top",
+        legend.title = element_blank())
 
+lm(Experiment_Enjoyment ~ Prolific, data = df) |> 
+  modelbased::estimate_contrasts(p_adjust="none", contrast = "Prolific") |> 
+  display()
+
+m1 <- lm(Experiment_Enjoyment ~ Prolific, data=df)
+
+summary(m1)
 ```
@@
 m1 <- glm(Failed ~ Prolific, 
-          data=mutate(df, Prolific = ifelse(Condition == "Prolific", "Prolific", "SONA")), 
+          data=df, 
           family="binomial")
@@
 
+modelbased::estimate_contrasts(m1)
 modelbased::estimate_means(m1, by="Condition") |> 

### 2025-07-01 study2/analysis/0_preprocessing.R

@@ -69,6 +69,7 @@ convert_stones_to_kg <- function(weight) {
   weight[weight == "64"] <- "6'4"
   weight[weight == "135"] <- "13'5"
   weight[weight == "125"] <- "12'5"
+  weight[weight == "205"] <- "20'5"
   weight <- trimws(gsub("\"", "", weight))
 
   # Handle integer input like "6" (assume stones only, zero pounds)
@@ -158,7 +159,8 @@ for (file in files) {
   data_ppt$Education <- ifelse(stringr::str_detect(data_ppt$Education, "equivalent to a Bachelors"), "Bachelor", data_ppt$Education)
   data_ppt$Education <- ifelse(data_ppt$Education %in% c("3rd year BSc", "Bachelor non-university", "graduate certificate (Certificate IV)"), "Bachelor", data_ppt$Education)
   data_ppt$Education <- ifelse(data_ppt$Education %in% c("NVQ 4", "Professional", "Vocational degree.", "level 3 nvq's",
-                                                         "tech college", "College - HND", "Vocational diploma", "Vocational Qualification"), "High school", data_ppt$Education)
+                                                         "tech college", "College - HND", "Vocational diploma", "Vocational Qualification",
+                                                         "Professional qualification"), "High school", data_ppt$Education)
 
   data_ppt$Student <- ifelse(!is.null(resp$Student), resp$Student, NA)
   data_ppt$Country <- ifelse(!is.null(resp$Country), resp$Country, NA)
@@ -350,12 +352,12 @@ for (file in files) {
   alldata <- merge(data_ppt, alldata, all = TRUE)
 }
 
-unique(alldata$Disorders_Psychiatric)
-unique(alldata$Disorders_PsychiatricTreatment)
-unique(alldata$Disorders_Somatic)
-unique(alldata$Education)
-unique(alldata$Ethnicity)
-unique(alldata$Recruitment)
+# unique(alldata$Disorders_Psychiatric)
+# unique(alldata$Disorders_PsychiatricTreatment)
+# unique(alldata$Disorders_Somatic)
+# table(alldata$Education)
+# table(alldata$Ethnicity)
+# table(alldata$Recruitment)
 
 # Attention checks --------------------------------------------------------
 checks <- data.frame(
@@ -374,7 +376,7 @@ checks$Reward <- alldata$Reward
 checks <- checks[!is.na(checks$ID), ]
[…]

### 2025-07-01 paper/manuscript.qmd
updated manuscript
@DominiqueMakowski I also added the PHQ-15 on the somatic section as it was not there before

@@
 The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% UK, 26.65% USA).
-This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).
+This study was approved by the University of Sussex' Ethics Committee (ER/MB2021/1).
 
@@
 The final sample includes 737 participants (age = 36.8 $\pm$ 14.7 [18, 87]; 57.3\% women; Country of residence: 75.17% United Kingdom, 24.83% other).
-This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).
+This study was approved by the University of Sussex' Ethics Committee (ER/EB672/2).
 
@@
 
-##### Multidimensional Assessment of Interoceptive Awareness (MAIA)
+##### Multidimensional Assessment of Interoceptive Awareness - Second Version (MAIA-2)
 
-The X items of the MAIA...
+The 37 items of the MAIA-2 [@mehling2018multidimensional] on a 7-point Likert scale from *Never* (0) to *Always* (6).
+The MAIA-2 consists of 8 scales: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening and Trust.
+The scales address 5 dimensions of body awareness: Awareness of Body Sensations, Emotional Reaction and Attentional Response to Sensations, Capacity to Regulate Attention, Awareness of Mind-Body Integration, Trusting Body Sensations.
 
-##### The Body Perception Questionnaire (BPQ)
+##### The Body Perception Questionnaire - Very Short Form (BPQ- VSF)
 
-**TODO**
+The 12 item BPQ-VSF [@cabrera2018assessing] related to bodily awareness on a 5-point Likert scale from *Never* (0) to *Always* (5).
 
-##### The Interoceptive Awareness Scale (IAS)
+##### The Interoceptive Accuracy Scale (IAS)
 
-**TODO**
+The 21 items of the IAS [@murphy2020testing] assessing interoceptive accuracy to physical sensations on a 5-point Likert scale ranging from *Disagree Strongly* (1) to *Strongly Agree*.
 
@@
 
-**TODO**
+The 20-items TAS [@leising2009toronto] assessing Alexithymia traits grouped into three dimensions: Difficulty Identifying Feelings, Difficulty Describing Feelings, and Externally Oriented Thinking.
+Items are rated in a 5-point Likert scale from *Strongly Disagree* (1) to *Strongly Agree*(5).
 
-##### Emotion Reactivity Scale (ERS)
+##### Emotion Reactivity Scale - Brief Version (B-ERS)
 
-**TODO**
+The 6-item B-ERS [@veilleux2024development] assessing emotional sensitivity on a 5-point Likert scale from *Not like me at all* (0) to *Extremely like me* (4).
 
-##### Cognitive Emotion Regulation Questionnaire (CERQ)
+##### Cognitive Emotion Regulation Questionnaire-short (CERQ-short)
 
-**TODO**
+The 18 items CERQ-short [@garnefski2006cognitive] on a 5-point Likert scale ranging from *Almost Never* (1) to *Almost Always* (5).
+This questionnaire measures eight cognitive responses to threatening or stressful events, including: Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.
 
-##### TODO (CEFSA)
+##### Černis Felt Sense of Anomaly scale - short-form (CEFSA-14)
 
-**TODO**
+The 14 item CEFSA [@vcernis2024measuring] assessing a specific sub-type of dissociative experiences in adolescence and adulthood - i.e., felt sense of anomaly-type
+dissociation.
+the items are rated ON A 5-point Likert scale from *Never* (0) to *Always* (4), forming seven factors: Anomalous Experience of the Self, Anomalous Experience of the Body , Anomalous Experiences of Emotion , Altered Sense of Familiarity , Altered Sense of Connection, Altered Sense of Agency , and Altered Sense of Reality
 
@@
 
-**TODO**
+the 18 items PI [@clifton2021brief] measuring highest-order primal world beliefs - i.e., beliefs about the basic character of the world: Good, Safe, Enticing, Alive.
+Responses are scored on a 6-point Likert scale from *Strongly Disagree* (0) to *Strongly Agree* (5).
 
@@
 
-**TODO**
+The 4 item scale of the PHQ [@kroenke2009ultra] assessing depression and anxiety, with responses scored as *Not at all* (0), *Once or twice* (0.5), *Several days* (1), *More than half of the days* (2), *nearly every day* (3).
+This revised version added as a response option (i.e., Once or twice) as a way to improve the scale's sensitivity to milder mood fluctuations [@makowskimeasuring].
 
@@
 
+##### Patient Health Questionnaire - Somatic Symptoms (PHQ-15)
+
+The PHQ-15 [@kroenke2002phq] is comprised of 15 somatic symptoms, with responses scored as *Not at all* (0), *Bothered a little* (1) and *bothered a lot* (2).
+
 #### Lifestyle
 
-**TODO**
+Participants were asked to report on their use of wearable devices to monitor several health indices: heart rate, number of steps, calories burned, sleep quality, and weight (including via a regular scale).
+For each selected index, a question appeared asking them to rate how often they check that index; responses were scored as *Never*, *Very rarely*, *A few times per week*, *Once a day*, *A few times per day*, and *A few times per hour*.
+Additionally, participants were asked to rate how important this information was to them on an 8-point Likert scale ranging from *Not at all* (0) to *Very much* (7).
 
-Physical activity.
-
-Wearables.
+Questions regarding physical activity were also included.
+Participants were asked to rate how physically active they consider themselves on an 8-point Likert scale, from *Not at all* (0) to *Very much* (7), and to self-report how many hours of active workout they engage in per week.
 
@@
 Then, we will test the predictive power of the Mint scale (relative to the other interoception questionnaires) on various measures.
-We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary
+We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary...)
 

### 2025-07-01 paper/manuscript.qmd
minor

--- 2025-07-01 paper/manuscript.qmd
@@
 Main issues in existing questionnaires:
-- Either heavily based on theories (e.g., focusing on a specific dimensions), despite shaky evidence for said-theories
+
+- Either heavily based on theories (e.g., focusing on specific "alleged" dimensions), despite shaky evidence for said-theories
 - Do not control for context (which leads to variability in interpretation and occurence)
-- Often quite narrow in the modalities covered
+- Often quite narrow in the modalities covered (or scattered, like the IAS)
 
@@
 
+We grouped some of the dimensions under "Awareness", despite being similar to items included in the IAS typically conceptualized as "Accuracy".
+However, we believe that subjective scales cannot be pure measures of accuracy, as they are inherently subjective and thus reflect a degree of awareness (of one's accurate noticing or sensation).
+
 # Study 2: Validation
@@
 The experiment included the following questionnaires.
+
+**TODO: What about attention checks?**
 
@@
 
-In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned them into three groups (and randomized their order within them): (1) interoception questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18), and (3) pathology (somatic health, mental health, LS + PHQ-4, CEFSA).
+In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned them into three groups (and randomized their order within them): (1) interoception questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18), and (3) health (somatic symptoms, mental health, LS + PHQ-4, CEFSA).
 After completing demographic questions, participants always started with the Mint scale, and each following interoception questionnaire was interspersed with two questionnaires from the emotions and pathology groups.
@@
 
-We will start by confirming and further refining the structure of the Mint scale using the same EGA model as in Study 1.
+We will start by confirming and further refining the structure of the Mint scale (see @fig-two) using the same EGA model as in Study 1. 
+We will then compute the lower-level dimensions as well as the higher-level metaclusters' scores by averaging the items in each cluster.
 The convergent validity of the final set of items will be assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
-Then, we will test the predictive power of the Mint scale (relative to the other interoception questionnaires) on various measures.
-We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary
 
@@
 
+Then, we will test the predictive power of the Mint scale relative to the other interoception questionnaires.
+We will first assess the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict various outcomes, and compare the best between the 4 interoception scales (based on the R2).
+We will then assess the predictive performance of each scale as a whole by comparing regression models with all the dimensions entered as predictors (note that the IAS and BPQ only have one total score variable).
+We will evaluate models based on their total explained variance (R2), as well as on the Bayesian Information Criterion (BIC), which penalizes for predictor numbers, thus offering a balance between model parsimony and predictive power.
+For the logistic model, we will quantify the discriminative power by computing the Area Under the Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which assesses the model's discriminative power (the combination of sensitivity and specificity).
+
+In order to evaluate the potential of a short version of our scale, we will compare 4 variants of the Mint models: the (full) Mint (including all lower-level dimensions), the "metaMint" (only including the metaclusters), the "miniMint" (including the metaclusters computed from a reduced number of items), and the "microMint" (including only the most representative dimension of each metacluster).
+Moreover, we will also include an alternative "interoception-only" version of the MAIA ("iMAIA") that only includes the 3 most interoceptive dimensions (Body Listening, Noticing, and Emotional Awareness).
+
+**TODO: Ana: do you think that this selection of dims for the iMAIA is fair? Or should I include other dimensions that you think are also very low-level and interoceptive?**
+
 ## Results
+
+The first application of EGA to the initial set of 42 items, which reproduced the expected 14 lower-level clusters of triplets and 3 higher-order metaclusters, with the exception of the *UrSe* (Urointestinal Sensitivity), for which one item moved to the *Olfa* (Olfactory Compensation) cluster.
+In order to further balance and reduce the items, we removedt the *UrSe* cluster, as well as *StaS* (State Specificity; which in comparison to the other items stood out as containing vague and overlapping items (e.g., "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)"); *SexO* (Sexual Organs Sensitivity), which overlapped with the *SexS* (Sexual Arousal Sensitivity) cluster; and *CaNo* (Cardiorespiratory Noticing), which overlapped with the *CaCo* (Cardiorespiratory Confusion) cluster.
+
+The final set of 36 items yielded a good fit (Generalized Total Entropy Fit Index = -77.23), with all items showing high cluster stability (> 90\%), with the exception of *Olfa*.
+The final structure included 11 lower-level clusters, grouped into 3 higher-order metaclusters: "Interoceptive Deficit" (containing *CaCo*, *UrIn*, *Derm*, *Sati*, *Olfa*), "Interoceptive Awareness" (containing *ExAc*, *RelA*, *SexS*), and "Visceroception" (containing *Card*, *Resp*, *Gast*).
+Item centrality (intepretable as loadings) are shown in @fig-three.
+Additionally, we also ran a hierarchical clustering analysis which replicated this structure (see @fig-two).
 
@@
 ```
+
+The correlation matrix of the Mint dimensions (i.e., clusters)
 
@@
 #| label: fig-five
-#| fig-cap: "TODO." 
+#| fig-cap: "Stars indicate dimensions that have been score-reversed for better in-context interpretation." 
 #| fig-align: "center"

### 2025-07-01 study2/analysis/2_analysis.qmd
minor

@@
 p_stab
+
+ega2$EGA
 ```
@@
                 data = select(df, all_of(outcome),
-                              starts_with("MAIA"), 
-                              -contains("NotWorrying"),
-                              -contains("NotDistracting")),
-              family = "binomial")
-  m_imaia <- glm(as.formula(paste0(outcome, " ~ .")),
-                data = select(df, all_of(outcome),
                               # MAIA_AttentionRegulation, # remove?

### 2025-07-01 paper/manuscript.qmd

@@
 
-Then, we will test the predictive power of the Mint scale relative to the other interoception questionnaires.
+Next, we will test the predictive power of the Mint scale relative to the other interoception questionnaires.
 We will first assess the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict various outcomes, and compare the best between the 4 interoception scales (based on the R2).

### 2025-07-01 paper/manuscript.qmd
manuscript updated

@@
 The experiment included the following questionnaires.
-
-**TODO: What about attention checks?**
+The procedure included a total of seven attention checks, each embedded within a different questionnaire.
+For example, the MINT questionnaire included an item such as: *"I can always accurately answer to the extreme left on this question to show that I am reading it."*
 
@@
 The scales address 5 dimensions of body awareness: Awareness of Body Sensations, Emotional Reaction and Attentional Response to Sensations, Capacity to Regulate Attention, Awareness of Mind-Body Integration, Trusting Body Sensations.
+
+The scale includes both high-level interoceptive dimensions - such as Body Listening, Noticing, and Emotional Awareness - and low-level dimensions, including Attention Regulation, Trust, and Self-Regulation [**ref**].
+It also features dimensions whose relationship to interoception remains debated, and which tend to show weak or non-existent correlations with the other MAIA subscales -namely, Not-Distracting and Not-Worrying [@ferentzi2021examining].
 

### 2025-07-01 paper/manuscript.qmd
update

--- 2025-07-01 paper/manuscript.qmd
@@
 #| label: fig-two
-#| fig-cap: "TODO."
+#| fig-cap: "EGA stability and Hclust. TODO."
 #| fig-align: "center"
@@
 In order to evaluate the potential of a short version of our scale, we will compare 4 variants of the Mint models: the (full) Mint (including all lower-level dimensions), the "metaMint" (only including the metaclusters), the "miniMint" (including the metaclusters computed from a reduced number of items), and the "microMint" (including only the most representative dimension of each metacluster).
-Moreover, we will also include an alternative "interoception-only" version of the MAIA ("iMAIA") that only includes the 3 most interoceptive dimensions (Body Listening, Noticing, and Emotional Awareness).
+Moreover, we will also include an alternative "interoception-only" version of the MAIA ("iMAIA") that only includes the 3 most interoceptive dimensions (Body Listening, Noticing, and Emotional Awareness)^[See correlation results to further justify this selection.].
 
@@
 #| label: fig-three
-#| fig-cap: "TODO."
+#| fig-cap: "Item loadings. TODO."
 #| fig-align: "center"
@@
 
-The correlation matrix of the Mint dimensions (i.e., clusters)
+The correlation matrix of the Mint dimensions (i.e., clusters) revealed an interesting and rich pattern of associations (see @fig-four), with some displaying contrasting patterns of associations compared to dimensions from the same clusters.
+For instance, *Derm* and *Olfa*, despite being positively correlated with the other dimensions from its *Deficit* cluster but contrary to them, were not negatively correlated to the *Awareness* metacluster and its dimensions.
+Similarly, *Sati*, unlike the other *Deficit* dimensions, was not positively correlated to *Visceroception*.
+This complex structure suggests that the dimensions indeed capture distinct aspects of interoception, and that the metaclusters, rather than being simple aggregates of rather-redundant elements, might actually capture unique combinations greater than the sum of its part.
+It also provides evidence against a simplistic adaptive *vs.* maladaptive dichotomy, as the *Deficit* dimensions are not negatively correlated with the *Visceroceptive* dimensions.
+
+**TODO: this paragraph probably needs to be rewritten and made clearer**
 
@@
 #| label: fig-four
-#| fig-cap: "TODO."
+#| fig-cap: "Correlation Matrices. TODO. Stars indicate dimensions that have been score-reversed for better in-context interpretation."
 #| fig-align: "center"
@@
 
+The correlation matrix between the Mint and the other interoception scales showed high level of redundancies as well as some unique contributions (see @fig-four).
+The BPQ was positively correlated with most Mint dimensions (the highest with *Visceroception*, $r = .46$).
+The IAS was positively correlated with *Visceroception* and *Awareness* dimensions (the highest with *Awareness*, $r = .63$), but negatively with most *Deficit* dimensions (with the exception of *Olfa* and *Derm*).
+In turn, the *Visceroception* metacluster most strongly correlated with MAIA's Noticing ($r = .55$).
+Interestingly, MAIA's TTrusting correlated selectively with *Awareness*, and negatively with *Deficit* dimensions, but not with *Visceroceptive* dimensions (underlining its high-level metacognitive nature).
+MAIA's Emotional Awareness and Body Listening displayed a similar pattern to Noticing, and Attention Regulation and Self Regulation positively correlated with *Awareness* and *Visceroception* dimensions, but negatively with some *Deficit* dimensions (*CaCo* and *UrIn*).
+Not-distracting only yielded mild negative associations with *Sati* and *Olfa*.
+Overall, the Mint dimensions were able to capture most of the (relevant) variance and intricacies present in the other interoception scales.
+
+Exploratory correlations with the emotion regulation (CERQ) dimensions revealed stronger associations with most of the MAIA dimensions (supporting its proximity with emotion regulation).
+Interestingly, Rumination (and Self-Blame) stood out as selectively related to the Mint's *Visceroception* and *Deficit* dimensions (note that Rumination was also related to the MAIA's interoceptive dimensions, namely Noticing, Emotional Awareness and Body Listening).
+The only primal world belief that correlated particuarly with the Mint's *Visceroception* and the MAIA's interoceptive dimension was the belief that the world was alive (**Ana maybe throw in a couple more words about what this belief means and is defined**).
+
+Most of the target outcomes measured in the study to assess validity were best predicted by one of the Mint dimension (see @fig-five).
+This included Alexithymia (best predicted by *Deficit*); ERS' Arousal (best predicted by *Deficit*); CEFSA's anomalous experiences of the body (best predicted by *CaCo*), Self and Reality (best predicted by *Deficit*); ADHD and Autism (best predicted by *Deficit*), Somatic symptoms (best predicted by *Deficit*); BMI (best predicted by *Sati*).
+Most of the exceptions showed an advantage for MAIA dimensions, in particular Not-worrying (which best predicted ERS' Sensitivity and Persistence) and Trusting (which best predicted LS, Depression and Anxiety, CEFSA's Emotion and Connection, and self-reported physical activity).
+
 ```{r}
 #| label: fig-five
-#| fig-cap: "Stars indicate dimensions that have been score-reversed for better in-context interpretation." 
+#| fig-cap: "Best model table. TODO."
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+
+knitr::include_graphics("../study2/analysis/figures/table2.png")
+```
+
+Model comparison included 4 variants of the Mint scale, the full *Mint* (including all lower-level clusters - 33 items), the *metaMint* (including only the 3 metaclusters based on all items), the *miniMint* (including the 3 metaclusters computed from 2 of its most loading triplets - 18 items), and the *microMint* (including only the most representative dimension of each metacluster - 9 items).
+This analysis confirmed the clear advantage for the Mint over the other interoception scales.
+The full *Mint* model was typically the best model based on R2, and the *metaMint* was the best model when parsimony was taken into account (i.e., based on BIC).
+Moreover, most of the instances were the *MAIA* was the best model were explainable by the inclusion of Trusting, and the interoception-only version *iMAIA* typically yielded worse performance than the Mint.
+In many instances, the *miniMint* yielded reasonable performance, although the *microMint* was typically less promising.
+
+The predictive performance for the mental health outcomes (see @fig-six) displayed a consistent pattern, with an advantage for the *MAIA* for depression and anxiety which dropped below the *Mint* versions for its *iMAIA* variant.
+The *Mint*, however, displayed a clear advantage for the prediction of autism, ADHD, and all somatic groups of symptoms (with the exception of Central Sensitization, which was best predicted by the *MAIA*).
+
+Finally, the importance of heart monitoring (for owners of such wearable) was best predicted by MAIA's body listening ($r = .36$), followed the *Card* dimension of the Mint ($r = .31$).
+The importance of sleep monitoring importance was best predicted by *RelA* ($r = .22$), followed by MAIA's not worrying ($r = -.219$).
+Daily activity via steps monitoring was best predicted by MAIA's Noticing ($r = .28$), folowed by *Awareness* ($r = .26$).
+
+```{r}
+#| label: fig-six
+#| fig-cap: "Predictive Performance (ROC curves). TODO." 
 #| fig-align: "center"
@@
 
-```{r}
-#| label: fig-six
-#| fig-cap: "TODO."
-#| fig-align: "center"
-#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
-#| out-width: "100%"
-
-knitr::include_graphics("../study2/analysis/figures/table2.png")
-```
-
 ## Discussion
 
+Main contender is MAIA.
+But its most sensitive dimensions seem to be the least related to interoception, which is dangerous as it might lead to findings with associations misattributed to "Interoception" (just because it correlate with some MAIA dimensions), but it might have nothing to do with interoception per se and more with emotion regulation.
+
+Basically the pattern is clear: everything high-level, metacognitive and highly subjective related to wellbeing and general affective state is the most strongly related to the MAIA through some of its Emotion regulation dimensions.
+All the other outcomes actually related to interoceptive processes are most strongly predicted by the Mint.
+
 # General Discussion
+
+Future directions: needs to test relationship with physiological measures of interoception.
+
+Also, the structure might still require a bit of deeper investigation, in particular with some of its facets (*Olfa* and *Derm*) which might display different associations depending on the context or the population.
 

### 2025-07-01 study2/analysis/2_analysis.qmd
update

@@
 ```{r}
-#| code-fold: false
-
 items <- select(df, starts_with("MINT_"))
@@
 ```
+
+See the list of item labels in the code below.
 
@@
 )
-
+```
+
+```{r}
 cleanlabels <- function(x, qname=FALSE) {
@@
 ### Full
+
+Additionally to EGA, we explored Hierarchical Clustering to see if the results are consistent.
 
@@
 ### Item Reduction
+
+To help us in confirming which clusters to keep or to remove, we empirically tested the "importance" (normalized R2) of each cluster in predicting various outcomes present in our dataset, and aggregating the average importance of each cluster different categories of outcomes.
+This approach yielded patterns which highlighted some clusters as providing a unique contribution (e.g., Olfa and Sati).
 
@@
 ### Final
+
+Initially, we fought about also removing Olfa and Sati to provide a more parsimonious and balanced final set, but they seem to withhold interesting value.
 
@@
   test$p_Omega2 <- NULL
+  test$LR <- NULL
+  test$p_LR <- NULL
   test$R2 <- table$R2
@@
 
+  test <- datawizard::data_select(test, c("Name", "R2", "BIC", "BF"))
+
   if(length(coefs) == length(models)) test$Coefficient <- coefs
-  format(test, zap_small = TRUE)
-}
-
+
+  test
+}
+
+display_models <- function(table, title = "", subtitle = "") {
+  numcols <- c("R2", "BIC", "Coefficient")[c("R2", "BIC", "Coefficient") %in% names(table)]
+  table |> 
+    mutate(BF = format_bf(BF, name = NULL, stars = TRUE)) |> 
+    gt::gt() |> 
+    gt::fmt_number(columns = numcols, decimals = 3) |>
+    gt::tab_header(title = title, subtitle = subtitle) |>
+    gt::data_color(
+      columns = c("R2"),
+      palette = c("white", "green")
+    ) |> 
+    gt::data_color(
+      columns = c("BIC"),
+      palette = c("green", "white")
+    ) |> 
+    gt::opt_interactive(use_compact_mode=TRUE)
+
+}
 # Individual predictors ------------------------------------------------------
@@
 preds_dif <- compare_predictors("TAS_DIF")
-display(preds_dif$table, title="DIF")
+display_models(preds_dif$table, title="Best Predictor", subtitle = "TAS - DIF")
 preds_dif$p
 mods_dif <- compare_models_lm("TAS_DIF")
-display(mods_dif, title="DIF")
+display_models(mods_dif, title="Best Model", subtitle = "DIF")
 
 preds_ddf <- compare_predictors("TAS_DDF")
-display(preds_ddf$table, title="DDF")
+display_models(preds_ddf$table, title="Best Predictor", subtitle = "DDF")
 preds_ddf$p
 mods_ddf <- compare_models_lm("TAS_DDF")
-display(mods_ddf, title="DDF")
+display_models(mods_ddf, title="Best Model", subtitle = "DDF")
 
 preds_eot <- compare_predictors("TAS_EOT")
-display(preds_eot$table, title="EOT")
+display_models(preds_eot$table, title="Best Predictor", subtitle = "EOT")
 preds_eot$p
 mods_eot <- compare_models_lm("TAS_EOT")
-display(mods_eot, title="EOT")
+display_models(mods_eot, title="Best Model", subtitle = "EOT")
 ```
@@
 preds_ls <- compare_predictors("LifeSatisfaction")
-display(preds_ls$table, title="Life Satisfaction")
+display_models(preds_ls$table, title="Best Predictor", subtitle = "Life Satisfaction")
 preds_ls$p
 mods_ls <- compare_models_lm("LifeSatisfaction")
-display(mods_ls, title="Life Satisfaction")
+display_models(mods_ls, title="Best Model", subtitle = "Life Satisfaction")
 
 preds_anx <- compare_predictors("PHQ4_Anxiety")
-display(preds_anx$table, title="PHQ4 Anxiety")
+display_models(preds_anx$table, title="Best Predictor", subtitle = "PHQ4 Anxiety")
 preds_anx$p
 mods_anx <- compare_models_lm("PHQ4_Anxiety")
-display(mods_anx, title="PHQ4 Anxiety")
+display_models(mods_anx, title="Best Model", subtitle = "PHQ4 Anxiety")
 
 preds_dep <- compare_predictors("PHQ4_Depression")
-display(preds_dep$table, title="PHQ4 Depression")
+display_models(preds_dep$table, title="Best Predictor", subtitle = "PHQ4 Depression")
 preds_dep$p
 mods_dep <- compare_models_lm("PHQ4_Depression")
-display(mods_dep, title="PHQ4 Depression")
+display_models(mods_dep, title="Best Model", subtitle = "PHQ4 Depression")
 ```
@@
 preds_arou <- compare_predictors("ERS_Arousal")
-display(preds_arou$table, title="ERS Arousal")
+display_models(preds_arou$table, title="Best Predictor", subtitle = "ERS Arousal")
 preds_arou$p
 mods_arou <- compare_models_lm("ERS_Arousal")
-display(mods_arou, title="ERS Arousal")
+display_models(mods_arou, title="Best Model", subtitle = "ERS Arousal")
 
 preds_sens <- compare_predictors("ERS_Sensitivity")
-display(preds_sens$table, title="ERS Sensitivity")
+display_models(preds_sens$table, title="Best Predictor", subtitle = "ERS Sensitivity")
 preds_sens$p
 mods_sens <- compare_models_lm("ERS_Sensitivity")
-display(mods_sens, title="ERS Sensitivity")
+display_models(mods_sens, title="Best Model", subtitle = "ERS Sensitivity")
 
 preds_pers <- compare_predictors("ERS_Persistence")
-display(preds_pers$table, title="ERS Persistence")
+display_models(preds_pers$table, title="Best Predictor", subtitle = "ERS Persistence")
 preds_pers$p
 mods_pers <- compare_models_lm("ERS_Persistence")
-display(mods_pers, title="ERS Persistence")
+display_models(mods_pers, title="Best Model", subtitle = "ERS Persistence")
 ```
@@
 ```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("CEFSA")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("CEFSA")))
+#| warning: false
+
+make_cor(select(df, starts_with("CEFSA")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
 ```
@@
 preds_cefsabody <- compare_predictors("CEFSA_Body")
-display(preds_cefsabody$table, title="CEFSA - Body")
+display_models(preds_cefsabody$table, title="Best Predictor", subtitle = "CEFSA - Body")
 preds_cefsabody$p
 mods_cefsabody <- compare_models_lm("CEFSA_Body")
-display(mods_cefsabody, title="CEFSA - Body")
+display_models(mods_cefsabody, title="Best Model", subtitle = "CEFSA - Body")
 
 preds_cefsaself <- compare_predictors("CEFSA_Self")
-display(preds_cefsaself$table, title="CEFSA - Self")
+display_models(preds_cefsaself$table, title="Best Predictor", subtitle = "CEFSA - Self")
 preds_cefsaself$p
 mods_cefsaself <- compare_models_lm("CEFSA_Self")
-display(mods_cefsaself, title="CEFSA - Self")
+display_models(mods_cefsaself, title="Best Model", subtitle = "CEFSA - Self")
 
 preds_cefsaemo <- compare_predictors("CEFSA_Emotion")
-display(preds_cefsaemo$table, title="CEFSA - Emotion")
+display_models(preds_cefsaemo$table, title="Best Predictor", subtitle = "CEFSA - Emotion")
 preds_cefsaemo$p
 mods_cefsaemo <- compare_models_lm("CEFSA_Emotion")
-display(mods_cefsaemo, title="CEFSA - Emotion")
+display_models(mods_cefsaemo, title="Best Model", subtitle = "CEFSA - Emotion")
 
 preds_cefsareal <- compare_predictors("CEFSA_Reality")
-display(preds_cefsareal$table, title="CEFSA - Reality")
+display_models(preds_cefsareal$table, title="Best Predictor", subtitle = "CEFSA - Reality")
 preds_cefsareal$p
 mods_cefsareal <- compare_models_lm("CEFSA_Reality")
-display(mods_cefsareal, title="CEFSA - Reality")
+display_models(mods_cefsareal, title="Best Model", subtitle = "CEFSA - Reality")
 
 preds_cefsacon <- compare_predictors("CEFSA_Connection")
-display(preds_cefsacon$table, title="CEFSA - Connection")
+display_models(preds_cefsacon$table, title="Best Predictor", subtitle = "CEFSA - Connection")
 preds_cefsacon$p
 mods_cefsacon <- compare_models_lm("CEFSA_Connection")
-display(mods_cefsacon, title="CEFSA - Connection")
+display_models(mods_cefsacon, title="Best Model", subtitle = "CEFSA - Connection")
 
 preds_cefsagency <- compare_predictors("CEFSA_Agency")
-display(preds_cefsagency$table, title="CEFSA - Agency")
+display_models(preds_cefsagency$table, title="Best Predictor", subtitle = "CEFSA - Agency")
 preds_cefsagency$p
 mods_cefsagency <- compare_models_lm("CEFSA_Agency")
-display(mods_cefsagency, title="CEFSA - Agency")
+display_models(mods_cefsagency, title="Best Model", subtitle = "CEFSA - Agency")
 ```
@@
 ```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("CERQ")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("CERQ")))
+#| warning: false
+
+make_cor(select(df, starts_with("CERQ")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
 ```
@@
 preds_cerqreapp <- compare_predictors("CERQ_PositiveReappraisal")
-display(preds_cerqreapp$table, title="CERQ - Positive Reappraisal")
+display_models(preds_cerqreapp$table, title="Best Predictor", subtitle = "CERQ - Positive Reappraisal")
 preds_cerqreapp$p
 mods_cerqreapp <- compare_models_lm("CERQ_PositiveReappraisal")
-display(mods_cerqreapp, title="CERQ - Positive Reappraisal")
+display_models(mods_cerqreapp, title="Best Model", subtitle = "CERQ - Positive Reappraisal")
 
 preds_cerqrefocus <- compare_predictors("CERQ_PositiveRefocusing")
-display(preds_cerqrefocus$table, title="CERQ - Positive Refocusing")
+display_models(preds_cerqrefocus$table, title="Best Predictor", subtitle = "CERQ - Positive Refocusing")
 preds_cerqrefocus$p
 mods_cerqrefocus <- compare_models_lm("CERQ_PositiveRefocusing")
-display(mods_cerqrefocus, title="CERQ - Positive Refocusing")
+display_models(mods_cerqrefocus, title="Best Model", subtitle = "CERQ - Positive Refocusing")
 
 preds_cerqpersp <- compare_predictors("CERQ_Perspective")
-display(preds_cerqpersp$table, title="CERQ - Perspective")
+display_models(preds_cerqpersp$table, title="Best Predictor", subtitle = "CERQ - Perspective")
 preds_cerqpersp$p
 mods_cerqpersp <- compare_models_lm("CERQ_Perspective")
-display(mods_cerqpersp, title="CERQ - Perspective")
+display_models(mods_cerqpersp, title="Best Model", subtitle = "CERQ - Perspective")
 
 preds_cerqacceptance <- compare_predictors("CERQ_Acceptance")
-display(preds_cerqacceptance$table, title="CERQ - Acceptance")
+display_models(preds_cerqacceptance$table, title="Best Predictor", subtitle = "CERQ - Acceptance")
 preds_cerqacceptance$p
 mods_cerqacceptance <- compare_models_lm("CERQ_Acceptance")
-display(mods_cerqacceptance, title="CERQ - Acceptance")
+display_models(mods_cerqacceptance, title="Best Model", subtitle = "CERQ - Acceptance")
 ```
@@
 ```{r}
-make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
-         select(df, starts_with("PI")))
-
-make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
-         select(df, starts_with("PI")))
+#| warning: false
+
+make_cor(select(df, starts_with("PI")),
+         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
 ```
@@
 preds_pialive <- compare_predictors("PI_Alive")
-display(preds_pialive$table, title="Primals - Alive")
+display_models(preds_pialive$table, title="Best Predictor", subtitle = "Primals - Alive")
 preds_pialive$p
 mods_pialive <- compare_models_lm("PI_Alive")
-display(mods_pialive, title="Primals - Alive")
+display_models(mods_pialive, title="Best Model", subtitle = "Primals - Alive")
 
 preds_pisafe <- compare_predictors("PI_Safe")
-display(preds_pisafe$table, title="Primals - Safe")
+display_models(preds_pisafe$table, title="Best Predictor", subtitle = "Primals - Safe")
 preds_pisafe$p
 mods_pisafe <- compare_models_lm("PI_Safe")
-display(mods_pisafe, title="Primals - Safe")
+display_models(mods_pisafe, title="Best Model", subtitle = "Primals - Safe")
 
 preds_pient <- compare_predictors("PI_Enticing")
-display(preds_pient$table, title="Primals - Enticing")
+display_models(preds_pient$table, title="Best Predictor", subtitle = "Primals - Enticing")
 preds_pient$p
 mods_pient <- compare_models_lm("PI_Enticing")
-display(mods_pient, title="Primals - Enticing")
+display_models(mods_pient, title="Best Model", subtitle = "Primals - Enticing")
 
 preds_pigood <- compare_predictors("PI_Good")
-display(preds_pigood$table, title="Primals - Good")
+display_models(preds_pigood$table, title="Best Predictor", subtitle = "Primals - Good")
 preds_pigood$p
 mods_pigood <- compare_models_lm("PI_Good")
-display(mods_pigood, title="Primals - Good")
+display_models(mods_pigood, title="Best Model", subtitle = "Primals - Good")
 ```
@@
 preds_mood <- compare_predictors("Disorders_Psychiatric_Mood")
-display(preds_mood$table, title="Mood Disorders")
+display_models(preds_mood$table, title="Best Predictor", subtitle = "Mood Disorders")
 preds_mood$p
 mods_mood <- compare_models_glm("Disorders_Psychiatric_Mood")
-display(mods_mood$table, title="Mood Disorders")
+display_models(mods_mood$table, title="Best Predictor", subtitle = "Mood Disorders")
 mods_mood$p
@@
 preds_moodt <- compare_predictors("Disorders_Psychiatric_MoodTreatment")
-display(preds_moodt$table, title="Mood Disorders (with Treatment)")
+display_models(preds_moodt$table, title="Best Predictor", subtitle = "Mood Disorders (with Treatment)")
 preds_moodt$p
@@
                                  title="Mood Disorders", subtitle = "MDD, GAD, Bipolar (with Treatment)")
-display(mods_moodt$table, title="Mood Disorders (with Treatment)")
+display_models(mods_moodt$table, title="Best Predictor", subtitle = "Mood Disorders (with Treatment)")
 mods_moodt$p
@@
 preds_anxdis <- compare_predictors("Disorders_Psychiatric_Anxiety")
-display(preds_anxdis$table, title="Anxiety Disorders")
+display_models(preds_anxdis$table, title="Best Predictor", subtitle = "Anxiety Disorders")
 preds_anxdis$p
 mods_anxdis <- compare_models_glm("Disorders_Psychiatric_Anxiety")
-display(mods_anxdis$table, title="Anxiety Disorders")
+display_models(mods_anxdis$table, title="Best Model", subtitle = "Anxiety Disorders")
 mods_anxdis$p
@@
 preds_anxdist <- compare_predictors("Disorders_Psychiatric_AnxietyTreatment")
-display(preds_anxdist$table, title="Anxiety Disorders (with Treatment)")
+display_models(preds_anxdist$table, title="Best Predictor", subtitle = "Anxiety Disorders (with Treatment)")
 preds_anxdist$p
 mods_anxdist <- compare_models_glm("Disorders_Psychiatric_AnxietyTreatment")
-display(mods_anxdist$table, title="Anxiety Disorders (with Treatment)")
+display_models(mods_anxdist$table, title="Best Model", subtitle = "Anxiety Disorders (with Treatment)")
 mods_anxdist$p
@@
 preds_eat <- compare_predictors("Disorders_Psychiatric_Eating")
-display(preds_eat$table, title="Eating Disorders")
+display_models(preds_eat$table, title="Best Predictor", subtitle = "Eating Disorders")
 preds_eat$p
 mods_eat <- compare_models_glm("Disorders_Psychiatric_Eating")
-display(mods_eat$table, title="Eating Disorders")
+display_models(mods_eat$table, title="Best Model", subtitle = "Eating Disorders")
 mods_eat$p
@@
 preds_addict <- compare_predictors("Disorders_Psychiatric_Addiction")
-display(preds_addict$table, title="Addiction")
+display_models(preds_addict$table, title="Best Predictor", subtitle = "Addiction")
 preds_addict$p
 mods_addict <- compare_models_glm("Disorders_Psychiatric_Addiction")
-display(mods_addict$table, title="Addiction")
+display_models(mods_addict$table, title="Best Model", subtitle = "Addiction")
 mods_addict$p
@@
 preds_adhd <- compare_predictors("Disorders_Psychiatric_ADHD")
-display(preds_adhd$table, title="ADHD")
+display_models(preds_adhd$table, title="Best Predictor", subtitle = "ADHD")
 preds_adhd$p
@@
                                 title = "ADHD", subtitle = "Attention Deficit/Hyperactivity Disorder")
-display(mods_adhd$table, title="ADHD")
+display_models(mods_adhd$table, title="Best Model", subtitle = "ADHD")
 mods_adhd$p
@@
 preds_asd <- compare_predictors("Disorders_Psychiatric_Autism")
-display(preds_asd$table, title="Autism")
+display_models(preds_asd$table, title="Best Predictor", subtitle = "Autism")
 preds_asd$p
@@
                                 title = "ASD", subtitle = "Autism Spectrum Disorder")
-display(mods_asd$table, title="Autism")
+display_models(mods_asd$table, title="Best Model", subtitle = "Autism")
 mods_asd$p
@@
 preds_bpd <- compare_predictors("Disorders_Psychiatric_Borderline")
-display(preds_bpd$table, title="Borderline Personality Disorder")
+display_models(preds_bpd$table, title="Best Predictor", subtitle = "Borderline Personality Disorder")
 preds_bpd$p
 mods_bpd <- compare_models_glm("Disorders_Psychiatric_Borderline")
-display(mods_bpd$table, title="Borderline Personality Disorder")
+display_models(mods_bpd$table, title="Best Model", subtitle = "Borderline Personality Disorder")
 mods_bpd$p
@@
 preds_afferent <- compare_predictors("Disorders_Somatic_AfferentSensitivity")
-display(preds_afferent$table, title="Afferent Sensitivity Symptoms")
+display_models(preds_afferent$table, title="Best Predictor", subtitle = "Afferent Sensitivity Symptoms")
 preds_afferent$p
@@
                                     subtitle = "Migraine, neuropathy, muscle tension, dizziness, ...")
-display(mods_afferent$table, title="Afferent Sensitivity Symptoms")
+display_models(mods_afferent$table, title="Best Model", subtitle = "Afferent Sensitivity Symptoms")
 mods_afferent$p
@@
 preds_central <- compare_predictors("Disorders_Somatic_CentralSensitization")
-display(preds_central$table, title="Central Sensitization Symptoms")
+display_models(preds_central$table, title="Best Predictor", subtitle = "Central Sensitization Symptoms")
 preds_central$p
@@
                                    subtitle = "Fibromyalgia, chronic fatigue, back pain, IBS, ...")
-display(mods_central$table, title="Central Sensitization Symptoms")
+display_models(mods_central$table, title="Best Model", subtitle = "Central Sensitization Symptoms")
 mods_central$p
@@
 preds_autonomic <- compare_predictors("Disorders_Somatic_AutonomicDysfunction")
-display(preds_autonomic$table, title="Autonomic Dysfunction")
+display_models(preds_autonomic$table, title="Best Predictor", subtitle = "Autonomic Dysfunction")
 preds_autonomic$p
@@
                                      subtitle = "Hypermobility, chest pain, hypo/hypertension, ....")
-display(mods_autonomic$table, title="Autonomic Dysfunction")
+display_models(mods_autonomic$table, title="Best Model", subtitle = "Autonomic Dysfunction")
 mods_autonomic$p
@@
 preds_immune <- compare_predictors("Disorders_Somatic_ImmuneInflammatory")
-display(preds_immune$table, title="Immune-Inflammatory Symptoms")
+display_models(preds_immune$table, title="Best Predictor", subtitle = "Immune-Inflammatory Symptoms")
 preds_immune$p
@@
                                   subtitle = "Allergies, asthma, eczema, autoimmune, ...")
-display(mods_immune$table, title="Immune-Inflammatory Symptoms")
+display_models(mods_immune$table, title="Best Model", subtitle = "Immune-Inflammatory Symptoms")
 mods_immune$p
@@
 preds_age <- compare_predictors("Age")
-display(preds_age$table, title="Age")
+display_models(preds_age$table, title="Best Predictor", subtitle = "Age")
 preds_age$p
 mods_age <- compare_models_lm("Age")
-display(mods_age, title="Age")
+display_models(mods_age, title="Best Model", subtitle = "Age")
 ```
@@
 preds_sex <- compare_predictors("Sex")
-display(preds_sex$table, title="Sex")
+display_models(preds_sex$table, title="Best Predictor", subtitle = "Sex")
 preds_sex$p
 mods_sex <- compare_models_glm("Sex")
-display(mods_sex$table, title="Sex")
+display_models(mods_sex$table, title="Best Model", subtitle = "Sex")
 mods_sex$p
@@
 preds_bmi <- compare_predictors("BMI")
-display(preds_bmi$table, title="BMI")
+display_models(preds_bmi$table, title="Best Predictor", subtitle = "BMI")
 preds_bmi$p
 mods_bmi <- compare_models_lm("BMI")
-display(mods_bmi, title="BMI")
+display_models(mods_bmi, title="Best Model", subtitle = "BMI")
 ```
@@
 preds_physactiv <- compare_predictors("Physical_Active")
-display(preds_physactiv$table, title="Physical Activity")
+display_models(preds_physactiv$table, title="Best Predictor", subtitle = "Physical Activity")
 preds_physactiv$p
 mods_physactiv <- compare_models_lm("Physical_Active")
-display(mods_physactiv, title="Physical Activity")
+display_models(mods_physactiv, title="Best Model", subtitle = "Physical Activity")
 ```
@@
 preds_wearN <- compare_predictors("Wearables_Number", family = "poisson")
-display(preds_wearN$table, title="Wearables Number")
+display_models(preds_wearN$table, title="Best Predictor", subtitle = "Wearables Number")
 preds_wearN$p
@@
 preds_wearHeartOwn <- compare_predictors("Wearables_HeartOwn")
-display(preds_wearHeartOwn$table, title="Wearables Heart Ownership")
+display_models(preds_wearHeartOwn$table, title="Best Predictor", subtitle = "Wearables Heart Ownership")
 preds_wearHeartOwn$p
 mods_wearHeartOwn <- compare_models_glm("Wearables_HeartOwn")
-display(mods_wearHeartOwn$table, title="Wearables Heart Ownership")
+display_models(mods_wearHeartOwn$table, title="Best Model", subtitle = "Wearables Heart Ownership")
 mods_wearHeartOwn$p
@@
 preds_wearHeartImp <- compare_predictors("Wearables_HeartImportance")
-display(preds_wearHeartImp$table, title="Wearables Heart Importance")
+display_models(preds_wearHeartImp$table, title="Best Predictor", subtitle = "Wearables Heart Importance")
 preds_wearHeartImp$p
 mods_wearHeartImp <- compare_models_lm("Wearables_HeartImportance")
-display(mods_wearHeartImp, title="Wearables Heart Importance")
+display_models(mods_wearHeartImp, title="Best Model", subtitle = "Wearables Heart Importance")
 ```
@@
 preds_wearSleepOwn <- compare_predictors("Wearables_SleepOwn")
-display(preds_wearSleepOwn$table, title="Wearables Sleep Ownership")
+display_models(preds_wearSleepOwn$table, title="Best Predictor", subtitle = "Wearables Sleep Ownership")
 preds_wearSleepOwn$p
 mods_wearSleepOwn <- compare_models_glm("Wearables_SleepOwn")
-display(mods_wearSleepOwn$table, title="Wearables Sleep Ownership")
+display_models(mods_wearSleepOwn$table, title="Best Model", subtitle = "Wearables Sleep Ownership")
 
 preds_wearSleepImp <- compare_predictors("Wearables_SleepImportance")
-display(preds_wearSleepImp$table, title="Wearables Sleep Importance")
+display_models(preds_wearSleepImp$table, title="Best Predictor", subtitle = "Wearables Sleep Importance")
 preds_wearSleepImp$p
 mods_wearSleepImp <- compare_models_lm("Wearables_SleepImportance")
-display(mods_wearSleepImp, title="Wearables Sleep Importance")
+display_models(mods_wearSleepImp, title="Best Model", subtitle = "Wearables Sleep Importance")
 ```
@@
 preds_wearStepsOwn <- compare_predictors("Wearables_StepsOwn")
-display(preds_wearStepsOwn$table, title="Wearables Steps Ownership")
+display_models(preds_wearStepsOwn$table, title="Best Predictor", subtitle = "Wearables Steps Ownership")
 preds_wearStepsOwn$p
 mods_wearStepsOwn <- compare_models_glm("Wearables_StepsOwn")
-display(mods_wearStepsOwn$table, title="Wearables Steps Ownership")
+display_models(mods_wearStepsOwn$table, title="Best Model", subtitle = "Wearables Steps Ownership")
 
 preds_wearStepsImp <- compare_predictors("Wearables_StepsImportance")
-display(preds_wearStepsImp$table, title="Wearables Steps Importance")
+display_models(preds_wearStepsImp$table, title="Best Predictor", subtitle = "Wearables Steps Importance")
 preds_wearStepsImp$p
 mods_wearStepsImp <- compare_models_lm("Wearables_StepsImportance")
-display(mods_wearStepsImp, title="Wearables Steps Importance")
+display_models(mods_wearStepsImp, title="Best Model", subtitle = "Wearables Steps Importance")
 ```
@@
 preds_wearWeightOwn <- compare_predictors("Wearables_WeightOwn")
-display(preds_wearWeightOwn$table, title="Wearables Weight Ownership")
+display_models(preds_wearWeightOwn$table, title="Best Predictor", subtitle = "Wearables Weight Ownership")
 preds_wearWeightOwn$p
 mods_wearWeightOwn <- compare_models_glm("Wearables_WeightOwn")
-display(mods_wearWeightOwn$table, title="Wearables Weight Ownership")
+display_models(mods_wearWeightOwn$table, title="Best Model", subtitle = "Wearables Weight Ownership")
 
 preds_wearWeightImp <- compare_predictors("Wearables_WeightImportance")
-display(preds_wearWeightImp$table, title="Wearables Weight Importance")
+display_models(preds_wearWeightImp$table, title="Best Predictor", subtitle = "Wearables Weight Importance")
 preds_wearWeightImp$p
 mods_wearWeightImp <- compare_models_lm("Wearables_WeightImportance")
-display(mods_wearWeightImp, title="Wearables Weight Importance")
+display_models(mods_wearWeightImp, title="Best Model", subtitle = "Wearables Weight Importance")
 ```

### 2025-07-02 paper/manuscript.qmd
update

--- 2025-07-01 paper/manuscript.qmd
@@
       - Writing – review & editing
+    affiliations:
+      - ref: "id1"
+  - name: Emma Benn 
+    role:
+      - Investigation
+    affiliations:
+      - ref: "id1"
+  - name: Maisie Bennett
+    role:
+      - Investigation
     affiliations:
@@
 
-TODO: write general intro.
-
 Main issues in existing questionnaires:
@@
 
-Goal of study 1: to generate a lot of items, analyze its structure and reduce them to a balanced set of items.
+- Goal of study 1: to generate a lot of items, analyze its structure and reduce them to a balanced set of items.
 
@@
 We excluded 191 for failing at least one attention check, and 10 based on measures significantly related to the probability of failing attention checks [namely, the multivariate distance obtained with the OPTICS algorithm, @theriault2024check].
-The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% UK, 26.65% USA).
+The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; country of residence: 63.86% UK, 26.65% USA).
 This study was approved by the University of Sussex' Ethics Committee (ER/MB2021/1).
@@
 
-Based on the two goals outlined for this scale, namely to include different interoceptive modalities, and to explicitly state the context of the interoceptive experience (e.g., whether negative or positive), we generated items in a systematic way following a combinatory approach, where each item's category corresponds to the combination of a specific modality and context (@fig-one).
+Based on the two goals outlined for this scale, namely to include different interoceptive modalities, and to explicitly state the context of the interoceptive experience (e.g., whether negative or positive), we generated items in a systematic way following a combinatory approach, where each item's category corresponds to the union of a specific modality and context (@fig-one).
 
@@
 #| fig-cap: "The conceptual grid used to generate the 120 initial items (top-left).
-Each item belong both to an interoceptive modalitiy and a facet, with the number of each item per category indicated in the circles.
-The askterisk denotes the additional presence of an attention check item in that category.
-In the experiment, these items were presented on different pages grouped either by modality (bottom-left), by facet (top-right), or entirely randomly.
-The Correlation Similarity (bottom-right) analysis suggested that the correlation matrix obtained from the participants assigned to the random-grouping condition was slightly more similar (but non-significantly) to the one obtained in the modality-grouping condition, suggesting that 1) the scale's structure is robust to different presentation conditions; 2) modality-grouping might tend to facilitate the emergence of the underlying item structure (and thus be interpreted as being more natural)."
+Each item belongs both to an interoceptive modality (vertical) and a facet (horizontal), with the number of each item per category indicated in the circles.
+The asterisk denotes the additional presence of an attention check item in that category.
+In the experiment, these items were presented on different pages grouped either by modality (bottom-left), by facet (top-right), or randomly.
+The Correlation Similarity (bottom-right) analysis suggested that the correlation matrix obtained from the participants assigned to the random-grouping condition was slightly more similar (but non-significantly) to the one obtained in the modality-grouping condition, suggesting that the scale's structure is robust to different presentation conditions, and that the modality-grouping might potentially tend to facilitate the emergence of the underlying item structure (and thus be interpreted as being more \"natural\")."
 #| fig-align: "center"
@@
 
-We identified 7 "modalities" (cardiac, respiratory, gastric, genital, skin & temperature, bladder & colon, and a "general state" category corresponding to a holistic and general awareness of an interoceptive state or dimension).
-Through iterative refinement (e.g., splitting or merging different categories together), we settled on 6 "facets", which encompass both *contexts* of experience (negative and positive arousal, namely anxious and sexual states), and potential distinct *mechanisms* (nociception & pleasure, sensitivity, accuracy, and confusion).
+We identified 7 "modalities" (cardiac, respiratory, gastric, genital, skin & temperature (thermoregulation), bladder & colon, and a "general state" category corresponding to a holistic and general awareness of an interoceptive state or dimension).
+Through iterative refinement (e.g., splitting or merging different categories together), we settled on 6 "facets", which encompass both *contexts* of experience (negative and positive arousal, e.g., anxious and sexual states), and potential distinct *mechanisms* (nociception & pleasure, sensitivity, accuracy, and confusion).
 
@@
 To avoid presenting all the 120 items on a single long and discouraging page, we split them into different pages.
-Participants were randomly assigned to one of three conditions, driving how items were grouped on the same page: 1) items grouped by modality (i.e., all cardiac items on the first page, all colon & bladder  items on the second, etc.), 2) items grouped by facet, or 3) items presented fully randomly (but balanced randomly across 6 pages).
-The order of the item on any given page and the order of the modalities/facets were randomized.
-Each participant completed the full set of 120 items, with the 8 attention check items interspersed throughout.
+Participants were randomly assigned to one of three conditions, driving how items were grouped on the same page: 1) items grouped by modality (i.e., all cardiac items on the first page, all colon & bladder items on the second, etc.), 2) items grouped by facet, or 3) items presented fully randomly (but with their number balanced across 6 pages).
+The order of the item on any given page and the order of the modalities/facets was randomized.
+Each participant completed the full set of 120 items, with 8 attention check items interspersed throughout.
 The online experiment was implemented using JsPsych [@de2015jspsych], and item responses were recorded using 7-points Likert scales (0 = Disagree, 6 = Agree).
@@
 
-Items deemed "redundant" (which can distort the item structure estimation by introducing multicollinearity or local dependencies) will be identified (using the recommended threshold of 0.25) using Unique Variable Analysis [UVA, @christensen2023unique], a novel and principled method derived from network psychometrics.
+Items deemed "redundant" (which can distort the item structure estimation by introducing multicollinearity or local dependencies) were identified (using the recommended threshold of 0.25) using Unique Variable Analysis [UVA, @christensen2023unique], a novel and principled method derived from network psychometrics.
 
-The structure of the items will be analyzed using the recently-developed Exploratory Graph Analysis [EGA, @golino2017exploratory] framework, which allows to jointly estimate the number of dimensions (i.e., clusters of items), the structure, as well as its stability using bootstrapping [@golino2020investigating].
+The structure of the items was analyzed using the recently-developed Exploratory Graph Analysis [EGA, @golino2017exploratory] framework, which allows to jointly estimate the number of dimensions (i.e., clusters of items), the structure, as well as its stability using bootstrapping [@golino2020investigating].
 At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them.
@@
 
-After removing redundant items using UVA, we will iteratively fit hierarchical EGA models (which additionally estimates higher-order "meta" clusters) using "glasso" [**REF**] and the "leiden" algorithm [**REF**] for community detection, refining the item pool at each step.
-We will start by removing items with a low (< 80%) cluster stability (i.e., volatile items which jump between clusters across bootstrapped samples), followed by odd items belonging to no clusters or pairs of items (i.e., we keep items belonging to clusters of more than 2 items).
-Finally, for each lower-level cluster, we will select the 3 items with the highest node centrality (i.e., the highest loading in the cluster).
+After removing redundant items using UVA, we iteratively fitted hierarchical EGA models (which additionally estimates higher-order "meta" clusters) using "glasso" [@friedman2008sparse] and the "Leiden" algorithm [@traag2019louvain] for community detection, refining the item pool at each step.
+We started by removing items with a low (< 80%) cluster stability (i.e., volatile items which jump between clusters across bootstrapped samples), followed by odd items belonging to no clusters or pairs of items (i.e., we keep items belonging to clusters of more than 2 items).
+Finally, for each lower-level cluster, we selected the 3 items with the highest node centrality (i.e., the highest loading in the cluster).
 
@@
 Facet}} = 0.49$, $SMI_{\text{Random vs.
-Modality}} = 0.51$, $p = .52$).
+Modality}} = 0.51$, $p = .52$), despite a consistent bias in favour of the modality-grouping condition.
 
-From the 120 initial items, UVA flagged 4 redundant items that we removed.
+From the 120 initial items, 4 redundant items were flagged by UVA.
 We then removed 40 items that showed low cluster stability, and 9 items that were part of clusters with less than 3 items.
@@
 
-Possible (although not at all significant) bias consistent across indices in favour of a greater similarity with the modality-grouping condition.
-
-We grouped some of the dimensions under "Awareness", despite being similar to items included in the IAS typically conceptualized as "Accuracy".
+- Possible (although not at all significant) bias consistent across indices in favour of a greater similarity with the modality-grouping condition.
+Futher research with more data (here we only had ~200 observation per condition) might be able to yield more conclusive results.
+In general, testing the presentation mode is a novel approach which should be more widely applied to psychometric validations.
+- We grouped some of the dimensions under "Awareness", despite being similar to items included in the IAS typically conceptualized as "Accuracy".
 However, we believe that subjective scales cannot be pure measures of accuracy, as they are inherently subjective and thus reflect a degree of awareness (of one's accurate noticing or sensation).
+- Olfactory compensation: pseudo-interoceptive pathway whereby people with interoceptive deficits would compensate by gathering evidence about their internal state externally (e.g., via smell).
+- The metacluster "Sensitivity" seems to be grouping iterms related to visceropcetion and (hyper)sensitivity (Derm).
 
@@
 
-TODO: write intro.
-Goal of study 2: to validate the Mint scale against other interoception scales.
+- Goal of study 2: to validate the Mint scale against other interoception scales.
 
@@
 
-We recruited 921 English-speaking participants via Prolific\textcopyright and SONA, from which 118 were excluded for failing at least one attention check and 6 based on multivariate distance (using the same procedure as for study 1).
-60 participants were further excluded due to missing data following a technical error.
+We recruited 921 English-speaking participants via SONA and Prolific\textcopyright, from which 118 were excluded for failing at least one attention check and 6 based on multivariate distance (using the same procedure as for study 1).
+60 participants were further excluded due to missing data following a technical issue.
 The final sample includes 737 participants (age = 36.8 $\pm$ 14.7 [18, 87]; 57.3\% women; Country of residence: 75.17% United Kingdom, 24.83% other).
@@
 
-### Procedure
+### Measures
 
-The experiment included the following questionnaires.
+```{r}
+#| label: fig-two
+#| fig-cap: "Structure analysis of the final set of 33 Mint items.
+Hierarchical Exploratory Graph Analysis (EGA) was applied to jointly identify clusters of items, as well as higher-order metaclusters.
+The reliability of each item can be quantified by the proportion of structure replication across bootstrapped samples, with high values indicative of high structural stability.
+The Mint scale displayed an excellent structural consistency, with the exception of the *Olfa* cluster which belonging to the *Deficit* metaclusters warrants further research.
+Bottom plot shows the result of hierarchical clustering, providing evidence for structure statbility across methods, and allowing for more granular understanding of the relationships between variables."
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "80%"
 
-**TODO: What about attention checks?**
+knitr::include_graphics("../study2/analysis/figures/fig1.png")
+```
 
@@
 
-##### The Multimodal Interoception Questionnaire (Mint)
+The 45 items of the Multimodal Interoception Questionnaire (Mint) scale were presented in a random order, with the same 7-point Likert scale as in study 1 (0 = *Disagree*, 6 = *Agree*).
 
-The 45 items of the Mint scale were presented in a random order, with the same 7-point Likert scale as in study 1 (0 = Disagree, 6 = Agree).
+The Multidimensional Assessment of Interoceptive Awareness [MAIA-2, @mehling2018multidimensional] measures 8 dimensions with 37 items presented on a 7-point Likert scale (0 = *Never*, 6 = *Always*).
+It includes bodily dimensions such as Body Listening, Noticing, Emotional Awareness, dimensions related to emotion regulation, such as Trust, Not-worrying, and Self-Regulation, as well as dimensions related to attention, such as Attention Regulation and Not-Distracting.
+The relationship of some of these dimensions to interoception remains debated, particularly Not-Distracting and Not-Worrying, which tend to show weak or non-existent correlations with the other MAIA subscales [@ferentzi2021examining].
 
-##### Multidimensional Assessment of Interoceptive Awareness - Second Version (MAIA-2)
+The Body Perception Questionnaire - Very Short Form [BPQ-VSF, @cabrera2018assessing]  measures a general score of bodily awareness with 12 items presented on 5-point Likert scale (0 = *Never*, 5 = *Always*).
 
-The 37 items of the MAIA-2 [@mehling2018multidimensional] on a 7-point Likert scale from *Never* (0) to *Always* (6).
-The MAIA-2 consists of 8 scales: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening and Trust.
-The scales address 5 dimensions of body awareness: Awareness of Body Sensations, Emotional Reaction and Attentional Response to Sensations, Capacity to Regulate Attention, Awareness of Mind-Body Integration, Trusting Body Sensations.
-
-##### The Body Perception Questionnaire - Very Short Form (BPQ- VSF)
-
-The 12 item BPQ-VSF [@cabrera2018assessing] related to bodily awareness on a 5-point Likert scale from *Never* (0) to *Always* (5).
-
-##### The Interoceptive Accuracy Scale (IAS)
-
-The 21 items of the IAS [@murphy2020testing] assessing interoceptive accuracy to physical sensations on a 5-point Likert scale ranging from *Disagree Strongly* (1) to *Strongly Agree*.
+The Interoceptive Accuracy Scale [IAS, @murphy2020testing] measures a general score of interoceptive accuracy to physical sensations with 21 items presented on a 5-point Likert scale (1 = *Disagree Strongly*, 5 = *Strongly Agree*).
 
@@
 
-##### Toronto Alexithymia Scale (TAS-20)
+The Toronto Alexithymia Scale TAS [TAS-20, @leising2009toronto] measures 3 Alexithymia dimensions with 20 items 5-point Likert scale (1 = *Strongly Disagree*, 5 = *Strongly Agree*: Difficulty Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and Externally Oriented Thinking (EOR).
 
-The 20-items TAS [@leising2009toronto] assessing Alexithymia traits grouped into three dimensions: Difficulty Identifying Feelings, Difficulty Describing Feelings, and Externally Oriented Thinking.
-Items are rated in a 5-point Likert scale from *Strongly Disagree* (1) to *Strongly Agree*(5).
+The Emotion Reactivity Scale - Brief Version [B-ERS, @veilleux2024development] measures 3 dimensions with 6 items on a 5-point Likert scale (0 = *Not like me at all*, 4 = *Extremely like me*): Arousal (*"My moods are very strong and powerful"*), Sensitivity (*"I tend to get very emotional very easily"*), and Persistence (*"When I am angry/upset, it takes me much longer than most people to calm down"*).
 
-##### Emotion Reactivity Scale - Brief Version (B-ERS)
+The Cognitive Emotion Regulation Questionnaire [CERQ-short, @garnefski2006cognitive] measures 9 adaptive and maladaptive emotion regulation strategies with 18 items (1 = *Almost Never*, 5 = *Almost Always*).
+The strategies include Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.
 
-The 6-item B-ERS [@veilleux2024development] assessing emotional sensitivity on a 5-point Likert scale from *Not like me at all* (0) to *Extremely like me* (4).
+The Černis Felt Sense of Anomaly scale - short form [CEFSA-14, @vcernis2024measuring] measures 7 dissociative experiences with 14 items on a 5-point Likert scale (0 = *Never*, 4 = *Always*).
+This scale is designed to measure dissociative experiences in adolescence and adulthood, specifically focusing on the felt sense of anomaly-type dissociation.
+It includes Anomalous Experience of the Self, Anomalous Experience of the Body, Anomalous Experiences of Emotion, Altered Sense of Familiarity, Altered Sense of Connection, Altered Sense of Agency, and Altered Sense of Reality.
 
-##### Cognitive Emotion Regulation Questionnaire-short (CERQ-short)
-
-The 18 items CERQ-short [@garnefski2006cognitive] on a 5-point Likert scale ranging from *Almost Never* (1) to *Almost Always* (5).
-This questionnaire measures eight cognitive responses to threatening or stressful events, including: Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.
-
-##### Černis Felt Sense of Anomaly scale - short-form (CEFSA-14)
-
-The 14 item CEFSA [@vcernis2024measuring] assessing a specific sub-type of dissociative experiences in adolescence and adulthood - i.e., felt sense of anomaly-type
-dissociation.
-the items are rated ON A 5-point Likert scale from *Never* (0) to *Always* (4), forming seven factors: Anomalous Experience of the Self, Anomalous Experience of the Body , Anomalous Experiences of Emotion , Altered Sense of Familiarity , Altered Sense of Connection, Altered Sense of Agency , and Altered Sense of Reality
-
-##### Primal World Beliefs (PI-18)
-
-the 18 items PI [@clifton2021brief] measuring highest-order primal world beliefs - i.e., beliefs about the basic character of the world: Good, Safe, Enticing, Alive.
-Responses are scored on a 6-point Likert scale from *Strongly Disagree* (0) to *Strongly Agree* (5).
+The Primal World Beliefs Inventory [PI-18, @clifton2021brief] measures higher-order beliefs about the basic character of the world: Good, Safe, Enticing, and Alive.
+The 18 items are presented on a 6-point Likert scale (0 = *Strongly Disagree*, 5 = *Strongly Agree*).
 
@@
 
-##### Life Satisfaction, Depression and Anxiety (PHQ-4)
-
-The 4 item scale of the PHQ [@kroenke2009ultra] assessing depression and anxiety, with responses scored as *Not at all* (0), *Once or twice* (0.5), *Several days* (1), *More than half of the days* (2), *nearly every day* (3).
-This revised version added as a response option (i.e., Once or twice) as a way to improve the scale's sensitivity to milder mood fluctuations [@makowskimeasuring].
-
-<!-- PHQ-4 + LS: presented together -->
-
-##### Mental Health
+The Single Item Life Satisfaction scale [SILS, @jovanovic2020longer] was followed by the PHQ-4 [@kroenke2009ultra] assessing depression and anxiety symptoms with 4 items.
+We used the refined version of the PHQ-4 [@makowski2025measuring], which adds an additional response option ("Once or twice"), increasing sensitivity to subclinical fluctuations.
 
@@
 Binary variables (0 = absent, 1 = present) were created to identify participants reporting mood disorders (MDD, GAD, Bipolar Disorder; with a stricter subgroup of participants undergoing a pharma- or psychological treatment), anxiety-centred disorders (GAD, Panic Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders, addiction-related disorders, borderline personality disorder, autism spectrum disorder (ASD), and ADHD.
-
-##### Somatic Health
 
@@
 
-##### Patient Health Questionnaire - Somatic Symptoms (PHQ-15)
-
-The PHQ-15 [@kroenke2002phq] is comprised of 15 somatic symptoms, with responses scored as *Not at all* (0), *Bothered a little* (1) and *bothered a lot* (2).
-
 #### Lifestyle
 
-Participants were asked to report on their use of wearable devices to monitor several health indices: heart rate, number of steps, calories burned, sleep quality, and weight (including via a regular scale).
-For each selected index, a question appeared asking them to rate how often they check that index; responses were scored as *Never*, *Very rarely*, *A few times per week*, *Once a day*, *A few times per day*, and *A few times per hour*.
-Additionally, participants were asked to rate how important this information was to them on an 8-point Likert scale ranging from *Not at all* (0) to *Very much* (7).
+Participants reported about owning any wearable devices to monitor health indices such as heart rate, number of steps, calories burned, sleep quality, and weight.
+For each selected device, a follow-up question inquired about the frequency of usage and subjective importance of that measure.
 
-Questions regarding physical activity were also included.
-Participants were asked to rate how physically active they consider themselves on an 8-point Likert scale, from *Not at all* (0) to *Very much* (7), and to self-report how many hours of active workout they engage in per week.
+Participants were asked to rate how physically active they consider themselves and how many hours of active workout they engage in per week. Participant's BMI was computed using height and weight.
 
-#### Randomization
+### Procedure
 
-In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned them into three groups (and randomized their order within them): (1) interoception questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18), and (3) health (somatic symptoms, mental health, LS + PHQ-4, CEFSA).
+In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned the measures into three groups (and randomized the order within them): 1) interoception questionnaires (MAIA, IAS, BPQ), 2) emotions (TAS, CERQ, ERS, PI-18), and 3) health (somatic symptoms, mental health, LS + PHQ-4, CEFSA).
 After completing demographic questions, participants always started with the Mint scale, and each following interoception questionnaire was interspersed with two questionnaires from the emotions and pathology groups.
+7 attention checks were embedded throughout (one within each major questionnaire).
 In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on https://github.com/RealityBending/InteroceptionScale].
-
-### Data Analysis
-
-We will start by confirming and further refining the structure of the Mint scale (see @fig-two) using the same EGA model as in Study 1. 
-We will then compute the lower-level dimensions as well as the higher-level metaclusters' scores by averaging the items in each cluster.
-The convergent validity of the final set of items will be assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
-
-```{r}
-#| label: fig-two
-#| fig-cap: "EGA stability and Hclust. TODO."
-#| fig-align: "center"
-#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
-#| out-width: "100%"
-
-knitr::include_graphics("../study2/analysis/figures/fig1.png")
-```
-
-Next, we will test the predictive power of the Mint scale relative to the other interoception questionnaires.
-We will first assess the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict various outcomes, and compare the best between the 4 interoception scales (based on the R2).
-We will then assess the predictive performance of each scale as a whole by comparing regression models with all the dimensions entered as predictors (note that the IAS and BPQ only have one total score variable).
-We will evaluate models based on their total explained variance (R2), as well as on the Bayesian Information Criterion (BIC), which penalizes for predictor numbers, thus offering a balance between model parsimony and predictive power.
-For the logistic model, we will quantify the discriminative power by computing the Area Under the Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which assesses the model's discriminative power (the combination of sensitivity and specificity).
-
-In order to evaluate the potential of a short version of our scale, we will compare 4 variants of the Mint models: the (full) Mint (including all lower-level dimensions), the "metaMint" (only including the metaclusters), the "miniMint" (including the metaclusters computed from a reduced number of items), and the "microMint" (including only the most representative dimension of each metacluster).
-Moreover, we will also include an alternative "interoception-only" version of the MAIA ("iMAIA") that only includes the 3 most interoceptive dimensions (Body Listening, Noticing, and Emotional Awareness)^[See correlation results to further justify this selection.].
-
-**TODO: Ana: do you think that this selection of dims for the iMAIA is fair? Or should I include other dimensions that you think are also very low-level and interoceptive?**
-
-## Results
-
-The first application of EGA to the initial set of 42 items, which reproduced the expected 14 lower-level clusters of triplets and 3 higher-order metaclusters, with the exception of the *UrSe* (Urointestinal Sensitivity), for which one item moved to the *Olfa* (Olfactory Compensation) cluster.
-In order to further balance and reduce the items, we removedt the *UrSe* cluster, as well as *StaS* (State Specificity; which in comparison to the other items stood out as containing vague and overlapping items (e.g., "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)"); *SexO* (Sexual Organs Sensitivity), which overlapped with the *SexS* (Sexual Arousal Sensitivity) cluster; and *CaNo* (Cardiorespiratory Noticing), which overlapped with the *CaCo* (Cardiorespiratory Confusion) cluster.
-
-The final set of 36 items yielded a good fit (Generalized Total Entropy Fit Index = -77.23), with all items showing high cluster stability (> 90\%), with the exception of *Olfa*.
-The final structure included 11 lower-level clusters, grouped into 3 higher-order metaclusters: "Interoceptive Deficit" (containing *CaCo*, *UrIn*, *Derm*, *Sati*, *Olfa*), "Interoceptive Awareness" (containing *ExAc*, *RelA*, *SexS*), and "Visceroception" (containing *Card*, *Resp*, *Gast*).
-Item centrality (intepretable as loadings) are shown in @fig-three.
-Additionally, we also ran a hierarchical clustering analysis which replicated this structure (see @fig-two).
 
@@
 #| label: fig-three
-#| fig-cap: "Item loadings. TODO."
+#| fig-cap: "Item loadings.
+The table shows each item of the Mint with its cluster centrality, which is the EGA equivalent (in terms of interpretation) of factor loadings.
+It also shows how each lower-level cluster is related to higher-order metaclusters."
 #| fig-align: "center"
@@
 
-The correlation matrix of the Mint dimensions (i.e., clusters) revealed an interesting and rich pattern of associations (see @fig-four), with some displaying contrasting patterns of associations compared to dimensions from the same clusters.
-For instance, *Derm* and *Olfa*, despite being positively correlated with the other dimensions from its *Deficit* cluster but contrary to them, were not negatively correlated to the *Awareness* metacluster and its dimensions.
-Similarly, *Sati*, unlike the other *Deficit* dimensions, was not positively correlated to *Visceroception*.
-This complex structure suggests that the dimensions indeed capture distinct aspects of interoception, and that the metaclusters, rather than being simple aggregates of rather-redundant elements, might actually capture unique combinations greater than the sum of its part.
-It also provides evidence against a simplistic adaptive *vs.* maladaptive dichotomy, as the *Deficit* dimensions are not negatively correlated with the *Visceroceptive* dimensions.
+### Data Analysis
 
-**TODO: this paragraph probably needs to be rewritten and made clearer**
+We started by confirming and further refining the structure of the Mint scale (see @fig-two) using the same EGA model as in Study 1. 
+We then computed the lower-level dimensions and the higher-level metaclusters' scores by averaging their corresponding items.
+The convergent validity of the final set of items was assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
+
+Next, we tested the predictive power of the Mint scale relative to other interoception questionnaires.
+We will assessed the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict different outcomes, and compare the best between the 4 interoception scales (based on the R2).
+We then evaluated the predictive performance of each scale as a whole by comparing regression models with all the dimensions entered as predictors (note that the IAS and BPQ only have one total score variable).
+We assessed the models based on their total explained variance (R2), as well as on the Bayesian Information Criterion (BIC), which penalizes for predictor number, thus offering a balance between model parsimony and predictive power.
+For the logistic models, we quantified the discriminative power by computing the Area Under the Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which assesses the model's discriminative power (the combination of sensitivity and specificity).
+
+In order to evaluate the potential for a short version of our scale, we compared 4 variants of the Mint: the (full) *Mint* (including all lower-level dimensions), the *metaMint* (only including the metaclusters), the *miniMint* (including the metaclusters computed from a reduced number of items), and the *microMint* (including only the most representative dimension of each metacluster).
+Moreover, we also included an alternative "interoception-focused" version of the MAIA (*iMAIA*) that only contains the 3 most interoceptive dimensions (Body Listening, Noticing, and Emotional Awareness)^[See correlation results to further justify this selection.].
+
+## Results
+
+The application of EGA to the initial set of 42 items reproduced the expected 14 lower-level clusters of triplets and 3 higher-order metaclusters, with the exception of the *UrSe* (Urointestinal Sensitivity), for which one item moved to the *Olfa* (Olfactory Compensation) cluster.
+In order to further balance and reduce the items, we removed the *UrSe* cluster, as well as *StaS* (State Specificity), which in comparison to the other items stood out as containing vague and overlapping items
+<!-- ; e.g., "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)" -->
+; *SexO* (Sexual Organs Sensitivity), which overlapped with the *SexS* (Sexual Arousal Sensitivity) cluster; and *CaNo* (Cardiorespiratory Noticing), which overlapped with the *CaCo* (Cardiorespiratory Confusion) cluster.
+
+The final set of 33 items yielded a good fit (Generalized Total Entropy Fit Index = -77.23), with all items showing high cluster stability (> 90\%), with the exception of *Olfa*.
+The final structure included 11 lower-level clusters, grouped into 3 higher-order metaclusters: "Interoceptive Deficit" (containing *CaCo*, *UrIn*, *Derm*, *Sati*, *Olfa*), "Interoceptive Awareness" (containing *ExAc*, *RelA*, *SexS*), and "Visceroception" (containing *Card*, *Resp*, *Gast*).
+Item centrality (intepretable as loadings in traditional factor analysis frameworks) are shown in @fig-three.
+Additionally, we applied hierarchical clustering analysis which replicated this structure (see @fig-two), suggesting consistency across methods.
 
@@
 #| label: fig-four
-#| fig-cap: "Correlation Matrices. TODO. Stars indicate dimensions that have been score-reversed for better in-context interpretation."
+#| fig-cap: "Correlation Matrices between the Mint dimensions (upper-left), and between the Mint and other interoception questionnaires (MAIA, BPQ and IAS; upper-right).
+The bottom matrix shows the relationships between interoception and other measures included in the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4), emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA), and Primal World Beliefs.
+Stars indicate dimensions that have been score-reversed for better in-context interpretation.
+Correlation coefficients are shown for significant correlations."
 #| fig-align: "center"
@@
 
-The correlation matrix between the Mint and the other interoception scales showed high level of redundancies as well as some unique contributions (see @fig-four).
+The correlation matrix of the Mint dimensions revealed an interesting and rich tapestry of relationships (see @fig-four), with contrasting patterns of associations with dimensions from the same group.
+For instance, *Derm* and *Olfa*, despite being positively correlated with the other dimensions from the *Deficit* cluster,
+were not negatively correlated to *Awareness* and its dimensions.
+Similarly, *Sati*, unlike the other *Deficit* dimensions, was not positively correlated to *Visceroception*.
+This complex structure suggests that the dimensions indeed capture distinct aspects of interoception, and that the metaclusters, rather than being simple aggregates of rather-redundant elements, might actually capture unique combinations (greater than the sum of their parts).
+It also provides evidence against a simplistic adaptive *vs.* maladaptive dichotomy, as *Deficit* was not negatively bit positively correlated with *Visceroception*.
+Interestingly, while *Awareness* was also positively correlated with *Visceroception*, it yielded an insignificant negative correlation with *Deficit* (this finding was also aligned with the hierarchical clustering results, showing a greater proximity between *Deficit* and *Visceroception* than with *Awareness*), underlining again the complex web of relationships captured by the Mint.
+
+The correlation matrix between the Mint and the other interoception scales revealed high levels of overlap, as well as some unique contributions (see @fig-four).
 The BPQ was positively correlated with most Mint dimensions (the highest with *Visceroception*, $r = .46$).
@@
 Interestingly, Rumination (and Self-Blame) stood out as selectively related to the Mint's *Visceroception* and *Deficit* dimensions (note that Rumination was also related to the MAIA's interoceptive dimensions, namely Noticing, Emotional Awareness and Body Listening).
-The only primal world belief that correlated particuarly with the Mint's *Visceroception* and the MAIA's interoceptive dimension was the belief that the world was alive (**Ana maybe throw in a couple more words about what this belief means and is defined**).
+The only primal world belief that correlated particularly with the Mint's *Visceroception* and the MAIA's interoceptive dimension was the belief that the world was alive (**TODO: Ana maybe throw in a couple more words about what this belief means and is defined**).
+
+```{r}
+#| label: fig-five
+#| fig-cap: "Summary table of the comparison between interoception questionnaires (Mint, MAIA, BPQ and IAS).
+For various outcomes included the study, we tested the Mint and Non-Mint dimension that had the strongest link (as a unique predictor).
+Values in parenthesis represents correlation coefficient for continuous variables and log-odds ratios for binary variables (the occurrence of mental and somatic health conditions).
+We also compared the predictive performance of regression models including multiple predictors, and present their ranking based on raw predictive power (R2) and BIC, which favours more parsimonious models (with less predictors).
+Green background indicates an advantage for the Mint, while red backgrounds indicate an advantage for another interoception scale.
+Orange backgrounds indicate an advantage for the MAIA driven by its emotion-regulation dimensions (Trusting and Not-Worrying)."
+#| fig-align: "center"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "82%"
+
+knitr::include_graphics("../study2/analysis/figures/table2.png")
+```
 
@@
 Most of the exceptions showed an advantage for MAIA dimensions, in particular Not-worrying (which best predicted ERS' Sensitivity and Persistence) and Trusting (which best predicted LS, Depression and Anxiety, CEFSA's Emotion and Connection, and self-reported physical activity).
-
-```{r}
-#| label: fig-five
-#| fig-cap: "Best model table. TODO."
-#| fig-align: "center"
-#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
-#| out-width: "100%"
-
-knitr::include_graphics("../study2/analysis/figures/table2.png")
-```
 
@@
 
-Finally, the importance of heart monitoring (for owners of such wearable) was best predicted by MAIA's body listening ($r = .36$), followed the *Card* dimension of the Mint ($r = .31$).
+Finally, the importance of heart monitoring (for owners of such wearable) was best predicted by MAIA's Body listening ($r = .36$), followed the *Card* dimension of the Mint ($r = .31$).
 The importance of sleep monitoring importance was best predicted by *RelA* ($r = .22$), followed by MAIA's not worrying ($r = -.219$).
-Daily activity via steps monitoring was best predicted by MAIA's Noticing ($r = .28$), folowed by *Awareness* ($r = .26$).
+Daily activity via steps monitoring was best predicted by MAIA's Noticing ($r = .28$), followed by *Awareness* ($r = .26$).
 
@@
 #| label: fig-six
-#| fig-cap: "Predictive Performance (ROC curves). TODO." 
+#| fig-cap: "Predictive performance of interoception questionnaires for various self-reported mental health conditions (mood disorders with psychopharmacological treatment, ADHD and ASD) and somatic symptoms.
+The Receiver Operating Characteristic (ROC) curves are shown for the logistic regression models for various questionnaires and versions.
+A high Area Under the Curve (AUC) indicates a good discriminative power of the model (i.e., a strong combination of sensitivity and specificity).
+The Mint scale (in blue-green) consistently outperformed the other interoception scales, with the exception of the MAIA which, driven by its emotion-regulation dimensions (Trusting and Not-worrying), performed better for mood disorders and central sensitization symptoms.
+In several instances, the short versions of the Mint scale (miniMint and microMint) yielded reasonable performance, still outperforming other measures."
 #| fig-align: "center"
@@
 
-Main contender is MAIA.
+- Structure: Low stability of *Olfa* as belonging in the deficit group.
+More studies are needed to investigate its place and cluster invariance: it is possible that its association might depend on other factors or categories.
+- Main contender is MAIA.
 But its most sensitive dimensions seem to be the least related to interoception, which is dangerous as it might lead to findings with associations misattributed to "Interoception" (just because it correlate with some MAIA dimensions), but it might have nothing to do with interoception per se and more with emotion regulation.
-
-Basically the pattern is clear: everything high-level, metacognitive and highly subjective related to wellbeing and general affective state is the most strongly related to the MAIA through some of its Emotion regulation dimensions.
+- Basically the pattern is clear: everything high-level, metacognitive and highly subjective related to wellbeing and general affective state is the most strongly related to the MAIA through some of its Emotion regulation dimensions.
 All the other outcomes actually related to interoceptive processes are most strongly predicted by the Mint.
@@
 
-Future directions: needs to test relationship with physiological measures of interoception.
-
-Also, the structure might still require a bit of deeper investigation, in particular with some of its facets (*Olfa* and *Derm*) which might display different associations depending on the context or the population.
+- Future directions: needs to test relationship with physiological measures of interoception.
+- Also, the structure might still require a bit of deeper investigation, in particular with some of its facets (*Olfa* and *Derm*) which might display different associations depending on the context or the population.
 

### 2025-07-02 paper/manuscript.tex
update

@@
 
-\authorsnames[{1,2},{1},{1}]{Dominique Makowski,Ana Neves,Giulia
-Poreiro}
+\authorsnames[{1,2},{1},{1},{1},{1}]{Dominique Makowski,Ana Neves,Emma
+Benn,Maisie Bennett,Giulia Poreiro}
 
@@
 
-\leftheader{Makowski, Neves and Poreiro}
+\leftheader{Makowski, Neves, Benn, Bennett and Poreiro}
 
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, toprule=.15mm, arc=.35mm, left=2mm, breakable, colback=white, rightrule=.15mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]
+\par{     \begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colframe=quarto-callout-note-color-frame, colback=white, opacityback=0, left=2mm, arc=.35mm, leftrule=.75mm, breakable, bottomrule=.15mm, rightrule=.15mm]
 
@@
 administration, Supervision, Writing -- original draft, Writing --
-review \& editing; Giulia Poreiro:   Investigation, Methodology, Writing
--- original draft, Writing -- review \& editing}
+review \& editing; Emma Benn:   Investigation; Maisie
+Bennett:   Investigation; Giulia
+Poreiro:   Investigation, Methodology, Writing -- original
+draft, Writing -- review \& editing}
 \par{Correspondence concerning this article should be addressed
@@
 
-TODO: write general intro.
+Main issues in existing questionnaires:
 
-Main issues in existing questionnaires: - Either heavily based on
-theories (e.g., focusing on a specific dimensions), despite shaky
-evidence for said-theories - Do not control for context (which leads to
-variability in interpretation and occurence) - Often quite narrow in the
-modalities covered
+\begin{itemize}
+\tightlist
+\item
+  Either heavily based on theories (e.g., focusing on specific
+  ``alleged'' dimensions), despite shaky evidence for said-theories
+\item
+  Do not control for context (which leads to variability in
+  interpretation and occurence)
+\item
+  Often quite narrow in the modalities covered (or scattered, like the
+  IAS)
+\end{itemize}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
   Goal of study 1: to generate a lot of items, analyze its structure and
   reduce them to a balanced set of items.
+\end{itemize}
 
@@
 sample includes 559 participants (age = 37.0 \(\pm\) 12.2 {[}18, 77{]};
-50.8\% women; Country of residence: 63.86\% UK, 26.65\% USA). This study
+50.8\% women; country of residence: 63.86\% UK, 26.65\% USA). This study
 was approved by the University of Sussex' Ethics Committee
-(\textbf{NUMBER}).
+(ER/MB2021/1).
 
@@
 of the interoceptive experience (e.g., whether negative or positive), we
-generated items in a systematic way following a combinatorial approach,
-where each item's category was a combination of a specific modality and
-context (Figure~\ref{fig-one}).
+generated items in a systematic way following a combinatory approach,
+where each item's category corresponds to the union of a specific
+modality and context (Figure~\ref{fig-one}).
 
@@
 {\caption{{The conceptual grid used to generate the 120 initial items
-(top-left). Each item belong both to an interoceptive modalitiy and a
-facet, with the number of each item per category indicated in the
-circles. The askterisk denotes the additional presence of an attention
-check item in that category. In the experiment, these items were
-presented on different pages grouped either by modality (bottom-left),
-by facet (top-right), or entirely randomly. The Correlation Similarity
-(bottom-right) analysis suggested that the correlation matrix obtained
-from the participants assigned to the random-grouping condition was
-slightly more similar (but non-significantly) to the one obtained in the
-modality-grouping condition, suggesting that 1) the scale's structure is
-robust to different presentation conditions; 2) modality-grouping might
-tend to facilitate the emergence of the underlying item structure (and
-thus be interpreted as being more natural).}{\label{fig-one}}}}
+(top-left). Each item belongs both to an interoceptive modality
+(vertical) and a facet (horizontal), with the number of each item per
+category indicated in the circles. The asterisk denotes the additional
+presence of an attention check item in that category. In the experiment,
+these items were presented on different pages grouped either by modality
+(bottom-left), by facet (top-right), or randomly. The Correlation
+Similarity (bottom-right) analysis suggested that the correlation matrix
+obtained from the participants assigned to the random-grouping condition
+was slightly more similar (but non-significantly) to the one obtained in
+the modality-grouping condition, suggesting that the scale's structure
+is robust to different presentation conditions, and that the
+modality-grouping might potentially tend to facilitate the emergence of
+the underlying item structure (and thus be interpreted as being more
+``natural'').}{\label{fig-one}}}}
 
@@
 
-We firstly identified 7 ``modalities'' (cardiac, respiratory, gastric,
-genital, skin \& temperature, bladder \& colon, and a ``general state''
-category corresponding to a holistic and general awareness of an
-interoceptive state or dimension). Through iterative refinement (e.g.,
-splitting or merging different categories together), we then settled on
-6 ``facets'', which encompass both \emph{contexts} of experience
-(negative and positive arousal, namely anxious and sexual states), and
-potential distinct \emph{mechanisms} (nociception \& pleasure,
-sensitivity, accuracy, and confusion).
+We identified 7 ``modalities'' (cardiac, respiratory, gastric, genital,
+skin \& temperature (thermoregulation), bladder \& colon, and a
+``general state'' category corresponding to a holistic and general
+awareness of an interoceptive state or dimension). Through iterative
+refinement (e.g., splitting or merging different categories together),
+we settled on 6 ``facets'', which encompass both \emph{contexts} of
+experience (negative and positive arousal, e.g., anxious and sexual
+states), and potential distinct \emph{mechanisms} (nociception \&
+pleasure, sensitivity, accuracy, and confusion).
 
@@
 number of items with consistent phrasing within modalities and
-facets\footnote{The initial item list at
+facets\footnote{The initial item list is available at
   \href{https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html}{realitybending.github.io/InteroceptionScale/study1/analysis/2\_analysis.html}}.
@@
 the first page, all colon \& bladder items on the second, etc.), 2)
-items grouped by facet, or 3) items presented fully randomly (but
-balanced randomly across 6 pages). The order of the item on any given
-page and the order of the modalities/facets were randomized. Each
-participant completed the full set of 120 items, with the attention
-check items interspersed throughout. The online experiment was
-implemented using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw,
-2015}), and item responses were recorded using 7-points Likert scales (0
-= Disagree, 6 = Agree).
+items grouped by facet, or 3) items presented fully randomly (but with
+their number balanced across 6 pages). The order of the item on any
+given page and the order of the modalities/facets was randomized. Each
+participant completed the full set of 120 items, with 8 attention check
+items interspersed throughout. The online experiment was implemented
+using JsPsych (\citeproc{ref-de2015jspsych}{De Leeuw, 2015}), and item
+responses were recorded using 7-points Likert scales (0 = Disagree, 6 =
+Agree).
 
@@
 Items deemed ``redundant'' (which can distort the item structure
-estimation by introducing multicollinearity or local dependencies) will
-be identified (using the recommended threshold of 0.25) using Unique
+estimation by introducing multicollinearity or local dependencies) were
+identified (using the recommended threshold of 0.25) using Unique
 Variable Analysis (UVA, \citeproc{ref-christensen2023unique}{Christensen
@@
 
-The structure of the items will be analyzed using the recently-developed
+The structure of the items was analyzed using the recently-developed
 Exploratory Graph Analysis (EGA, \citeproc{ref-golino2017exploratory}{H.
@@
 
-After removing redundant items using UVA, we will iteratively fit
+After removing redundant items using UVA, we iteratively fitted
 hierarchical EGA models (which additionally estimates higher-order
-``meta'' clusters) using ``glasso'' {[}\textbf{REF}{]} and the
-``leiden'' algorithm {[}\textbf{REF}{]} for community detection,
-refining the item pool at each step. We will start by removing items
-with a low (\textless{} 80\%) cluster stability (i.e., volatile items
-which jump between clusters across bootstrapped samples), followed by
-odd items belonging to no clusters or pairs of items (i.e., we keep
-items belonging to clusters of more than 2 items). Finally, for each
-lower-level cluster, we will select the 3 items with the highest node
-centrality (i.e., the highest loading in the cluster).
+``meta'' clusters) using ``glasso''
+(\citeproc{ref-friedman2008sparse}{Friedman et al., 2008}) and the
+``Leiden'' algorithm (\citeproc{ref-traag2019louvain}{Traag et al.,
+2019}) for community detection, refining the item pool at each step. We
+started by removing items with a low (\textless{} 80\%) cluster
+stability (i.e., volatile items which jump between clusters across
+bootstrapped samples), followed by odd items belonging to no clusters or
+pairs of items (i.e., we keep items belonging to clusters of more than 2
+items). Finally, for each lower-level cluster, we selected the 3 items
+with the highest node centrality (i.e., the highest loading in the
+cluster).
 
@@
 \(SMI_{\text{Random vs. Facet}} = 0.49\),
-\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .52\)).
+\(SMI_{\text{Random vs. Modality}} = 0.51\), \(p = .52\)), despite a
+consistent bias in favour of the modality-grouping condition.
 
-From the 120 initial items, UVA flagged 4 redundant items that we
-removed. We then removed 40 items that showed low cluster stability, and
-9 items that were part of clusters with less than 3 items. Finally, We
-kept the 3 items with the highest loading in their lower-level structure
+From the 120 initial items, 4 redundant items were flagged by UVA. We
+then removed 40 items that showed low cluster stability, and 9 items
+that were part of clusters with less than 3 items. Finally, We kept the
+3 items with the highest loading in their lower-level structure
 (removing 13 items in the process), resulting in 54 items in the final
@@
 
+\begin{itemize}
+\tightlist
+\item
   Possible (although not at all significant) bias consistent across
   indices in favour of a greater similarity with the modality-grouping
-condition.
+  condition. Futher research with more data (here we only had
+  \textasciitilde200 observation per condition) might be able to yield
+  more conclusive results. In general, testing the presentation mode is
+  a novel approach which should be more widely applied to psychometric
+  validations.
+\item
+  We grouped some of the dimensions under ``Awareness'', despite being
+  similar to items included in the IAS typically conceptualized as
+  ``Accuracy''. However, we believe that subjective scales cannot be
+  pure measures of accuracy, as they are inherently subjective and thus
+  reflect a degree of awareness (of one's accurate noticing or
+  sensation).
+\item
+  Olfactory compensation: pseudo-interoceptive pathway whereby people
+  with interoceptive deficits would compensate by gathering evidence
+  about their internal state externally (e.g., via smell).
+\item
+  The metacluster ``Sensitivity'' seems to be grouping iterms related to
+  visceropcetion and (hyper)sensitivity (Derm).
+\end{itemize}
 
@@
 
-TODO: write intro. Goal of study 2: to validate the Mint scale against
-other interoception scales.
+\begin{itemize}
+\tightlist
+\item
+  Goal of study 2: to validate the Mint scale against other
+  interoception scales.
+\end{itemize}
 
@@
 
-We recruited 921 English-speaking participants via
-Prolific\textcopyright and SONA, from which 118 were excluded for
-failing at least one attention check and 6 based on multivariate
-distance (using the same procedure as for study 1). 60 participants were
-further excluded due to missing data following a technical error. The
-final sample includes 737 participants (age = 36.8 \(\pm\) 14.7 {[}18,
-87{]}; 57.3\% women; Country of residence: 75.17\% United Kingdom,
-24.83\% other). This study was approved by the University of Sussex'
-Ethics Committee (\textbf{NUMBER}).
+We recruited 921 English-speaking participants via SONA and
+Prolific\textcopyright, from which 118 were excluded for failing at
+least one attention check and 6 based on multivariate distance (using
+the same procedure as for study 1). 60 participants were further
+excluded due to missing data following a technical issue. The final
+sample includes 737 participants (age = 36.8 \(\pm\) 14.7 {[}18, 87{]};
+57.3\% women; Country of residence: 75.17\% United Kingdom, 24.83\%
+other). This study was approved by the University of Sussex' Ethics
+Committee (ER/EB672/2).
 
-\subsubsection{Procedure}\label{procedure-1}
+\subsubsection{Measures}\label{measures}
 
-The experiment included the following questionnaires.
+\begin{figure*}[!htbp]
+
+{\caption{{Structure analysis of the final set of 33 Mint items.
+Hierarchical Exploratory Graph Analysis (EGA) was applied to jointly
+identify clusters of items, as well as higher-order metaclusters. The
+reliability of each item can be quantified by the proportion of
+structure replication across bootstrapped samples, with high values
+indicative of high structural stability. The Mint scale displayed an
+excellent structural consistency, with the exception of the \emph{Olfa}
+cluster which belonging to the \emph{Deficit} metaclusters warrants
+further research. Bottom plot shows the result of hierarchical
+clustering, providing evidence for structure statbility across methods,
+and allowing for more granular understanding of the relationships
+between variables.}{\label{fig-two}}}}
+
+\begin{center}
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig1.png}
+\end{center}
+
+\end{figure*}
 
@@
 
-\subparagraph{The Multimodal Interoception Questionnaire
-(Mint).}\label{the-multimodal-interoception-questionnaire-mint}
+The 45 items of the Multimodal Interoception Questionnaire (Mint) scale
+were presented in a random order, with the same 7-point Likert scale as
+in study 1 (0 = \emph{Disagree}, 6 = \emph{Agree}).
 
-The 45 items of the Mint scale were presented in a random order, with
-the same 7-point Likert scale as in study 1 (0 = Disagree, 6 = Agree).
+The Multidimensional Assessment of Interoceptive Awareness (MAIA-2,
+\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018})
+measures 8 dimensions with 37 items presented on a 7-point Likert scale
+(0 = \emph{Never}, 6 = \emph{Always}). It includes bodily dimensions
+such as Body Listening, Noticing, Emotional Awareness, dimensions
+related to emotion regulation, such as Trust, Not-worrying, and
+Self-Regulation, as well as dimensions related to attention, such as
+Attention Regulation and Not-Distracting. The relationship of some of
+these dimensions to interoception remains debated, particularly
+Not-Distracting and Not-Worrying, which tend to show weak or
+non-existent correlations with the other MAIA subscales
+(\citeproc{ref-ferentzi2021examining}{Ferentzi et al., 2021}).
 
-\subparagraph{Multidimensional Assessment of Interoceptive Awareness
-(MAIA).}\label{multidimensional-assessment-of-interoceptive-awareness-maia}
+The Body Perception Questionnaire - Very Short Form (BPQ-VSF,
+\citeproc{ref-cabrera2018assessing}{Cabrera et al., 2018}) measures a
+general score of bodily awareness with 12 items presented on 5-point
+Likert scale (0 = \emph{Never}, 5 = \emph{Always}).
 
-The X items of the MAIA\ldots{}
-
-\subparagraph{The Body Perception Questionnaire
-(BPQ).}\label{the-body-perception-questionnaire-bpq}
-
-\textbf{TODO}
-
-\subparagraph{The Interoceptive Awareness Scale
-(IAS).}\label{the-interoceptive-awareness-scale-ias}
-
-\textbf{TODO}
+The Interoceptive Accuracy Scale (IAS,
+\citeproc{ref-murphy2020testing}{Murphy et al., 2020}) measures a
+general score of interoceptive accuracy to physical sensations with 21
+items presented on a 5-point Likert scale (1 = \emph{Disagree Strongly},
+5 = \emph{Strongly Agree}).
 
@@
 
-\subparagraph{Toronto Alexithymia Scale
-(TAS-20).}\label{toronto-alexithymia-scale-tas-20}
+The Toronto Alexithymia Scale TAS (TAS-20,
+\citeproc{ref-leising2009toronto}{Leising et al., 2009}) measures 3
+Alexithymia dimensions with 20 items 5-point Likert scale (1 =
+\emph{Strongly Disagree}, 5 = \emph{Strongly Agree}: Difficulty
+Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and
+Externally Oriented Thinking (EOR).
 
-\textbf{TODO}
+The Emotion Reactivity Scale - Brief Version (B-ERS,
+\citeproc{ref-veilleux2024development}{Veilleux et al., 2024}) measures
+3 dimensions with 6 items on a 5-point Likert scale (0 = \emph{Not like
+me at all}, 4 = \emph{Extremely like me}): Arousal (\emph{``My moods are
+very strong and powerful''}), Sensitivity (\emph{``I tend to get very
+emotional very easily''}), and Persistence (\emph{``When I am
+angry/upset, it takes me much longer than most people to calm down''}).
 
-\subparagraph{Emotion Reactivity Scale
-(ERS).}\label{emotion-reactivity-scale-ers}
+The Cognitive Emotion Regulation Questionnaire (CERQ-short,
+\citeproc{ref-garnefski2006cognitive}{Garnefski \& Kraaij, 2006})
+measures 9 adaptive and maladaptive emotion regulation strategies with
+18 items (1 = \emph{Almost Never}, 5 = \emph{Almost Always}). The
+strategies include Self-blame, Other-blame, Rumination, Catastrophizing,
+Putting into Perspective, Positive Refocusing, Positive Reappraisal,
+Acceptance, and Planning.
 
-\textbf{TODO}
+The Černis Felt Sense of Anomaly scale - short form (CEFSA-14,
+\citeproc{ref-vcernis2024measuring}{Černis et al., 2024}) measures 7
+dissociative experiences with 14 items on a 5-point Likert scale (0 =
+\emph{Never}, 4 = \emph{Always}). This scale is designed to measure
+dissociative experiences in adolescence and adulthood, specifically
+focusing on the felt sense of anomaly-type dissociation. It includes
+Anomalous Experience of the Self, Anomalous Experience of the Body,
+Anomalous Experiences of Emotion, Altered Sense of Familiarity, Altered
+Sense of Connection, Altered Sense of Agency, and Altered Sense of
+Reality.
 
-\subparagraph{Cognitive Emotion Regulation Questionnaire
-(CERQ).}\label{cognitive-emotion-regulation-questionnaire-cerq}
-
-\textbf{TODO}
-
-\subparagraph{TODO (CEFSA).}\label{todo-cefsa}
-
-\textbf{TODO}
-
-\subparagraph{Primal World Beliefs
-(PI-18).}\label{primal-world-beliefs-pi-18}
-
-\textbf{TODO}
+The Primal World Beliefs Inventory (PI-18,
+\citeproc{ref-clifton2021brief}{Clifton \& Yaden, 2021}) measures
+higher-order beliefs about the basic character of the world: Good, Safe,
+Enticing, and Alive. The 18 items are presented on a 6-point Likert
+scale (0 = \emph{Strongly Disagree}, 5 = \emph{Strongly Agree}).
 
@@
 
-\subparagraph{Life Satisfaction, Depression and Anxiety
-(PHQ-4).}\label{life-satisfaction-depression-and-anxiety-phq-4}
-
-\textbf{TODO}
-
-\subparagraph{Mental Health.}\label{mental-health}
+The Single Item Life Satisfaction scale (SILS,
+\citeproc{ref-jovanovic2020longer}{Jovanović \& Lazić, 2020}) was
+followed by the PHQ-4 (\citeproc{ref-kroenke2009ultra}{Kroenke et al.,
+2009}) assessing depression and anxiety symptoms with 4 items. We used
+the refined version of the PHQ-4
+(\citeproc{ref-makowski2025measuring}{Makowski et al., 2025}), which
+adds an additional response option (``Once or twice''), increasing
+sensitivity to subclinical fluctuations.
 
@@
 spectrum disorder (ASD), and ADHD.
-
-\subparagraph{Somatic Health.}\label{somatic-health}
 
@@
 
-\textbf{TODO}
+Participants reported about owning any wearable devices to monitor
+health indices such as heart rate, number of steps, calories burned,
+sleep quality, and weight. For each selected device, a follow-up
+question inquired about the frequency of usage and subjective importance
+of that measure.
 
-Physical activity.
+Participants were asked to rate how physically active they consider
+themselves and how many hours of active workout they engage in per week.
+Participant's BMI was computed using height and weight.
 
-Wearables.
-
-\paragraph{Randomization.}\label{randomization}
+\subsubsection{Procedure}\label{procedure-1}
 
 In order to avoid the repetition of similar types of questions and and
-balance longer and shorter questionnaires, we partitioned them into
-three groups (and randomized their order within them): (1) interoception
-questionnaires (MAIA, IAS, BPQ), (2) emotions (TAS, CERQ, ERS, PI-18),
-and (3) pathology (somatic health, mental health, LS + PHQ-4, CEFSA).
-After completing demographic questions, participants always started with
-the Mint scale, and each following interoception questionnaire was
-interspersed with two questionnaires from the emotions and pathology
-groups. In order to make the experiment more enjoyable, the experiment
-ended with a radar chart summarizing the participants' responses to the
-Mint scale\footnote{The experiment can be tested by following the link
-  on https://github.com/RealityBending/InteroceptionScale}.
-
-\subsubsection{Data Analysis}\label{data-analysis-1}
-
-We will start by confirming and further refining the structure of the
-Mint scale using the same EGA model as in Study 1. The convergent
-validity of the final set of items will be assessed by computing the
-correlations between the Mint scale and the other interoception
-questionnaires (MAIA, BPQ, IAS). Then, we will test the predictive power
-of the Mint scale (relative to the other interoception questionnaires)
-on various measures. We will start by fitting regression (linear for
-continuous measures - e.g., depression score - and logistic for binary
+balance longer and shorter questionnaires, we partitioned the measures
+into three groups (and randomized the order within them): 1)
+interoception questionnaires (MAIA, IAS, BPQ), 2) emotions (TAS, CERQ,
+ERS, PI-18), and 3) health (somatic symptoms, mental health, LS + PHQ-4,
+CEFSA). After completing demographic questions, participants always
+started with the Mint scale, and each following interoception
+questionnaire was interspersed with two questionnaires from the emotions
+and pathology groups. 7 attention checks were embedded throughout (one
+within each major questionnaire). In order to make the experiment more
+enjoyable, the experiment ended with a radar chart summarizing the
+participants' responses to the Mint scale\footnote{The experiment can be
+  tested by following the link on
+  https://github.com/RealityBending/InteroceptionScale}.
 
@@
 
-{\caption{{TODO.}{\label{fig-two}}}}
-
-\begin{center}
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/fig1.png}
-\end{center}
-
-\end{figure*}
-
-\subsection{Results}\label{results-1}
-
-\begin{figure*}[!htbp]
-
-{\caption{{TODO.}{\label{fig-three}}}}
+{\caption{{Item loadings. The table shows each item of the Mint with its
+cluster centrality, which is the EGA equivalent (in terms of
+interpretation) of factor loadings. It also shows how each lower-level
+cluster is related to higher-order metaclusters.}{\label{fig-three}}}}
 
@@
 
+\subsubsection{Data Analysis}\label{data-analysis-1}
+
+We started by confirming and further refining the structure of the Mint
+scale (see Figure~\ref{fig-two}) using the same EGA model as in Study 1.
+We then computed the lower-level dimensions and the higher-level
+metaclusters' scores by averaging their corresponding items. The
+convergent validity of the final set of items was assessed by computing
+the correlations between the Mint scale and the other interoception
+questionnaires (MAIA, BPQ, IAS).
+
+Next, we tested the predictive power of the Mint scale relative to other
+interoception questionnaires. We will assessed the importance of each
+interoceptive dimension (from all the scales) as a unique predictor by
+fitting regression models (linear for continuous measures - e.g.,
+depression score - and logistic for binary variables - e.g., presence
+\emph{vs.} absence of mood disorders) to predict different outcomes, and
+compare the best between the 4 interoception scales (based on the R2).
+We then evaluated the predictive performance of each scale as a whole by
+comparing regression models with all the dimensions entered as
+predictors (note that the IAS and BPQ only have one total score
+variable). We assessed the models based on their total explained
+variance (R2), as well as on the Bayesian Information Criterion (BIC),
+which penalizes for predictor number, thus offering a balance between
+model parsimony and predictive power. For the logistic models, we
+quantified the discriminative power by computing the Area Under the
+Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which
+assesses the model's discriminative power (the combination of
+sensitivity and specificity).
+
+In order to evaluate the potential for a short version of our scale, we
+compared 4 variants of the Mint: the (full) \emph{Mint} (including all
+lower-level dimensions), the \emph{metaMint} (only including the
+metaclusters), the \emph{miniMint} (including the metaclusters computed
+from a reduced number of items), and the \emph{microMint} (including
+only the most representative dimension of each metacluster). Moreover,
+we also included an alternative ``interoception-focused'' version of the
+MAIA (\emph{iMAIA}) that only contains the 3 most interoceptive
+dimensions (Body Listening, Noticing, and Emotional
+Awareness)\footnote{See correlation results to further justify this
+  selection.}.
+
+\subsection{Results}\label{results-1}
+
+The application of EGA to the initial set of 42 items reproduced the
+expected 14 lower-level clusters of triplets and 3 higher-order
+metaclusters, with the exception of the \emph{UrSe} (Urointestinal
+Sensitivity), for which one item moved to the \emph{Olfa} (Olfactory
+Compensation) cluster. In order to further balance and reduce the items,
+we removed the \emph{UrSe} cluster, as well as \emph{StaS} (State
+Specificity), which in comparison to the other items stood out as
+containing vague and overlapping items ; \emph{SexO} (Sexual Organs
+Sensitivity), which overlapped with the \emph{SexS} (Sexual Arousal
+Sensitivity) cluster; and \emph{CaNo} (Cardiorespiratory Noticing),
+which overlapped with the \emph{CaCo} (Cardiorespiratory Confusion)
+cluster.
+
+The final set of 33 items yielded a good fit (Generalized Total Entropy
+Fit Index = -77.23), with all items showing high cluster stability
+(\textgreater{} 90\%), with the exception of \emph{Olfa}. The final
+structure included 11 lower-level clusters, grouped into 3 higher-order
+metaclusters: ``Interoceptive Deficit'' (containing \emph{CaCo},
+\emph{UrIn}, \emph{Derm}, \emph{Sati}, \emph{Olfa}), ``Interoceptive
+Awareness'' (containing \emph{ExAc}, \emph{RelA}, \emph{SexS}), and
+``Visceroception'' (containing \emph{Card}, \emph{Resp}, \emph{Gast}).
+Item centrality (intepretable as loadings in traditional factor analysis
+frameworks) are shown in Figure~\ref{fig-three}. Additionally, we
+applied hierarchical clustering analysis which replicated this structure
+(see Figure~\ref{fig-two}), suggesting consistency across methods.
+
 \begin{figure*}[!htbp]
 
-{\caption{{TODO.}{\label{fig-four}}}}
+{\caption{{Correlation Matrices between the Mint dimensions
+(upper-left), and between the Mint and other interoception
+questionnaires (MAIA, BPQ and IAS; upper-right). The bottom matrix shows
+the relationships between interoception and other measures included in
+the study, such as alexithymia (TAS-20), depression and anxiety (PHQ-4),
+emotion reactivity (ERS), abnormal and dissociative experiences (CEFSA),
+and Primal World Beliefs. Stars indicate dimensions that have been
+score-reversed for better in-context interpretation. Correlation
+coefficients are shown for significant
+correlations.}{\label{fig-four}}}}
 
@@
 
+The correlation matrix of the Mint dimensions revealed an interesting
+and rich tapestry of relationships (see Figure~\ref{fig-four}), with
+contrasting patterns of associations with dimensions from the same
+group. For instance, \emph{Derm} and \emph{Olfa}, despite being
+positively correlated with the other dimensions from the \emph{Deficit}
+cluster, were not negatively correlated to \emph{Awareness} and its
+dimensions. Similarly, \emph{Sati}, unlike the other \emph{Deficit}
+dimensions, was not positively correlated to \emph{Visceroception}. This
+complex structure suggests that the dimensions indeed capture distinct
+aspects of interoception, and that the metaclusters, rather than being
+simple aggregates of rather-redundant elements, might actually capture
+unique combinations (greater than the sum of their parts). It also
+provides evidence against a simplistic adaptive \emph{vs.} maladaptive
+dichotomy, as \emph{Deficit} was not negatively bit positively
+correlated with \emph{Visceroception}. Interestingly, while
+\emph{Awareness} was also positively correlated with
+\emph{Visceroception}, it yielded an insignificant negative correlation
+with \emph{Deficit} (this finding was also aligned with the hierarchical
+clustering results, showing a greater proximity between \emph{Deficit}
+and \emph{Visceroception} than with \emph{Awareness}), underlining again
+the complex web of relationships captured by the Mint.
+
+The correlation matrix between the Mint and the other interoception
+scales revealed high levels of overlap, as well as some unique
+contributions (see Figure~\ref{fig-four}). The BPQ was positively
+correlated with most Mint dimensions (the highest with
+\emph{Visceroception}, \(r = .46\)). The IAS was positively correlated
+with \emph{Visceroception} and \emph{Awareness} dimensions (the highest
+with \emph{Awareness}, \(r = .63\)), but negatively with most
+\emph{Deficit} dimensions (with the exception of \emph{Olfa} and
+\emph{Derm}). In turn, the \emph{Visceroception} metacluster most
+strongly correlated with MAIA's Noticing (\(r = .55\)). Interestingly,
+MAIA's TTrusting correlated selectively with \emph{Awareness}, and
+negatively with \emph{Deficit} dimensions, but not with
+\emph{Visceroceptive} dimensions (underlining its high-level
+metacognitive nature). MAIA's Emotional Awareness and Body Listening
+displayed a similar pattern to Noticing, and Attention Regulation and
+Self Regulation positively correlated with \emph{Awareness} and
+\emph{Visceroception} dimensions, but negatively with some
+\emph{Deficit} dimensions (\emph{CaCo} and \emph{UrIn}). Not-distracting
+only yielded mild negative associations with \emph{Sati} and
+\emph{Olfa}. Overall, the Mint dimensions were able to capture most of
+the (relevant) variance and intricacies present in the other
+interoception scales.
+
+Exploratory correlations with the emotion regulation (CERQ) dimensions
+revealed stronger associations with most of the MAIA dimensions
+(supporting its proximity with emotion regulation). Interestingly,
+Rumination (and Self-Blame) stood out as selectively related to the
+Mint's \emph{Visceroception} and \emph{Deficit} dimensions (note that
+Rumination was also related to the MAIA's interoceptive dimensions,
+namely Noticing, Emotional Awareness and Body Listening). The only
+primal world belief that correlated particularly with the Mint's
+\emph{Visceroception} and the MAIA's interoceptive dimension was the
+belief that the world was alive (\textbf{TODO: Ana maybe throw in a
+couple more words about what this belief means and is defined}).
+
 \begin{figure*}[!htbp]
 
-{\caption{{TODO.}{\label{fig-five}}}}
+{\caption{{Summary table of the comparison between interoception
+questionnaires (Mint, MAIA, BPQ and IAS). For various outcomes included
+the study, we tested the Mint and Non-Mint dimension that had the
+strongest link (as a unique predictor). Values in parenthesis represents
+correlation coefficient for continuous variables and log-odds ratios for
+binary variables (the occurrence of mental and somatic health
+conditions). We also compared the predictive performance of regression
+models including multiple predictors, and present their ranking based on
+raw predictive power (R2) and BIC, which favours more parsimonious
+models (with less predictors). Green background indicates an advantage
+for the Mint, while red backgrounds indicate an advantage for another
+interoception scale. Orange backgrounds indicate an advantage for the
+MAIA driven by its emotion-regulation dimensions (Trusting and
+Not-Worrying).}{\label{fig-five}}}}
+
+\begin{center}
+\includegraphics[width=0.82\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table2.png}
+\end{center}
+
+\end{figure*}
+
+Most of the target outcomes measured in the study to assess validity
+were best predicted by one of the Mint dimension (see
+Figure~\ref{fig-five}). This included Alexithymia (best predicted by
+\emph{Deficit}); ERS' Arousal (best predicted by \emph{Deficit});
+CEFSA's anomalous experiences of the body (best predicted by
+\emph{CaCo}), Self and Reality (best predicted by \emph{Deficit}); ADHD
+and Autism (best predicted by \emph{Deficit}), Somatic symptoms (best
+predicted by \emph{Deficit}); BMI (best predicted by \emph{Sati}). Most
+of the exceptions showed an advantage for MAIA dimensions, in particular
+Not-worrying (which best predicted ERS' Sensitivity and Persistence) and
+Trusting (which best predicted LS, Depression and Anxiety, CEFSA's
+Emotion and Connection, and self-reported physical activity).
+
+Model comparison included 4 variants of the Mint scale, the full
+\emph{Mint} (including all lower-level clusters - 33 items), the
+\emph{metaMint} (including only the 3 metaclusters based on all items),
+the \emph{miniMint} (including the 3 metaclusters computed from 2 of its
+most loading triplets - 18 items), and the \emph{microMint} (including
+only the most representative dimension of each metacluster - 9 items).
+This analysis confirmed the clear advantage for the Mint over the other
+interoception scales. The full \emph{Mint} model was typically the best
+model based on R2, and the \emph{metaMint} was the best model when
+parsimony was taken into account (i.e., based on BIC). Moreover, most of
+the instances were the \emph{MAIA} was the best model were explainable
+by the inclusion of Trusting, and the interoception-only version
+\emph{iMAIA} typically yielded worse performance than the Mint. In many
+instances, the \emph{miniMint} yielded reasonable performance, although
+the \emph{microMint} was typically less promising.
+
+The predictive performance for the mental health outcomes (see
+Figure~\ref{fig-six}) displayed a consistent pattern, with an advantage
+for the \emph{MAIA} for depression and anxiety which dropped below the
+\emph{Mint} versions for its \emph{iMAIA} variant. The \emph{Mint},
+however, displayed a clear advantage for the prediction of autism, ADHD,
+and all somatic groups of symptoms (with the exception of Central
+Sensitization, which was best predicted by the \emph{MAIA}).
+
+Finally, the importance of heart monitoring (for owners of such
+wearable) was best predicted by MAIA's Body listening (\(r = .36\)),
+followed the \emph{Card} dimension of the Mint (\(r = .31\)). The
+importance of sleep monitoring importance was best predicted by
+\emph{RelA} (\(r = .22\)), followed by MAIA's not worrying
+(\(r = -.219\)). Daily activity via steps monitoring was best predicted
+by MAIA's Noticing (\(r = .28\)), followed by \emph{Awareness}
+(\(r = .26\)).
+
+\begin{figure*}[!htbp]
+
+{\caption{{Predictive performance of interoception questionnaires for
+various self-reported mental health conditions (mood disorders with
+psychopharmacological treatment, ADHD and ASD) and somatic symptoms. The
+Receiver Operating Characteristic (ROC) curves are shown for the
+logistic regression models for various questionnaires and versions. A
+high Area Under the Curve (AUC) indicates a good discriminative power of
+the model (i.e., a strong combination of sensitivity and specificity).
+The Mint scale (in blue-green) consistently outperformed the other
+interoception scales, with the exception of the MAIA which, driven by
+its emotion-regulation dimensions (Trusting and Not-worrying), performed
+better for mood disorders and central sensitization symptoms. In several
+instances, the short versions of the Mint scale (miniMint and microMint)
+yielded reasonable performance, still outperforming other
+measures.}{\label{fig-six}}}}
 
@@
 
-\begin{figure*}[!htbp]
-
-{\caption{{TODO.}{\label{fig-six}}}}
-
-\begin{center}
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../study2/analysis/figures/table2.png}
-\end{center}
-
-\end{figure*}
-
 \subsection{Discussion}\label{discussion-1}
 
+\begin{itemize}
+\tightlist
+\item
+  Structure: Low stability of \emph{Olfa} as belonging in the deficit
+  group. More studies are needed to investigate its place and cluster
+  invariance: it is possible that its association might depend on other
+  factors or categories.
+\item
+  Main contender is MAIA. But its most sensitive dimensions seem to be
+  the least related to interoception, which is dangerous as it might
+  lead to findings with associations misattributed to ``Interoception''
+  (just because it correlate with some MAIA dimensions), but it might
+  have nothing to do with interoception per se and more with emotion
+  regulation.
+\item
+  Basically the pattern is clear: everything high-level, metacognitive
+  and highly subjective related to wellbeing and general affective state
+  is the most strongly related to the MAIA through some of its Emotion
+  regulation dimensions. All the other outcomes actually related to
+  interoceptive processes are most strongly predicted by the Mint.
+\end{itemize}
+
 \section{General Discussion}\label{general-discussion}
+
+\begin{itemize}
+\tightlist
+\item
+  Future directions: needs to test relationship with physiological
+  measures of interoception.
+\item
+  Also, the structure might still require a bit of deeper investigation,
+  in particular with some of its facets (\emph{Olfa} and \emph{Derm})
+  which might display different associations depending on the context or
+  the population.
+\end{itemize}
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-cabrera2018assessing}
+Cabrera, A., Kolacz, J., Pailhez, G., Bulbena-Cabre, A., Bulbena, A., \&
+Porges, S. W. (2018). Assessing body awareness and autonomic reactivity:
+Factor structure and psychometric properties of the body perception
+questionnaire-short form (BPQ-SF). \emph{International Journal of
+Methods in Psychiatric Research}, \emph{27}(2), e1596.
+
+\bibitem[\citeproctext]{ref-vcernis2024measuring}
+Černis, E., Loe, B. S., Lofthouse, K., Waite, P., Molodynski, A.,
+Ehlers, A., \& Freeman, D. (2024). Measuring dissociation across
+adolescence and adulthood: Developing the short-form {Č}ernis felt sense
+of anomaly scale ({Č}EFSA-14). \emph{Behavioural and Cognitive
+Psychotherapy}, \emph{52}(2), 163--177.
+
 \bibitem[\citeproctext]{ref-christensen2023unique}
@@
 
+\bibitem[\citeproctext]{ref-clifton2021brief}
+Clifton, J. D., \& Yaden, D. B. (2021). Brief measures of the four
+highest-order primal world beliefs. \emph{Psychological Assessment},
+\emph{33}(12), 1267.
+
 \bibitem[\citeproctext]{ref-de2015jspsych}
@@
 Methods}, \emph{47}, 1--12.
+
+\bibitem[\citeproctext]{ref-ferentzi2021examining}
+Ferentzi, E., Olaru, G., Geiger, M., Vig, L., Köteles, F., \& Wilhelm,
+O. (2021). Examining the factor structure and validity of the
+multidimensional assessment of interoceptive awareness. \emph{Journal of
+Personality Assessment}, \emph{103}(5), 675--684.
+
+\bibitem[\citeproctext]{ref-friedman2008sparse}
+Friedman, J., Hastie, T., \& Tibshirani, R. (2008). Sparse inverse
+covariance estimation with the graphical lasso. \emph{Biostatistics},
+\emph{9}(3), 432--441.
+
+\bibitem[\citeproctext]{ref-garnefski2006cognitive}
+Garnefski, N., \& Kraaij, V. (2006). Cognitive emotion regulation
+questionnaire--development of a short 18-item version (CERQ-short).
+\emph{Personality and Individual Differences}, \emph{41}(6), 1045--1053.
 
@@
 
+\bibitem[\citeproctext]{ref-jovanovic2020longer}
+Jovanović, V., \& Lazić, M. (2020). Is longer always better? A
+comparison of the validity of single-item versus multiple-item measures
+of life satisfaction. \emph{Applied Research in Quality of Life},
+\emph{15}, 675--692.
+
+\bibitem[\citeproctext]{ref-kroenke2009ultra}
+Kroenke, K., Spitzer, R. L., Williams, J. B., \& Löwe, B. (2009). An
+ultra-brief screening scale for anxiety and depression: The PHQ--4.
+\emph{Psychosomatics}, \emph{50}(6), 613--621.
+
+\bibitem[\citeproctext]{ref-leising2009toronto}
+Leising, D., Grande, T., \& Faber, R. (2009). The toronto alexithymia
+scale (TAS-20): A measure of general psychological distress.
+\emph{Journal of Research in Personality}, \emph{43}(4), 707--710.
+
+\bibitem[\citeproctext]{ref-makowski2025measuring}
+Makowski, D., Te, A., Neves, A., \& Chen, S. A. (2025). \emph{Measuring
+depression and anxiety with 4 items? Adaptation of the PHQ-4 to increase
+its sensitivity to subclinical variability}. PsyArXiv.
+\url{https://doi.org/10.31234/osf.io/436np_v2}
+
 \bibitem[\citeproctext]{ref-mayer2011exploratory}
@@
 \emph{10}(1).
+
+\bibitem[\citeproctext]{ref-mehling2018multidimensional}
+Mehling, W. E., Acree, M., Stewart, A., Silas, J., \& Jones, A. (2018).
+The multidimensional assessment of interoceptive awareness, version 2
+(MAIA-2). \emph{PloS One}, \emph{13}(12), e0208034.
+
+\bibitem[\citeproctext]{ref-murphy2020testing}
+Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., \& Bird,
+G. (2020). Testing the independence of self-reported interoceptive
+accuracy and attention. \emph{Quarterly Journal of Experimental
+Psychology}, \emph{73}(1), 115--133.
 
@@
 
+\bibitem[\citeproctext]{ref-traag2019louvain}
+Traag, V. A., Waltman, L., \& Van Eck, N. J. (2019). From louvain to
+leiden: Guaranteeing well-connected communities. \emph{Scientific
+Reports}, \emph{9}(1), 1--12.
+
+\bibitem[\citeproctext]{ref-veilleux2024development}
+Veilleux, J. C., Schreiber, R. E., Warner, E. A., \& Brott, K. H.
+(2024). Development and validation of a brief version of the emotion
+reactivity scale: The b-ERS. \emph{Current Psychology}, \emph{43}(14),
+12586--12600.
+
 \end{CSLReferences}

### 2025-07-02 study2/analysis/1_cleaning.qmd
update

@@
 dfchecks |>
-  mutate(Total = as.factor(paste0(Total, "/8"))) |> 
+  mutate(Total = as.factor(paste0(Total, "/7"))) |> 
   ggplot(aes(x = Total)) +
@@
 
-We removed `r length(outliers$attentionchecks)` (`r insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 8).
+We removed `r length(outliers$attentionchecks)` (`r insight::format_percent(length(outliers$attentionchecks) / nrow(df))`) participants for having failed at least 1 attention check (out of 7).
 

### 2025-07-02 study2/analysis/2_analysis.qmd
update

@@
     label = ifelse(label != "NA", label, NA),
-    x = x * 1.05,
-    y = y * 1.05,
+    x = x * 1.07,
+    y = y * 1.07,
     filter = label != "",
@@
 ggsave("figures/fig1a.png", p_stab, width=10, height=10*0.8, dpi=300)
-ggsave("figures/fig1b.png", p_hclust, width=12, height=8, dpi=300)
+ggsave("figures/fig1b.png", p_hclust, width=8, height=8*0.8, dpi=300)
 ```
@@
     # GLMs - display log-odds
-    r_mint <- best_pred_mint$Coefficient
-    r_nonmint <- best_pred_nonmint$Coefficient
+    r_mint <- insight::format_value(best_pred_mint$Coefficient)
+    r_nonmint <- insight::format_value(best_pred_nonmint$Coefficient)
   }
@@
   gt::tab_header(
-    title = gt::md("**Interoceptive Questionnaires Comparison**"),
+    title = gt::md("**Interoception Questionnaires Comparison**"),
     subtitle = "MINT vs. MAIA, IAS, BPQ"
@@
 
-gt::gtsave(tab2, "figures/table2.png", vwidth=1400, expand=0, quiet=TRUE)
+# gt::gtsave(tab2, "figures/table2.png", vwidth=1400, expand=0, quiet=TRUE)
+# gt::gtsave(tab2, "figures/table2b.png", vwidth=1600, expand=0, quiet=TRUE)
+
+tab2 |> 
+  gt::cols_width(
+    Outcome ~ gt::pct(21),
+    Best_MINT_Predictor ~ gt::pct(17),
+    Best_NonMINT_Predictor ~ gt::pct(18),
+    Best_Models_R2 ~ gt::pct(22),
+    Best_Models_BIC ~ gt::pct(22)
+  ) |> 
+  gt::gtsave("figures/table2.png", vwidth=1700, expand=0, quiet=TRUE)
 ```
@@
   patchwork::plot_annotation(title = "Exploratory Graphical Analysis (EGA)",
-                             subtitle = "Bootstrapped replication of hierarchical clusters (Methhod = leiden)",
+                             subtitle = "Bootstrapped replication of clusters (Method = Leiden)",
                              theme = theme(plot.title = element_text(face="bold", hjust = 0, size = rel(1.4)),

### 2025-07-02 paper/manuscript.qmd
line number

@@
 keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, Mint Validation, Body Awareness"
-numbered-lines: false
+numbered-lines: true
 floatsintext: true

### 2025-07-02 paper/manuscript.tex
line number

@@
 
+\usepackage[nolongtablepatch]{lineno}
+\linenumbers
+
 \usepackage{newtx}
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colframe=quarto-callout-note-color-frame, colback=white, opacityback=0, left=2mm, arc=.35mm, leftrule=.75mm, breakable, bottomrule=.15mm, rightrule=.15mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, toprule=.15mm, opacityback=0, breakable, colback=white, arc=.35mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm]
 
@@
 
+\resetlinenumber[1]
+
 \section{Introduction}\label{introduction}

### 2025-07-02 paper/manuscript.qmd
add dim names

@@
 The table shows each item of the Mint with its cluster centrality, which is the EGA equivalent (in terms of interpretation) of factor loadings.
-It also shows how each lower-level cluster is related to higher-order metaclusters."
+It also shows how each lower-level cluster is related to higher-order metaclusters.
+The lower-level clusters are Expulsion Accuracy (ExAc), Relaxation Awareness (RelA), Sexual Arousal Sensitivity (SexS), Cardiorespiratory Confusion (CaCo), Urointestinal Inaccuracy (UrIn), Dermal Hypersensitivity (Derm), Satiety Noticing (Sati), Olfactory Compensation (Olfa), Respiroception (Resp), Cardioception (Card),  Gastroception (Gast)."
 #| fig-align: "center"

### 2025-07-02 paper/manuscript.tex
add dim names

@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, toprule=.15mm, opacityback=0, breakable, colback=white, arc=.35mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, breakable, colback=white, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, leftrule=.75mm, opacityback=0]
 
@@
 interpretation) of factor loadings. It also shows how each lower-level
-cluster is related to higher-order metaclusters.}{\label{fig-three}}}}
+cluster is related to higher-order metaclusters. The lower-level
+clusters are Expulsion Accuracy (ExAc), Relaxation Awareness (RelA),
+Sexual Arousal Sensitivity (SexS), Cardiorespiratory Confusion (CaCo),
+Urointestinal Inaccuracy (UrIn), Dermal Hypersensitivity (Derm), Satiety
+Noticing (Sati), Olfactory Compensation (Olfa), Respiroception (Resp),
+Cardioception (Card), Gastroception (Gast).}{\label{fig-three}}}}
 

### 2025-07-04 paper/manuscript.qmd
minor

@@
 Stars indicate dimensions that have been score-reversed for better in-context interpretation.
-Correlation coefficients are shown for significant correlations."
+Correlation coefficients are shown only for significant correlations (p < .001)."
 #| fig-align: "center"

### 2025-07-04 paper/manuscript.tex
minor

@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, breakable, colback=white, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, leftrule=.75mm, opacityback=0]
+\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, rightrule=.15mm, colback=white, breakable, opacityback=0, colframe=quarto-callout-note-color-frame, toprule=.15mm]
 
@@
 score-reversed for better in-context interpretation. Correlation
-coefficients are shown for significant
-correlations.}{\label{fig-four}}}}
+coefficients are shown only for significant correlations (p \textless{}
+.001).}{\label{fig-four}}}}
 

### 2025-07-04 study2/analysis/2_analysis.qmd
minor

@@
 
-make_cor <- function(df1, df2=NULL, qname_x=TRUE, qname_y=TRUE, textsize = 2.9, xcol = "#424242", ycol="#424242") {
+make_cor <- function(df1, df2=NULL, qname_x=TRUE, qname_y=TRUE, textsize = 3, xcol = "#424242", ycol="#424242") {
 
@@
     correlation::cor_sort() |>
-    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
+    mutate(label = ifelse(p < .001, paste0(insight::format_value(r, lead_zero = FALSE, zap_small = TRUE)), ""),
            Parameter1 = cleanlabels(Parameter1, qname=qname_x),
@@
 
-p_cormint <- make_cor(cbind(mint, metamint), qname_x = FALSE, qname_y = FALSE, textsize = 2.5,
+p_cormint <- make_cor(cbind(mint, metamint), qname_x = FALSE, qname_y = FALSE, textsize = 2.8,
                       xcol = "#00838F", ycol = "#00838F") +
@@
 p_corintero <- make_cor(select(df, starts_with("MAIA"), IAS, BPQ),
-                        cbind(mint, metamint), qname_y = FALSE, textsize = 2.5,
+                        cbind(mint, metamint), qname_y = FALSE, textsize = 2.8,
                         ycol = "#00838F") +
@@
 #| warning: false
-#| eval: false
+#| eval: true
 

### 2025-08-12 paper/manuscript.qmd
push

@@
 #   **Significance Statement**. TODO.
-keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, Mint Validation, Body Awareness"
-numbered-lines: true
+keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, Mint Validation, Body Awareness, Health"
+numbered-lines: false
 floatsintext: true
@@
 
-Main issues in existing questionnaires:
+Interoception - the sensing and interpretation of the body's internal physiological signals - plays a fundamental role in processes ranging from homeostatic regulation to emotion, decision-making, and mental health [@craig2002how; @critchley2017interoception].
+Despite its growing recognition, the field is hindered by inconsistent definitions and fragmented measurement approaches [@khalsa2018interoception; @desmedt2025discrepancies; @desmedt2022measures].
+Available tools include "objective" physiological tasks (e.g., heartbeat counting or tracking) and "subjective" self-reports, and encompass both "explicit" paradigms that direct participants' attention and consciousness to internal sensations and "implicit" paradigms that do not (e.g., heartbeat evoked potentials recorded during rest).
+These assessments are often targeted at only one of several interoceptive modalities (e.g., cardioception, respiroception, gastroception), and are mapped onto theoretical dimensions [e.g., accuracy, sensitivity, awareness, @garfinkel2015knowing] within a rapidly evolving theoretical scaffolding.
+However, no consensus exists on a gold-standard measure, and each approach has distinct limitations: physiological tasks often require specialised equipment and expertise, are time-consuming, and are challenging to administer at scale, whereas questionnaires are constrained by their inherent subjectivity.
+Crucially, the psychometric quality of many of these measures is questionable [e.g., see criticism about the heartbeat counting task, @zamariola2018interoceptive], yielding low inter-task correlations [@murphy2018classifying], raising serious concerns about their reliability and validity (e.g., measures presented as measuring one theoretical dimension but likely measuring something else).
+This measurement conundrum hinders progress in comparing, replicating, and interpreting interoception-related findings, underscoring the need to develop improved tools that align with modern psychometric standards.
 
-- Either heavily based on theories (e.g., focusing on specific "alleged" dimensions), despite shaky evidence for said-theories
-- Do not control for context (which leads to variability in interpretation and occurence)
-- Often quite narrow in the modalities covered (or scattered, like the IAS)
+<!-- There are many questionnaire measures – 14 of which are commonly used and 5 (BPQ, MAIA, BAQ, SAQ, and PBCS) which cover 86.5% of all citations of interoceptive sensibility questionnaires – Desmedt et al., 2022 -->
+The present work focuses on self-report questionnaires, which offer a scalable and accessible tool complementing physiological tasks.
+Among the numerous questionnaires available, a handful seem to dominate the literature [@desmedt2022measures], including the Body Perception Questionnaire [BPQ, @kolacz2018body], the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2018multidimensional], and the Interoceptive Accuracy Scale [IAS, @murphy2018classifying].
+These tools were developed in different eras of a rapidly evolving field, each with its own objectives and philosophies.
+The BPQ, one of the earliest measures, emphasizes the assessment of body awareness and autonomic nervous system (ANS) reactivity, focusing on subjective experiences of physiological stress reactions in organs innervated by the ANS, such as those triggered by stress or trauma [@porges1993body].
+The MAIA incorporated ideas from the then-booming emotion regulation and mindfulness fields, including subscales assessing adaptive coping strategies and metacognitive insights about the body.
+By contrast, the IAS was recently crafted to sidestep such high-level - possibly tangential - constructs and instead capture subjective reports of concrete bodily events (e.g., coughing, sneezing) as proxies for interoceptive accuracy.
+
+These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measurand differences, which in turn hinders replication and theoretical integration.
+Recent work has been focused on aligning subjective measures and facets with theoretical models, debating whether they measure interoceptive "sensitivity" or other dimensions (accuracy, attention, deficits).
+However, this focus on a theory-driven approach might be premature when theoretical models are in flux, and when a topographic mapping to self-report dimensions is not guaranteed (e.g.
+distinctions that are relevant at a neuroanatomical or cognitive level might not necessarily translate into the same structural landscape of subjective experiences).
+More fundamentally, existing questionnaires suffer from two major structural blind spots.
+First, they are often narrow or unsystematic in their coverage of bodily *modalities*, with a heavy bias towards cardio-respiratory sensations and a neglect of others like gastric, urogenital, or thermoregulatory signals.
+Second, and perhaps most critically, they fail to control for the *context* in which an interoceptive experience occurs, introducing significant variability in how participants interpret and respond to items.
+For example, an item about "feeling your heart beat" is ambiguous; its frequency, experience and its interpretation differ vastly depending on whether it occurs during physical exercise, a moment of anxiety, or quiet rest (e.g., someone who exercises regularly, or is anxious, might more easily recall an instance of occurrence of feeling their heart beating and respond based on that contextual saliency).
+
+To address these gaps, we introduce the Multimodal Interoception Questionnaire (Mint).
+The overarching aim of this work is to develop and validate a new questionnaire that systematically addresses these limitations.
+In Study 1, we detail the bottom-up development of the Mint, using a "modality-by-context" framework to generate a comprehensive item pool, which is then refined using cutting-edge psychometric network analysis.
+In Study 2, we validate the final version of the Mint against the established interoception questionnaires, demonstrating its robust structure and predictive validity for a range of clinically-relevant outcomes.
 
@@
 
-TODO: write intro.
+The primary goal of Study 1 was to develop a new interoception questionnaire by generating a comprehensive item pool and refining it into a psychometrically robust scale.
+To overcome the limitations of existing measures, we adopted a bottom-up, theoretically agnostic approach.
+Instead of imposing a pre-defined theoretical structure, we focused on two tangible and systematically controllable aspects of interoceptive experience: the *modality* of the sensation and the *context* in which it occurs.
+The objective was not to create *yet another scale* measuring an alleged distinct construct or variation, but rather to synthesize existing ideas and frameworks into a comprehensive and modern tool that captures the richness of interoceptive experiences and encompasses the most relevant facets of interoception.
 
-- Goal of study 1: to generate a lot of items, analyze its structure and reduce them to a balanced set of items.
+<!-- Give examples of items for each part of the framework here so that the method makes more sense? -->
+Our item generation process was guided by a "modality-by-context" grid designed to overcome the limitations of existing scales.
+For *modalities*, we expanded beyond the typical cardio-respiratory focus to include a broader range of bodily systems: cardiac, respiratory, gastric, genital, bladder & colon, and skin & temperature [the latter of which being increasingly recognized as a key interoceptive channel, @crucianelli2023role].
+We also included a "general state" category to capture the integrated sense of the body's overall physiological condition [@craig2002how; @craig2003interoception].
+For *contexts*, we designed facets to capture specific situational contexts like negative (anxious) and positive (sexual) arousal, which reflect distinct bodily states with differing interoceptive signatures, as well as other experiential qualities tapping into elaboration and threshold of perception, such as sensitivity, accuracy, and confusion.
+To maintain continuity with established work while making targeted improvements, we purposefully adapted items from existing questionnaires (e.g., IAS-like items related to observable behaviors).
+This systematic framework yielded a diverse pool of 120 initial items, ensuring comprehensive coverage while minimizing the ambiguity inherent in context-free questions.
+
+The final step involved a data-driven reduction of this item pool.
+We employed cutting-edge psychometric network-based techniques to identify and remove redundant items and to uncover the most stable and coherent dimensional structure.
+Additionally, we designed the study so that we could explore an often overlooked psychometric quality: the invariance of the structure to the presentation format (how items are grouped together on the screen, whether by modality, facet, or randomly) influences the resulting psychometric structure.
+This rigorous, multi-stage process was designed to produce a subset of items with a clear, stable, and theoretically rich hierarchical structure, ready for formal validation.
 
@@
 
-After removing redundant items using UVA, we iteratively fitted hierarchical EGA models (which additionally estimates higher-order "meta" clusters) using "glasso" [@friedman2008sparse] and the "Leiden" algorithm [@traag2019louvain] for community detection, refining the item pool at each step.
+After removing redundant items using UVA, we iteratively fitted hierarchical EGA models (which additionally estimate higher-order "meta" clusters) using "glasso" [@friedman2008sparse] and the "Leiden" algorithm [@traag2019louvain] for community detection, refining the item pool at each step.
 We started by removing items with a low (< 80%) cluster stability (i.e., volatile items which jump between clusters across bootstrapped samples), followed by odd items belonging to no clusters or pairs of items (i.e., we keep items belonging to clusters of more than 2 items).
@@
 
-- Possible (although not at all significant) bias consistent across indices in favour of a greater similarity with the modality-grouping condition.
-Futher research with more data (here we only had ~200 observation per condition) might be able to yield more conclusive results.
-In general, testing the presentation mode is a novel approach which should be more widely applied to psychometric validations.
-- We grouped some of the dimensions under "Awareness", despite being similar to items included in the IAS typically conceptualized as "Accuracy".
-However, we believe that subjective scales cannot be pure measures of accuracy, as they are inherently subjective and thus reflect a degree of awareness (of one's accurate noticing or sensation).
-- Olfactory compensation: pseudo-interoceptive pathway whereby people with interoceptive deficits would compensate by gathering evidence about their internal state externally (e.g., via smell).
-- The metacluster "Sensitivity" seems to be grouping iterms related to visceropcetion and (hyper)sensitivity (Derm).
+<!-- summary -->
+The primary aim of Study 1 was to develop and refine a large, systematically generated pool of interoceptive items into a psychometrically sound and structurally coherent questionnaire.
+Starting with 120 items derived from a modality-by-context grid, we employed a multi-step, data-driven reduction process using cutting-edge structure analysis methods.
+This rigorous procedure yielded a final, balanced set of 45 items, organized within a stable hierarchical structure comprising three higher-order dimensions (Interoceptive Deficits, Interoceptive Awareness, Interoceptive Sensitivity) and 12 distinct lower-level facets.
+
+<!-- Effect of item presentation -->
+One innovation of this study was to test the effect of item presentation by comparing structures across different grouping conditions.
+While the analysis revealed no significant effect, a consistent (though non-significant) trend suggested that grouping items by modality may be slightly more conducive to revealing the underlying psychometric structure than grouping by facet or randomly.
+This finding, while preliminary due to the sample size per condition ($N \pm 200$), highlights a potentially important and under-investigated aspect of questionnaire design that warrants future research.
+<!-- The final reduction from 54 to 45 items was a consensus-based decision to remove three clusters for reasons of conceptual clarity and parsimony, a necessary step to ensure the final scale's usability and content validity.
+-->
+
+The resulting hierarchical structure offers novel yet interpretable insights into self-reported interoception, with flexible degrees of granularity.
+Notably, we categorised several facets (typically related to objective external behaviours, like coughing or sneezing) under the label "Awareness", that might traditionally be named "Accuracy" in other scales.
+Our rationale is that subjective self-report, by its very nature, cannot be a pure measure of objective accuracy, but at best a proxy of an individual's subjective certainty or awareness of their interoceptive processes.
+Furthermore, our bottom-up approach revealed intriguing facets, such as "Olfactory Compensation".
+This finding provide further evidence for a pseudo-interoceptive pathway, whereby individuals with potentially poorer access to internal signals may compensate by relying on external cues (e.g., odours) to infer their bodily state.
+The "Sensitivity" metacluster also grouped core visceroceptive facets (e.g., "Cardioception", "Gastroception") with "Dermal Hypersensitivity", pointing to a potential common dimension of heightened perceptual sensitivity to bodily sensations.
+
+In summary, Study 1 successfully leveraged a systematic item generation process and modern analytical techniques to produce a 45-item questionnaire with a clear, stable, and theoretically rich hierarchical structure.
+The next crucial step is to formally validate this new instrument by examining its psychometric properties and its relationship with existing measures in a new, independent sample, which is the objective of Study 2.
 
@@
 
-- Goal of study 2: to validate the Mint scale against other interoception scales.
+Following the generation and selection of a set of 45 interoceptive items, the next objective is to formally validate this new instrument in a large, independent sample, a crucial step for establishing the psychometric soundness and unique contribution of the Mint scale to the field of interoception research.
+To this end, we sought to 1) re-assess the structure of the shorter version and 2) establish its convergent validity by examining the correlations with other established and popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS), as well as other related measures (e.g., alexithymia).
+Finally, we assessed its criterion validity by directly comparing the predictive power of the interoceptive scales across a broad range of outcomes, including emotional, cognitive, and clinical variables.
 
@@
 The *Autonomic Dysfunction* cluster captured disorders linked to dysregulation of the autonomic and cardiopulmonary systems, including joint hypermobility, cardiac arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep apnea, chronic obstructive pulmonary disease (COPD), and chronic bronchitis.
-Finally, the *Immune-Inflammatory* cluster encompassed conditions associated with immune dysregulation, barrier dysfunction, and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes, asthma, celiac disease, gluten and lactose sensitivity, inflammatory bowel diseases (Crohn’s disease and ulcerative colitis), gastroesophageal reflux disease (GERD), multiple sclerosis, and Sjögren’s syndrome.
+Finally, the *Immune-Inflammatory* cluster encompassed conditions associated with immune dysregulation, barrier dysfunction, and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes, asthma, celiac disease, gluten and lactose sensitivity, inflammatory bowel diseases (Crohn's disease and ulcerative colitis), gastroesophageal reflux disease (GERD), multiple sclerosis, and Sjögren's syndrome.
 <!-- Each symptom was assigned to a single cluster to preserve orthogonality and support subsequent analyses linking symptom profiles to interoceptive processes. -->
@@
 
-- Structure: Low stability of *Olfa* as belonging in the deficit group.
-More studies are needed to investigate its place and cluster invariance: it is possible that its association might depend on other factors or categories.
-- Main contender is MAIA.
-But its most sensitive dimensions seem to be the least related to interoception, which is dangerous as it might lead to findings with associations misattributed to "Interoception" (just because it correlate with some MAIA dimensions), but it might have nothing to do with interoception per se and more with emotion regulation.
-- Basically the pattern is clear: everything high-level, metacognitive and highly subjective related to wellbeing and general affective state is the most strongly related to the MAIA through some of its Emotion regulation dimensions.
-All the other outcomes actually related to interoceptive processes are most strongly predicted by the Mint.
+The primary goal of Study 2 was to validate the items selected in Study 1.
+This involved re-assessing its structure in a new, large sample, and establishing its convergent and criterion validity against other established interoception questionnaires.
+The analysis led to a final, refined 33-item Mint scale with a stable and theoretically coherent hierarchical structure, which demonstrated substantial predictive power across a range of outcomes.
+
+Re-validating the structure after item selection is a crucial step in questionnaire development.
+When a large item pool is reduced, the context changes, which can alter the perceived meaning and relationships between the remaining items.
+For instance, a questionnaire with many items suggesting abnormality or pathology might colour other neutral items with a negative connotation.
+While the original structure was mostly replicated, the re-validation allowed for a clarification of some of the higher-order dimensions (for instance, the "Sensitivity" metacluster became more clearly defined around core interoceptive clusters).
+The final structure, comprising 11 facets and 3 metaclusters, showed excellent structural consistency and stability, providing a solid foundation for the scale.
+However, the *Olfa* (Olfactory Compensation) cluster showed lower stability in its placement within the *Deficit* metacluster.
+This suggests its role may be more complex, and future studies are needed to investigate its place and invariance across different populations and contexts.
+
+The criterion validity analysis revealed a clear and compelling pattern of results.
+The Mint scale, particularly its *Deficit* metacluster, consistently outperformed other scales in predicting outcomes directly related to alterations in bodily experience and self-regulation, such as alexithymia, dissociative experiences, ADHD, autism, and various somatic symptoms.
+The main contender, the MAIA-2, showed an advantage primarily for outcomes related to general well-being, such as life satisfaction, depression, and anxiety.
+However, this advantage was almost entirely driven by dimensions highly related to emotion regulation abilities, namely *Trusting* and *Not-Worrying*, whose inclusion as core interoceptive facets has been questioned [@ferentzi2021examining].
+When these dimensions were removed (in the *iMAIA* version), the MAIA-2's predictive power for these outcomes dropped considerably, often below that of the Mint.
+
+This highlights a crucial issue in the field: the potential for misattributing findings to "interoception" when they may be driven by broader emotion regulation capacities [@murphy2020testing].
+While valuable, the MAIA-2's most predictive subscales appear less related to core interoceptive processing and more to metacognitive beliefs about one's body and emotional coping.
+The Mint, in contrast, appears to tap more directly into distinct facets of interoceptive experience, from visceral sensitivity to perceived deficits.
+The pattern is clear: for high-level, metacognitive aspects of affective state and well-being, the MAIA-2's emotion regulation facets are highly relevant.
+For outcomes tied more specifically to bodily processes, clinical conditions characterized by sensory dysregulation, and nuanced interoceptive experiences, the Mint offers superior predictive validity and specificity.
 
@@
 
-- Future directions: needs to test relationship with physiological measures of interoception.
-- Also, the structure might still require a bit of deeper investigation, in particular with some of its facets (*Olfa* and *Derm*) which might display different associations depending on the context or the population.
+Across two studies, we developed and validated the Multimodal Interoception Questionnaire (Mint), a new 33-item self-report measure of interoception.
+Our approach addressed key limitations of existing scales by starting with a systematically generated, broad item pool that explicitly controlled for context and modality, and then using a data-driven reduction process.
+The result is a psychometrically robust instrument with a stable, hierarchical structure comprising three higher-order metaclusters, namely *Interoceptive Deficit*, *Interoceptive Awareness*, and *Visceroception*, and 11 distinct lower-level facets.
+The validation study demonstrated that the Mint not only captures variance present in other popular scales (MAIA-2, BPQ and IAS) but also offers superior predictive power for a range of clinical and cognitive outcomes, particularly those tied to altered bodily perception.
+
+A key contribution of the Mint is its potential ability to disentangle core interoceptive experiences from more general emotion regulation capacities.
+Our findings show that while the MAIA-2 is a potent predictor of general well-being, this is largely driven by its *Trusting* and *Not-Worrying* subscales, which heavily tap into emotion regulation skills and coping strategies.
+The Mint, conversely, excelled at predicting conditions like alexithymia, ADHD, autism, and somatic symptoms, where alterations in bodily sensing are a core feature.
+This suggests the Mint provides a more specific measure of interoceptive processing, offering researchers a finer-grained tool to probe the role of bodily awareness in health and disease.
+
+Despite these strengths, the present work has limitations that open avenues for future research.
+First, as a self-report measure, the Mint captures subjective beliefs about interoceptive abilities, not objective accuracy.
+A crucial next step is to investigate the relationship between Mint scores and physiological or behavioural measures of interoception (e.g., heartbeat tracking tasks, heartbeat evoked potentials).
+This would help establish the extent to which subjective reports on the Mint correspond to objective interoceptive performance.
+Future research could also systematically examine the cost of shorter versions, by investigating the tradeoffs incurred by versions with only the one or two most central facets per metacluster and their impact on psychometric qualities and predictive power.
+
+While the overall structure of the Mint is stable, some facets warrant deeper investigation.
+The *Olfa* (Olfactory Compensation) and *Derm* (Dermal Hypersensitivity) clusters, for instance, showed more complex patterns of association.
+Their placement within the *Deficit* metacluster is theoretically intriguing but requires further validation.
+The former aligns with predictive coding models suggesting that individuals may rely on exteroceptive cues (like odours) to infer internal states  [@paulus2010interoception], a form of pseudo-interoception (or extero-interoception).
+The latter points to a potential link between visceral and cutaneous sensitivity, possibly reflecting a general trait of heightened bodily awareness or a shared mechanism of central sensitization, which has been observed in conditions like chronic pain [@di2016alexithymia].
+Future studies should examine the invariance of the Mint's structure across different populations (e.g., clinical vs.
+non-clinical groups) and contexts (e.g., heightened arousal vs.
+rest) to clarify the role of these more nuanced facets.
+Such work could reveal whether their relevance and pattern of associations differs in conditions like anxiety disorders, chronic pain, or neurodevelopmental disorders.
+
+In conclusion, the Mint scale represents a significant methodological advancement for the field of interoception research.
+By providing a validated, structurally coherent, and nuanced tool, it allows for a more precise assessment of self-reported interoceptive experiences.
+Its various forms (full, meta, mini, and micro) offer flexibility for researchers and clinicians, paving the way for a deeper understanding of the multifaceted role of interoception in human psychology and pathophysiology.
 
@@
 We would like to thank the dissertation students from the University of Sussex for their help in data collection.
-DM would also like to thank ... for the motivation provided to write this paper.
+DM would also like to thank Anastasia for the motivation provided to write this paper.
 

### 2025-08-12 paper/manuscript.tex
push

@@
 
-\usepackage[nolongtablepatch]{lineno}
-\linenumbers
-
 \usepackage{newtx}
@@
 \keywords{Interoception questionnaire, interoceptive accuracy scale,
-MAIA, Mint Validation, Body Awareness}
+MAIA, Mint Validation, Body Awareness, Health}
 
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, rightrule=.15mm, colback=white, breakable, opacityback=0, colframe=quarto-callout-note-color-frame, toprule=.15mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, arc=.35mm, left=2mm, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0, colback=white]
 
@@
 \href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
-\begin{center}
 \includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
-\end{center}
 
@@
 
-\resetlinenumber[1]
-
 \section{Introduction}\label{introduction}
 
-Main issues in existing questionnaires:
-
-\begin{itemize}
-\tightlist
-\item
-  Either heavily based on theories (e.g., focusing on specific
-  ``alleged'' dimensions), despite shaky evidence for said-theories
-\item
-  Do not control for context (which leads to variability in
-  interpretation and occurence)
-\item
-  Often quite narrow in the modalities covered (or scattered, like the
-  IAS)
-\end{itemize}
+Interoception - the sensing and interpretation of the body's internal
+physiological signals - plays a fundamental role in processes ranging
+from homeostatic regulation to emotion, decision-making, and mental
+health (\citeproc{ref-craig2002how}{Craig, 2002};
+\citeproc{ref-critchley2017interoception}{Critchley \& Garfinkel,
+2017}). Despite its growing recognition, the field is hindered by
+inconsistent definitions and fragmented measurement approaches
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022},
+\citeproc{ref-desmedt2025discrepancies}{2025};
+\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018}). Available
+tools include ``objective'' physiological tasks (e.g., heartbeat
+counting or tracking) and ``subjective'' self-reports, and encompass
+both ``explicit'' paradigms that direct participants' attention and
+consciousness to internal sensations and ``implicit'' paradigms that do
+not (e.g., heartbeat evoked potentials recorded during rest). These
+assessments are often targeted at only one of several interoceptive
+modalities (e.g., cardioception, respiroception, gastroception), and are
+mapped onto theoretical dimensions (e.g., accuracy, sensitivity,
+awareness, \citeproc{ref-garfinkel2015knowing}{Garfinkel et al., 2015})
+within a rapidly evolving theoretical scaffolding. However, no consensus
+exists on a gold-standard measure, and each approach has distinct
+limitations: physiological tasks often require specialised equipment and
+expertise, are time-consuming, and are challenging to administer at
+scale, whereas questionnaires are constrained by their inherent
+subjectivity. Crucially, the psychometric quality of many of these
+measures is questionable (e.g., see criticism about the heartbeat
+counting task, \citeproc{ref-zamariola2018interoceptive}{Zamariola et
+al., 2018}), yielding low inter-task correlations
+(\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}), raising
+serious concerns about their reliability and validity (e.g., measures
+presented as measuring one theoretical dimension but likely measuring
+something else). This measurement conundrum hinders progress in
+comparing, replicating, and interpreting interoception-related findings,
+underscoring the need to develop improved tools that align with modern
+psychometric standards.
+
+The present work focuses on self-report questionnaires, which offer a
+scalable and accessible tool complementing physiological tasks. Among
+the numerous questionnaires available, a handful seem to dominate the
+literature (\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}),
+including the Body Perception Questionnaire (BPQ,
+\citeproc{ref-kolacz2018body}{Kolacz et al., 2018}), the
+Multidimensional Assessment of Interoceptive Awareness (MAIA,
+\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), and
+the Interoceptive Accuracy Scale (IAS,
+\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}). These tools
+were developed in different eras of a rapidly evolving field, each with
+its own objectives and philosophies. The BPQ, one of the earliest
+measures, emphasizes the assessment of body awareness and autonomic
+nervous system (ANS) reactivity, focusing on subjective experiences of
+physiological stress reactions in organs innervated by the ANS, such as
+those triggered by stress or trauma
+(\citeproc{ref-porges1993body}{\textbf{porges1993body?}}). The MAIA
+incorporated ideas from the then-booming emotion regulation and
+mindfulness fields, including subscales assessing adaptive coping
+strategies and metacognitive insights about the body. By contrast, the
+IAS was recently crafted to sidestep such high-level - possibly
+tangential - constructs and instead capture subjective reports of
+concrete bodily events (e.g., coughing, sneezing) as proxies for
+interoceptive accuracy.
+
+These differing philosophies have practical consequences, leading to
+poor convergence between scales that are assumed to measure the same
+construct (\citeproc{ref-vig2022questionnaires}{Vig et al., 2022}) - a
+classic example of the ``jingle fallacy'' where the shared label of
+``interoception'' can mask underlying measurand differences, which in
+turn hinders replication and theoretical integration. Recent work has
+been focused on aligning subjective measures and facets with theoretical
+models, debating whether they measure interoceptive ``sensitivity'' or
+other dimensions (accuracy, attention, deficits). However, this focus on
+a theory-driven approach might be premature when theoretical models are
+in flux, and when a topographic mapping to self-report dimensions is not
+guaranteed (e.g.~distinctions that are relevant at a neuroanatomical or
+cognitive level might not necessarily translate into the same structural
+landscape of subjective experiences). More fundamentally, existing
+questionnaires suffer from two major structural blind spots. First, they
+are often narrow or unsystematic in their coverage of bodily
+\emph{modalities}, with a heavy bias towards cardio-respiratory
+sensations and a neglect of others like gastric, urogenital, or
+thermoregulatory signals. Second, and perhaps most critically, they fail
+to control for the \emph{context} in which an interoceptive experience
+occurs, introducing significant variability in how participants
+interpret and respond to items. For example, an item about ``feeling
+your heart beat'' is ambiguous; its frequency, experience and its
+interpretation differ vastly depending on whether it occurs during
+physical exercise, a moment of anxiety, or quiet rest (e.g., someone who
+exercises regularly, or is anxious, might more easily recall an instance
+of occurrence of feeling their heart beating and respond based on that
+contextual saliency).
+
+To address these gaps, we introduce the Multimodal Interoception
+Questionnaire (Mint). The overarching aim of this work is to develop and
+validate a new questionnaire that systematically addresses these
+limitations. In Study 1, we detail the bottom-up development of the
+Mint, using a ``modality-by-context'' framework to generate a
+comprehensive item pool, which is then refined using cutting-edge
+psychometric network analysis. In Study 2, we validate the final version
+of the Mint against the established interoception questionnaires,
+demonstrating its robust structure and predictive validity for a range
+of clinically-relevant outcomes.
 
@@
 
-TODO: write intro.
-
-\begin{itemize}
-\tightlist
-\item
-  Goal of study 1: to generate a lot of items, analyze its structure and
-  reduce them to a balanced set of items.
-\end{itemize}
+The primary goal of Study 1 was to develop a new interoception
+questionnaire by generating a comprehensive item pool and refining it
+into a psychometrically robust scale. To overcome the limitations of
+existing measures, we adopted a bottom-up, theoretically agnostic
+approach. Instead of imposing a pre-defined theoretical structure, we
+focused on two tangible and systematically controllable aspects of
+interoceptive experience: the \emph{modality} of the sensation and the
+\emph{context} in which it occurs. The objective was not to create
+\emph{yet another scale} measuring an alleged distinct construct or
+variation, but rather to synthesize existing ideas and frameworks into a
+comprehensive and modern tool that captures the richness of
+interoceptive experiences and encompasses the most relevant facets of
+interoception.
+
+Our item generation process was guided by a ``modality-by-context'' grid
+designed to overcome the limitations of existing scales. For
+\emph{modalities}, we expanded beyond the typical cardio-respiratory
+focus to include a broader range of bodily systems: cardiac,
+respiratory, gastric, genital, bladder \& colon, and skin \& temperature
+(the latter of which being increasingly recognized as a key
+interoceptive channel, \citeproc{ref-crucianelli2023role}{Crucianelli \&
+Ehrsson, 2023}). We also included a ``general state'' category to
+capture the integrated sense of the body's overall physiological
+condition (\citeproc{ref-craig2002how}{Craig, 2002};
+\citeproc{ref-craig2003interoception}{Craig, 2003}). For
+\emph{contexts}, we designed facets to capture specific situational
+contexts like negative (anxious) and positive (sexual) arousal, which
+reflect distinct bodily states with differing interoceptive signatures,
+as well as other experiential qualities tapping into elaboration and
+threshold of perception, such as sensitivity, accuracy, and confusion.
+To maintain continuity with established work while making targeted
+improvements, we purposefully adapted items from existing questionnaires
+(e.g., IAS-like items related to observable behaviors). This systematic
+framework yielded a diverse pool of 120 initial items, ensuring
+comprehensive coverage while minimizing the ambiguity inherent in
+context-free questions.
+
+The final step involved a data-driven reduction of this item pool. We
+employed cutting-edge psychometric network-based techniques to identify
+and remove redundant items and to uncover the most stable and coherent
+dimensional structure. Additionally, we designed the study so that we
+could explore an often overlooked psychometric quality: the invariance
+of the structure to the presentation format (how items are grouped
+together on the screen, whether by modality, facet, or randomly)
+influences the resulting psychometric structure. This rigorous,
+multi-stage process was designed to produce a subset of items with a
+clear, stable, and theoretically rich hierarchical structure, ready for
+formal validation.
 
@@
 After removing redundant items using UVA, we iteratively fitted
-hierarchical EGA models (which additionally estimates higher-order
+hierarchical EGA models (which additionally estimate higher-order
 ``meta'' clusters) using ``glasso''
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Possible (although not at all significant) bias consistent across
-  indices in favour of a greater similarity with the modality-grouping
-  condition. Futher research with more data (here we only had
-  \textasciitilde200 observation per condition) might be able to yield
-  more conclusive results. In general, testing the presentation mode is
-  a novel approach which should be more widely applied to psychometric
-  validations.
-\item
-  We grouped some of the dimensions under ``Awareness'', despite being
-  similar to items included in the IAS typically conceptualized as
-  ``Accuracy''. However, we believe that subjective scales cannot be
-  pure measures of accuracy, as they are inherently subjective and thus
-  reflect a degree of awareness (of one's accurate noticing or
-  sensation).
-\item
-  Olfactory compensation: pseudo-interoceptive pathway whereby people
-  with interoceptive deficits would compensate by gathering evidence
-  about their internal state externally (e.g., via smell).
-\item
-  The metacluster ``Sensitivity'' seems to be grouping iterms related to
-  visceropcetion and (hyper)sensitivity (Derm).
-\end{itemize}
+The primary aim of Study 1 was to develop and refine a large,
+systematically generated pool of interoceptive items into a
+psychometrically sound and structurally coherent questionnaire. Starting
+with 120 items derived from a modality-by-context grid, we employed a
+multi-step, data-driven reduction process using cutting-edge structure
+analysis methods. This rigorous procedure yielded a final, balanced set
+of 45 items, organized within a stable hierarchical structure comprising
+three higher-order dimensions (Interoceptive Deficits, Interoceptive
+Awareness, Interoceptive Sensitivity) and 12 distinct lower-level
+facets.
+
+One innovation of this study was to test the effect of item presentation
+by comparing structures across different grouping conditions. While the
+analysis revealed no significant effect, a consistent (though
+non-significant) trend suggested that grouping items by modality may be
+slightly more conducive to revealing the underlying psychometric
+structure than grouping by facet or randomly. This finding, while
+preliminary due to the sample size per condition (\(N \pm 200\)),
+highlights a potentially important and under-investigated aspect of
+questionnaire design that warrants future research.
+
+The resulting hierarchical structure offers novel yet interpretable
+insights into self-reported interoception, with flexible degrees of
+granularity. Notably, we categorised several facets (typically related
+to objective external behaviours, like coughing or sneezing) under the
+label ``Awareness'', that might traditionally be named ``Accuracy'' in
+other scales. Our rationale is that subjective self-report, by its very
+nature, cannot be a pure measure of objective accuracy, but at best a
+proxy of an individual's subjective certainty or awareness of their
+interoceptive processes. Furthermore, our bottom-up approach revealed
+intriguing facets, such as ``Olfactory Compensation''. This finding
+provide further evidence for a pseudo-interoceptive pathway, whereby
+individuals with potentially poorer access to internal signals may
+compensate by relying on external cues (e.g., odours) to infer their
+bodily state. The ``Sensitivity'' metacluster also grouped core
+visceroceptive facets (e.g., ``Cardioception'', ``Gastroception'') with
+``Dermal Hypersensitivity'', pointing to a potential common dimension of
+heightened perceptual sensitivity to bodily sensations.
+
+In summary, Study 1 successfully leveraged a systematic item generation
+process and modern analytical techniques to produce a 45-item
+questionnaire with a clear, stable, and theoretically rich hierarchical
+structure. The next crucial step is to formally validate this new
+instrument by examining its psychometric properties and its relationship
+with existing measures in a new, independent sample, which is the
+objective of Study 2.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Goal of study 2: to validate the Mint scale against other
-  interoception scales.
-\end{itemize}
+Following the generation and selection of a set of 45 interoceptive
+items, the next objective is to formally validate this new instrument in
+a large, independent sample, a crucial step for establishing the
+psychometric soundness and unique contribution of the Mint scale to the
+field of interoception research. To this end, we sought to 1) re-assess
+the structure of the shorter version and 2) establish its convergent
+validity by examining the correlations with other established and
+popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS),
+as well as other related measures (e.g., alexithymia). Finally, we
+assessed its criterion validity by directly comparing the predictive
+power of the interoceptive scales across a broad range of outcomes,
+including emotional, cognitive, and clinical variables.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Structure: Low stability of \emph{Olfa} as belonging in the deficit
-  group. More studies are needed to investigate its place and cluster
-  invariance: it is possible that its association might depend on other
-  factors or categories.
-\item
-  Main contender is MAIA. But its most sensitive dimensions seem to be
-  the least related to interoception, which is dangerous as it might
-  lead to findings with associations misattributed to ``Interoception''
-  (just because it correlate with some MAIA dimensions), but it might
-  have nothing to do with interoception per se and more with emotion
-  regulation.
-\item
-  Basically the pattern is clear: everything high-level, metacognitive
-  and highly subjective related to wellbeing and general affective state
-  is the most strongly related to the MAIA through some of its Emotion
-  regulation dimensions. All the other outcomes actually related to
-  interoceptive processes are most strongly predicted by the Mint.
-\end{itemize}
+The primary goal of Study 2 was to validate the items selected in Study
+1. This involved re-assessing its structure in a new, large sample, and
+establishing its convergent and criterion validity against other
+established interoception questionnaires. The analysis led to a final,
+refined 33-item Mint scale with a stable and theoretically coherent
+hierarchical structure, which demonstrated substantial predictive power
+across a range of outcomes.
+
+Re-validating the structure after item selection is a crucial step in
+questionnaire development. When a large item pool is reduced, the
+context changes, which can alter the perceived meaning and relationships
+between the remaining items. For instance, a questionnaire with many
+items suggesting abnormality or pathology might colour other neutral
+items with a negative connotation. While the original structure was
+mostly replicated, the re-validation allowed for a clarification of some
+of the higher-order dimensions (for instance, the ``Sensitivity''
+metacluster became more clearly defined around core interoceptive
+clusters). The final structure, comprising 11 facets and 3 metaclusters,
+showed excellent structural consistency and stability, providing a solid
+foundation for the scale. However, the \emph{Olfa} (Olfactory
+Compensation) cluster showed lower stability in its placement within the
+\emph{Deficit} metacluster. This suggests its role may be more complex,
+and future studies are needed to investigate its place and invariance
+across different populations and contexts.
+
+The criterion validity analysis revealed a clear and compelling pattern
+of results. The Mint scale, particularly its \emph{Deficit} metacluster,
+consistently outperformed other scales in predicting outcomes directly
+related to alterations in bodily experience and self-regulation, such as
+alexithymia, dissociative experiences, ADHD, autism, and various somatic
+symptoms. The main contender, the MAIA-2, showed an advantage primarily
+for outcomes related to general well-being, such as life satisfaction,
+depression, and anxiety. However, this advantage was almost entirely
+driven by dimensions highly related to emotion regulation abilities,
+namely \emph{Trusting} and \emph{Not-Worrying}, whose inclusion as core
+interoceptive facets has been questioned
+(\citeproc{ref-ferentzi2021examining}{Ferentzi et al., 2021}). When
+these dimensions were removed (in the \emph{iMAIA} version), the
+MAIA-2's predictive power for these outcomes dropped considerably, often
+below that of the Mint.
+
+This highlights a crucial issue in the field: the potential for
+misattributing findings to ``interoception'' when they may be driven by
+broader emotion regulation capacities
+(\citeproc{ref-murphy2020testing}{Murphy et al., 2020}). While valuable,
+the MAIA-2's most predictive subscales appear less related to core
+interoceptive processing and more to metacognitive beliefs about one's
+body and emotional coping. The Mint, in contrast, appears to tap more
+directly into distinct facets of interoceptive experience, from visceral
+sensitivity to perceived deficits. The pattern is clear: for high-level,
+metacognitive aspects of affective state and well-being, the MAIA-2's
+emotion regulation facets are highly relevant. For outcomes tied more
+specifically to bodily processes, clinical conditions characterized by
+sensory dysregulation, and nuanced interoceptive experiences, the Mint
+offers superior predictive validity and specificity.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Future directions: needs to test relationship with physiological
-  measures of interoception.
-\item
-  Also, the structure might still require a bit of deeper investigation,
-  in particular with some of its facets (\emph{Olfa} and \emph{Derm})
-  which might display different associations depending on the context or
-  the population.
-\end{itemize}
+Across two studies, we developed and validated the Multimodal
+Interoception Questionnaire (Mint), a new 33-item self-report measure of
+interoception. Our approach addressed key limitations of existing scales
+by starting with a systematically generated, broad item pool that
+explicitly controlled for context and modality, and then using a
+data-driven reduction process. The result is a psychometrically robust
+instrument with a stable, hierarchical structure comprising three
+higher-order metaclusters, namely \emph{Interoceptive Deficit},
+\emph{Interoceptive Awareness}, and \emph{Visceroception}, and 11
+distinct lower-level facets. The validation study demonstrated that the
+Mint not only captures variance present in other popular scales (MAIA-2,
+BPQ and IAS) but also offers superior predictive power for a range of
+clinical and cognitive outcomes, particularly those tied to altered
+bodily perception.
+
+A key contribution of the Mint is its potential ability to disentangle
+core interoceptive experiences from more general emotion regulation
+capacities. Our findings show that while the MAIA-2 is a potent
+predictor of general well-being, this is largely driven by its
+\emph{Trusting} and \emph{Not-Worrying} subscales, which heavily tap
+into emotion regulation skills and coping strategies. The Mint,
+conversely, excelled at predicting conditions like alexithymia, ADHD,
+autism, and somatic symptoms, where alterations in bodily sensing are a
+core feature. This suggests the Mint provides a more specific measure of
+interoceptive processing, offering researchers a finer-grained tool to
+probe the role of bodily awareness in health and disease.
+
+Despite these strengths, the present work has limitations that open
+avenues for future research. First, as a self-report measure, the Mint
+captures subjective beliefs about interoceptive abilities, not objective
+accuracy. A crucial next step is to investigate the relationship between
+Mint scores and physiological or behavioural measures of interoception
+(e.g., heartbeat tracking tasks, heartbeat evoked potentials). This
+would help establish the extent to which subjective reports on the Mint
+correspond to objective interoceptive performance. Future research could
+also systematically examine the cost of shorter versions, by
+investigating the tradeoffs incurred by versions with only the one or
+two most central facets per metacluster and their impact on psychometric
+qualities and predictive power.
+
+While the overall structure of the Mint is stable, some facets warrant
+deeper investigation. The \emph{Olfa} (Olfactory Compensation) and
+\emph{Derm} (Dermal Hypersensitivity) clusters, for instance, showed
+more complex patterns of association. Their placement within the
+\emph{Deficit} metacluster is theoretically intriguing but requires
+further validation. The former aligns with predictive coding models
+suggesting that individuals may rely on exteroceptive cues (like odours)
+to infer internal states (\citeproc{ref-paulus2010interoception}{Paulus
+\& Stein, 2010}), a form of pseudo-interoception (or
+extero-interoception). The latter points to a potential link between
+visceral and cutaneous sensitivity, possibly reflecting a general trait
+of heightened bodily awareness or a shared mechanism of central
+sensitization, which has been observed in conditions like chronic pain
+(\citeproc{ref-di2016alexithymia}{Di Tella \& Castelli, 2016}). Future
+studies should examine the invariance of the Mint's structure across
+different populations (e.g., clinical vs.~non-clinical groups) and
+contexts (e.g., heightened arousal vs.~rest) to clarify the role of
+these more nuanced facets. Such work could reveal whether their
+relevance and pattern of associations differs in conditions like anxiety
+disorders, chronic pain, or neurodevelopmental disorders.
+
+In conclusion, the Mint scale represents a significant methodological
+advancement for the field of interoception research. By providing a
+validated, structurally coherent, and nuanced tool, it allows for a more
+precise assessment of self-reported interoceptive experiences. Its
+various forms (full, meta, mini, and micro) offer flexibility for
+researchers and clinicians, paving the way for a deeper understanding of
+the multifaceted role of interoception in human psychology and
+pathophysiology.
 
@@
 Sussex for their help in data collection. DM would also like to thank
-\ldots{} for the motivation provided to write this paper.
+Anastasia for the motivation provided to write this paper.
 
@@
 
+\bibitem[\citeproctext]{ref-craig2002how}
+Craig, A. D. (2002). How do you feel? Interoception: The sense of the
+physiological condition of the body. \emph{Nature Reviews Neuroscience},
+\emph{3}(8), 655--666. \url{https://doi.org/10.1038/nrn894}
+
+\bibitem[\citeproctext]{ref-craig2003interoception}
+Craig, A. D. (2003). Interoception: The sense of the physiological
+condition of the body. \emph{Current Opinion in Neurobiology},
+\emph{13}(4), 500--505.
+
+\bibitem[\citeproctext]{ref-critchley2017interoception}
+Critchley, H. D., \& Garfinkel, S. N. (2017). Interoception and emotion.
+\emph{Current Opinion in Psychology}, \emph{17}, 7--14.
+\url{https://doi.org/10.1016/j.copsyc.2017.04.020}
+
+\bibitem[\citeproctext]{ref-crucianelli2023role}
+Crucianelli, L., \& Ehrsson, H. H. (2023). The role of the skin in
+interoception: A neglected organ? \emph{Perspectives on Psychological
+Science}, \emph{18}(1), 224--238.
+
 \bibitem[\citeproctext]{ref-de2015jspsych}
@@
 Methods}, \emph{47}, 1--12.
+
+\bibitem[\citeproctext]{ref-desmedt2022measures}
+Desmedt, O., Heeren, A., Corneille, O., \& Luminet, O. (2022). What do
+measures of self-report interoception measure? Insights from a
+systematic review, latent factor analysis, and network approach.
+\emph{Biological Psychology}, \emph{169}, 108289.
+
+\bibitem[\citeproctext]{ref-desmedt2025discrepancies}
+Desmedt, O., Luminet, O., Maurage, P., \& Corneille, O. (2025).
+Discrepancies in the definition and measurement of human interoception:
+A comprehensive discussion and suggested ways forward.
+\emph{Perspectives on Psychological Science}, \emph{20}(1), 76--98.
+
+\bibitem[\citeproctext]{ref-di2016alexithymia}
+Di Tella, M., \& Castelli, L. (2016). Alexithymia in chronic pain
+disorders. \emph{Current Rheumatology Reports}, \emph{18}(7), 41.
 
@@
 \emph{9}(3), 432--441.
+
+\bibitem[\citeproctext]{ref-garfinkel2015knowing}
+Garfinkel, S. N., Seth, A. K., Barrett, A. B., Suzuki, K., \& Critchley,
+H. D. (2015). Knowing your own heart: Distinguishing interoceptive
+accuracy from interoceptive awareness. \emph{Biological Psychology},
+\emph{104}, 65--74.
+\url{https://doi.org/10.1016/j.biopsycho.2014.11.004}
 
@@
 
+\bibitem[\citeproctext]{ref-khalsa2018interoception}
+Khalsa, S. S., Adolphs, R., Cameron, O. G., Critchley, H. D., Davenport,
+P. W., Feinstein, J. S., \& Zucker, N. (2018). Interoception and mental
+health: A roadmap. \emph{Biological Psychiatry: Cognitive Neuroscience
+and Neuroimaging}, \emph{3}(6), 501--513.
+\url{https://doi.org/10.1016/j.bpsc.2017.12.004}
+
+\bibitem[\citeproctext]{ref-kolacz2018body}
+Kolacz, J., Holmes, L., \& Porges, S. W. (2018). Body perception
+questionnaire (BPQ) manual. \emph{Traumatic Stress Research Consortium}.
+
 \bibitem[\citeproctext]{ref-kroenke2009ultra}
@@
 
+\bibitem[\citeproctext]{ref-murphy2018classifying}
+Murphy, J., Catmur, C., \& Bird, G. (2018). Classifying individual
+differences in interoception: Implications for the measurement of
+interoceptive accuracy. \emph{Psychonomic Bulletin \& Review},
+\emph{25}(4), 1424--1431.
+\url{https://doi.org/10.3758/s13423-017-1339-z}
+
+\bibitem[\citeproctext]{ref-paulus2010interoception}
+Paulus, M. P., \& Stein, M. B. (2010). Interoception in anxiety and
+depression. \emph{Brain Structure and Function}, \emph{214}(5),
+451--463.
+
 \bibitem[\citeproctext]{ref-sibson1978studies}
@@
 
+\bibitem[\citeproctext]{ref-vig2022questionnaires}
+Vig, L., Köteles, F., \& Ferentzi, E. (2022). Questionnaires of
+interoception do not assess the same construct. \emph{PLoS One},
+\emph{17}(8), e0273299.
+
+\bibitem[\citeproctext]{ref-zamariola2018interoceptive}
+Zamariola, G., Maurage, P., Luminet, O., \& Corneille, O. (2018).
+Interoceptive accuracy scores from the heartbeat counting task are
+problematic: Evidence from simple bivariate correlations.
+\emph{Biological Psychology}, \emph{137}, 12--17.
+
 \end{CSLReferences}

### 2025-08-12 paper/manuscript.qmd
add alive def

@@
 Interestingly, Rumination (and Self-Blame) stood out as selectively related to the Mint's *Visceroception* and *Deficit* dimensions (note that Rumination was also related to the MAIA's interoceptive dimensions, namely Noticing, Emotional Awareness and Body Listening).
-The only primal world belief that correlated particularly with the Mint's *Visceroception* and the MAIA's interoceptive dimension was the belief that the world was alive (**TODO: Ana maybe throw in a couple more words about what this belief means and is defined**).
+The only primal world belief that correlated particularly with the Mint's *Visceroception* and the MAIA's interoceptive dimension was the belief that the world was alive [i.e., the belief that the universe is conscious, purposeful, and in active relationship with oneself, @clifton2021brief].
 

### 2025-08-12 paper/manuscript.qmd
boom

@@
 abstract: |
-  TO DO.
+  Interoception, the sense of the body's internal state, is crucial for mental and physical health, yet its measurement is hindered by tools with conceptual and psychometric issues.
+To address these limitations, we developed and validated the Multimodal Interoception Questionnaire (Mint).
+In Study 1 (N=559), we generated a comprehensive item pool using a novel "modality-by-context" framework and employed the recently developed psychometric network analysis for data-driven item reduction.
+In Study 2 (N=737), we validated the resulting instrument in an independent sample, establishing its structure and comparing its predictive power against established interoception questionnaires (MAIA-2, BPQ, IAS) across a wide range of clinical and cognitive outcomes.
+This rigorous process yielded a 33-item scale with a stable hierarchical structure comprising three metaclusters (Interoceptive Deficit, Interoceptive Awareness, Visceroception) and 11 distinct facets.
+The Mint demonstrated superior criterion validity, consistently outperforming existing scales in predicting outcomes tied to altered bodily perception, including alexithymia, ADHD, autism, and somatic symptom clusters.
+The Mint offers a psychometrically robust and nuanced measure of self-reported interoception that integrates and extends existing scales, providing researchers and clinicians with a practical and readily usable tool to investigate the role of bodily sensations in health and disease.
 #   **Significance Statement**. TODO.
@@
 These tools were developed in different eras of a rapidly evolving field, each with its own objectives and philosophies.
-The BPQ, one of the earliest measures, emphasizes the assessment of body awareness and autonomic nervous system (ANS) reactivity, focusing on subjective experiences of physiological stress reactions in organs innervated by the ANS, such as those triggered by stress or trauma [@porges1993body].
+The BPQ, one of the earliest measures, emphasizes the assessment of body awareness and autonomic nervous system (ANS) reactivity, focusing on subjective experiences of physiological stress reactions in organs innervated by the ANS, such as those triggered by stress or trauma [@kolacz2018body].
 The MAIA incorporated ideas from the then-booming emotion regulation and mindfulness fields, including subscales assessing adaptive coping strategies and metacognitive insights about the body.
@@
 rest) to clarify the role of these more nuanced facets.
-Such work could reveal whether their relevance and pattern of associations differs in conditions like anxiety disorders, chronic pain, or neurodevelopmental disorders.
+Such work could reveal whether their relevance and pattern of associations differ in conditions like anxiety disorders, chronic pain, or neurodevelopmental disorders.
 

### 2025-08-12 paper/manuscript.tex
boom

@@
 
-\abstract{TO DO. }
+\abstract{Interoception, the sense of the body's internal state, is
+crucial for mental and physical health, yet its measurement is hindered
+by tools with conceptual and psychometric issues. To address these
+limitations, we developed and validated the Multimodal Interoception
+Questionnaire (Mint). In Study 1 (N=559), we generated a comprehensive
+item pool using a novel ``modality-by-context'' framework and employed
+the recently developed psychometric network analysis for data-driven
+item reduction. In Study 2 (N=737), we validated the resulting
+instrument in an independent sample, establishing its structure and
+comparing its predictive power against established interoception
+questionnaires (MAIA-2, BPQ, IAS) across a wide range of clinical and
+cognitive outcomes. This rigorous process yielded a 33-item scale with a
+stable hierarchical structure comprising three metaclusters
+(Interoceptive Deficit, Interoceptive Awareness, Visceroception) and 11
+distinct facets. The Mint demonstrated superior criterion validity,
+consistently outperforming existing scales in predicting outcomes tied
+to altered bodily perception, including alexithymia, ADHD, autism, and
+somatic symptom clusters. The Mint offers a psychometrically robust and
+nuanced measure of self-reported interoception that integrates and
+extends existing scales, providing researchers and clinicians with a
+practical and readily usable tool to investigate the role of bodily
+sensations in health and disease. }
 
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, arc=.35mm, left=2mm, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0, colback=white]
+\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, left=2mm, arc=.35mm, colback=white, bottomrule=.15mm, toprule=.15mm]
 
@@
 those triggered by stress or trauma
-(\citeproc{ref-porges1993body}{\textbf{porges1993body?}}). The MAIA
+(\citeproc{ref-kolacz2018body}{Kolacz et al., 2018}). The MAIA
 incorporated ideas from the then-booming emotion regulation and
@@
 \emph{Visceroception} and the MAIA's interoceptive dimension was the
-belief that the world was alive (\textbf{TODO: Ana maybe throw in a
-couple more words about what this belief means and is defined}).
+belief that the world was alive (i.e., the belief that the universe is
+conscious, purposeful, and in active relationship with oneself,
+\citeproc{ref-clifton2021brief}{Clifton \& Yaden, 2021}).
 
@@
 these more nuanced facets. Such work could reveal whether their
-relevance and pattern of associations differs in conditions like anxiety
+relevance and pattern of associations differ in conditions like anxiety
 disorders, chronic pain, or neurodevelopmental disorders.

### 2025-08-19 paper/manuscript.qmd
final

@@
 abstract: |
-  Interoception, the sense of the body's internal state, is crucial for mental and physical health, yet its measurement is hindered by tools with conceptual and psychometric issues.
+  Interoception, the sensing of the body's internal state, is an important component of homeostatic and allostatic regulation with wide-ranging implications for mental and physical health, yet its measurement is hindered by tools with conceptual and psychometric issues.
 To address these limitations, we developed and validated the Multimodal Interoception Questionnaire (Mint).
-In Study 1 (N=559), we generated a comprehensive item pool using a novel "modality-by-context" framework and employed the recently developed psychometric network analysis for data-driven item reduction.
-In Study 2 (N=737), we validated the resulting instrument in an independent sample, establishing its structure and comparing its predictive power against established interoception questionnaires (MAIA-2, BPQ, IAS) across a wide range of clinical and cognitive outcomes.
+In Study 1 (N=559), a comprehensive item pool using a novel "modality-by-context" framework was generated and then reduced using psychometric network analysis.
+In Study 2 (N=737), we validated the Mint in an independent sample, establishing its structure,  comparing its predictive power against established interoception questionnaires (MAIA-2, BPQ, IAS), and across a wide range of clinical and cognitive outcomes.
 This rigorous process yielded a 33-item scale with a stable hierarchical structure comprising three metaclusters (Interoceptive Deficit, Interoceptive Awareness, Visceroception) and 11 distinct facets.
@@
 Interoception - the sensing and interpretation of the body's internal physiological signals - plays a fundamental role in processes ranging from homeostatic regulation to emotion, decision-making, and mental health [@craig2002how; @critchley2017interoception].
-Despite its growing recognition, the field is hindered by inconsistent definitions and fragmented measurement approaches [@khalsa2018interoception; @desmedt2025discrepancies; @desmedt2022measures].
-Available tools include "objective" physiological tasks (e.g., heartbeat counting or tracking) and "subjective" self-reports, and encompass both "explicit" paradigms that direct participants' attention and consciousness to internal sensations and "implicit" paradigms that do not (e.g., heartbeat evoked potentials recorded during rest).
-These assessments are often targeted at only one of several interoceptive modalities (e.g., cardioception, respiroception, gastroception), and are mapped onto theoretical dimensions [e.g., accuracy, sensitivity, awareness, @garfinkel2015knowing] within a rapidly evolving theoretical scaffolding.
-However, no consensus exists on a gold-standard measure, and each approach has distinct limitations: physiological tasks often require specialised equipment and expertise, are time-consuming, and are challenging to administer at scale, whereas questionnaires are constrained by their inherent subjectivity.
-Crucially, the psychometric quality of many of these measures is questionable [e.g., see criticism about the heartbeat counting task, @zamariola2018interoceptive], yielding low inter-task correlations [@murphy2018classifying], raising serious concerns about their reliability and validity (e.g., measures presented as measuring one theoretical dimension but likely measuring something else).
-This measurement conundrum hinders progress in comparing, replicating, and interpreting interoception-related findings, underscoring the need to develop improved tools that align with modern psychometric standards.
+Despite its growing recognition, the field has been hindered by inconsistent definitions and fragmented measurement approaches [@khalsa2018interoception; @desmedt2025discrepancies; @desmedt2022measures].
+Available tools include "objective" physiological tasks (e.g., heartbeat counting or tracking) and "subjective" self-reports, and encompass both "explicit" paradigms that direct participants' attention to internal sensations and "implicit" paradigms that do not (e.g., heartbeat evoked potentials recorded during rest).
+These assessments are often targeted at only one of several interoceptive modalities (e.g., cardioception, respiroception, gastroception), and are mapped onto theoretical dimensions [e.g., accuracy, sensitivity, awareness, @garfinkel2015knowing] within a rapidly evolving theoretical landscape.
+However, no consensus exists on a gold-standard measure witheach approach having distinct limitations.
+For example, physiological tasks often require specialised equipment and expertise, are time-consuming, and are challenging to administer at scale, whereas questionnaires are constrained by their inherent subjectivity.
+Crucially, the psychometric quality of many of these measures is questionable [e.g., see criticism about the heartbeat counting task, @zamariola2018interoceptive], yielding low inter-task correlations [@murphy2018classifying] and raising important concerns regarding their reliability and validity (e.g., measures presented as measuring one theoretical dimension but likely measuring something else).
+This lack of conceptual clarity and measurement convergence impedes scientific progress in comparing, replicating, and interpreting interoception-related findings, emphasising the need to develop improved tools that align with modern psychometric standards.
 
@@
 The present work focuses on self-report questionnaires, which offer a scalable and accessible tool complementing physiological tasks.
-Among the numerous questionnaires available, a handful seem to dominate the literature [@desmedt2022measures], including the Body Perception Questionnaire [BPQ, @kolacz2018body], the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2018multidimensional], and the Interoceptive Accuracy Scale [IAS, @murphy2018classifying].
+Among the numerous interoceptive questionnaires available, a handful dominate the literature [@desmedt2022measures], including the Body Perception Questionnaire [BPQ, @kolacz2018body], the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2018multidimensional], and the Interoceptive Accuracy Scale [IAS, @murphy2018classifying].
 These tools were developed in different eras of a rapidly evolving field, each with its own objectives and philosophies.
-The BPQ, one of the earliest measures, emphasizes the assessment of body awareness and autonomic nervous system (ANS) reactivity, focusing on subjective experiences of physiological stress reactions in organs innervated by the ANS, such as those triggered by stress or trauma [@kolacz2018body].
+For example, the BPQ, one of the earliest measures, captures bodily awareness and autonomic nervous system (ANS) reactivity by focusing on experiences of physiological stress reactions in organs innervated by the ANS, such as those triggered by stress or trauma [@kolacz2018body].
 The MAIA incorporated ideas from the then-booming emotion regulation and mindfulness fields, including subscales assessing adaptive coping strategies and metacognitive insights about the body.
-By contrast, the IAS was recently crafted to sidestep such high-level - possibly tangential - constructs and instead capture subjective reports of concrete bodily events (e.g., coughing, sneezing) as proxies for interoceptive accuracy.
+In contrast, the IAS was recently developed to circumvent these high-level - possibly tangential - constructs, instead capturing subjective reports of concrete bodily events (e.g., coughing, sneezing) as proxies for interoceptive accuracy.
 
-These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measurand differences, which in turn hinders replication and theoretical integration.
-Recent work has been focused on aligning subjective measures and facets with theoretical models, debating whether they measure interoceptive "sensitivity" or other dimensions (accuracy, attention, deficits).
-However, this focus on a theory-driven approach might be premature when theoretical models are in flux, and when a topographic mapping to self-report dimensions is not guaranteed (e.g.
-distinctions that are relevant at a neuroanatomical or cognitive level might not necessarily translate into the same structural landscape of subjective experiences).
-More fundamentally, existing questionnaires suffer from two major structural blind spots.
-First, they are often narrow or unsystematic in their coverage of bodily *modalities*, with a heavy bias towards cardio-respiratory sensations and a neglect of others like gastric, urogenital, or thermoregulatory signals.
-Second, and perhaps most critically, they fail to control for the *context* in which an interoceptive experience occurs, introducing significant variability in how participants interpret and respond to items.
-For example, an item about "feeling your heart beat" is ambiguous; its frequency, experience and its interpretation differ vastly depending on whether it occurs during physical exercise, a moment of anxiety, or quiet rest (e.g., someone who exercises regularly, or is anxious, might more easily recall an instance of occurrence of feeling their heart beating and respond based on that contextual saliency).
+These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measurand differences, hindering replication and theoretical integration.
+In acknowledgement of this issue, efforts have been made to align subjective measures with theoretical models that outline different facets of interoception (e.g., accuracy, attention, deficits).
+However, focusing on developing measures that are theory-driven may however be premature when theoretical models are in flux, and when a topographic mapping to self-report dimensions is not guaranteed.
+For example,  interoceptive distinctions that are relevant at a neuroanatomical or cognitive level might not necessarily map onto the structure of subjective experiences.
+More fundamentally, existing interoception questionnaires typically fail to consider the full range of interoceptive modalities and the context in which interoceptive experiences occur.
+Most existing questionnaires focus on a narrow range of bodily modalities, with a heavy bias towards cardio-respiratory sensations at the expense of others like gastric, urogenital, or thermoregulatory signals.
+Perhaps most critically, existing measures ask participants to make general assessments across most/all contexts, which does not capture the potential homeostatic relevance of attending or detecting internal signals.
+Without a contextual reference point, there is likely to be substantial variability in how participants interpret and respond to items.
+For example, a general item about "feeling your heart beat" is ambiguous since its salience, frequency, experience and interpretation would differ depending on the context, e.g., on whether it occurs during physical exercise, a moment of anxiety, or quiet rest (e.g., someone who exercises regularly, or is anxious, might more easily recall an instance of occurrence of feeling their heart beating and respond based on that contextual saliency).
 
-To address these gaps, we introduce the Multimodal Interoception Questionnaire (Mint).
-The overarching aim of this work is to develop and validate a new questionnaire that systematically addresses these limitations.
-In Study 1, we detail the bottom-up development of the Mint, using a "modality-by-context" framework to generate a comprehensive item pool, which is then refined using cutting-edge psychometric network analysis.
-In Study 2, we validate the final version of the Mint against the established interoception questionnaires, demonstrating its robust structure and predictive validity for a range of clinically-relevant outcomes.
+To address these gaps, we developed and validated the Multimodal Interoception Questionnaire (Mint), a new questionnaire that systematically addresses the above limitations.
+In Study 1, we describe the bottom-up development of the Mint, using a "modality-by-context" framework to generate a comprehensive item pool, which was then refined using cutting-edge psychometric network analysis.
+In Study 2, we validated the final 33-item version of the Mint against the established interoception questionnaires, demonstrating its robust structure and predictive validity for a range of clinically-relevant outcomes.
 
@@
 
-The primary goal of Study 1 was to develop a new interoception questionnaire by generating a comprehensive item pool and refining it into a psychometrically robust scale.
-To overcome the limitations of existing measures, we adopted a bottom-up, theoretically agnostic approach.
-Instead of imposing a pre-defined theoretical structure, we focused on two tangible and systematically controllable aspects of interoceptive experience: the *modality* of the sensation and the *context* in which it occurs.
-The objective was not to create *yet another scale* measuring an alleged distinct construct or variation, but rather to synthesize existing ideas and frameworks into a comprehensive and modern tool that captures the richness of interoceptive experiences and encompasses the most relevant facets of interoception.
+The aim of Study 1 was to develop a new interoception questionnaire by generating a comprehensive item pool and subsequently refining it into a psychometrically robust scale.
+To overcome the limitations of existing questionnaires, we adopted a bottom-up, theoretically agnostic approach.
+Rather than imposing a pre-defined theoretical structure on questionnaire items, we instead focused on two tangible and systematically controllable aspects of interoceptive experience: the *modality* of the sensation and the *context* in which it occurs.
+Our objective was not to develop a questionnaire measuring a new or theoretically distinct facet, but instead build on existing research and synthesise existing ideas and frameworks into a comprehensive and modern tool that captures both the richness of interoceptive experiences and the most prominent facets of interoception.
 
-<!-- Give examples of items for each part of the framework here so that the method makes more sense? -->
-Our item generation process was guided by a "modality-by-context" grid designed to overcome the limitations of existing scales.
-For *modalities*, we expanded beyond the typical cardio-respiratory focus to include a broader range of bodily systems: cardiac, respiratory, gastric, genital, bladder & colon, and skin & temperature [the latter of which being increasingly recognized as a key interoceptive channel, @crucianelli2023role].
+Item generation was guided by a "modality-by-context" grid.
+For *modalities*, we expanded beyond the typical cardio-respiratory focus to encompass a wide range of bodily systems: cardiac, respiratory, gastric, genital, bladder & colon, and skin & temperature [the latter of which being increasingly recognized as a key interoceptive channel, @crucianelli2023role].
 We also included a "general state" category to capture the integrated sense of the body's overall physiological condition [@craig2002how; @craig2003interoception].
-For *contexts*, we designed facets to capture specific situational contexts like negative (anxious) and positive (sexual) arousal, which reflect distinct bodily states with differing interoceptive signatures, as well as other experiential qualities tapping into elaboration and threshold of perception, such as sensitivity, accuracy, and confusion.
-To maintain continuity with established work while making targeted improvements, we purposefully adapted items from existing questionnaires (e.g., IAS-like items related to observable behaviors).
-This systematic framework yielded a diverse pool of 120 initial items, ensuring comprehensive coverage while minimizing the ambiguity inherent in context-free questions.
+For *contexts*, we designed facets to capture specific situational contexts like negative (anxious) and positive (sexual) arousal, which reflect distinct bodily states with differing interoceptive signatures.
+Facets were also designed to capture other experiential qualities tapping into elaboration and threshold of perception, such as sensitivity, accuracy, and confusion.
+This systematic framework yielded a diverse pool of 120 initial items, ensuring comprehensive coverage while minimising the ambiguity inherent in context-free questions.
 
-The final step involved a data-driven reduction of this item pool.
-We employed cutting-edge psychometric network-based techniques to identify and remove redundant items and to uncover the most stable and coherent dimensional structure.
-Additionally, we designed the study so that we could explore an often overlooked psychometric quality: the invariance of the structure to the presentation format (how items are grouped together on the screen, whether by modality, facet, or randomly) influences the resulting psychometric structure.
-This rigorous, multi-stage process was designed to produce a subset of items with a clear, stable, and theoretically rich hierarchical structure, ready for formal validation.
+The initial pool of 120 was then reduced using cutting-edge psychometric network-based techniques, identifying and removing redundant items and revealing  the most stable and coherent dimensional structure.
+We also designed the study to enable an examination of structural invariance depending on presentation format (e.g., how items are grouped together, whether by modality, facet or randomly) which is an often overlooked psychometric quality.
+This rigorous, multi-stage process was designed to produce a subset of items with a clear, stable, and theoretically rich hierarchical structure, ready for formal validation in Study 2.
 
@@
 <!-- summary -->
-The primary aim of Study 1 was to develop and refine a large, systematically generated pool of interoceptive items into a psychometrically sound and structurally coherent questionnaire.
+The aim of Study 1 was to develop and refine a large, systematically generated pool of interoceptive items into a psychometrically sound and structurally coherent questionnaire.
 Starting with 120 items derived from a modality-by-context grid, we employed a multi-step, data-driven reduction process using cutting-edge structure analysis methods.
-This rigorous procedure yielded a final, balanced set of 45 items, organized within a stable hierarchical structure comprising three higher-order dimensions (Interoceptive Deficits, Interoceptive Awareness, Interoceptive Sensitivity) and 12 distinct lower-level facets.
+This procedure yielded a final, balanced set of 45 items, organised within a stable hierarchical structure comprising three higher-order dimensions (Interoceptive Deficits, Interoceptive Awareness, Interoceptive Sensitivity) and 12 distinct lower-level facets.
 
-<!-- Effect of item presentation -->
-One innovation of this study was to test the effect of item presentation by comparing structures across different grouping conditions.
-While the analysis revealed no significant effect, a consistent (though non-significant) trend suggested that grouping items by modality may be slightly more conducive to revealing the underlying psychometric structure than grouping by facet or randomly.
-This finding, while preliminary due to the sample size per condition ($N \pm 200$), highlights a potentially important and under-investigated aspect of questionnaire design that warrants future research.
 <!-- The final reduction from 54 to 45 items was a consensus-based decision to remove three clusters for reasons of conceptual clarity and parsimony, a necessary step to ensure the final scale's usability and content validity.
@@
 The resulting hierarchical structure offers novel yet interpretable insights into self-reported interoception, with flexible degrees of granularity.
-Notably, we categorised several facets (typically related to objective external behaviours, like coughing or sneezing) under the label "Awareness", that might traditionally be named "Accuracy" in other scales.
-Our rationale is that subjective self-report, by its very nature, cannot be a pure measure of objective accuracy, but at best a proxy of an individual's subjective certainty or awareness of their interoceptive processes.
+Notably, we categorised several facets (typically related to objective external behaviours, like coughing or sneezing) under the label "Awareness".
+Although other questionnaires might refer to this as "Accuracy", we preferred to preserve the notion that subjective self-reports, by their very nature, cannot be a pure measure of objective accuracy and are, at best, a proxy for subjective certainty or awareness of interoceptive processes.
 Furthermore, our bottom-up approach revealed intriguing facets, such as "Olfactory Compensation".
-This finding provide further evidence for a pseudo-interoceptive pathway, whereby individuals with potentially poorer access to internal signals may compensate by relying on external cues (e.g., odours) to infer their bodily state.
+This finding provides evidence for a pseudo-interoceptive pathway, whereby individuals with poorer access to internal signals may compensate by relying on external cues (e.g., odours) to infer their bodily state.
 The "Sensitivity" metacluster also grouped core visceroceptive facets (e.g., "Cardioception", "Gastroception") with "Dermal Hypersensitivity", pointing to a potential common dimension of heightened perceptual sensitivity to bodily sensations.
 
-In summary, Study 1 successfully leveraged a systematic item generation process and modern analytical techniques to produce a 45-item questionnaire with a clear, stable, and theoretically rich hierarchical structure.
-The next crucial step is to formally validate this new instrument by examining its psychometric properties and its relationship with existing measures in a new, independent sample, which is the objective of Study 2.
+<!-- Effect of item presentation -->
+An additional innovation of Study 1 was examining the effect of item presentation on the resulting psychometric structure by comparing structures across different grouping conditions.
+Although there were no significant effects of item presentation, a consistent (though non-significant) trend suggested that grouping items by modality (rather than by facet or randomly) could be more conducive to revealing the underlying psychometric structure.
+This finding, while preliminary due to the sample size per condition ($N \pm 200$), highlights a potentially important and under-investigated aspect of questionnaire design worthy of future research.
 
@@
 
-Following the generation and selection of a set of 45 interoceptive items, the next objective is to formally validate this new instrument in a large, independent sample, a crucial step for establishing the psychometric soundness and unique contribution of the Mint scale to the field of interoception research.
-To this end, we sought to 1) re-assess the structure of the shorter version and 2) establish its convergent validity by examining the correlations with other established and popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS), as well as other related measures (e.g., alexithymia).
-Finally, we assessed its criterion validity by directly comparing the predictive power of the interoceptive scales across a broad range of outcomes, including emotional, cognitive, and clinical variables.
+Study 1 successfully leveraged a systematic item generation process and modern analytical techniques to produce a 45-item interoception questionnaire with a clear, stable, and theoretically rich hierarchical structure.
+Study 2 then sought to formally validate the Mint scale by examining its psychometric properties and its relationship with existing measures in a large, independent sample.
+To this end, we sought to 1) re-assess the structure of the shorter Mint version and 2) establish its convergent validity by examining correlations with other established and popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS), as well as other related measures (e.g., alexithymia).
+Finally, we assessed the Mint’s criterion validity by directly comparing the predictive power of all interoception questionnaires across a broad range of outcomes, including emotional, cognitive, and clinical variables.
 
@@
 
-The primary goal of Study 2 was to validate the items selected in Study 1.
-This involved re-assessing its structure in a new, large sample, and establishing its convergent and criterion validity against other established interoception questionnaires.
+Study 2 sought to formally validate the Mint in a large, independent sample, a crucial step for establishing the psychometric soundness and unique contribution of the scale for interoception research.
+This involved re-assessing its structure in a new sample and establishing its convergent and criterion validity against other existing interoception questionnaires.
 The analysis led to a final, refined 33-item Mint scale with a stable and theoretically coherent hierarchical structure, which demonstrated substantial predictive power across a range of outcomes.
 
-Re-validating the structure after item selection is a crucial step in questionnaire development.
-When a large item pool is reduced, the context changes, which can alter the perceived meaning and relationships between the remaining items.
-For instance, a questionnaire with many items suggesting abnormality or pathology might colour other neutral items with a negative connotation.
-While the original structure was mostly replicated, the re-validation allowed for a clarification of some of the higher-order dimensions (for instance, the "Sensitivity" metacluster became more clearly defined around core interoceptive clusters).
-The final structure, comprising 11 facets and 3 metaclusters, showed excellent structural consistency and stability, providing a solid foundation for the scale.
-However, the *Olfa* (Olfactory Compensation) cluster showed lower stability in its placement within the *Deficit* metacluster.
-This suggests its role may be more complex, and future studies are needed to investigate its place and invariance across different populations and contexts.
+Structure re-validation is an important step following item reduction since reducing a large item pool can alter the perceived meaning and relationships between the remaining items.
+For instance, a questionnaire with many items suggesting abnormality or pathology might influence the interpretation of otherwise neutral items.
+While the original structure of the Mint was mostly replicated, the re-validation facilitated the clarification of several higher-order dimensions (e.g., the "Sensitivity" metacluster became more clearly defined around core interoceptive clusters).
+The final Mint structure, comprising 11 facets within 3 metaclusters, yielded excellent structural consistency and stability.
+The *Olfa* (Olfactory Compensation) cluster had lower stability within the *Deficit* metacluster, possibly indicative of a more complex role.
+For instance, this cluster could be related to adaptive compensatory processes in some participants and maladaptive strategies in others.
+Future studies should further investigate its place and invariance across different populations and contexts.
 
 The criterion validity analysis revealed a clear and compelling pattern of results.
-The Mint scale, particularly its *Deficit* metacluster, consistently outperformed other scales in predicting outcomes directly related to alterations in bodily experience and self-regulation, such as alexithymia, dissociative experiences, ADHD, autism, and various somatic symptoms.
-The main contender, the MAIA-2, showed an advantage primarily for outcomes related to general well-being, such as life satisfaction, depression, and anxiety.
-However, this advantage was almost entirely driven by dimensions highly related to emotion regulation abilities, namely *Trusting* and *Not-Worrying*, whose inclusion as core interoceptive facets has been questioned [@ferentzi2021examining].
-When these dimensions were removed (in the *iMAIA* version), the MAIA-2's predictive power for these outcomes dropped considerably, often below that of the Mint.
-
-This highlights a crucial issue in the field: the potential for misattributing findings to "interoception" when they may be driven by broader emotion regulation capacities [@murphy2020testing].
+The Mint scale, particularly its *Deficit* metacluster, consistently outperformed existing interoceptive scales in predicting outcomes directly related to alterations in bodily experience and self-regulation, including alexithymia, dissociative experiences, ADHD, autism, and various somatic symptoms.
+The MAIA-2 showed an advantage over the Mint for predicting outcomes related to general well-being (e.g., life satisfaction, depression, and anxiety).
+However, its predictive superiority was almost entirely driven by dimensions related to emotion regulation abilities, namely *Trusting* and *Not-Worrying*, whose inclusion as core interoceptive facets have been questioned [@ferentzi2021examining].
 While valuable, the MAIA-2's most predictive subscales appear less related to core interoceptive processing and more to metacognitive beliefs about one's body and emotional coping.
 The Mint, in contrast, appears to tap more directly into distinct facets of interoceptive experience, from visceral sensitivity to perceived deficits.
-The pattern is clear: for high-level, metacognitive aspects of affective state and well-being, the MAIA-2's emotion regulation facets are highly relevant.
-For outcomes tied more specifically to bodily processes, clinical conditions characterized by sensory dysregulation, and nuanced interoceptive experiences, the Mint offers superior predictive validity and specificity.
+Indeed, when the emotion-regulation dimensions were removed (in the *iMAIA* version), the MAIA-2's predictive power for well-being outcomes dropped considerably, often below that of the Mint.
+Overall, for high-level, metacognitive aspects of affective state and well-being, the MAIA-2's emotion regulation facets are highly informative.
+For outcomes tied more specifically to bodily processes, clinical conditions characterised by sensory dysregulation, and nuanced interoceptive experiences, the Mint offers superior predictive validity and specificity.
 
@@
 Across two studies, we developed and validated the Multimodal Interoception Questionnaire (Mint), a new 33-item self-report measure of interoception.
-Our approach addressed key limitations of existing scales by starting with a systematically generated, broad item pool that explicitly controlled for context and modality, and then using a data-driven reduction process.
-The result is a psychometrically robust instrument with a stable, hierarchical structure comprising three higher-order metaclusters, namely *Interoceptive Deficit*, *Interoceptive Awareness*, and *Visceroception*, and 11 distinct lower-level facets.
-The validation study demonstrated that the Mint not only captures variance present in other popular scales (MAIA-2, BPQ and IAS) but also offers superior predictive power for a range of clinical and cognitive outcomes, particularly those tied to altered bodily perception.
+Our approach addressed key limitations of existing questionnaires by starting with a systematically generated, broad item pool that explicitly accounted for context and assessed a wide range of interoceptive modalities.
+The Mint is a psychometrically robust instrument with a stable, hierarchical structure comprising three higher-order metaclusters, namely *Interoceptive Deficit*, *Interoceptive Awareness*, and *Visceroception*, and 11 distinct lower-level facets.
+Study 2 validated the Mint, demonstrating that it not only captures variance present in other popular scales (MAIA-2, BPQ and IAS) but also offers superior predictive power for a range of clinical and cognitive outcomes, particularly those tied to altered bodily perception.
 
-A key contribution of the Mint is its potential ability to disentangle core interoceptive experiences from more general emotion regulation capacities.
-Our findings show that while the MAIA-2 is a potent predictor of general well-being, this is largely driven by its *Trusting* and *Not-Worrying* subscales, which heavily tap into emotion regulation skills and coping strategies.
-The Mint, conversely, excelled at predicting conditions like alexithymia, ADHD, autism, and somatic symptoms, where alterations in bodily sensing are a core feature.
-This suggests the Mint provides a more specific measure of interoceptive processing, offering researchers a finer-grained tool to probe the role of bodily awareness in health and disease.
+A key advantage of the Mint is its potential ability to disentangle core interoceptive experiences from more general emotion regulation abilities, an identified problem in interoception research where findings may be misattributed to "interoception" when they are driven by emotion regulation capacities [@murphy2020testing].
+Our findings show that although the MAIA-2 is a strong predictor of general well-being, this predictive power is driven by its *Trusting* and *Not-Worrying* subscales, which heavily tap into emotion regulation skills and coping strategies.
+The Mint, in contrast, taps more directly into interoceptive components, and has excellent predictive power for conditions where alterations in bodily sensing are a core feature, including alexithymia, ADHD, autism, and somatic symptoms.
+Overall,  the Mint provides a more specific measure of self-reported interoceptive processing across contexts and modalities, offering researchers a granular and comprehensive tool with which to further understand the contribution of bodily awareness to human health and disease.
 
-Despite these strengths, the present work has limitations that open avenues for future research.
+We note several limitations that could serve as the impetus for future research efforts.
 First, as a self-report measure, the Mint captures subjective beliefs about interoceptive abilities, not objective accuracy.
-A crucial next step is to investigate the relationship between Mint scores and physiological or behavioural measures of interoception (e.g., heartbeat tracking tasks, heartbeat evoked potentials).
-This would help establish the extent to which subjective reports on the Mint correspond to objective interoceptive performance.
-Future research could also systematically examine the cost of shorter versions, by investigating the tradeoffs incurred by versions with only the one or two most central facets per metacluster and their impact on psychometric qualities and predictive power.
+A natural next step will be to establish the extent to which subjective reports on the Mint correspond to objective interoceptive performance (e.g., heartbeat tracking tasks, heartbeat evoked potentials).
+Second, future research could systematically examine the usefulness of shorter versions of the Mint, for example, by investigating the tradeoffs incurred by versions with only the one or two most central facets per metacluster on psychometric qualities and predictive power.
 
@@
 The *Olfa* (Olfactory Compensation) and *Derm* (Dermal Hypersensitivity) clusters, for instance, showed more complex patterns of association.
-Their placement within the *Deficit* metacluster is theoretically intriguing but requires further validation.
-The former aligns with predictive coding models suggesting that individuals may rely on exteroceptive cues (like odours) to infer internal states  [@paulus2010interoception], a form of pseudo-interoception (or extero-interoception).
-The latter points to a potential link between visceral and cutaneous sensitivity, possibly reflecting a general trait of heightened bodily awareness or a shared mechanism of central sensitization, which has been observed in conditions like chronic pain [@di2016alexithymia].
-Future studies should examine the invariance of the Mint's structure across different populations (e.g., clinical vs.
-non-clinical groups) and contexts (e.g., heightened arousal vs.
-rest) to clarify the role of these more nuanced facets.
-Such work could reveal whether their relevance and pattern of associations differ in conditions like anxiety disorders, chronic pain, or neurodevelopmental disorders.
+Their placement within the *Deficit* metacluster is theoretically intriguing since the former aligns with predictive coding models of pseudo-interoception (or extero-interoception) where individuals rely on exteroceptive cues (like odours) to infer internal states  [@paulus2010interoception], while the latter links visceral and cutaneous sensitivity, possibly reflecting a general trait of heightened bodily awareness or a shared mechanism of central sensitization, observed in conditions like chronic pain [@di2016alexithymia].
+Future studies should examine the invariance of the Mint's structure across different populations (e.g., clinical *vs.* non-clinical groups) and contexts (e.g., heightened arousal *vs.* rest) to clarify the role of these more nuanced facets.
+This work could reveal whether the relevance and pattern of associations are shared or dissociable across conditions like anxiety disorders, chronic pain, and neurodevelopmental disorders.
 
-In conclusion, the Mint scale represents a significant methodological advancement for the field of interoception research.
-By providing a validated, structurally coherent, and nuanced tool, it allows for a more precise assessment of self-reported interoceptive experiences.
-Its various forms (full, meta, mini, and micro) offer flexibility for researchers and clinicians, paving the way for a deeper understanding of the multifaceted role of interoception in human psychology and pathophysiology.
+In conclusion, the Mint scale represents a fresh take on interoception questionnaires and a significant methodological advancement for the field of interoception research.
+By providing a validated, structurally coherent, and nuanced tool, it allows for a more precise assessment of self-reported interoceptive experiences, paving the way for a deeper understanding of the multifaceted role of interoception in human psychology and pathophysiology.
 

### 2025-08-19 paper/manuscript.tex
final

--- 2025-07-04 paper/manuscript.tex
@@
 
-\abstract{TO DO. }
+\abstract{Interoception, the sensing of the body's internal state, is an
+important component of homeostatic and allostatic regulation with
+wide-ranging implications for mental and physical health, yet its
+measurement is hindered by tools with conceptual and psychometric
+issues. To address these limitations, we developed and validated the
+Multimodal Interoception Questionnaire (Mint). In Study 1 (N=559), a
+comprehensive item pool using a novel ``modality-by-context'' framework
+was generated and then reduced using psychometric network analysis. In
+Study 2 (N=737), we validated the Mint in an independent sample,
+establishing its structure, comparing its predictive power against
+established interoception questionnaires (MAIA-2, BPQ, IAS), and across
+a wide range of clinical and cognitive outcomes. This rigorous process
+yielded a 33-item scale with a stable hierarchical structure comprising
+three metaclusters (Interoceptive Deficit, Interoceptive Awareness,
+Visceroception) and 11 distinct facets. The Mint demonstrated superior
+criterion validity, consistently outperforming existing scales in
+predicting outcomes tied to altered bodily perception, including
+alexithymia, ADHD, autism, and somatic symptom clusters. The Mint offers
+a psychometrically robust and nuanced measure of self-reported
+interoception that integrates and extends existing scales, providing
+researchers and clinicians with a practical and readily usable tool to
+investigate the role of bodily sensations in health and disease. }
 
 \keywords{Interoception questionnaire, interoceptive accuracy scale,
-MAIA, Mint Validation, Body Awareness}
+MAIA, Mint Validation, Body Awareness, Health}
 
@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, rightrule=.15mm, colback=white, breakable, opacityback=0, colframe=quarto-callout-note-color-frame, toprule=.15mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, opacityback=0, colback=white, breakable, toprule=.15mm, arc=.35mm, left=2mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame]
 
@@
 
-\resetlinenumber[1]
-
 \section{Introduction}\label{introduction}
 
-Main issues in existing questionnaires:
-
-\begin{itemize}
-\tightlist
-\item
-  Either heavily based on theories (e.g., focusing on specific
-  ``alleged'' dimensions), despite shaky evidence for said-theories
-\item
-  Do not control for context (which leads to variability in
-  interpretation and occurence)
-\item
-  Often quite narrow in the modalities covered (or scattered, like the
-  IAS)
-\end{itemize}
+Interoception - the sensing and interpretation of the body's internal
+physiological signals - plays a fundamental role in processes ranging
+from homeostatic regulation to emotion, decision-making, and mental
+health (\citeproc{ref-craig2002how}{Craig, 2002};
+\citeproc{ref-critchley2017interoception}{Critchley \& Garfinkel,
+2017}). Despite its growing recognition, the field has been hindered by
+inconsistent definitions and fragmented measurement approaches
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022},
+\citeproc{ref-desmedt2025discrepancies}{2025};
+\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018}). Available
+tools include ``objective'' physiological tasks (e.g., heartbeat
+counting or tracking) and ``subjective'' self-reports, and encompass
+both ``explicit'' paradigms that direct participants' attention to
+internal sensations and ``implicit'' paradigms that do not (e.g.,
+heartbeat evoked potentials recorded during rest). These assessments are
+often targeted at only one of several interoceptive modalities (e.g.,
+cardioception, respiroception, gastroception), and are mapped onto
+theoretical dimensions (e.g., accuracy, sensitivity, awareness,
+\citeproc{ref-garfinkel2015knowing}{Garfinkel et al., 2015}) within a
+rapidly evolving theoretical landscape. However, no consensus exists on
+a gold-standard measure witheach approach having distinct limitations.
+For example, physiological tasks often require specialised equipment and
+expertise, are time-consuming, and are challenging to administer at
+scale, whereas questionnaires are constrained by their inherent
+subjectivity. Crucially, the psychometric quality of many of these
+measures is questionable (e.g., see criticism about the heartbeat
+counting task, \citeproc{ref-zamariola2018interoceptive}{Zamariola et
+al., 2018}), yielding low inter-task correlations
+(\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}) and raising
+important concerns regarding their reliability and validity (e.g.,
+measures presented as measuring one theoretical dimension but likely
+measuring something else). This lack of conceptual clarity and
+measurement convergence impedes scientific progress in comparing,
+replicating, and interpreting interoception-related findings,
+emphasising the need to develop improved tools that align with modern
+psychometric standards.
+
+The present work focuses on self-report questionnaires, which offer a
+scalable and accessible tool complementing physiological tasks. Among
+the numerous interoceptive questionnaires available, a handful dominate
+the literature (\citeproc{ref-desmedt2022measures}{Desmedt et al.,
+2022}), including the Body Perception Questionnaire (BPQ,
+\citeproc{ref-kolacz2018body}{Kolacz et al., 2018}), the
+Multidimensional Assessment of Interoceptive Awareness (MAIA,
+\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), and
+the Interoceptive Accuracy Scale (IAS,
+\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}). These tools
+were developed in different eras of a rapidly evolving field, each with
+its own objectives and philosophies. For example, the BPQ, one of the
+earliest measures, captures bodily awareness and autonomic nervous
+system (ANS) reactivity by focusing on experiences of physiological
+stress reactions in organs innervated by the ANS, such as those
+triggered by stress or trauma (\citeproc{ref-kolacz2018body}{Kolacz et
+al., 2018}). The MAIA incorporated ideas from the then-booming emotion
+regulation and mindfulness fields, including subscales assessing
+adaptive coping strategies and metacognitive insights about the body. In
+contrast, the IAS was recently developed to circumvent these high-level
+- possibly tangential - constructs, instead capturing subjective reports
+of concrete bodily events (e.g., coughing, sneezing) as proxies for
+interoceptive accuracy.
+
+These differing philosophies have practical consequences, leading to
+poor convergence between scales that are assumed to measure the same
+construct (\citeproc{ref-vig2022questionnaires}{Vig et al., 2022}) - a
+classic example of the ``jingle fallacy'' where the shared label of
+``interoception'' can mask underlying measurand differences, hindering
+replication and theoretical integration. In acknowledgement of this
+issue, efforts have been made to align subjective measures with
+theoretical models that outline different facets of interoception (e.g.,
+accuracy, attention, deficits). However, focusing on developing measures
+that are theory-driven may however be premature when theoretical models
+are in flux, and when a topographic mapping to self-report dimensions is
+not guaranteed. For example, interoceptive distinctions that are
+relevant at a neuroanatomical or cognitive level might not necessarily
+map onto the structure of subjective experiences. More fundamentally,
+existing interoception questionnaires typically fail to consider the
+full range of interoceptive modalities and the context in which
+interoceptive experiences occur. Most existing questionnaires focus on a
+narrow range of bodily modalities, with a heavy bias towards
+cardio-respiratory sensations at the expense of others like gastric,
+urogenital, or thermoregulatory signals. Perhaps most critically,
+existing measures ask participants to make general assessments across
+most/all contexts, which does not capture the potential homeostatic
+relevance of attending or detecting internal signals. Without a
+contextual reference point, there is likely to be substantial
+variability in how participants interpret and respond to items. For
+example, a general item about ``feeling your heart beat'' is ambiguous
+since its salience, frequency, experience and interpretation would
+differ depending on the context, e.g., on whether it occurs during
+physical exercise, a moment of anxiety, or quiet rest (e.g., someone who
+exercises regularly, or is anxious, might more easily recall an instance
+of occurrence of feeling their heart beating and respond based on that
+contextual saliency).
+
+To address these gaps, we developed and validated the Multimodal
+Interoception Questionnaire (Mint), a new questionnaire that
+systematically addresses the above limitations. In Study 1, we describe
+the bottom-up development of the Mint, using a ``modality-by-context''
+framework to generate a comprehensive item pool, which was then refined
+using cutting-edge psychometric network analysis. In Study 2, we
+validated the final 33-item version of the Mint against the established
+interoception questionnaires, demonstrating its robust structure and
+predictive validity for a range of clinically-relevant outcomes.
 
@@
 
-TODO: write intro.
-
-\begin{itemize}
-\tightlist
-\item
-  Goal of study 1: to generate a lot of items, analyze its structure and
-  reduce them to a balanced set of items.
-\end{itemize}
+The aim of Study 1 was to develop a new interoception questionnaire by
+generating a comprehensive item pool and subsequently refining it into a
+psychometrically robust scale. To overcome the limitations of existing
+questionnaires, we adopted a bottom-up, theoretically agnostic approach.
+Rather than imposing a pre-defined theoretical structure on
+questionnaire items, we instead focused on two tangible and
+systematically controllable aspects of interoceptive experience: the
+\emph{modality} of the sensation and the \emph{context} in which it
+occurs. Our objective was not to develop a questionnaire measuring a new
+or theoretically distinct facet, but instead build on existing research
+and synthesise existing ideas and frameworks into a comprehensive and
+modern tool that captures both the richness of interoceptive experiences
+and the most prominent facets of interoception.
+
+Item generation was guided by a ``modality-by-context'' grid. For
+\emph{modalities}, we expanded beyond the typical cardio-respiratory
+focus to encompass a wide range of bodily systems: cardiac, respiratory,
+gastric, genital, bladder \& colon, and skin \& temperature (the latter
+of which being increasingly recognized as a key interoceptive channel,
+\citeproc{ref-crucianelli2023role}{Crucianelli \& Ehrsson, 2023}). We
+also included a ``general state'' category to capture the integrated
+sense of the body's overall physiological condition
+(\citeproc{ref-craig2002how}{Craig, 2002};
+\citeproc{ref-craig2003interoception}{Craig, 2003}). For
+\emph{contexts}, we designed facets to capture specific situational
+contexts like negative (anxious) and positive (sexual) arousal, which
+reflect distinct bodily states with differing interoceptive signatures.
+Facets were also designed to capture other experiential qualities
+tapping into elaboration and threshold of perception, such as
+sensitivity, accuracy, and confusion. This systematic framework yielded
+a diverse pool of 120 initial items, ensuring comprehensive coverage
+while minimising the ambiguity inherent in context-free questions.
+
+The initial pool of 120 was then reduced using cutting-edge psychometric
+network-based techniques, identifying and removing redundant items and
+revealing the most stable and coherent dimensional structure. We also
+designed the study to enable an examination of structural invariance
+depending on presentation format (e.g., how items are grouped together,
+whether by modality, facet or randomly) which is an often overlooked
+psychometric quality. This rigorous, multi-stage process was designed to
+produce a subset of items with a clear, stable, and theoretically rich
+hierarchical structure, ready for formal validation in Study 2.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Possible (although not at all significant) bias consistent across
-  indices in favour of a greater similarity with the modality-grouping
-  condition. Futher research with more data (here we only had
-  \textasciitilde200 observation per condition) might be able to yield
-  more conclusive results. In general, testing the presentation mode is
-  a novel approach which should be more widely applied to psychometric
-  validations.
-\item
-  We grouped some of the dimensions under ``Awareness'', despite being
-  similar to items included in the IAS typically conceptualized as
-  ``Accuracy''. However, we believe that subjective scales cannot be
-  pure measures of accuracy, as they are inherently subjective and thus
-  reflect a degree of awareness (of one's accurate noticing or
-  sensation).
-\item
-  Olfactory compensation: pseudo-interoceptive pathway whereby people
-  with interoceptive deficits would compensate by gathering evidence
-  about their internal state externally (e.g., via smell).
-\item
-  The metacluster ``Sensitivity'' seems to be grouping iterms related to
-  visceropcetion and (hyper)sensitivity (Derm).
-\end{itemize}
+The aim of Study 1 was to develop and refine a large, systematically
+generated pool of interoceptive items into a psychometrically sound and
+structurally coherent questionnaire. Starting with 120 items derived
+from a modality-by-context grid, we employed a multi-step, data-driven
+reduction process using cutting-edge structure analysis methods. This
+procedure yielded a final, balanced set of 45 items, organised within a
+stable hierarchical structure comprising three higher-order dimensions
+(Interoceptive Deficits, Interoceptive Awareness, Interoceptive
+Sensitivity) and 12 distinct lower-level facets.
+
+The resulting hierarchical structure offers novel yet interpretable
+insights into self-reported interoception, with flexible degrees of
+granularity. Notably, we categorised several facets (typically related
+to objective external behaviours, like coughing or sneezing) under the
+label ``Awareness''. Although other questionnaires might refer to this
+as ``Accuracy'', we preferred to preserve the notion that subjective
+self-reports, by their very nature, cannot be a pure measure of
+objective accuracy and are, at best, a proxy for subjective certainty or
+awareness of interoceptive processes. Furthermore, our bottom-up
+approach revealed intriguing facets, such as ``Olfactory Compensation''.
+This finding provides evidence for a pseudo-interoceptive pathway,
+whereby individuals with poorer access to internal signals may
+compensate by relying on external cues (e.g., odours) to infer their
+bodily state. The ``Sensitivity'' metacluster also grouped core
+visceroceptive facets (e.g., ``Cardioception'', ``Gastroception'') with
+``Dermal Hypersensitivity'', pointing to a potential common dimension of
+heightened perceptual sensitivity to bodily sensations.
+
+An additional innovation of Study 1 was examining the effect of item
+presentation on the resulting psychometric structure by comparing
+structures across different grouping conditions. Although there were no
+significant effects of item presentation, a consistent (though
+non-significant) trend suggested that grouping items by modality (rather
+than by facet or randomly) could be more conducive to revealing the
+underlying psychometric structure. This finding, while preliminary due
+to the sample size per condition (\(N \pm 200\)), highlights a
+potentially important and under-investigated aspect of questionnaire
+design worthy of future research.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Goal of study 2: to validate the Mint scale against other
-  interoception scales.
-\end{itemize}
+Study 1 successfully leveraged a systematic item generation process and
+modern analytical techniques to produce a 45-item interoception
+questionnaire with a clear, stable, and theoretically rich hierarchical
+structure. Study 2 then sought to formally validate the Mint scale by
+examining its psychometric properties and its relationship with existing
+measures in a large, independent sample. To this end, we sought to 1)
+re-assess the structure of the shorter Mint version and 2) establish its
+convergent validity by examining correlations with other established and
+popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS),
+as well as other related measures (e.g., alexithymia). Finally, we
+assessed the Mint's criterion validity by directly comparing the
+predictive power of all interoception questionnaires across a broad
+range of outcomes, including emotional, cognitive, and clinical
+variables.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Structure: Low stability of \emph{Olfa} as belonging in the deficit
-  group. More studies are needed to investigate its place and cluster
-  invariance: it is possible that its association might depend on other
-  factors or categories.
-\item
-  Main contender is MAIA. But its most sensitive dimensions seem to be
-  the least related to interoception, which is dangerous as it might
-  lead to findings with associations misattributed to ``Interoception''
-  (just because it correlate with some MAIA dimensions), but it might
-  have nothing to do with interoception per se and more with emotion
-  regulation.
-\item
-  Basically the pattern is clear: everything high-level, metacognitive
-  and highly subjective related to wellbeing and general affective state
-  is the most strongly related to the MAIA through some of its Emotion
-  regulation dimensions. All the other outcomes actually related to
-  interoceptive processes are most strongly predicted by the Mint.
-\end{itemize}
+Study 2 sought to formally validate the Mint in a large, independent
+sample, a crucial step for establishing the psychometric soundness and
+unique contribution of the scale for interoception research. This
+involved re-assessing its structure in a new sample and establishing its
+convergent and criterion validity against other existing interoception
+questionnaires. The analysis led to a final, refined 33-item Mint scale
+with a stable and theoretically coherent hierarchical structure, which
+demonstrated substantial predictive power across a range of outcomes.
+
+Structure re-validation is an important step following item reduction
+since reducing a large item pool can alter the perceived meaning and
+relationships between the remaining items. For instance, a questionnaire
+with many items suggesting abnormality or pathology might influence the
+interpretation of otherwise neutral items. While the original structure
+of the Mint was mostly replicated, the re-validation facilitated the
+clarification of several higher-order dimensions (e.g., the
+``Sensitivity'' metacluster became more clearly defined around core
+interoceptive clusters). The final Mint structure, comprising 11 facets
+within 3 metaclusters, yielded excellent structural consistency and
+stability. The \emph{Olfa} (Olfactory Compensation) cluster had lower
+stability within the \emph{Deficit} metacluster, possibly indicative of
+a more complex role. For instance, this cluster could be related to
+adaptive compensatory processes in some participants and maladaptive
+strategies in others. Future studies should further investigate its
+place and invariance across different populations and contexts.
+
+The criterion validity analysis revealed a clear and compelling pattern
+of results. The Mint scale, particularly its \emph{Deficit} metacluster,
+consistently outperformed existing interoceptive scales in predicting
+outcomes directly related to alterations in bodily experience and
+self-regulation, including alexithymia, dissociative experiences, ADHD,
+autism, and various somatic symptoms. The MAIA-2 showed an advantage
+over the Mint for predicting outcomes related to general well-being
+(e.g., life satisfaction, depression, and anxiety). However, its
+predictive superiority was almost entirely driven by dimensions related
+to emotion regulation abilities, namely \emph{Trusting} and
+\emph{Not-Worrying}, whose inclusion as core interoceptive facets have
+been questioned (\citeproc{ref-ferentzi2021examining}{Ferentzi et al.,
+2021}). While valuable, the MAIA-2's most predictive subscales appear
+less related to core interoceptive processing and more to metacognitive
+beliefs about one's body and emotional coping. The Mint, in contrast,
+appears to tap more directly into distinct facets of interoceptive
+experience, from visceral sensitivity to perceived deficits. Indeed,
+when the emotion-regulation dimensions were removed (in the \emph{iMAIA}
+version), the MAIA-2's predictive power for well-being outcomes dropped
+considerably, often below that of the Mint. Overall, for high-level,
+metacognitive aspects of affective state and well-being, the MAIA-2's
+emotion regulation facets are highly informative. For outcomes tied more
+specifically to bodily processes, clinical conditions characterised by
+sensory dysregulation, and nuanced interoceptive experiences, the Mint
+offers superior predictive validity and specificity.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Future directions: needs to test relationship with physiological
-  measures of interoception.
-\item
-  Also, the structure might still require a bit of deeper investigation,
-  in particular with some of its facets (\emph{Olfa} and \emph{Derm})
-  which might display different associations depending on the context or
-  the population.
-\end{itemize}
+Across two studies, we developed and validated the Multimodal
+Interoception Questionnaire (Mint), a new 33-item self-report measure of
+interoception. Our approach addressed key limitations of existing
+questionnaires by starting with a systematically generated, broad item
+pool that explicitly accounted for context and assessed a wide range of
+interoceptive modalities. The Mint is a psychometrically robust
+instrument with a stable, hierarchical structure comprising three
+higher-order metaclusters, namely \emph{Interoceptive Deficit},
+\emph{Interoceptive Awareness}, and \emph{Visceroception}, and 11
+distinct lower-level facets. Study 2 validated the Mint, demonstrating
+that it not only captures variance present in other popular scales
+(MAIA-2, BPQ and IAS) but also offers superior predictive power for a
+range of clinical and cognitive outcomes, particularly those tied to
+altered bodily perception.
+
+A key advantage of the Mint is its potential ability to disentangle core
+interoceptive experiences from more general emotion regulation
+abilities, an identified problem in interoception research where
+findings may be misattributed to ``interoception'' when they are driven
+by emotion regulation capacities
+(\citeproc{ref-murphy2020testing}{Murphy et al., 2020}). Our findings
+show that although the MAIA-2 is a strong predictor of general
+well-being, this predictive power is driven by its \emph{Trusting} and
+\emph{Not-Worrying} subscales, which heavily tap into emotion regulation
+skills and coping strategies. The Mint, in contrast, taps more directly
+into interoceptive components, and has excellent predictive power for
+conditions where alterations in bodily sensing are a core feature,
+including alexithymia, ADHD, autism, and somatic symptoms. Overall, the
+Mint provides a more specific measure of self-reported interoceptive
+processing across contexts and modalities, offering researchers a
+granular and comprehensive tool with which to further understand the
+contribution of bodily awareness to human health and disease.
+
+We note several limitations that could serve as the impetus for future
+research efforts. First, as a self-report measure, the Mint captures
+subjective beliefs about interoceptive abilities, not objective
+accuracy. A natural next step will be to establish the extent to which
+subjective reports on the Mint correspond to objective interoceptive
+performance (e.g., heartbeat tracking tasks, heartbeat evoked
+potentials). Second, future research could systematically examine the
+usefulness of shorter versions of the Mint, for example, by
+investigating the tradeoffs incurred by versions with only the one or
+two most central facets per metacluster on psychometric qualities and
+predictive power.
+
+While the overall structure of the Mint is stable, some facets warrant
+deeper investigation. The \emph{Olfa} (Olfactory Compensation) and
+\emph{Derm} (Dermal Hypersensitivity) clusters, for instance, showed
+more complex patterns of association. Their placement within the
+\emph{Deficit} metacluster is theoretically intriguing since the former
+aligns with predictive coding models of pseudo-interoception (or
+extero-interoception) where individuals rely on exteroceptive cues (like
+odours) to infer internal states
+(\citeproc{ref-paulus2010interoception}{Paulus \& Stein, 2010}), while
+the latter links visceral and cutaneous sensitivity, possibly reflecting
+a general trait of heightened bodily awareness or a shared mechanism of
+central sensitization, observed in conditions like chronic pain
+(\citeproc{ref-di2016alexithymia}{Di Tella \& Castelli, 2016}). Future
+studies should examine the invariance of the Mint's structure across
+different populations (e.g., clinical \emph{vs.} non-clinical groups)
+and contexts (e.g., heightened arousal \emph{vs.} rest) to clarify the
+role of these more nuanced facets. This work could reveal whether the
+relevance and pattern of associations are shared or dissociable across
+conditions like anxiety disorders, chronic pain, and neurodevelopmental
+disorders.
+
+In conclusion, the Mint scale represents a fresh take on interoception
+questionnaires and a significant methodological advancement for the
+field of interoception research. By providing a validated, structurally
+coherent, and nuanced tool, it allows for a more precise assessment of
+self-reported interoceptive experiences, paving the way for a deeper
+understanding of the multifaceted role of interoception in human
+psychology and pathophysiology.
 

### 2025-08-19 paper/manuscript.qmd
Update manuscript.qmd
fixed some typos and formatting issues

@@
 These assessments are often targeted at only one of several interoceptive modalities (e.g., cardioception, respiroception, gastroception), and are mapped onto theoretical dimensions [e.g., accuracy, sensitivity, awareness, @garfinkel2015knowing] within a rapidly evolving theoretical landscape.
-However, no consensus exists on a gold-standard measure witheach approach having distinct limitations.
+However, no consensus exists on a gold-standard measure with each approach having distinct limitations.
 For example, physiological tasks often require specialised equipment and expertise, are time-consuming, and are challenging to administer at scale, whereas questionnaires are constrained by their inherent subjectivity.
@@
 
-These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measurand differences, hindering replication and theoretical integration.
+These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measures and differences, hindering replication and theoretical integration.
 In acknowledgement of this issue, efforts have been made to align subjective measures with theoretical models that outline different facets of interoception (e.g., accuracy, attention, deficits).
@@
 
-To further reduce and balance the remaining items, we collectively decided on removing the lower-level clusters *Sexual Arousal Awareness* (too general and overlapping with the other more specific sex-related items), *Signalling* (which items started with "when something important is happening in my life", which meaning we deemed too much open to interpretation), and *Sexual Arousal Changes* (low fit with the other modality-focused clusters of its group).
+To further reduce and balance the remaining items, we collectively decided on removing the lower-level clusters *Sexual Arousal Awareness* (too general and overlapping with the other more specific sex-related items), *Signalling* (which items started with "when something important is happening in my life", which meaning we deemed too open to interpretation), and *Sexual Arousal Changes* (low fit with the other modality-focused clusters of its group).
 The final set included 45 items.
@@
 If one or more conditions were endorsed, participants were asked to indicate any current treatments, including pharmacological (e.g., antidepressants, anxiolytics, antipsychotics, mood stabilizers), psychological (e.g., psychotherapy, mindfulness), or lifestyle interventions.
-Binary variables (0 = absent, 1 = present) were created to identify participants reporting mood disorders (MDD, GAD, Bipolar Disorder; with a stricter subgroup of participants undergoing a pharma- or psychological treatment), anxiety-centred disorders (GAD, Panic Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders, addiction-related disorders, borderline personality disorder, autism spectrum disorder (ASD), and ADHD.
+Binary variables (0 = absent, 1 = present) were created to identify participants reporting mood disorders (Major Depressive Disorder, Bipolar Disorder; with a stricter subgroup of participants undergoing a pharma- or psychological treatment), anxiety-centred disorders (Generalised Anxiety Disorder, Panic Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders, addiction-related disorders, borderline personality disorder, autism spectrum disorder (ASD), and ADHD.
 
@@
 Next, we tested the predictive power of the Mint scale relative to other interoception questionnaires.
-We will assessed the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict different outcomes, and compare the best between the 4 interoception scales (based on the R2).
+We assessed the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict different outcomes, and compare the best between the 4 interoception scales based on the total explained variance (R2).
 We then evaluated the predictive performance of each scale as a whole by comparing regression models with all the dimensions entered as predictors (note that the IAS and BPQ only have one total score variable).
-We assessed the models based on their total explained variance (R2), as well as on the Bayesian Information Criterion (BIC), which penalizes for predictor number, thus offering a balance between model parsimony and predictive power.
+We assessed the models based on their R2, as well as on the Bayesian Information Criterion (BIC), which penalizes for predictor number, thus offering a balance between model parsimony and predictive power.
 For the logistic models, we quantified the discriminative power by computing the Area Under the Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which assesses the model's discriminative power (the combination of sensitivity and specificity).
@@
 This complex structure suggests that the dimensions indeed capture distinct aspects of interoception, and that the metaclusters, rather than being simple aggregates of rather-redundant elements, might actually capture unique combinations (greater than the sum of their parts).
-It also provides evidence against a simplistic adaptive *vs.* maladaptive dichotomy, as *Deficit* was not negatively bit positively correlated with *Visceroception*.
+It also provides evidence against a simplistic adaptive *vs.* maladaptive dichotomy, as *Deficit* was not negatively but positively correlated with *Visceroception*.
 Interestingly, while *Awareness* was also positively correlated with *Visceroception*, it yielded an insignificant negative correlation with *Deficit* (this finding was also aligned with the hierarchical clustering results, showing a greater proximity between *Deficit* and *Visceroception* than with *Awareness*), underlining again the complex web of relationships captured by the Mint.

### 2025-08-19 paper/manuscript.tex
manuscript pdf

@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, opacityback=0, colback=white, breakable, toprule=.15mm, arc=.35mm, left=2mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame]
+\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, colframe=quarto-callout-note-color-frame, leftrule=.75mm, arc=.35mm, colback=white, toprule=.15mm, bottomrule=.15mm, rightrule=.15mm, opacityback=0, left=2mm]
 
@@
 \href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
+\begin{center}
 \includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
+\end{center}
 
@@
 rapidly evolving theoretical landscape. However, no consensus exists on
-a gold-standard measure witheach approach having distinct limitations.
+a gold-standard measure with each approach having distinct limitations.
 For example, physiological tasks often require specialised equipment and
@@
 classic example of the ``jingle fallacy'' where the shared label of
-``interoception'' can mask underlying measurand differences, hindering
-replication and theoretical integration. In acknowledgement of this
-issue, efforts have been made to align subjective measures with
+``interoception'' can mask underlying measures and differences,
+hindering replication and theoretical integration. In acknowledgement of
+this issue, efforts have been made to align subjective measures with
 theoretical models that outline different facets of interoception (e.g.,
@@
 something important is happening in my life'', which meaning we deemed
-too much open to interpretation), and \emph{Sexual Arousal Changes} (low
-fit with the other modality-focused clusters of its group). The final
-set included 45 items.
+too open to interpretation), and \emph{Sexual Arousal Changes} (low fit
+with the other modality-focused clusters of its group). The final set
+included 45 items.
 
@@
 interventions. Binary variables (0 = absent, 1 = present) were created
-to identify participants reporting mood disorders (MDD, GAD, Bipolar
-Disorder; with a stricter subgroup of participants undergoing a pharma-
-or psychological treatment), anxiety-centred disorders (GAD, Panic
-Disorder, Social Anxiety Disorder, Specific Phobias), eating disorders,
-addiction-related disorders, borderline personality disorder, autism
-spectrum disorder (ASD), and ADHD.
+to identify participants reporting mood disorders (Major Depressive
+Disorder, Bipolar Disorder; with a stricter subgroup of participants
+undergoing a pharma- or psychological treatment), anxiety-centred
+disorders (Generalised Anxiety Disorder, Panic Disorder, Social Anxiety
+Disorder, Specific Phobias), eating disorders, addiction-related
+disorders, borderline personality disorder, autism spectrum disorder
+(ASD), and ADHD.
 
@@
 Next, we tested the predictive power of the Mint scale relative to other
-interoception questionnaires. We will assessed the importance of each
+interoception questionnaires. We assessed the importance of each
 interoceptive dimension (from all the scales) as a unique predictor by
@@
 \emph{vs.} absence of mood disorders) to predict different outcomes, and
-compare the best between the 4 interoception scales (based on the R2).
-We then evaluated the predictive performance of each scale as a whole by
-comparing regression models with all the dimensions entered as
-predictors (note that the IAS and BPQ only have one total score
-variable). We assessed the models based on their total explained
-variance (R2), as well as on the Bayesian Information Criterion (BIC),
-which penalizes for predictor number, thus offering a balance between
-model parsimony and predictive power. For the logistic models, we
-quantified the discriminative power by computing the Area Under the
-Curve (AUC) of the Receiver Operating Characteristic (ROC) curve, which
-assesses the model's discriminative power (the combination of
-sensitivity and specificity).
+compare the best between the 4 interoception scales based on the total
+explained variance (R2). We then evaluated the predictive performance of
+each scale as a whole by comparing regression models with all the
+dimensions entered as predictors (note that the IAS and BPQ only have
+one total score variable). We assessed the models based on their R2, as
+well as on the Bayesian Information Criterion (BIC), which penalizes for
+predictor number, thus offering a balance between model parsimony and
+predictive power. For the logistic models, we quantified the
+discriminative power by computing the Area Under the Curve (AUC) of the
+Receiver Operating Characteristic (ROC) curve, which assesses the
+model's discriminative power (the combination of sensitivity and
+specificity).
 
@@
 provides evidence against a simplistic adaptive \emph{vs.} maladaptive
-dichotomy, as \emph{Deficit} was not negatively bit positively
+dichotomy, as \emph{Deficit} was not negatively but positively
 correlated with \emph{Visceroception}. Interestingly, while

### 2025-08-20 paper/manuscript.qmd
measurand is a real word lol @AnafNeves

@@
 
-These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measures and differences, hindering replication and theoretical integration.
+These differing philosophies have practical consequences, leading to poor convergence between scales that are assumed to measure the same construct [@vig2022questionnaires] - a classic example of the "jingle fallacy" where the shared label of "interoception" can mask underlying measurand differences, hindering replication and theoretical integration.
 In acknowledgement of this issue, efforts have been made to align subjective measures with theoretical models that outline different facets of interoception (e.g., accuracy, attention, deficits).

### 2025-08-20 paper/manuscript.qmd
update

@@
 
+For both studies, data analysis was carried out using R [4.4.3, @Rcoreteam], leveraging the *easystats* ecosystem [@ludecke2019insight; @ludecke2020extracting] and the *EGAnet* package [@christensen2021estimating].
+The reproducible code and additional details are available at https://github.com/RealityBending/InteroceptionScale.
+
 ## Results
@@
 Next, we tested the predictive power of the Mint scale relative to other interoception questionnaires.
-We assessed the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict different outcomes, and compare the best between the 4 interoception scales based on the total explained variance (R2).
+We assessed the importance of each interoceptive dimension (from all the scales) as a unique predictor by fitting regression models (linear for continuous measures - e.g., depression score - and logistic for binary variables - e.g., presence *vs.* absence of mood disorders) to predict different outcomes, and compare the best between the 4 interoception scales based on the total explained variance [R2 or pseudo-R2 for logistic models, @ludecke2021performance].
 We then evaluated the predictive performance of each scale as a whole by comparing regression models with all the dimensions entered as predictors (note that the IAS and BPQ only have one total score variable).

### 2025-08-20 paper/manuscript.tex
update

@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, colframe=quarto-callout-note-color-frame, leftrule=.75mm, arc=.35mm, colback=white, toprule=.15mm, bottomrule=.15mm, rightrule=.15mm, opacityback=0, left=2mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, opacityback=0, rightrule=.15mm, colback=white, toprule=.15mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, leftrule=.75mm]
 
@@
 classic example of the ``jingle fallacy'' where the shared label of
-``interoception'' can mask underlying measures and differences,
-hindering replication and theoretical integration. In acknowledgement of
-this issue, efforts have been made to align subjective measures with
+``interoception'' can mask underlying measurand differences, hindering
+replication and theoretical integration. In acknowledgement of this
+issue, efforts have been made to align subjective measures with
 theoretical models that outline different facets of interoception (e.g.,
@@
 while remaining comparable and interpretable
-(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino, 2021};
-\citeproc{ref-jimenez2023dimensionality}{Jiménez et al., 2023}). In
-particular, nodes communities (i.e., clusters of items) can be in
+(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino,
+2021b}; \citeproc{ref-jimenez2023dimensionality}{Jiménez et al., 2023}).
+In particular, nodes communities (i.e., clusters of items) can be in
 practice interpreted as distinct ``dimensions'', similarly to
@@
 existence (\citeproc{ref-christensen2021equivalency}{Christensen \&
-Golino, 2021}).
+Golino, 2021b}).
 
@@
 cluster).
+
+For both studies, data analysis was carried out using R (4.4.3,
+\citeproc{ref-Rcoreteam}{R Core Team, 2025}), leveraging the
+\emph{easystats} ecosystem (\citeproc{ref-ludecke2019insight}{Lüdecke et
+al., 2019}, \citeproc{ref-ludecke2020extracting}{2020}) and the
+\emph{EGAnet} package
+(\citeproc{ref-christensen2021estimating}{Christensen \& Golino,
+2021a}). The reproducible code and additional details are available at
+https://github.com/RealityBending/InteroceptionScale.
 
@@
 compare the best between the 4 interoception scales based on the total
-explained variance (R2). We then evaluated the predictive performance of
-each scale as a whole by comparing regression models with all the
-dimensions entered as predictors (note that the IAS and BPQ only have
-one total score variable). We assessed the models based on their R2, as
-well as on the Bayesian Information Criterion (BIC), which penalizes for
-predictor number, thus offering a balance between model parsimony and
-predictive power. For the logistic models, we quantified the
-discriminative power by computing the Area Under the Curve (AUC) of the
-Receiver Operating Characteristic (ROC) curve, which assesses the
-model's discriminative power (the combination of sensitivity and
-specificity).
+explained variance (R2 or pseudo-R2 for logistic models,
+\citeproc{ref-ludecke2021performance}{Lüdecke et al., 2021}). We then
+evaluated the predictive performance of each scale as a whole by
+comparing regression models with all the dimensions entered as
+predictors (note that the IAS and BPQ only have one total score
+variable). We assessed the models based on their R2, as well as on the
+Bayesian Information Criterion (BIC), which penalizes for predictor
+number, thus offering a balance between model parsimony and predictive
+power. For the logistic models, we quantified the discriminative power
+by computing the Area Under the Curve (AUC) of the Receiver Operating
+Characteristic (ROC) curve, which assesses the model's discriminative
+power (the combination of sensitivity and specificity).
 
@@
 
+\bibitem[\citeproctext]{ref-christensen2021estimating}
+Christensen, A. P., \& Golino, H. (2021a). Estimating the stability of
+psychological dimensions via bootstrap exploratory graph analysis: A
+monte carlo simulation and tutorial. \emph{Psych}, \emph{3}(3),
+479--500.
+
 \bibitem[\citeproctext]{ref-christensen2021equivalency}
-Christensen, A. P., \& Golino, H. (2021). On the equivalency of factor
+Christensen, A. P., \& Golino, H. (2021b). On the equivalency of factor
 and network loadings. \emph{Behavior Research Methods}, \emph{53}(4),
@@
 
+\bibitem[\citeproctext]{ref-ludecke2020extracting}
+Lüdecke, D., Ben-Shachar, M. S., Patil, I., \& Makowski, D. (2020).
+Extracting, computing and exploring the parameters of statistical models
+using r. \emph{Journal of Open Source Software}, \emph{5}(53), 2445.
+
+\bibitem[\citeproctext]{ref-ludecke2021performance}
+Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., \& Makowski,
+D. (2021). Performance: An r package for assessment, comparison and
+testing of statistical models. \emph{Journal of Open Source Software},
+\emph{6}(60).
+
+\bibitem[\citeproctext]{ref-ludecke2019insight}
+Lüdecke, D., Waggoner, P. D., \& Makowski, D. (2019). Insight: A unified
+interface to access information from model objects in r. \emph{Journal
+of Open Source Software}, \emph{4}(38), 1412.
+
 \bibitem[\citeproctext]{ref-makowski2025measuring}
@@
 
+\bibitem[\citeproctext]{ref-Rcoreteam}
+R Core Team. (2025). \emph{R: A language and environment for statistical
+computing}. R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}
+
 \bibitem[\citeproctext]{ref-sibson1978studies}

### 2025-08-20 paper/manuscript.qmd
update

@@
 Most existing questionnaires focus on a narrow range of bodily modalities, with a heavy bias towards cardio-respiratory sensations at the expense of others like gastric, urogenital, or thermoregulatory signals.
-Perhaps most critically, existing measures ask participants to make general assessments across most/all contexts, which does not capture the potential homeostatic relevance of attending or detecting internal signals.
-Without a contextual reference point, there is likely to be substantial variability in how participants interpret and respond to items.
-For example, a general item about "feeling your heart beat" is ambiguous since its salience, frequency, experience and interpretation would differ depending on the context, e.g., on whether it occurs during physical exercise, a moment of anxiety, or quiet rest (e.g., someone who exercises regularly, or is anxious, might more easily recall an instance of occurrence of feeling their heart beating and respond based on that contextual saliency).
 
-To address these gaps, we developed and validated the Multimodal Interoception Questionnaire (Mint), a new questionnaire that systematically addresses the above limitations.
+Perhaps most critically, existing measures often ask participants to make general assessments across most/all contexts, which does not capture the potential homeostatic relevance of attending or detecting internal signals.
+For example, the BPQ asks participants to reflect on how often during most situations a person is aware of various bodily sensations, such as their heart beating.
+Without a contextual reference point, there is likely to be substantial variability in how participants interpret and respond to items as well as what those responses might mean about their interoceptive abilities.
+A general item about "feeling your heart beat" is ambiguous since its salience, frequency, experience and interpretation would differ depending on the context, which may or may not be relevant homeostatically.
+For instance, awareness of one’s heartbeat may occur across multiple contexts, including during physical exercise, a moment of anxiety, excitement, or quiet rest with awareness across different contexts reflecting something different about interoceptive sensations.
+This is further complicated by retrospective memory biases such that individuals respond with the most easily accessible or recent instances of awareness; for example,  someone who exercises regularly, or is anxious, might more easily recall an instance of occurrence of feeling their heart beating and respond based on that contextual saliency.
+As an exception, the MAIA does provide some contextual cues for participants (e.g., “When something is wrong in my life I can feel it in my body”) but this is inconsistent across items and focuses almost exclusively on negative (e.g., painful) and emotional (e.g., angry, joyful) contexts as well as general ‘body’ sensations rather than specific interoceptive modalities.
+Thus, no existing scale captures subjective assessments across multiple interoceptive modalities and across different contexts in which interoceptive experiences occur.
+
+To address this gap, we developed and validated the Multimodal Interoception Questionnaire (Mint), a new questionnaire that systematically addresses the above limitations.
 In Study 1, we describe the bottom-up development of the Mint, using a "modality-by-context" framework to generate a comprehensive item pool, which was then refined using cutting-edge psychometric network analysis.
@@
 
-We would like to thank the dissertation students from the University of Sussex for their help in data collection.
+We would like to thank Hugo Critchley for his valuable feedback on the manuscript.
 DM would also like to thank Anastasia for the motivation provided to write this paper.

### 2025-08-20 paper/manuscript.tex
update

@@
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, opacityback=0, rightrule=.15mm, colback=white, toprule=.15mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, leftrule=.75mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, rightrule=.15mm, colback=white, toprule=.15mm, breakable, left=2mm, opacityback=0, leftrule=.75mm, bottomrule=.15mm, arc=.35mm]
 
@@
 cardio-respiratory sensations at the expense of others like gastric,
-urogenital, or thermoregulatory signals. Perhaps most critically,
-existing measures ask participants to make general assessments across
-most/all contexts, which does not capture the potential homeostatic
-relevance of attending or detecting internal signals. Without a
-contextual reference point, there is likely to be substantial
-variability in how participants interpret and respond to items. For
-example, a general item about ``feeling your heart beat'' is ambiguous
-since its salience, frequency, experience and interpretation would
-differ depending on the context, e.g., on whether it occurs during
-physical exercise, a moment of anxiety, or quiet rest (e.g., someone who
+urogenital, or thermoregulatory signals.
+
+Perhaps most critically, existing measures often ask participants to
+make general assessments across most/all contexts, which does not
+capture the potential homeostatic relevance of attending or detecting
+internal signals. For example, the BPQ asks participants to reflect on
+how often during most situations a person is aware of various bodily
+sensations, such as their heart beating. Without a contextual reference
+point, there is likely to be substantial variability in how participants
+interpret and respond to items as well as what those responses might
+mean about their interoceptive abilities. A general item about ``feeling
+your heart beat'' is ambiguous since its salience, frequency, experience
+and interpretation would differ depending on the context, which may or
+may not be relevant homeostatically. For instance, awareness of one's
+heartbeat may occur across multiple contexts, including during physical
+exercise, a moment of anxiety, excitement, or quiet rest with awareness
+across different contexts reflecting something different about
+interoceptive sensations. This is further complicated by retrospective
+memory biases such that individuals respond with the most easily
+accessible or recent instances of awareness; for example, someone who
 exercises regularly, or is anxious, might more easily recall an instance
 of occurrence of feeling their heart beating and respond based on that
-contextual saliency).
-
-To address these gaps, we developed and validated the Multimodal
+contextual saliency. As an exception, the MAIA does provide some
+contextual cues for participants (e.g., ``When something is wrong in my
+life I can feel it in my body'') but this is inconsistent across items
+and focuses almost exclusively on negative (e.g., painful) and emotional
+(e.g., angry, joyful) contexts as well as general `body' sensations
+rather than specific interoceptive modalities. Thus, no existing scale
+captures subjective assessments across multiple interoceptive modalities
+and across different contexts in which interoceptive experiences occur.
+
+To address this gap, we developed and validated the Multimodal
 Interoception Questionnaire (Mint), a new questionnaire that
@@
 
-We would like to thank the dissertation students from the University of
-Sussex for their help in data collection. DM would also like to thank
-Anastasia for the motivation provided to write this paper.
+We would like to thank Hugo Critchley for his valuable feedback on the
+manuscript. DM would also like to thank Anastasia for the motivation
+provided to write this paper.
 

### 2025-08-21 paper/manuscript.qmd
typo name

@@
       - ref: "id1"
-  - name: Giulia Poreiro
+  - name: Giulia Poerio
     orcid: 0000-0002-2343-5109
@@
 
-Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)].
-We additionally crafted 8 "attention check" items blending in (and distributed across) each category.
+Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at
+[realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)]
+<!-- *[MASKED FOR REVIEW]* -->
+. We additionally crafted 8 "attention check" items blending in (and distributed across) each category.
 
@@
 For both studies, data analysis was carried out using R [4.4.3, @Rcoreteam], leveraging the *easystats* ecosystem [@ludecke2019insight; @ludecke2020extracting] and the *EGAnet* package [@christensen2021estimating].
-The reproducible code and additional details are available at https://github.com/RealityBending/InteroceptionScale.
+The reproducible code and additional details are available at
+<!-- *[MASKED FOR REVIEW]*. -->
+https://github.com/RealityBending/InteroceptionScale.
 
@@
 7 attention checks were embedded throughout (one within each major questionnaire).
-In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on https://github.com/RealityBending/InteroceptionScale].
+In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on
+<!-- *[MASKED FOR REVIEW]*. -->
+https://github.com/RealityBending/InteroceptionScale].
 
@@
 
-Data, code, and all materials are available at https://github.com/RealityBending/InteroceptionScale.
+Data, code, and all materials are available at 
+<!-- *[MASKED FOR REVIEW]*. -->
+https://github.com/RealityBending/InteroceptionScale.
 

### 2025-08-21 paper/manuscript.tex
typo name

@@
 \authorsnames[{1,2},{1},{1},{1},{1}]{Dominique Makowski,Ana Neves,Emma
-Benn,Maisie Bennett,Giulia Poreiro}
+Benn,Maisie Bennett,Giulia Poerio}
 
@@
 
-\leftheader{Makowski, Neves, Benn, Bennett and Poreiro}
+\leftheader{Makowski, Neves, Benn, Bennett and Poerio}
 
@@
 Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
-Poreiro}{0000-0002-2343-5109}} 
+Poerio}{0000-0002-2343-5109}} 
 \par{ }
-\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, rightrule=.15mm, colback=white, toprule=.15mm, breakable, left=2mm, opacityback=0, leftrule=.75mm, bottomrule=.15mm, arc=.35mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, colback=white, arc=.35mm, left=2mm, breakable, rightrule=.15mm, leftrule=.75mm, opacityback=0, toprule=.15mm, bottomrule=.15mm]
 
@@
 Bennett:   Investigation; Giulia
-Poreiro:   Investigation, Methodology, Writing -- original
-draft, Writing -- review \& editing}
+Poerio:   Investigation, Methodology, Writing -- original draft, Writing
+-- review \& editing}
 \par{Correspondence concerning this article should be addressed
@@
 facets\footnote{The initial item list is available at
-  \href{https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html}{realitybending.github.io/InteroceptionScale/study1/analysis/2\_analysis.html}}.
-We additionally crafted 8 ``attention check'' items blending in (and
+  \href{https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html}{realitybending.github.io/InteroceptionScale/study1/analysis/2\_analysis.html}}
+. We additionally crafted 8 ``attention check'' items blending in (and
 distributed across) each category.

### 2025-08-22 paper/manuscript.qmd
update

--- 2025-08-20 paper/manuscript.qmd
@@
 keywords: "Interoception questionnaire, interoceptive accuracy scale, MAIA, Mint Validation, Body Awareness, Health"
-numbered-lines: false
+numbered-lines: true
 floatsintext: true
-mask: false
+mask: true
 bibliography: bibliography.bib
@@
 
-Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)].
-We additionally crafted 8 "attention check" items blending in (and distributed across) each category.
+Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at
+<!-- [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)] -->
+*[MASKED FOR REVIEW]*
+. We additionally crafted 8 "attention check" items blending in (and distributed across) each category.
 
@@
 For both studies, data analysis was carried out using R [4.4.3, @Rcoreteam], leveraging the *easystats* ecosystem [@ludecke2019insight; @ludecke2020extracting] and the *EGAnet* package [@christensen2021estimating].
-The reproducible code and additional details are available at https://github.com/RealityBending/InteroceptionScale.
+The reproducible code and additional details are available at
+*[MASKED FOR REVIEW]*.
+<!-- https://github.com/RealityBending/InteroceptionScale. -->
 
@@
 7 attention checks were embedded throughout (one within each major questionnaire).
-In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on https://github.com/RealityBending/InteroceptionScale].
+In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on
+*[MASKED FOR REVIEW]*.
+<!-- https://github.com/RealityBending/InteroceptionScale]. -->
 
@@
 
-Data, code, and all materials are available at https://github.com/RealityBending/InteroceptionScale.
+Data, code, and all materials are available at 
+*[MASKED FOR REVIEW]*.
+<!-- https://github.com/RealityBending/InteroceptionScale. -->
 
-# Acknowledgements
+<!-- # Acknowledgements -->
 
-We would like to thank Hugo Critchley for his valuable feedback on the manuscript.
-DM would also like to thank Anastasia for the motivation provided to write this paper.
+<!-- We would like to thank Hugo Critchley for his valuable feedback on the manuscript. -->
+<!-- DM would also like to thank Anastasia for the motivation provided to write this paper. -->
 

### 2025-12-29 study2/analysis/1_cleaning.qmd
added internal consistency for MAIA subscales

@@
 df <- filter(df, !Participant %in% c(outliers$attentionchecks, outliers$duration, outliers$distance))
+```
+
+## Internal Consistency
+
+- MAIA [x]
+- MINT []
+- BPQ []
+- IAS []
+- TAS-20 []
+- B-ERS []
+- CERQ-Short []
+- CEFSA-14 []
+- PI-18 []
+- SILS (only one item)
+- PHQ-4 []
+
+```{r}
+df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
+maia_ar <- df[, grepl("^MAIA_AttentionRegulation_", names(df))]
+maia_bl <-  df[, grepl("^MAIA_BodyListening_", names(df))]
+maia_ea <-  df[, grepl("^MAIA_EmotionalAwareness_", names(df))]
+maia_nd <-  df[, grepl("^MAIA_NotDistracting_", names(df))]
+maia_n <-  df[, grepl("^MAIA_Noticing_", names(df))]
+maia_nw <-  df[, grepl("^MAIA_NotWorrying_", names(df))]
+maia_sr <-  df[, grepl("^MAIA_SelfRegulation_", names(df))]
+maia_t <-  df[, grepl("^MAIA_Trusting_", names(df))]
+
+psych::omega(maia_ar, nfactors = 1)
+psych::omega(maia_bl, nfactors = 1)
+psych::omega(maia_ea, nfactors = 1)
+psych::omega(maia_nd, nfactors = 1)
+psych::omega(maia_n, nfactors = 1)
+psych::omega(maia_nw, nfactors = 1)
+psych::omega(maia_sr, nfactors = 1)
+psych::omega(maia_t, nfactors = 1)
 ```

### 2025-12-29 paper/manuscript.qmd
added internal consistency for MAIA subscales
added internal consistency for BPQ and IAS

@@
 The Multidimensional Assessment of Interoceptive Awareness [MAIA-2, @mehling2018multidimensional] measures 8 dimensions with 37 items presented on a 7-point Likert scale (0 = *Never*, 6 = *Always*).
-It includes bodily dimensions such as Body Listening, Noticing, Emotional Awareness, dimensions related to emotion regulation, such as Trust, Not-worrying, and Self-Regulation, as well as dimensions related to attention, such as Attention Regulation and Not-Distracting.
+It includes bodily dimensions such as Body Listening, Noticing, Emotional Awareness, dimensions related to emotion regulation, such as Trust, Not-worrying, and Self-Regulation, as well as dimensions related to attention, such as Attention Regulation and Not-distracting.
 The relationship of some of these dimensions to interoception remains debated, particularly Not-Distracting and Not-Worrying, which tend to show weak or non-existent correlations with the other MAIA subscales [@ferentzi2021examining].
+The subscales of the MAIA-2 showed an acceptable to good internal consistency: ωAttention regulation = 0.87, ωBody listening = 0.76, ωEmotional awareness = 0.79, ωNot-distracting = 0.80, ωNoticing = 0.68,  ωNot-worrying = 0.79, ωSelf regulation =  0.84, and ωTrusting = 0.84.
 
 The Body Perception Questionnaire - Very Short Form [BPQ-VSF, @cabrera2018assessing] measures a general score of bodily awareness with 12 items presented on 5-point Likert scale (0 = *Never*, 5 = *Always*).
+Internal consistency for the BPQ-Awareness was good (ω = 0.91).
 
 The Interoceptive Accuracy Scale [IAS, @murphy2020testing] measures a general score of interoceptive accuracy to physical sensations with 21 items presented on a 5-point Likert scale (1 = *Disagree Strongly*, 5 = *Strongly Agree*).
+The IAS had good internal consistency (ω = 0.88).
 

### 2025-12-29 study2/analysis/1_cleaning.qmd
added internal consistency for BPQ and IAS

@@
 - MINT []
-- BPQ []
-- IAS []
+- BPQ [x]
+- IAS [x]
 - TAS-20 []
@@
 - PHQ-4 []
+
+```{r}
+df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
+maia_ar <- df[, grepl("^MAIA_AttentionRegulation_", names(df))]
+maia_bl <-  df[, grepl("^MAIA_BodyListening_", names(df))]
+maia_ea <-  df[, grepl("^MAIA_EmotionalAwareness_", names(df))]
+maia_nd <-  df[, grepl("^MAIA_NotDistracting_", names(df))]
+maia_n <-  df[, grepl("^MAIA_Noticing_", names(df))]
+maia_nw <-  df[, grepl("^MAIA_NotWorrying_", names(df))]
+maia_sr <-  df[, grepl("^MAIA_SelfRegulation_", names(df))]
+maia_t <-  df[, grepl("^MAIA_Trusting_", names(df))]
+
+psych::omega(maia_ar, nfactors = 1)
+psych::omega(maia_bl, nfactors = 1)
+psych::omega(maia_ea, nfactors = 1)
+psych::omega(maia_nd, nfactors = 1)
+psych::omega(maia_n, nfactors = 1)
+psych::omega(maia_nw, nfactors = 1)
+psych::omega(maia_sr, nfactors = 1)
+psych::omega(maia_t, nfactors = 1)
+```
+
+```{r}
+bpq <- df[,grepl("^BodyAwareness_", names(df))]
+bpq <- bpq[,(names(bpq) != "BodyAwareness_AttentionCheck_1")]
+psych::omega(bpq, nfactors = 1)
+
+```
+
+```{r}
+ias <- df[,grepl("^IAS_", names(df))]
+ias <- ias[,(names(ias) != "IAS_AttentionCheck_1")]
+psych::omega(ias, nfactors = 1)
+
+```
 

### 2025-12-29 paper/manuscript.qmd
Internal consistency for tas was added
@DominiqueMakowski tas items are now reversed

@@
 
-The Toronto Alexithymia Scale TAS [TAS-20, @leising2009toronto] measures 3 Alexithymia dimensions with 20 items 5-point Likert scale (1 = *Strongly Disagree*, 5 = *Strongly Agree*: Difficulty Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and Externally Oriented Thinking (EOR).
+The Toronto Alexithymia Scale TAS [TAS-20, @leising2009toronto] measures 3 Alexithymia dimensions with 20 items 5-point Likert scale (1 = *Strongly Disagree*, 5 = *Strongly Agree*: Difficulty Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and Externally Oriented Thinking (EOT).
+In this study, the  TAS subscales showed poor to acceptable internal consistency: ωDIF = 0.77, ωDDF = 0.53 and ωEOT = 0.69.
 

### 2025-12-29 study2/analysis/1_cleaning.qmd
Internal consistency for tas was added
@DominiqueMakowski tas items are now reversed

@@
 - IAS [x]
-- TAS-20 []
+- TAS-20 [x]
 - B-ERS []
@@
 psych::omega(ias, nfactors = 1)
-
 ```
@@
 ```{r}
-df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
-maia_ar <- df[, grepl("^MAIA_AttentionRegulation_", names(df))]
-maia_bl <-  df[, grepl("^MAIA_BodyListening_", names(df))]
-maia_ea <-  df[, grepl("^MAIA_EmotionalAwareness_", names(df))]
-maia_nd <-  df[, grepl("^MAIA_NotDistracting_", names(df))]
-maia_n <-  df[, grepl("^MAIA_Noticing_", names(df))]
-maia_nw <-  df[, grepl("^MAIA_NotWorrying_", names(df))]
-maia_sr <-  df[, grepl("^MAIA_SelfRegulation_", names(df))]
-maia_t <-  df[, grepl("^MAIA_Trusting_", names(df))]
+tas <- df |>
+  select(starts_with("TAS_"))|>
+  mutate(TAS_DIF_9 = 6 - TAS_DIF_9,
+         TAS_DIF_13 = 6- TAS_DIF_13 , 
+         TAS_EOT_15 = 6- TAS_EOT_15,
+         TAS_EOT_18 = 6- TAS_EOT_18,
+         TAS_EOT_19 = 6- TAS_EOT_19)
 
-psych::omega(maia_ar, nfactors = 1)
-psych::omega(maia_bl, nfactors = 1)
-psych::omega(maia_ea, nfactors = 1)
-psych::omega(maia_nd, nfactors = 1)
-psych::omega(maia_n, nfactors = 1)
-psych::omega(maia_nw, nfactors = 1)
-psych::omega(maia_sr, nfactors = 1)
-psych::omega(maia_t, nfactors = 1)
+tas_eot <- tas[, grepl("^TAS_EOT_", names(tas))]
+tas_ddf <-  tas[, grepl("^TAS_DDF_", names(tas))]
+tas_dif <-  tas[, grepl("^TAS_DIF_", names(tas))]
+
+psych::omega(tas_eot, nfactors = 1)
+psych::omega(tas_ddf, nfactors = 1)
+psych::omega(tas_dif, nfactors = 1)
 ```
@@
 # TODO: check if any reversed items in the following questionnaires
+#There are 5 items that are negatively keyed (items 9, 13, 15, 18 and 19) in the TAS
+
+df <- df |>
+  mutate(TAS_DIF_9 = 6 - TAS_DIF_9,
+         TAS_DIF_13 = 6- TAS_DIF_13 , 
+         TAS_EOT_15 = 6- TAS_EOT_15,
+         TAS_EOT_18 = 6- TAS_EOT_18,
+         TAS_EOT_19 = 6- TAS_EOT_19)
+
 df <- compute_and_remove(df, name="TAS_EOT", method="mean")

### 2025-12-29 paper/manuscript.qmd
added omega for ERS and CERQ

@@
 The Emotion Reactivity Scale - Brief Version [B-ERS, @veilleux2024development] measures 3 dimensions with 6 items on a 5-point Likert scale (0 = *Not like me at all*, 4 = *Extremely like me*): Arousal (*"My moods are very strong and powerful"*), Sensitivity (*"I tend to get very emotional very easily"*), and Persistence (*"When I am angry/upset, it takes me much longer than most people to calm down"*).
+The subscales of the B-ERS showed acceptable to good internal consistency: ωArousal = 0.76, ωSensitivity = 0.90 and ωPersistence = 0.74.
 
 The Cognitive Emotion Regulation Questionnaire [CERQ-short, @garnefski2006cognitive] measures 9 adaptive and maladaptive emotion regulation strategies with 18 items (1 = *Almost Never*, 5 = *Almost Always*).
-The strategies include Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.
+The strategies include Self-blame (ω= 0.78), Other-blame (ω= 0.8), Rumination (ω= 0.61), Catastrophizing (ω= 0.84), Putting into Perspective (ω= 0.70), Positive Refocusing (ω= 0.80), Positive Reappraisal (ω= 0.75), Acceptance (ω= 0.75), and Planning (ω= 0.66).
+The internal consistency for these dimensions ranged from acceptable to good.
 

### 2025-12-29 study2/analysis/1_cleaning.qmd
added omega for ERS and CERQ

@@
 psych::omega(tas_dif, nfactors = 1)
+```
+
+```{r}
+ers_a <- df[, grepl("^ERS_Arousal_", names(df))]
+ers_s <-  df[, grepl("^ERS_Sensitivity_", names(df))]
+ers_p <-  df[, grepl("^ERS_Persistence_", names(df))]
+
+psych::omega(ers_a, nfactors = 1)
+psych::omega(tas_ddf, nfactors = 1)
+psych::omega(tas_dif, nfactors = 1)
+
+```
+
+```{r}
+cerq_acept <- df[, grepl("^CERQ_Acceptance_", names(df))]
+cerq_posref <- df[, grepl("^CERQ_PositiveRefocusing_", names(df))]
+cerq_posrea <- df[, grepl("^CERQ_PositiveReappraisal_", names(df))]
+cerq_selfbla <- df[, grepl("^CERQ_SelfBlame_", names(df))]
+cerq_otherbla <- df[, grepl("^CERQ_OtherBlame_", names(df))]
+cerq_rum <- df[, grepl("^CERQ_Rumination_", names(df))]
+cerq_cat <- df[, grepl("^CERQ_Catastrophizing_", names(df))]
+cerq_refopla <- df[, grepl("^CERQ_RefocusPlanning_", names(df))]
+cerq_persp <- df[, grepl("^CERQ_Perspective_", names(df))]
+
+psych::omega(cerq_acept, nfactors = 1)
+psych::omega(cerq_posref, nfactors = 1)
+psych::omega(cerq_posrea, nfactors = 1)
+psych::omega(cerq_selfbla, nfactors = 1)
+psych::omega(cerq_otherbla, nfactors = 1)
+psych::omega(cerq_rum, nfactors = 1)
+psych::omega(cerq_cat, nfactors = 1)
+psych::omega(cerq_refopla, nfactors = 1)
+psych::omega(cerq_persp, nfactors = 1)
 ```

### 2025-12-29 paper/manuscript.qmd
added omega for CEFSA, PI and PHQ

@@
 This scale is designed to measure dissociative experiences in adolescence and adulthood, specifically focusing on the felt sense of anomaly-type dissociation.
-It includes Anomalous Experience of the Self, Anomalous Experience of the Body, Anomalous Experiences of Emotion, Altered Sense of Familiarity, Altered Sense of Connection, Altered Sense of Agency, and Altered Sense of Reality.
+It includes Anomalous Experience of the Self (ω= 0.75), Anomalous Experience of the Body (ω= 0.77), Anomalous Experiences of Emotion (ω= 0.81), Altered Sense of Familiarity (ω= 0.72), Altered Sense of Connection (ω= 0.86), Altered Sense of Agency (ω= 0.78), and Altered Sense of Reality (ω= 0.58).
+The internal consistency of the subscales were mostly good with the exception of Sense of Reality.
 
@@
 The 18 items are presented on a 6-point Likert scale (0 = *Strongly Disagree*, 5 = *Strongly Agree*).
+In this study, the internal consistency of the subscales were all good: ωGood = 0.84, ωSafe = 0.80, ωEnticing = 0.80 and ωAlive = 0.84.
 
@@
 We used the refined version of the PHQ-4 [@makowski2025measuring], which adds an additional response option ("Once or twice"), increasing sensitivity to subclinical fluctuations.
+PhQ-Anxiety showed excellent reliability (ω= 0.91) and PHQ-Depression showed good reliability (ω= 0.84).
 

### 2025-12-29 study2/analysis/1_cleaning.qmd
added omega for CEFSA, PI and PHQ

@@
 - TAS-20 [x]
-- B-ERS []
-- CERQ-Short []
-- CEFSA-14 []
-- PI-18 []
+- B-ERS [x]
+- CERQ-Short [x]
+- CEFSA-14 [x]
+- PI-18 [x]
 - SILS (only one item)
@@
 
+```{r}
+cefsa_emo <- df[, grepl("^CEFSA_Emotion_", names(df))]
+cefsa_con <- df[, grepl("^CEFSA_Connection_", names(df))]
+cefsa_body <- df[, grepl("^CEFSA_Body_", names(df))]
+cefsa_rea <- df[, grepl("^CEFSA_Reality_", names(df))]
+cefsa_fam <- df[, grepl("^CEFSA_Familiarity_", names(df))]
+cefsa_age <- df[, grepl("^CEFSA_Agency_", names(df))]
+cefsa_self <- df[, grepl("^CEFSA_Self_", names(df))]
+
+psych::omega(cefsa_emo, nfactors = 1)
+psych::omega(cefsa_con, nfactors = 1)
+psych::omega(cefsa_body, nfactors = 1)
+psych::omega(cefsa_rea, nfactors = 1)
+psych::omega(cefsa_fam, nfactors = 1)
+psych::omega(cefsa_age, nfactors = 1)
+psych::omega(cefsa_self, nfactors = 1)
+```
+
+```{r}
+
+df[grepl("^PI18.*_R$", names(df))] <- 6 - df[grepl("^PI18.*_R$", names(df))]  # Reverse
+
+pi_alive <- df[grep("^PI18.*A_", names(df))]
+pi_safe <- df[grep("^PI18.*GS", names(df))]
+pi_enticing <- df[grep("^PI18.*GE", names(df))]
+pi_good <- df[c(grep("^PI18.*GS", names(df)), grep("^PI18.*GE", names(df)))]
+
+psych::omega(pi_alive, nfactors = 1)
+psych::omega(pi_safe, nfactors = 1)
+psych::omega(pi_enticing, nfactors = 1)
+psych::omega(pi_good, nfactors = 1)
+```
+
+```{r}
+phq_a <- df[grep("^PHQ4_Anxiety", names(df))]
+phq_d <- df[grep("^PHQ4_Depression", names(df))]
+
+psych::omega(phq_a, nfactors = 1)
+psych::omega(phq_d, nfactors = 1)
+```
+
 ## Dimension Computation
@@
   mutate(TAS_DIF_9 = 6 - TAS_DIF_9,
-         TAS_DIF_13 = 6- TAS_DIF_13 , 
+         TAS_DIF_13 = 6- TAS_DIF_13, 
          TAS_EOT_15 = 6- TAS_EOT_15,
